### 2014-04-10 writeup/dm_angular_ps.tex
Imported latex source.

%\documentclass[onecolumn,amsmath,amssymb,floatfix,12pt,nofootinbib]{revtex4}
\documentclass[twocolumn,prd,noshowpacs,nofootinbib,amsmath,amssymb]{revtex4}
\usepackage{graphicx,epsfig,psfrag,bm,amssymb}
\usepackage{dcolumn}
\usepackage{bm}
\usepackage{mciteplus}
\usepackage{color}
\usepackage{mathrsfs,amsfonts,hepunits, color}
\usepackage{mciteplus}
\usepackage{tikz}
\usepackage{slashed}
\usetikzlibrary{arrows,shapes}
\usetikzlibrary{trees}
\usetikzlibrary{matrix,arrows} 				% For commutative diagram
											% http://www.felixl.de/commu.pdf
\usetikzlibrary{positioning}				% For "above of=" commands
\usetikzlibrary{calc,through}				% For coordinates
\usetikzlibrary{decorations.pathreplacing}  % For curly braces
\usepackage{pgffor}							% For repeating patterns

\usetikzlibrary{decorations.pathmorphing}	% For Feynman Diagrams
\usetikzlibrary{decorations.markings}
\usetikzlibrary{snakes}

\tikzset{
	% >=stealth', %%  Uncomment for more conventional arrows
    vector/.style={decorate, decoration={snake}, draw},
	provector/.style={decorate, decoration={snake,amplitude=2.5pt}, draw},
	antivector/.style={decorate, decoration={snake,amplitude=-2.5pt}, draw},
    fermion/.style={draw, postaction={decorate},
        decoration={markings,mark=at position .55 with {\arrow[draw]{>}}}},
    fermionbar/.style={draw, postaction={decorate},
        decoration={markings,mark=at position .55 with {\arrow[draw=black]{<}}}},
    fermionnoarrow/.style={draw},
    gluon/.style={decorate, draw,decoration={coil,amplitude=4pt, segment length=6pt}, line width=1},
    scalar/.style={dashed,draw, postaction={decorate},
        decoration={markings,mark=at position .55 with {\arrow[draw]{>}}}},
    scalarbar/.style={dashed,draw, postaction={decorate},
        decoration={markings,mark=at position .55 with {\arrow[draw]{<}}}},
    scalarnoarrow/.style={dash pattern = on 6 pt off 3 pt,draw},
    electron/.style={draw, postaction={decorate},
        decoration={markings,mark=at position .55 with {\arrow[draw]{>}}}},
	bigvector/.style={decorate, decoration={snake,amplitude=4pt}, draw},
	vectorscalar/.style={loosely dotted,draw, postaction={decorate}},
}
\RequirePackage{xspace}
\usepackage{relsize}
\usepackage{slashed}
\newcommand{\fb}{{\rm fb}}
\newcommand{\ab}{{\rm ab}}

\newcommand{\be}{\begin{eqnarray}}
\newcommand{\ee}{\end{eqnarray}}
\def\lsim{\mathrel{\rlap{\lower4pt\hbox{\hskip 0.5 pt$\sim$}}
    \raise1pt\hbox{$<$}}}                % less than or approx. symbol
\def\gsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
    \raise1pt\hbox{$>$}}}

\newcommand{\schi}{s_{\chi\bar\chi}}  % tried to use this throughout off-shell derivation so that we can change notation later if desired.
\newcommand{\scratch}[1]{{\textcolor{red}{ #1}}}
\newcommand{\f}{\frac}
\newcommand{\pf}[2]{\left(\frac{#1}{#2}\right)}
\newcommand{\g}{{\rm g}}
\newcommand{\s}{{\rm s}}
\newcommand{\m}{{\rm m}}
\def\lsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
    \raise1pt\hbox{$<$}}}
\def\gsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
    \raise1pt\hbox{$>$}}}
\newcommand{\vev}[1]{ \left\langle {#1} \right\rangle }
\newcommand{\bra}[1]{ \langle {#1} | }
\newcommand{\ket}[1]{ | {#1} \rangle }
\newcommand{\ev}{ {\rm eV} }
\newcommand{\kev}{{\rm keV}}
\newcommand{\mev}{{\rm MeV}}
\newcommand{\gev}{{\rm GeV}}
\newcommand{\tev}{{\rm TeV}}
\newcommand{\mpl}{$M_{Pl}$}
\newcommand{\mw}{$M_{W}$}
\newcommand{\Ft}{F_{T}}
\newcommand{\Zparity}{\mathbb{Z}_2}
\newcommand{\BLambda}{\boldsymbol{\lambda}}

\begin{document}

\title{Fast Radio Burst Cosmology}

\author{Kris Sigurdson}
 \affiliation{Department of Physics and Astronomy, University of British 
Columbia, Vancouver, BC, Canada V6T 1Z1}

\begin{abstract}
In recent years a new astrophysical phenomena, fast radio bursts (FRBs), has been detected that potentially originates from cosmological distances.  These broadband radio bursts  typically last for only milliseconds and are a \emph{standard ping} that can be used to map the properties of the Universe.  In this paper,  under the assumption that these bursts originate from cosmological distances, we discuss how the detection of a large enough population of these events can be used to map the cosmological properties of the Universe.    We first discuss one point statistics and show that, even if FRBs are not standard candles, the dispersion-measure distance vs. luminosity-distance distribution of any observed population is a strong constraint on cosmology.  We then discuss how the two point statistics of an observed population of FRBs traces the large-scale structure of the Universe and make predictions for the angular power spectra of dispersion-measure distance.  It is possible that FRBs do not originate at cosmological distances, but if they do, we argue that they could open a remarkable window to observe the properties of the Universe.
\end{abstract}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%					Introduction
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
Several years ago an unusual radio event was discovered at the Parks radio telescope while searching for millisecond pulsars.  In a direction out of the plane of the Galaxy an event was discovered with an unusually large dispersion-measure, implying a column of electrons much large than expected in the Galaxy.

In this \emph{ Letter} we consider the implications of of a cosmological population of fast radio bursts (FRBs). 
 If FRBs originate at cosmological distances they provide a new window on the Universe. The key insight into the potential power of FRBs is that, while it is interesting and helpful to know the redshift of the burst, it is not necessary to do interesting studies of cosmology.

 The outline of this \emph{Letter} is as follows. In Section \ref{sec:notes} we discuss how dispersion measure provides a new distance measure in cosmology and how the joint distribution of dispersion-distance and luminosity-distance of a population of FRBs depends on cosmology and the intrinsic luminosity distance distribution.   In Section \ref{sec:notes} we then show how to calculate the angular power spectra of dispersion distance.  We then forecast how well these cosmological observables can be measured.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%					Basic Ingredients 
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Notes}\label{sec:notes}

%Let's define the dispersion-measure distance.

%The lets discuss how a given luminosity relationship and cosmology dictates an expected joint distribution of dispersion measure.

For some line of sight originating from redshift $z$

\begin{equation}
{\rm DM}^{z}(\hat{n}) = \int_0^{\eta^z} d\eta \frac{n_e(\eta\hat{n})}{(1+z(\eta))^2}
\end{equation}
is the dispersion-measure random field in angular direction $\hat{n}$ where
\begin{equation}
n_e(\eta^z\hat{n}) \equiv n_e(z,\hat{n}) =  \bar{n}_{e0} (1+z)^3 \left[1+\delta_e(z,\hat{n})\right]
\end{equation}
is the electron distribution of the Universe and $\bar{n}_{e0}$ is the mean cosmological density of free electrons today, and $\delta_e(z,\hat{n})$ is 
the fractional overdensity of electrons.
We define the dispersion-measure distance (or dispersion distance), the equivalent distance required to
produce a given amount of dispersion in an observed radio signal in the Universe today, as 
$ D = {{\rm DM}}/{\bar{n}_{e0}}$

The angular correlation function of dispersion distance between two lines of sight at redshift $z$ and direction $\hat{n}$ and redshift $z'$ and direction $\hat{n}'$ is
\begin{equation}
w^{z z'}(\hat{n}\cdot\hat{n}') = \langle D^z(\hat{n}) D^{z'}(\hat{n}') \rangle
\end{equation}
and the corresponding angular power spectrum is
\begin{equation}
w^{z z'}(\hat{n}\cdot\hat{n}') = \sum_l \frac{2l+1}{4 \pi} C_l^{z z'} P_l(\hat{n}\cdot\hat{n}')
\end{equation}

We can decompose the dispersion-distance field into spherical harmonics as
\begin{equation}
D^z(\hat{n}) = \sum_{l m} D^z_{l m} Y_{l m} (\hat{n})
\end{equation}

A plane wave can be expanded in terms of spherical eigenfunctions using the Rayleigh expansion
\begin{equation}
e^{i \vec{k}\cdot \hat{n} \eta} = 4\pi \sum_{l m} i^l j_{l}(k\eta) Y^*_{lm}(\hat{k})Y_{lm}(\hat{n})
\end{equation}
If we define 
\begin{equation}
N_e(\vec{k}) = \int d^3 \vec{x} e^{-i \vec{x}\cdot\vec{k}} n_e(\vec{x})
\end{equation}
to be the Fourier transform of the comoving electron density field then we can write
\begin{equation}
D^z_{l m} = \frac{4 \pi i^{l}}{\bar{n}_{e0}} \int \frac{d^3 \vec{k}}{(2\pi)^3} N_e(\vec{k}) Y^*_{l m}(\hat{k}) \int_0^{\eta^z} d\eta a^{-1}(\eta) j_{l}(k\eta)
\end{equation}
and the angular power spectra of dispersion-distance, assumed to be an isotropic random field, is thus
\begin{equation}
\langle D^z_{l m} D^{z'}_{l' m'} \rangle = C_l^{z z'} \delta_{l l'} \delta_{m m'}
\end{equation}
Now since we have 
\begin{equation}
\langle N_e(\vec{k}) N_e(\vec{k}')\rangle = \bar{n}_{e0}^2\left[\langle \delta_e(\vec{k})\delta_e(\vec{k}')\rangle + 1 \right]
\end{equation}
where
\begin{equation}
\langle \delta_e(\vec{k})\delta_e(\vec{k}')\rangle = (2\pi)^3 \delta_{D}^3(\vec{k}-\vec{k}') P_{ee}(k)
\end{equation}
we finally have
\begin{equation}
C_l^{zz'}=\frac{2}{\pi} \int_0^{\infty}k^2 dk P_{ee}(k) \int_0^{\eta^z}\frac{d\eta}{a(\eta)} \int_0^{\eta^{z'}}\frac{d\eta'}{a(\eta')}  j_l(k\eta) j_l(k\eta')
\end{equation}
The one-point variance in the dispersion-distance from a redshift $z$ is just
\begin{equation}
(\sigma^2)^{zz}=\sum_{l} \frac{2l+1}{4\pi} C_l^{zz}
\end{equation}
Using the addition identify for a complete sum over spherical bessel functions we find that
\begin{equation}
(\sigma^2)^{zz}= \frac{1}{2\pi^2} \int_0^{\infty}k^2 dk P_{ee}(k) \int_0^{\eta^z}\frac{d\eta}{a(\eta)} \int_0^{\eta^{z}}\frac{d\eta'}{a(\eta')}  j_0(k\eta-k\eta')
\end{equation}

Given a source-population redshift distribution ${\cal P}(\eta^z)$, where 
\begin{equation}
\int d\eta^z {\cal P}(\eta^z) = 1
\end{equation}

The observable power spectrum of mean dispersion distance $\bar{D}$ is then
\begin{equation}
C_l^{\bar{D}\bar{D}} = \int d\eta^z \int d\eta^{z'} {\cal P}(\eta^z){\cal P}(\eta^{z'}) C_l^{z z'}
\end{equation}

We use the halo model to calculate $P_{ee}(k)$ and a potential ${\cal P}(z)$.

\bigskip
\section*{Acknowledgments}
\medskip

\bibliographystyle{apsrevM}
\bibliography{BBD-Draft}

\end{document}

### 2014-04-10 writeup/dm_angular_ps.tex
Work on the estimator.

@@
 \usepackage{slashed}
+\usepackage{verbatim}
 \usetikzlibrary{arrows,shapes}
@@
 
+\author{Kiyoshi Wesley Masui}
+ \affiliation{Department of Physics and Astronomy, University of British 
+Columbia, Vancouver, BC, Canada V6T 1Z1}
+
 \begin{abstract}
@@
 
+\subsection{Dispersion measure and PDF}
+
 %Let's define the dispersion-measure distance.
@@
 
-For some line of sight originating from redshift $z$
+The dispersion measure of a FRB observed in some angular direction $\hat{n}$ and
+originating from redshift $z$ is
+\begin{equation}
+{\rm DM}^{z}(\hat{n}) = \int_0^{\eta^z} d\eta
+\frac{n_e(\eta\hat{n})}{(1+z(\eta))^2}.
+\end{equation}
+Here, $\eta$ is the conformal distance as a function of redshift, and
+$n_e(\eta^z\hat{n})$ is the three dimensional electron density.  We choose to
+separate $n_e$ into four components as follows:
+\begin{equation}
+\label{e:ne_sep}
+n_e(\hat{n}, z) = n_e^{\rm gal}(\hat{n}, z) + \bar{n}_e(z) +
+    \bar{n}_e(z)\delta_e(\hat{n}, z) + n_e^{\rm src}(\hat{n}, z).
+\end{equation}
+Here $n_e^{\rm gal}(\hat{n}, z)$ is the contribution to the electron density
+from the Milky Way galaxy and other local structures and only contributes at
+low redshift. $\bar{n}_e(z)$ is the mean electron density is and related to the
+current day electron density by $\bar{n}_e = \bar{n}_{e0} (1+z)^3$. 
+$\delta_e(z,\hat{n})$ is the large-scale fractional over-density of electrons.
+$n_e^{\rm src}(\hat{n}, z)$ are the electrons associated with the FRB source,
+which only contributes as $z \approx z^{\rm src}$ and accounts for two effects.
+First the FRB itself
+may have some intrinsic dispersion measure due to the environment of the
+progenitor.  Second, it is unlikely that FRB events are uniformly distributed
+throughout the Universe and they presumably trace matter in some way. When
+considering statics of FRB dispersion measures it is necessary to account for
+this bias.
 
+We define the dispersion-measure distance (or dispersion distance),
+the equivalent distance required to
+produce a given amount of dispersion in an observed radio signal in the
+Universe today, as $ D = {{\rm DM}}/{\bar{n}_{e0}}$
+We separate the dispersion distance into the contributions from each
+term in \ref{e:ne_sep}:
 \begin{equation}
-{\rm DM}^{z}(\hat{n}) = \int_0^{\eta^z} d\eta \frac{n_e(\eta\hat{n})}{(1+z(\eta))^2}
+\label{e:D_sep}
+D = D^{\rm gal} + D^{\bar{n}_e} + D^{\delta_e}
+         + D^{\rm src}.
 \end{equation}
+For a population of FRBs originating at cosmological distances, ${\rm DM}^{\rm
+src}$ is only a single function of $\hat{n}$ which can presumably be well
+measured.  In addition, this function could in principal be well characterized
+by independent data such as observations of pulsars.  As such, we will
+here-after we ignore this term.
+
+To relate observations to cosmology, we wish to determine how a set of observed
+dispersion measures $\{D_i\}$ with known angular positions but with unknown
+redshifts depends on cosmological parameters.  We begin by defining the
+redshift probability distribution function $p(\{z_i\})$. We assume that the
+redshifts of the FRB sources are independent, \emph{i.e.}~we assume
+\begin{equation}
+    p(\{z_i\}) = \prod_i p(z_i).
+\end{equation}
+This may not be strictly true since FRBs are expected to cluster and trace the
+large-scale structure. This is a potential source of bias in the estimator we
+derive.  From this assumption it follows that the $\{D^{\bar{n_e}}_i\}$ are
+uncorrelated:
+\begin{equation}
+\langle D^{\bar{n}_e}_i D^{\bar{n}_e}_j \rangle
+    - \langle D^{\bar{n}_e}_i \rangle \langle D^{\bar{n}_e}_j \rangle
+    = \delta_{ij} \times \textrm{(something to do with $p(z_i)$)}
+\end{equation}
+
+We further assume that $\{D^{\rm src}_i\}$ are uncorrelated. Again this may not
+be strictly true due to clustering of FRB sources and again this may bias our
+estimator. We parameterized the variance from this term as 
+\begin{equation}
+    \langle D^{\rm src}_i D^{\rm src}_j \rangle
+    - \langle D^{\rm src}_i \rangle \langle D^{\rm src}_j \rangle
+    = \delta_{ij} \sigma^2_{\rm src}
+\end{equation}
+
+We further assume that the terms in Equation \ref{e:D_sep} are mutually uncorrelated
+
+\begin{comment}
 is the dispersion-measure random field in angular direction $\hat{n}$ where
@@
 is the electron distribution of the Universe and $\bar{n}_{e0}$ is the mean cosmological density of free electrons today, and $\delta_e(z,\hat{n})$ is 
-the fractional overdensity of electrons.
-We define the dispersion-measure distance (or dispersion distance), the equivalent distance required to
-produce a given amount of dispersion in an observed radio signal in the Universe today, as 
-$ D = {{\rm DM}}/{\bar{n}_{e0}}$
+the fractional over-density of electrons.
+\end{comment}
+
+\subsection{Relating dispersion measure angular power-spectrum to cosmology}
 

### 2014-04-10 writeup/dm_angular_ps.tex
Sketched out how to get to teh estimator.

@@
 \newcommand{\BLambda}{\boldsymbol{\lambda}}
+
+\newcommand{\ud}{\,\mathrm{d}}
 
@@
     - \langle D^{\rm src}_i \rangle \langle D^{\rm src}_j \rangle
-    = \delta_{ij} \sigma^2_{\rm src}
+    = \delta_{ij} \sigma^2_{\rm src}.
 \end{equation}
 
-We further assume that the terms in Equation \ref{e:D_sep} are mutually uncorrelated
+The cosmological information lies in the correlations within the set
+$\{D^{\delta_e}_i\}$. If the redshifts of the observed FRBs where known, we
+would write the probability density function of this set as
+$p(\{D^{\delta_e}_i\} | \{z_i\})$, which has second moments
+\begin{equation}
+    w^{z_i z_j}(\hat{n}_i\cdot\hat{n}_j) \equiv \int \ud \{D^{\delta_e}_i\}
+        D^{\delta_e}_i D^{\delta_e}_j p(\{D^{\delta_e}_i\} | \{z_i\}).
+\end{equation}
+$w^{z_i z_j}(\hat{n}_i\cdot\hat{n}_j)$ is the redshift dependant DM angular
+correlation function, whose dependence on cosmology is derived below.
+Marginalizing $p(\{D^{\delta_e}_i\} | \{z_i\})$ over the unknown redshifts
+yields
+\begin{equation}
+    p(\{D^{\delta_e}_i\}) = \int_0^\infty \ud \{z_i\}
+        p(\{z_i\}) p(\{D^{\delta_e}_i\} | \{z_i\}).
+\end{equation}
+The second moment of the marginalized distribution is
+\begin{align}
+    \langle D^{\delta_e}_i D^{\delta_e}_j \rangle =& \\
+        =& \textrm{stuff} \\
+    =& \int \ud z \ud z' p(z) p(z') w^{z z'}(\hat{n}_i\cdot\hat{n}_j) \qquad (i \neq j) \\
+    =& \int \ud z \ud z' \delta(z - z') p(z) w^{z z'}(\hat{n}_i\cdot\hat{n}_j)
+    \qquad (i = j)
+\end{align}
+I think.
+
+The covariance matrix is
+\begin{align}
+    C_{ij} =& \langle D_i D_j \rangle - \langle D_i \rangle \langle D_j \rangle
+           = \textrm{a bunch of things we know (special case for $i=j$)}.
+\end{align}
+
+Now that we have the covariance matrix, the estimator is Equation~11.94 from
+Dodelson, although we have to modify it slightly to exclude the
+auto-correlations.  The error (assuming Gaussianity) is Equation~11.100.
+
+%We further assume that the terms in Equation \ref{e:D_sep} are mutually uncorrelated
 

### 2014-04-15 writeup/dm_angular_ps.tex
Filled in some details of estimator, started Sensitivty section.

@@
 uncorrelated:
-\begin{equation}
+\begin{align}
 \langle D^{\bar{n}_e}_i D^{\bar{n}_e}_j \rangle
     - \langle D^{\bar{n}_e}_i \rangle \langle D^{\bar{n}_e}_j \rangle
-    = \delta_{ij} \times \textrm{(something to do with $p(z_i)$)}
-\end{equation}
+    =& \delta_{ij} \int_0^\infty \ud z p(z) \int_0^{\eta(z)} \ud \eta'
+        (1 + z'(\eta')) \textrm{(not quite right, subtract off the mean.)}
+        \equiv& \sigma_{\bar{n}_e}^2
+\end{align}
 
@@
 \begin{align}
-    C_{ij} =& \langle D_i D_j \rangle - \langle D_i \rangle \langle D_j \rangle
-           = \textrm{a bunch of things we know (special case for $i=j$)}.
+    C_{ij} \equiv& \langle D_i D_j \rangle - \langle D_i \rangle \langle D_j \rangle
+           =& \textrm{a bunch of things we know (special case for $i=j$)}.
+           =& w(\hat{n}_i\cdot\hat{n}_j) \quad (i \neq j)
+    =& \sigma_{\bar{n}_e}^2 + \sigma^2_{\rm src} + \textrm(the $w$ term) \quad (i = j)
 \end{align}
 
-Now that we have the covariance matrix, the estimator is Equation~11.94 from
+Now that we have the covariance matrix, we construct a quadratic estimator for
+a chosen set of parameters $\{\lambda_\alpha\}$. The estimator is Equation~11.94 from
 Dodelson, although we have to modify it slightly to exclude the
 auto-correlations.  The error (assuming Gaussianity) is Equation~11.100.
+
+The dispersion measure angular correlation function 
+$w(\hat{n}_i\cdot\hat{n}_j)$ depends on the cosmology
+and the redshift distribution function $p(z)$, for which we may parameterize
+our ignorance. The
+cross-correlations between the observed dispersion measures are thus useful
+probes of cosmology.  The auto-correlations on the other hand are contaminated
+by the highly uncertain $\sigma^2_{\rm src}$ as well as the $C^{zz'}_\ell$ on
+very small scales and zero redshift separation, which is difficult to model
+theoretically.  As such they do not carry useful information.
+
+To explicitly ignore the information in the auto-correlations we define
+\begin{equation}
+    \tilde{C}_{ij,\alpha} \equiv
+\begin{cases}
+    C_{ij,\alpha} & \text{if } i \neq j,\\
+0 & \text{if } i = j
+\end{cases}.
+\end{equation}
+By replacing $C_{ij,\alpha}$ with this quantity in the above estimator, we
+obtain an estimator which explicitly excludes information in the auto-products
+and only uses the diagonal of the covariance in the noise weights. Our
+ignorance of $\sigma^2_{\rm src}$ then only affects the optimality of the
+estimator, although in practise
+$\langle D_i D_i \rangle - \langle D_i \rangle \langle D_i \rangle$ would
+simply be measured directly from the data to obtain accurate noise weights.
 
@@
 
+\section{Sensitivity}
+
+In this section we calculate the sensitivity of a hypothetical survey observing
+X FRBs. Because $C_\ell$ contains the all the information we use bins
+of $C_\ell$ as our parameters. We use the error bar on these parameters given
+in Equation~\ref{e:error}.  We note that it is highly unlikely that an observed
+set $\{D_i\}$ is even remotely Gaussian, and as such our error-bars are likely
+underestimated and out estimator sub-optimal at the order unity level. 
+However since given that the statistics of FRBs are currently essentially
+unconstrained, we continue with this assumption.
+
+We assume parameters X, Y, Z etc.
+
 \bigskip

### 2014-04-29 writeup/dm_angular_ps.tex
Fixed up some equation, clearified set notation.

@@
 To relate observations to cosmology, we wish to determine how a set of observed
-dispersion measures $\{D_i\}$ with known angular positions but with unknown
-redshifts depends on cosmological parameters.  We begin by defining the
-redshift probability distribution function $p(\{z_i\})$. We assume that the
+dispersion measures $\boldsymbol D$ (whose members are $D_i$)
+with known angular positions, $\hat n_i$, but with unknown
+redshifts, $z_i$, depends on cosmological parameters.  We begin by defining the
+redshift probability distribution function $p(\boldsymbol z)$. We assume that the
 redshifts of the FRB sources are independent, \emph{i.e.}~we assume
 \begin{equation}
-    p(\{z_i\}) = \prod_i p(z_i).
+    p(\boldsymbol z) = \prod_i p(z_i).
 \end{equation}
@@
 large-scale structure. This is a potential source of bias in the estimator we
-derive.  From this assumption it follows that the $\{D^{\bar{n_e}}_i\}$ are
-uncorrelated:
+derive.  From this assumption it follows that the $D^{\bar{n}_e}_i$ have
+uncorrelated probability distributions
+\begin{align}
+    p(D^{\bar{n}_e}_i)
+    &= p(z_i) \left|\frac{\ud D^{\bar{n}_e}}{\ud z} \right|_{z_i}^{-1} \\
+        &= p(z_i) \left(\frac{\ud \eta}{\ud z} \right)_{z_i}^{-1},
+\end{align}
+whose second moment is
 \begin{align}
     \langle D^{\bar{n}_e}_i D^{\bar{n}_e}_j \rangle
-    - \langle D^{\bar{n}_e}_i \rangle \langle D^{\bar{n}_e}_j \rangle
-    =& \delta_{ij} \int_0^\infty \ud z p(z) \int_0^{\eta(z)} \ud \eta'
-        (1 + z'(\eta')) \textrm{(not quite right, subtract off the mean.)}
-        \equiv& \sigma_{\bar{n}_e}^2
+        &- \langle D^{\bar{n}_e}_i \rangle \langle D^{\bar{n}_e}_j \rangle \\
+        &= \delta_{ij} \left[ \int_0^\infty \ud D^{\bar{n}_e} (D^{\bar{n}_e})^2
+            p(D^{\bar{n}_e})
+            - \left( \int_0^\infty \ud D^{\bar{n}_e} D^{\bar{n}_e}
+        p(D^{\bar{n}_e}) \right)^2 \right]\\
+        &\equiv \delta_{ij} \sigma_{\bar{n}_e}^2\\
 \end{align}
 
-We further assume that $\{D^{\rm src}_i\}$ are uncorrelated. Again this may not
+We further assume that $D^{\rm src}_i$ are uncorrelated. Again this may not
 be strictly true due to clustering of FRB sources and again this may bias our
@@
 
-The cosmological information lies in the correlations within the set
-$\{D^{\delta_e}_i\}$. If the redshifts of the observed FRBs where known, we
+The cosmological information lies in the correlations between the
+$D^{\delta_e}_i$. If the redshifts of the observed FRBs where known, we
 would write the probability density function of this set as
-$p(\{D^{\delta_e}_i\} | \{z_i\})$, which has second moments
+$p(\boldsymbol D^{\delta_e} | \boldsymbol z)$, which has second moments
 \begin{equation}
-    w^{z_i z_j}(\hat{n}_i\cdot\hat{n}_j) \equiv \int \ud \{D^{\delta_e}_i\}
-        D^{\delta_e}_i D^{\delta_e}_j p(\{D^{\delta_e}_i\} | \{z_i\}).
+    w^{z_i z_j}(\hat{n}_i\cdot\hat{n}_j) \equiv \int \ud \boldsymbol D^{\delta_e}
+        D^{\delta_e}_i D^{\delta_e}_j p(\boldsymbol D^{\delta_e} | \boldsymbol z).
 \end{equation}
@@
 correlation function, whose dependence on cosmology is derived below.
-Marginalizing $p(\{D^{\delta_e}_i\} | \{z_i\})$ over the unknown redshifts
+Marginalizing $p(\boldsymbol D^{\delta_e} | \boldsymbol z)$ over the unknown redshifts
 yields
 \begin{equation}
-    p(\{D^{\delta_e}_i\}) = \int_0^\infty \ud \{z_i\}
-        p(\{z_i\}) p(\{D^{\delta_e}_i\} | \{z_i\}).
+    p(\boldsymbol D^{\delta_e}) = \int_0^\infty \ud \boldsymbol z
+        p(\boldsymbol z) p(\boldsymbol D^{\delta_e} | \boldsymbol z).
 \end{equation}
@@
 \begin{align}
-    C_{ij} \equiv& \langle D_i D_j \rangle - \langle D_i \rangle \langle D_j \rangle
-           =& \textrm{a bunch of things we know (special case for $i=j$)}.
-           =& w(\hat{n}_i\cdot\hat{n}_j) \quad (i \neq j)
-    =& \sigma_{\bar{n}_e}^2 + \sigma^2_{\rm src} + \textrm(the $w$ term) \quad (i = j)
+    C_{ij} \equiv& \langle D_i D_j \rangle - \langle D_i \rangle \langle D_j
+    \rangle\\
+           =& w(\hat{n}_i\cdot\hat{n}_j) \quad (i \neq j)\\
+    =& \sigma_{\bar{n}_e}^2 + \sigma^2_{\rm src} + \textrm{(the $w$ term)} \quad (i = j)
 \end{align}
@@
 Now that we have the covariance matrix, we construct a quadratic estimator for
-a chosen set of parameters $\{\lambda_\alpha\}$. The estimator is Equation~11.94 from
+chosen parameters $\lambda_\alpha$. The estimator is Equation~11.94 from
 Dodelson, although we have to modify it slightly to exclude the

### 2014-04-29 writeup/dm_angular_ps.tex
Removed z superscript notation in introduction.
Re-ordered some sections.

@@
 
-\subsection{Dispersion measure and PDF}
+\subsection{Dispersion measure}
 
@@
 \begin{equation}
-{\rm DM}^{z}(\hat{n}) = \int_0^{\eta^z} d\eta
-\frac{n_e(\eta\hat{n})}{(1+z(\eta))^2}.
+    {\rm DM}(\hat{n}, z) = \int_0^{\eta(z)} d\eta'
+        \frac{n_e(\hat{n}, z')}{(1+z')^2}.
 \end{equation}
 Here, $\eta$ is the conformal distance as a function of redshift, and
-$n_e(\eta^z\hat{n})$ is the three dimensional electron density.  We choose to
+$n_e(\hat{n}, z)$ is the three dimensional electron density.  We choose to
 separate $n_e$ into four components as follows:
@@
 \label{e:D_sep}
-D = D^{\rm gal} + D^{\bar{n}_e} + D^{\delta_e}
-         + D^{\rm src}.
+D = D^{\rm gal} + D^{\bar{n}_e} + D^{\delta_e} + D^{\rm src}.
 \end{equation}
@@
 here-after we ignore this term.
+
+We are principally interested in the $D^{\delta_e}$ term as it is a probe of
+large-scale structure. In the next section we relate the statistics of this
+term to cosmology.
+
+\subsection{Relating dispersion measure angular power-spectrum to cosmology}
+
+The angular correlation function of dispersion distance between two lines of sight at redshift $z$ and direction $\hat{n}$ and redshift $z'$ and direction $\hat{n}'$ is
+\begin{equation}
+w^{z z'}(\hat{n}\cdot\hat{n}') = \langle D^{\delta_e}(\hat{n}, z) D^{\delta_e}(\hat{n}', z') \rangle
+\end{equation}
+and the corresponding angular power spectrum is
+\begin{equation}
+w^{z z'}(\hat{n}\cdot\hat{n}') = \sum_l \frac{2l+1}{4 \pi} C_l^{z z'} P_l(\hat{n}\cdot\hat{n}')
+\end{equation}
+
+We can decompose the dispersion-distance field into spherical harmonics as
+\begin{equation}
+    D^{\delta_e}(\hat{n}, z) = \sum_{l m} D^{\delta_e}_{l m}(z) Y_{l m} (\hat{n})
+\end{equation}
+
+A plane wave can be expanded in terms of spherical eigenfunctions using the Rayleigh expansion
+\begin{equation}
+e^{i \vec{k}\cdot \hat{n} \eta} = 4\pi \sum_{l m} i^l j_{l}(k\eta) Y^*_{lm}(\hat{k})Y_{lm}(\hat{n})
+\end{equation}
+If we define 
+\begin{equation}
+n_e(\vec{k}) = \int d^3 \vec{x} e^{-i \vec{x}\cdot\vec{k}} n_e(\vec{x})
+\end{equation}
+to be the Fourier transform of the comoving electron density field then we can write
+\begin{equation}
+    D^{\delta_e}_{l m}(z) = \frac{4 \pi i^{l}}{\bar{n}_{e0}} \int \frac{d^3
+    \vec{k}}{(2\pi)^3} n_e(\vec{k}) Y^*_{l m}(\hat{k}) \int_0^{\eta^z} d\eta a^{-1}(\eta) j_{l}(k\eta)
+\end{equation}
+and the angular power spectra of dispersion-distance, assumed to be an isotropic random field, is thus
+\begin{equation}
+    \langle D^{\delta_e}_{l m}(z) D^{\delta_e}_{l' m'}(z') \rangle = C_l^{z z'} \delta_{l l'} \delta_{m m'}
+\end{equation}
+Now since we have 
+\begin{equation}
+\langle n_e(\vec{k}) n_e(\vec{k}')\rangle = \bar{n}_{e0}^2\left[\langle \delta_e(\vec{k})\delta_e(\vec{k}')\rangle + 1 \right]
+\end{equation}
+where
+\begin{equation}
+\langle \delta_e(\vec{k})\delta_e(\vec{k}')\rangle = (2\pi)^3 \delta_{D}^3(\vec{k}-\vec{k}') P_{ee}(k)
+\end{equation}
+we finally have
+\begin{equation}
+C_l^{zz'}=\frac{2}{\pi} \int_0^{\infty}k^2 dk P_{ee}(k) \int_0^{\eta^z}\frac{d\eta}{a(\eta)} \int_0^{\eta^{z'}}\frac{d\eta'}{a(\eta')}  j_l(k\eta) j_l(k\eta')
+\end{equation}
+The one-point variance in the dispersion-distance from a redshift $z$ is just
+\begin{equation}
+(\sigma^2)^{zz}=\sum_{l} \frac{2l+1}{4\pi} C_l^{zz}
+\end{equation}
+Using the addition identify for a complete sum over spherical bessel functions we find that
+\begin{equation}
+(\sigma^2)^{zz}= \frac{1}{2\pi^2} \int_0^{\infty}k^2 dk P_{ee}(k) \int_0^{\eta^z}\frac{d\eta}{a(\eta)} \int_0^{\eta^{z}}\frac{d\eta'}{a(\eta')}  j_0(k\eta-k\eta')
+\end{equation}
+
+Given a source-population redshift distribution ${\cal P}(\eta^z)$, where 
+\begin{equation}
+\int d\eta^z {\cal P}(\eta^z) = 1
+\end{equation}
+
+The observable power spectrum of mean dispersion distance $\bar{D}$ is then
+\begin{equation}
+C_l^{\bar{D}\bar{D}} = \int d\eta^z \int d\eta^{z'} {\cal P}(\eta^z){\cal P}(\eta^{z'}) C_l^{z z'}
+\end{equation}
+
+We use the halo model to calculate $P_{ee}(k)$ and a potential ${\cal P}(z)$.
+
+\subsection{Estimating the DM angular power spectrum from a sample of observed
+FRBs}
 
@@
         =& \textrm{stuff} \\
-    =& \int \ud z \ud z' p(z) p(z') w^{z z'}(\hat{n}_i\cdot\hat{n}_j) \qquad (i \neq j) \\
-    =& \int \ud z \ud z' \delta(z - z') p(z) w^{z z'}(\hat{n}_i\cdot\hat{n}_j)
-    \qquad (i = j)
+        =&
+        \begin{cases}
+            \int \ud z \ud z' p(z) p(z') w^{z z'}(\hat{n}_i\cdot\hat{n}_j) 
+                &  \text{if } (i \neq j) \\
+            \int \ud z \ud z' \delta(z - z') p(z) w^{z z'}(\hat{n}_i\cdot\hat{n}_j)
+                &  \text{if } (i = j)
+        \end{cases}
 \end{align}
-I think.
 
@@
     \rangle\\
-           =& w(\hat{n}_i\cdot\hat{n}_j) \quad (i \neq j)\\
-    =& \sigma_{\bar{n}_e}^2 + \sigma^2_{\rm src} + \textrm{(the $w$ term)} \quad (i = j)
+    =&
+        \begin{cases}
+            w(\hat{n}_i\cdot\hat{n}_j)
+                &  \text{if } (i \neq j) \\
+            \sigma_{\bar{n}_e}^2 + \sigma^2_{\rm src}
+                + \textrm{(the $w$ term)}
+                &  \text{if } (i = j)
+        \end{cases}
 \end{align}
@@
 
-\subsection{Relating dispersion measure angular power-spectrum to cosmology}
-
-The angular correlation function of dispersion distance between two lines of sight at redshift $z$ and direction $\hat{n}$ and redshift $z'$ and direction $\hat{n}'$ is
-\begin{equation}
-w^{z z'}(\hat{n}\cdot\hat{n}') = \langle D^z(\hat{n}) D^{z'}(\hat{n}') \rangle
-\end{equation}
-and the corresponding angular power spectrum is
-\begin{equation}
-w^{z z'}(\hat{n}\cdot\hat{n}') = \sum_l \frac{2l+1}{4 \pi} C_l^{z z'} P_l(\hat{n}\cdot\hat{n}')
-\end{equation}
-
-We can decompose the dispersion-distance field into spherical harmonics as
-\begin{equation}
-D^z(\hat{n}) = \sum_{l m} D^z_{l m} Y_{l m} (\hat{n})
-\end{equation}
-
-A plane wave can be expanded in terms of spherical eigenfunctions using the Rayleigh expansion
-\begin{equation}
-e^{i \vec{k}\cdot \hat{n} \eta} = 4\pi \sum_{l m} i^l j_{l}(k\eta) Y^*_{lm}(\hat{k})Y_{lm}(\hat{n})
-\end{equation}
-If we define 
-\begin{equation}
-N_e(\vec{k}) = \int d^3 \vec{x} e^{-i \vec{x}\cdot\vec{k}} n_e(\vec{x})
-\end{equation}
-to be the Fourier transform of the comoving electron density field then we can write
-\begin{equation}
-D^z_{l m} = \frac{4 \pi i^{l}}{\bar{n}_{e0}} \int \frac{d^3 \vec{k}}{(2\pi)^3} N_e(\vec{k}) Y^*_{l m}(\hat{k}) \int_0^{\eta^z} d\eta a^{-1}(\eta) j_{l}(k\eta)
-\end{equation}
-and the angular power spectra of dispersion-distance, assumed to be an isotropic random field, is thus
-\begin{equation}
-\langle D^z_{l m} D^{z'}_{l' m'} \rangle = C_l^{z z'} \delta_{l l'} \delta_{m m'}
-\end{equation}
-Now since we have 
-\begin{equation}
-\langle N_e(\vec{k}) N_e(\vec{k}')\rangle = \bar{n}_{e0}^2\left[\langle \delta_e(\vec{k})\delta_e(\vec{k}')\rangle + 1 \right]
-\end{equation}
-where
-\begin{equation}
-\langle \delta_e(\vec{k})\delta_e(\vec{k}')\rangle = (2\pi)^3 \delta_{D}^3(\vec{k}-\vec{k}') P_{ee}(k)
-\end{equation}
-we finally have
-\begin{equation}
-C_l^{zz'}=\frac{2}{\pi} \int_0^{\infty}k^2 dk P_{ee}(k) \int_0^{\eta^z}\frac{d\eta}{a(\eta)} \int_0^{\eta^{z'}}\frac{d\eta'}{a(\eta')}  j_l(k\eta) j_l(k\eta')
-\end{equation}
-The one-point variance in the dispersion-distance from a redshift $z$ is just
-\begin{equation}
-(\sigma^2)^{zz}=\sum_{l} \frac{2l+1}{4\pi} C_l^{zz}
-\end{equation}
-Using the addition identify for a complete sum over spherical bessel functions we find that
-\begin{equation}
-(\sigma^2)^{zz}= \frac{1}{2\pi^2} \int_0^{\infty}k^2 dk P_{ee}(k) \int_0^{\eta^z}\frac{d\eta}{a(\eta)} \int_0^{\eta^{z}}\frac{d\eta'}{a(\eta')}  j_0(k\eta-k\eta')
-\end{equation}
-
-Given a source-population redshift distribution ${\cal P}(\eta^z)$, where 
-\begin{equation}
-\int d\eta^z {\cal P}(\eta^z) = 1
-\end{equation}
-
-The observable power spectrum of mean dispersion distance $\bar{D}$ is then
-\begin{equation}
-C_l^{\bar{D}\bar{D}} = \int d\eta^z \int d\eta^{z'} {\cal P}(\eta^z){\cal P}(\eta^{z'}) C_l^{z z'}
-\end{equation}
-
-We use the halo model to calculate $P_{ee}(k)$ and a potential ${\cal P}(z)$.
-
 \section{Sensitivity}

### 2014-04-30 writeup/dm_angular_ps.tex
Wrote down estimators.

@@
 
+% shortcuts
 \newcommand{\ud}{\,\mathrm{d}}
+\newcommand{\bD}{\boldsymbol D}
+\newcommand{\bC}{\boldsymbol C}
+\newcommand{\bDelta}{\boldsymbol \Delta}
+
+% for draft comments.
+\newcommand{\red}{\textcolor{red}}
+\newcommand{\blue}{\textcolor{blue}}
+\newcommand{\green}{\textcolor{green}}
 
@@
         \begin{cases}
-            w(\hat{n}_i\cdot\hat{n}_j)
+            \sum_l \frac{2l+1}{4 \pi} C_l P_l(\hat{n}_i\cdot\hat{n}_j)
                 &  \text{if } (i \neq j) \\
@@
 
-Now that we have the covariance matrix, we construct a quadratic estimator for
+\red{The cosmological term is probably negligible for the diagonal elements.}
+
+We have written the covariance matrix in terms of $C_l$, the
+redshift distribution function for FRBs, $p(z)$, and the unknown parameter
+$\sigma^2_{\rm src}$.  This will enable us to construct a quadratic estimator
+for a desired set of cosmological parameters from the observed set of
+dispersion measures.
+
+Now that we have the covariance matrix, we construct a quadratic estimator
+($\hat{\lambda}_\alpha$) for
 chosen parameters $\lambda_\alpha$. The estimator is Equation~11.94 from
@@
 auto-correlations.  The error (assuming Gaussianity) is Equation~11.100.
+
+Defining data vector $\bDelta = \bD - \bar{D}$ where $\bar{D}$ is the sample
+mean of dispersion measures.
+
+\begin{equation}
+    \hat{\lambda}_\alpha = \lambda_0
+    + \frac{F^{-1}_{\alpha\beta}}{2} 
+    \left[ \bDelta^t \bC^{-1} \bC_{,\beta} \bC^{-1} \bDelta
+    - \mathrm{Tr}\left[\bC^{-1} \bC_{,\beta}\right] \right],
+\end{equation}
+for some fiducial value of the parameter $\lambda_0$.  $F_{\alpha\beta}$ is the
+Fisher matrix, given by
+\begin{equation}
+    F_{\alpha \beta} = \frac{1}{2} \mathrm{Tr} 
+        \left[ \bC_{,\alpha} \bC^{-1} \bC_{,\beta} \bC^{-1} \right]
+\end{equation}
+
+The covariance of this estimator (assuming Gaussianity of the original
+data) is
+\begin{equation}
+    \langle \lambda_\alpha \lambda_\beta \rangle
+        - \langle \lambda_\alpha \rangle \langle \lambda_\beta \rangle
+        = F^{-1}_{\alpha\beta}
+\end{equation}
 

### 2014-04-30 writeup/dm_angular_ps.tex
small changes.
Modified estimator.

@@
 \begin{equation}
+    \label{e:est_dod}
     \hat{\lambda}_\alpha = \lambda_0
         + \frac{F^{-1}_{\alpha\beta}}{2} 
-    \left[ \bDelta^t \bC^{-1} \bC_{,\beta} \bC^{-1} \bDelta
+        \left[ \bDelta^T \bC^{-1} \bC_{,\beta} \bC^{-1} \bDelta
         - \mathrm{Tr}\left[\bC^{-1} \bC_{,\beta}\right] \right],
@@
 
+We can simplify our estimator by choosing band powers of $C_l$ as our
+parameters:
+\begin{equation}
+    C_l \approx c_\alpha \quad \textrm{for $l^{min}_\alpha \leq l <
+        l^{min}_{\alpha +1}$}
+\end{equation}
+giving
+\begin{equation}
+    C_{ij, \alpha} = \sum_{l = l^{min}_\alpha}^{l^{min}_{\alpha +1} - 1}
+        \frac{2l+1}{4 \pi} P_l(\hat{n}_i\cdot\hat{n}_j)
+        \quad\textrm{for $i \neq j$}.
+\end{equation}
+
+Because the covariance matrix is linear in our parameters, and because we are
+explicitly ignoring the noise biased auto-products in our estimator, we can
+safely drop the first and third terms in Equation~\ref{e:est_dod}.  Our final
+estimator is
+\begin{equation}
+    \hat{c}_\alpha = \frac{\tilde F^{-1}_{\alpha\beta}}{2} 
+        \left[ \bDelta^T \bC^{-1} \tilde\bC_{,\beta} \bC^{-1} \bDelta \right],
+\end{equation}
+with
+\begin{equation}
+    \tilde F_{\alpha \beta} = \frac{1}{2} \mathrm{Tr} 
+        \left[ \tilde \bC_{,\alpha} \bC^{-1} \tilde\bC_{,\beta} \bC^{-1}
+        \right].
+\end{equation}
+
 %We further assume that the terms in Equation \ref{e:D_sep} are mutually uncorrelated

### 2014-05-01 python/fisher.py
Started estimation script.

@@ -1,0 +1,40 @@
+
+import numpy as np
+from numpy.random import rand
+from scipy.special import eval_legendre
+import matplotlib.pyplot as plt
+
+n_frb = 1000
+
+l_bin_max = np.arange(1000, 100, 100)
+n_l_bin = len(l_bin_max)
+
+# Generate random catalogue positions.
+ra = rand(n_frb) * 2 * np.pi
+dec = np.arcsin(2*rand(n_frb) -1)
+
+n_dot_n = (np.sin(ra[:,None]) * np.sin(ra[None,:])
+           + np.cos(ra[:,None]) * np.cos(ra[None,:])
+           * np.cos(dec[:,None] - dec[None,:]))
+
+C_tilde_alpha = np.zeros((n_l_bin, n_frb, n_frb), dtype=np.float64)
+
+l_bin_min = 0
+for ii in range(n_l_bin):
+    for ll in range(l_bin_min, l_bin_max[ii]):
+        legendre = eval_legendre(ll, n_dot_n)
+        C_tilde_alpha[ii,:,:] += ((2 * ll + 1) / 2 / np.pi) * legendre
+    l_bin_min = l_bin_max[ii]
+C_tilde_alpha.flat[::n_frb + 1] = 0
+
+auto_var = 200**2   # Pulled random number from Matt McQuinn's paper. pc/cm^3.
+
+
+
+
+
+#plt.plot(n_dot_n, 'b.')
+#plt.show()
+
+#plt.plot(ra, dec, '.')
+#plt.show()

### 2014-05-01 python/fisher.py
Partially working script.

@@ -1,36 +1,85 @@
-
 import numpy as np
+from numpy import linalg
 from numpy.random import rand
 from scipy.special import eval_legendre
 import matplotlib.pyplot as plt
+from scipy.interpolate import interp1d
 
-n_frb = 1000
+from numpy import random
+#random.seed(10)  # XXX Repeatable.
 
-l_bin_max = np.arange(1000, 100, 100)
+n_frb = 500
+# DTYPE = np.float32
+DTYPE = np.float64
+
+#l_bin_max = np.arange(100, 500, 100)
+#l_bin_max = np.arange(20, 130, 20)
+l_min = 0
+step = 1
+stop = 5
+l_bin_max = np.arange(l_min + step, stop, step)
+l_max = l_bin_max[-1]
+c_alpha = np.ones(len(l_bin_max)) * 0   # XXX sample variance turned off.
 n_l_bin = len(l_bin_max)
 
 # Generate random catalogue positions.
 ra = rand(n_frb) * 2 * np.pi
-dec = np.arcsin(2*rand(n_frb) -1)
+dec = np.arcsin(2*rand(n_frb) - 1)
 
 n_dot_n = (np.sin(ra[:,None]) * np.sin(ra[None,:])
            + np.cos(ra[:,None]) * np.cos(ra[None,:])
            * np.cos(dec[:,None] - dec[None,:]))
+# Correct numerical errors on diagonal.
+n_dot_n.flat[::n_frb + 1] = 1
 
-C_tilde_alpha = np.zeros((n_l_bin, n_frb, n_frb), dtype=np.float64)
+C_tilde_alpha = np.zeros((n_l_bin, n_frb, n_frb), dtype=DTYPE)
 
-l_bin_min = 0
+this_l_bin_min = l_min
 for ii in range(n_l_bin):
-    for ll in range(l_bin_min, l_bin_max[ii]):
-        legendre = eval_legendre(ll, n_dot_n)
-        C_tilde_alpha[ii,:,:] += ((2 * ll + 1) / 2 / np.pi) * legendre
-    l_bin_min = l_bin_max[ii]
-C_tilde_alpha.flat[::n_frb + 1] = 0
+    for ll in range(this_l_bin_min, l_bin_max[ii]):
+        interp_domain = np.linspace(-1., 1., 4 * l_max, endpoint=True)
+        legen_interp = interp1d(interp_domain,
[…]

### 2014-05-22 writeup/dm_angular_ps.tex
Partially working script.
Wrote short road to sensitivity.

@@
 
+\red{$D^{\bar{n}_e}_i$ and $D^{\rm src}_i$ are likely correlated due to
+    redshift evolution of source events, but this does not affect the
+    measurement since both are treated as noise terms.}
+
 The cosmological information lies in the correlations between the
@@
 
+\section{Short road to sensitivity}
+
+The errorbar on the redshift averaged dispersion measure angular power spectrum
+is
+\begin{equation}
+    \sigma_{C_l} = \sqrt{\frac{2}{(2 l + 1) f_{\rm sky}}} (C_l + C^N_l),
+\end{equation}
+where the noise power spectrum is
+\begin{equation}
+    C^N_l = \frac{4 \pi \sigma_D^2 \sqrt{f_{\rm sky}}}{N_{\rm FRB}}.
+\end{equation}
+Here $N_{\rm FRB}$ is the number of dispersion measures measured from fast
+radio bursts. \red{I'm only 80\% sure about the factors of $f_{\rm sky}$}.
+
+$\sigma_D^2$ is the variance of the dispersion measures.  This would in
+practice be measured directly from the observed set, but in terms of
+theoretical parameters is
+\begin{equation}
+\sigma_D^2 = \sigma_{\bar{n}_e}^2 + \sigma^2_{\rm src} + \int \ud z \ud z'
+\delta(z - z') p(z) w^{z z'}(1),
+\end{equation}
+where the first two terms are defined above. The third term is likely
+neglidgable and could also be written as
+\begin{equation}
+    \int \ud z \ud z' \delta(z - z') p(z) w^{z z'}(1) = \int \ud z \ud z'
+    \delta(z - z') p(z) \sum_{l} \frac{2l+1}{4\pi} C_l^{zz}.
+\end{equation}
+
 \bigskip

### 2014-06-19 writeup/dm_angular_ps.tex
Minor edits.
Small clean ups.

@@
 %\documentclass[onecolumn,amsmath,amssymb,floatfix,12pt,nofootinbib]{revtex4}
-\documentclass[twocolumn,prd,noshowpacs,nofootinbib,amsmath,amssymb]{revtex4}
+\documentclass[onecolumn,prd,noshowpacs,nofootinbib,amsmath,amssymb]{revtex4}
 \usepackage{graphicx,epsfig,psfrag,bm,amssymb}
@@
 % for draft comments.
-\newcommand{\red}{\textcolor{red}}
+%\newcommand{\red}{\textcolor{red}}
+\newcommand{\red}{}
 \newcommand{\blue}{\textcolor{blue}}
@@
 \begin{align}
+    \label{e:sig_nebar}
     \langle D^{\bar{n}_e}_i D^{\bar{n}_e}_j \rangle
@@
         p(D^{\bar{n}_e}) \right)^2 \right]\\
-        &\equiv \delta_{ij} \sigma_{\bar{n}_e}^2\\
+        &\equiv \delta_{ij} \sigma_{\bar{n}_e}^2
 \end{align}
@@
 \begin{equation}
+    \label{e:sig_src}
     \langle D^{\rm src}_i D^{\rm src}_j \rangle
@@
     \langle D^{\delta_e}_i D^{\delta_e}_j \rangle =& \\
-        =& \textrm{stuff} \\
         =&
@@
 Here $N_{\rm FRB}$ is the number of dispersion measures measured from fast
-radio bursts. \red{I'm only 80\% sure about the factors of $f_{\rm sky}$}.
+radio bursts.
+%\red{I'm only 80\% sure about the factors of $f_{\rm sky}$}.
 
@@
 \end{equation}
-where the first two terms are defined above. The third term is likely
+where the first two terms are defined above in equations \ref{e:sig_nebar}
+through
+\ref{e:sig_src}. The third term is likely
 neglidgable and could also be written as

### 2014-06-19 writeup/dm_angular_ps.tex
small fixes.

@@
 
+\begin{comment}
+
 \section{Sensitivity}
@@
 
-We assume parameters X, Y, Z etc.
+% Note about cosmological parameters
 
-\section{Short road to sensitivity}
+\end{comment}
 
-The errorbar on the redshift averaged dispersion measure angular power spectrum
+\section{Simplified sensitivity calculation}
+
+In this section we present a simplified calculation for the sensitivity of the
+above estimator which is valid for sample of observed
+FRBs distributed roughly uniformly over some fraction of the sky.
+
+The error bar on the redshift averaged dispersion measure angular power spectrum
 is
@@
 $\sigma_D^2$ is the variance of the dispersion measures.  This would in
-practice be measured directly from the observed set, but in terms of
+practise be measured directly from the observed set, but in terms of
 theoretical parameters is
@@
 \ref{e:sig_src}. The third term is likely
-neglidgable and could also be written as
+negligible and could also be written as
 \begin{equation}

### 2014-07-24 writeup/dm_angular_ps.tex
New paper structure outline including Ue-Li's 3d seconds order statistics.

@@
 
-\section{Notes}\label{sec:notes}
+\section{Preliminaries}
 
@@
 term to cosmology.
+
+\section{2D statistics}
+% Need beter section title.
+
+Here we consider two dimentional statistics where the cosmological information
+lies in the correlations between dispersion measures at a given angular
+separation.  The information that is in principle available in the angular
+clustering of the FRB events is ignored.
+
+As a cosmological probe this almost perfectly analogouse to the weak lensing 
+of galaxies.
+We wish to estimate the line of site electron column density,
+which, like lensing shear, is an integral along the line-of-site to a source at an
+uncertain redshift. Our observerable the dispersion measure, like galaxy
+elipticity, gives a noisy estimate.  In both cases the angular clustering of
+the sources is ignored.
+
+The dispersion measures of two different FRBs are correlated by two effects.
+The first is correlations in the intervening line-of-site large-scale
+structure.  This correlates the $D^{\delta_e}$ part of the dispersion measures.
+The second effect is that two FRBs with small angular separation are likely to
+be at small redshift separations if FRB events trace large-scale structure.
+This correlates the $D^{\bar{n}_e}$ of the two FRBs.  In principle all
+permutations of $D^{\bar{n}_e}$, $D^{\delta_e}$ and $D^{\rm src}$ should be
+correlated to some degree, however we believe that the two effect described
+here are the dominatnt contributions and defer investications of other effect
+to future work.
+
+\subsection{The dispersion measure angular power-spectrum}
+
+\subsection{estimating the dispersion measure angular power-spectrum}
+
+\subsection{sensitivity estimates}
+
+\section{3D statistics}
+
+3D clustering of FRBs using DM as distance proxy.
+
+Dispersion measure space distortions.
+
+\subsection{First order DM space distortions}
+
+LOS election perturbations cause clusturing in unclustered FRBs.
+
+\subsection{Second order DM space distortions}
+
+LOS election perturbations cause non-stationarity/non-gaussianity in clustered FRBs.
+
+\section{Notes}\label{sec:notes}
 

### 2015-01-12 writeup/dm_angular_ps.tex
correlation function normalization.
Changes.

@@
 \newcommand{\bDelta}{\boldsymbol \Delta}
+\newcommand{\Dgal}{D^{\rm gal}}
+\newcommand{\Dne}{D^{\bar{n}_e}}
+\newcommand{\Dde}{D^{\delta_e}}
+\newcommand{\Dsrc}{D^{\rm src}}
+\newcommand{\del}{\delta\!}
+\newcommand{\calP}{{\cal P}}
 
 % for draft comments.
-%\newcommand{\red}{\textcolor{red}}
-\newcommand{\red}{}
+\newcommand{\red}{\textcolor{red}}
 \newcommand{\blue}{\textcolor{blue}}
@@
 
-\title{Fast Radio Burst Cosmology}
+\title{Fast radio burst cosmology: dispersion measure angular power spectrum}
 
@@
 
+In this paper we consider only the simplest statistic that captures some of
+the cosmological information present in an FRB survey.  This is the dispersion
+measure angular power-spectrum, which is conceptually in vary close analogy to
+the galaxy weak-lensing shear angular power spectrum. We start with a
+population of FRB events (the analogue of lensed galaxies) whose redshifts are
+unknown.  In the first instance we ignore the intrinsic clustering of these
+background sources.  The principal observable is the dispersion measure
+(shear) which is a line-of-sight integral of the intervening large-scale
+structure.  This is contaminated by a noise term (analogue of intrinsic
+ellipticity) which is the dispersion
+measure originating from the host halo as well as the dispersion measure
+originating from the spacial mean electron density coupled with the unknown
+redshift.  In both cases there is a systematic effect originating from the
+intrinsic clustering of source objects, which is that pairs of sources with
+small angular separation are likely associated with the same large-scale
+structure and thus have similar redshifts.  This induces correlations in the
+noise tern associated with the unknown distance through the mean electron
+density. The analogue in galaxy lensing is intrinsic alignments, however while
+intrinsic alignments are a non-linear effect, the redshift clustering term occurs
+at linear order.
+
 The outline of this \emph{Letter} is as follows.
@@
 \section{Preliminaries}
-
-\subsection{Dispersion measure}
 
@@
 \label{e:D_sep}
-D = D^{\rm gal} + D^{\bar{n}_e} + D^{\delta_e} + D^{\rm src}.
+D = \Dgal + \Dne + \Dde + \Dsrc
 \end{equation}
@@
 
+In addition, we define the mean subtracted values of the of the variouse dispersion
+measure quantites, $\del D = D - \langle D \rangle$. Here the angular brackets represent
+the ensemble average.
+
 We are principally interested in the $D^{\delta_e}$ term as it is a probe of
@@
 
-\section{2D statistics}
+\red{Introduce the redshift distribution function, assumption that FRB's trace
+LSS, bias, etc.}
+
+\red{Convensions: we use subscripts $i$, $j$, etc.~on coordinate-like
+    quantities to label observed FRB events. Thus $\vec x_i$ and $\hat{n}_i$
+    are respectively the 3D coordinates of and unit vector pointing to event $i$.
+    This should not be confused with superscripts, denoting the
+component of a vector, such that $x^1$ is the first componenent of vector $\vec
+x$.  }
+
+\red{$\calP$ is a probability, while $p$ is a PDF. $\calP(x < X < x + \ud x) =
+p(x) \ud x$ always.}
+
+\section{Dispersion measure angular correlations}
+
+The principle observable which we would like to consider is the correlations
+between the dispersion measures of observed fast radio bursts as a function of
+their angular separation.  For observed FRB events labeled by the indices $i$
+and $j$, and assuming $i \neq j$, we define the dispersion measure angular
+correlation function as
+\begin{equation}
+    w(\hat{n}_i\cdot\hat{n}_j) \equiv \langle \del D_i \del D_j \rangle.
+\end{equation}
+A move convienient quantity to work with is the corresponding angular
+power spectrum
+\begin{equation}
+w(\hat{n}_i \cdot\hat{n}_j) = \sum_l \frac{2l+1}{4 \pi} C_l
+P_l(\hat{n}_i\cdot\hat{n}_j).
+\end{equation}
+
+We have identified two effects that dominate the angular
+correlations and which depend on the large-scale structure of the Universe and
+thus cosmology.  The first effect is that the signals from two FRB events may
+propagate through shared structures along the line of sight.  Thus correlations
+in the election overdensities along the line of sight will correlate the 
+$\Dde$.  The second effect is that due to the intrisic clustering of source
+events, a pair of FRBs that are nearby in the angular coordinates are more
+likely to also be nearby in the line of sight coordinate, thus causing
+correations in $\Dne$.  In the remainder of this section we will calculate the
+contributions from each of these effects.
+
+\subsection{Correlations in $\Dde$}
+
+\begin{equation}
+C_l^{zz'}=\frac{2}{\pi} \int_0^{\infty}k^2 dk P_{ee}(k) \int_0^{\eta^z}\frac{d\eta}{a(\eta)} \int_0^{\eta^{z'}}\frac{d\eta'}{a(\eta')}  j_l(k\eta) j_l(k\eta')
+\end{equation}
+\begin{equation}
+C_l^{\Dde \Dde} = \int d\eta^z \int d\eta^{z'} {\cal P}(\eta^z){\cal P}(\eta^{z'}) C_l^{z z'}
+\end{equation}
+
+\subsection{Correlations in $\Dne$}
+
+The joint probablility of observing a pair of FRB events at 3D coordinates
+$\vec x_i$ and $\vec x_j$ in infintessimal volumes $\ud^3\vec x_i$ and
+$\ud^3\vec x_j$ is porportional to
+\begin{equation}
+    \calP(\vec x_i, \vec x_j) = \calP(\eta_i) \calP(\eta_j) \left[ 1 + b(z_i)
+    b(z_j) \xi(\vec x_i - \vec x_j) \right] \frac{\ud^3\vec x_i}{\eta_i^2}
+    \frac{\ud^3\vec x_j}{\eta_j^2}.
+\end{equation}
+The factors of $1/\eta^2$ are nessisary to achive the proper volume weighting,
+a fact that can be seen by taking the limit of $\xi \to 0$ and integrating of
+the angular coordinates.
+
+An observed event has known angular coordinates, and we are interested in
+correlations in $\Dne$ which is directly related to the line of sight
+coordinate.  Fixing the angular coordinates:
+\begin{equation}
+    \calP(\eta_i, \eta_j | \hat{n}_i, \hat{n}_i) = N(\hat{n}_i, \hat{n}_i)
+    \calP(\eta_i) \calP(\eta_j) \left[ 1 + b(z_i)
+    b(z_j) \xi(\vec x_i - \vec x_j) \right] \ud \eta_i \ud \eta_j,
+\end{equation}
+where $N(\hat{n}_i, \hat{n}_i)$ is a normalizing factor which ensures the
+expression integrates to unity over $\eta_i$ and $\eta_j$. \red{How to deal
+with the $1/\eta^2$ factors?.}
+Transforming to $\Dne$ as our distance measure, we obtain
+\begin{equation}
+\calP(\Dne_i, \Dne_j | \hat{n}_i, \hat{n}_i) = \calP(\eta_i, \eta_j |
+\hat{n}_i, \hat{n}_i) \frac{\ud }{}
+\end{equation}
+
+\section{Notes}\label{sec:notes}
+
+\subsection{2D statistics}
 % Need beter section title.
@@
 
-\subsection{The dispersion measure angular power-spectrum}
+\subsubsection{The dispersion measure angular power-spectrum}
 
-\subsection{estimating the dispersion measure angular power-spectrum}
+\subsubsection{estimating the dispersion measure angular power-spectrum}
 
-\subsection{sensitivity estimates}
+\subsubsection{sensitivity estimates}
 
-\section{3D statistics}
+\subsection{Random notes about correlation function normalization}
 
-3D clustering of FRBs using DM as distance proxy.
+\begin{equation}
+\langle D_i \rangle =  \langle D^{\rm src}_i \rangle
+    + \langle D^{\bar{n}_e}_i \rangle
+\end{equation}
 
-Dispersion measure space distortions.
-
-\subsection{First order DM space distortions}
-
-LOS election perturbations cause clusturing in unclustered FRBs.
-
-\subsection{Second order DM space distortions}
-
-LOS election perturbations cause non-stationarity/non-gaussianity in clustered FRBs.
-
-\section{Notes}\label{sec:notes}
+If $i \neq j$:
+\begin{align}
+\langle D_i D_j \rangle - \langle D_i \rangle \langle D_j \rangle
+    =& \langle (D^{\delta_e}_i + D^{\rm src}_i +  D^{\bar{n}_e}_i)
+              (D^{\delta_e}_j + D^{\rm src}_j +  D^{\bar{n}_e}_j) \rangle
+              - \langle D_i \rangle \langle D_j \rangle
+    \\
+    =& \langle [
+        D^{\delta_e}_i
+        + (D^{\rm src}_i - \langle D^{\rm src}_i \rangle)
+        + \langle D^{\rm src}_i \rangle
+        +  (D^{\bar{n}_e}_i -  \langle D^{\bar{n}_e}_i \rangle)
+        + \langle D^{\bar{n}_e}_i \rangle
+    ]
+    \nonumber \\
+    & \qquad [
+        D^{\delta_e}_j
+       + (D^{\rm src}_j - \langle D^{\rm src}_j \rangle)
+        + \langle D^{\rm src}_j \rangle
+        +  (D^{\bar{n}_e}_j -  \langle D^{\bar{n}_e}_j \rangle)
+        + \langle D^{\bar{n}_e}_j \rangle
+    ] \rangle
+    \nonumber \\
+    & \qquad - \langle D_i \rangle \langle D_j \rangle
+    \\
+    =& \langle D^{\delta_e}_i D^{\delta_e}_j \rangle
+        + \langle (D^{\rm src}_i - \langle D^{\rm src}_i \rangle)
+                 (D^{\rm src}_j - \langle D^{\rm src}_j \rangle) \rangle
+        + \langle (D^{\bar{n}_e}_i -  \langle D^{\bar{n}_e}_i \rangle)
+                  (D^{\bar{n}_e}_j -  \langle D^{\bar{n}_e}_j \rangle) \rangle
+    \nonumber \\
+    & \qquad
+        + \langle D^{\rm src}_i \rangle \langle D^{\rm src}_j \rangle
+        + \langle D^{\bar{n}_e}_i \rangle \langle D^{\bar{n}_e}_j \rangle
+        + \langle D^{\rm src}_i \rangle \langle D^{\bar{n}_e}_j \rangle
+        + \langle D^{\bar{n}_e}_i \rangle \langle D^{\rm src}_j \rangle
+    \nonumber \\
+    & \qquad - \langle D_i \rangle \langle D_j \rangle
+    \\
+    =& \langle D^{\delta_e}_i D^{\delta_e}_j \rangle
+        + \langle (D^{\rm src}_i - \langle D^{\rm src}_i \rangle)
+                 (D^{\rm src}_j - \langle D^{\rm src}_j \rangle) \rangle
+        + \langle (D^{\bar{n}_e}_i -  \langle D^{\bar{n}_e}_i \rangle)
+                  (D^{\bar{n}_e}_j -  \langle D^{\bar{n}_e}_j \rangle) \rangle
+\end{align}
+In the last equation, the first term is the term we've been dealing with, the
+second term is hopefully zero, and the third term is what Ue-Li is worried
+about, which we still have to calculate. I don't see anything unexpeced.
 
@@
 
-\section{Sensitivity}
+\subsection{Sensitivity}
 
@@
 
-\section{Simplified sensitivity calculation}
+\subsection{Simplified sensitivity calculation}
 

### 2015-01-20 writeup/dm_angular_ps.tex
Derivation of redshift clustering term.

@@
 a fact that can be seen by taking the limit of $\xi \to 0$ and integrating of
-the angular coordinates.
+the angular coordinates. Noting that $\calP(\eta_i)$ has units 
+$({\rm MPc}\,{\rm rad}^2)^{-1}$.
 
@@
     \calP(\eta_i, \eta_j | \hat{n}_i, \hat{n}_i) = N(\hat{n}_i, \hat{n}_i)
-    \calP(\eta_i) \calP(\eta_j) \left[ 1 + b(z_i)
+    \calP(\eta_i)\calP(\eta_j) \left[ 1 + b(z_i)
     b(z_j) \xi(\vec x_i - \vec x_j) \right] \ud \eta_i \ud \eta_j,
@@
 where $N(\hat{n}_i, \hat{n}_i)$ is a normalizing factor which ensures the
-expression integrates to unity over $\eta_i$ and $\eta_j$. \red{How to deal
-with the $1/\eta^2$ factors?.}
+expression integrates to unity over $\eta_i$ and $\eta_j$. The factors of
+$1/\eta^2$ have been canceled when converting $\ud^3 \vec x = \eta^2 \ud \eta \ud^2
+\vec \theta$. If the second term in brackets is small, then the normalizations
+$N$ is 1 (since the distributions $\calP{\eta_i}$ are already normalized. 
+This expression is
+only valid if $i \ne j$.
 Transforming to $\Dne$ as our distance measure, we obtain
+\begin{align}
+\calP(\Dne_i, \Dne_j | \hat{n}_i, \hat{n}_i)
+    &= \calP(\eta_i)\calP(\eta_j) \left[ 1 + b(z_i)
+        b(z_j) \xi(\vec x_i - \vec x_j) \right]
+        \frac{\ud \eta_i}{\ud \Dne_i} \frac{\ud \eta_j}{\ud \Dne_j}
+        \ud \Dne_i\ud \Dne_j
+        \\
+    &= \calP(\eta_i)\calP(\eta_j) \left[ 1 + b(z_i)
+        b(z_j) \xi(\vec x_i - \vec x_j) \right]
+        \frac{\ud \Dne_i}{1 + z_i}\frac{\ud \Dne_j}{1 + z_j}
+\end{align}
+Finally, taking the second moment and subtracting off the product of the first
+moments:
 \begin{equation}
-\calP(\Dne_i, \Dne_j | \hat{n}_i, \hat{n}_i) = \calP(\eta_i, \eta_j |
-\hat{n}_i, \hat{n}_i) \frac{\ud }{}
+\langle \Dne_i \Dne_j \rangle
+    - \langle \Dne_i \rangle \langle \Dne_j \rangle =
+    \int \Dne_i \Dne_j
+    \frac{\calP(\eta_i)}{1 + z_i}\frac{\calP(\eta_j)}{1 + z_j}
+    b(z_i) b(z_j) \xi(\vec x_i - \vec x_j)
+        \ud \Dne_i\ud \Dne_j
 \end{equation}

### 2015-01-26 writeup/dm_angular_ps.tex
Reorganized... again.

@@
-%\documentclass[onecolumn,amsmath,amssymb,floatfix,12pt,nofootinbib]{revtex4}
 \documentclass[onecolumn,prd,noshowpacs,nofootinbib,amsmath,amssymb]{revtex4}
@@
 \usepackage{verbatim}
-\usetikzlibrary{arrows,shapes}
-\usetikzlibrary{trees}
-\usetikzlibrary{matrix,arrows} 				% For commutative diagram
-											% http://www.felixl.de/commu.pdf
-\usetikzlibrary{positioning}				% For "above of=" commands
-\usetikzlibrary{calc,through}				% For coordinates
-\usetikzlibrary{decorations.pathreplacing}  % For curly braces
-\usepackage{pgffor}							% For repeating patterns
-
-\usetikzlibrary{decorations.pathmorphing}	% For Feynman Diagrams
-\usetikzlibrary{decorations.markings}
-\usetikzlibrary{snakes}
-
-\tikzset{
-	% >=stealth', %%  Uncomment for more conventional arrows
-    vector/.style={decorate, decoration={snake}, draw},
-	provector/.style={decorate, decoration={snake,amplitude=2.5pt}, draw},
-	antivector/.style={decorate, decoration={snake,amplitude=-2.5pt}, draw},
-    fermion/.style={draw, postaction={decorate},
-        decoration={markings,mark=at position .55 with {\arrow[draw]{>}}}},
-    fermionbar/.style={draw, postaction={decorate},
-        decoration={markings,mark=at position .55 with {\arrow[draw=black]{<}}}},
-    fermionnoarrow/.style={draw},
-    gluon/.style={decorate, draw,decoration={coil,amplitude=4pt, segment length=6pt}, line width=1},
-    scalar/.style={dashed,draw, postaction={decorate},
-        decoration={markings,mark=at position .55 with {\arrow[draw]{>}}}},
-    scalarbar/.style={dashed,draw, postaction={decorate},
-        decoration={markings,mark=at position .55 with {\arrow[draw]{<}}}},
-    scalarnoarrow/.style={dash pattern = on 6 pt off 3 pt,draw},
-    electron/.style={draw, postaction={decorate},
-        decoration={markings,mark=at position .55 with {\arrow[draw]{>}}}},
-	bigvector/.style={decorate, decoration={snake,amplitude=4pt}, draw},
-	vectorscalar/.style={loosely dotted,draw, postaction={decorate}},
-}
-\RequirePackage{xspace}
-\usepackage{relsize}
-\usepackage{slashed}
-\newcommand{\fb}{{\rm fb}}
-\newcommand{\ab}{{\rm ab}}
-
-\newcommand{\be}{\begin{eqnarray}}
-\newcommand{\ee}{\end{eqnarray}}
-\def\lsim{\mathrel{\rlap{\lower4pt\hbox{\hskip 0.5 pt$\sim$}}
-    \raise1pt\hbox{$<$}}}                % less than or approx. symbol
-\def\gsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
-    \raise1pt\hbox{$>$}}}
-
-\newcommand{\schi}{s_{\chi\bar\chi}}  % tried to use this throughout off-shell derivation so that we can change notation later if desired.
-\newcommand{\scratch}[1]{{\textcolor{red}{ #1}}}
-\newcommand{\f}{\frac}
-\newcommand{\pf}[2]{\left(\frac{#1}{#2}\right)}
-\newcommand{\g}{{\rm g}}
-\newcommand{\s}{{\rm s}}
-\newcommand{\m}{{\rm m}}
-\def\lsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
-    \raise1pt\hbox{$<$}}}
-\def\gsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
-    \raise1pt\hbox{$>$}}}
-\newcommand{\vev}[1]{ \left\langle {#1} \right\rangle }
-\newcommand{\bra}[1]{ \langle {#1} | }
-\newcommand{\ket}[1]{ | {#1} \rangle }
-\newcommand{\ev}{ {\rm eV} }
-\newcommand{\kev}{{\rm keV}}
-\newcommand{\mev}{{\rm MeV}}
-\newcommand{\gev}{{\rm GeV}}
-\newcommand{\tev}{{\rm TeV}}
-\newcommand{\mpl}{$M_{Pl}$}
-\newcommand{\mw}{$M_{W}$}
-\newcommand{\Ft}{F_{T}}
-\newcommand{\Zparity}{\mathbb{Z}_2}
-\newcommand{\BLambda}{\boldsymbol{\lambda}}
 
 % shortcuts
-\newcommand{\ud}{\,\mathrm{d}}
+%\newcommand{\ud}{\,\mathrm{d}}
 \newcommand{\bD}{\boldsymbol D}
@@
 \newcommand{\calP}{{\cal P}}
+\newcommand{\ud}{\,\mathrm{d}}
 
@@
 Columbia, Vancouver, BC, Canada V6T 1Z1}
+ \affiliation{Canadian Institute for Advanced Research, CIFAR Program in
+Cosmology and Gravity, Toronto, ON, M5G 1Z8}
 
 \begin{abstract}
-In recent years a new astrophysical phenomena, fast radio bursts (FRBs), has been detected that potentially originates from cosmological distances.
-These broadband radio bursts  typically last for only milliseconds and are a \emph{standard ping} that can be used to map the properties of the Universe.
-In this paper,  under the assumption that these bursts originate from cosmological distances, we discuss how the detection of a large enough population of these events can be used to map the cosmological properties of the Universe.
-We first discuss one point statistics and show that, even if FRBs are not standard candles, the dispersion-measure distance vs.
-luminosity-distance distribution of any observed population is a strong constraint on cosmology.
-We then discuss how the two point statistics of an observed population of FRBs traces the large-scale structure of the Universe and make predictions for the angular power spectra of dispersion-measure distance.
-It is possible that FRBs do not originate at cosmological distances, but if they do, we argue that they could open a remarkable window to observe the properties of the Universe.
+
 \end{abstract}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%					Introduction
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Introduction}
 
-\section{Introduction}
 Several years ago an unusual radio event was discovered at the Parks radio telescope while searching for millisecond pulsars.
@@
 
-The outline of this \emph{Letter} is as follows.
-In Section \ref{sec:notes} we discuss how dispersion measure provides a new distance measure in cosmology and how the joint distribution of dispersion-distance and luminosity-distance of a population of FRBs depends on cosmology and the intrinsic luminosity distance distribution.
-In Section \ref{sec:notes} we then show how to calculate the angular power spectra of dispersion distance.
-We then forecast how well these cosmological observables can be measured.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%					Basic Ingredients 
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Preliminaries}
-
-%Let's define the dispersion-measure distance.
-
-%The lets discuss how a given luminosity relationship and cosmology dictates an expected joint distribution of dispersion measure.
 
@@
 We separate the dispersion distance into the contributions from each
-term in \ref{e:ne_sep}:
+term in Equation~\ref{e:ne_sep}:
 \begin{equation}
@@
 \end{equation}
-For a population of FRBs originating at cosmological distances, ${\rm DM}^{\rm
-src}$ is only a single function of $\hat{n}$ which can presumably be well
+For a population of FRBs originating at cosmological distances, $\Dgal$
+is only a single function of $\hat{n}$ which can presumably be well
 measured.  In addition, this function could in principal be well characterized
@@
 the ensemble average.
-
-We are principally interested in the $D^{\delta_e}$ term as it is a probe of
-large-scale structure. In the next section we relate the statistics of this
-term to cosmology.
 
@@
 
-\section{Dispersion measure angular correlations}
+\section{Dispersion Measure angular correlations}
 
@@
 
+We assume that $D^{\rm src}_i$ are uncorrelated. Again this may not
+be strictly true due to clustering of FRB sources and environmental effects
+and this may bias results.  In addition $\Dsrc$ and $\Dne$ may be correlated due
+to redshift evolution of source events.
+
 \subsection{Correlations in $\Dde$}
@@
 \begin{equation}
-C_l^{\Dde \Dde} = \int d\eta^z \int d\eta^{z'} {\cal P}(\eta^z){\cal P}(\eta^{z'}) C_l^{z z'}
+C_l^{\Dde \Dde} = \int d\eta^z \int d\eta^{z'} p(\eta^z)p(\eta^{z'}) C_l^{z z'}
 \end{equation}
@@
 $\vec x_i$ and $\vec x_j$ in infintessimal volumes $\ud^3\vec x_i$ and
-$\ud^3\vec x_j$ is porportional to
+$\ud^3\vec x_j$ is
 \begin{equation}
-    \calP(\vec x_i, \vec x_j) = \calP(\eta_i) \calP(\eta_j) \left[ 1 + b(z_i)
+    \calP(\vec x_i, \vec x_j) = p(\eta_i) p(\eta_j) \left[ 1 + b(z_i)
     b(z_j) \xi(\vec x_i - \vec x_j) \right] \frac{\ud^3\vec x_i}{\eta_i^2}
@@
 a fact that can be seen by taking the limit of $\xi \to 0$ and integrating of
-the angular coordinates. Noting that $\calP(\eta_i)$ has units 
-$({\rm MPc}\,{\rm rad}^2)^{-1}$.
+the angular coordinates. Noting that $p(\eta_i)$ has units 
+\red{$({\rm MPc}\,{\rm rad}^2)^{-1}$ (conflicts with being normalized)}.
 
@@
     \calP(\eta_i, \eta_j | \hat{n}_i, \hat{n}_i) = N(\hat{n}_i, \hat{n}_i)
-    \calP(\eta_i)\calP(\eta_j) \left[ 1 + b(z_i)
+    p(\eta_i)p(\eta_j) \left[ 1 + b(z_i)
     b(z_j) \xi(\vec x_i - \vec x_j) \right] \ud \eta_i \ud \eta_j,
@@
 \vec \theta$. If the second term in brackets is small, then the normalizations
-$N$ is 1 (since the distributions $\calP{\eta_i}$ are already normalized. 
+$N$ is 1 (since the distributions $p{\eta_i}$ are already normalized. 
 This expression is
@@
 \calP(\Dne_i, \Dne_j | \hat{n}_i, \hat{n}_i)
-    &= \calP(\eta_i)\calP(\eta_j) \left[ 1 + b(z_i)
+    &= p(\eta_i)p(\eta_j) \left[ 1 + b(z_i)
         b(z_j) \xi(\vec x_i - \vec x_j) \right]
@@
         \\
-    &= \calP(\eta_i)\calP(\eta_j) \left[ 1 + b(z_i)
+    &= p(\eta_i)p(\eta_j) \left[ 1 + b(z_i)
         b(z_j) \xi(\vec x_i - \vec x_j) \right]
@@
     \int \Dne_i \Dne_j
-    \frac{\calP(\eta_i)}{1 + z_i}\frac{\calP(\eta_j)}{1 + z_j}
+    \frac{p(\eta_i)}{1 + z_i}\frac{p(\eta_j)}{1 + z_j}
     b(z_i) b(z_j) \xi(\vec x_i - \vec x_j)
@@
 \end{equation}
+And thus we have:
+\begin{equation}
+    w^{\bar{n}_e \bar{n}_e}(\hat{n}_i\cdot\hat{n}_j)
+        =\int \Dne_i \Dne_j
+    \frac{p(\eta_i)}{1 + z_i}\frac{p(\eta_j)}{1 + z_j}
+    b(z_i) b(z_j) \xi(\eta_i \hat{n}_i - \eta_j \hat{n}_j)
+        \ud \Dne_i\ud \Dne_j
+\end{equation}
+Where $\eta$ and $z$ are understood to be functions of $\Dne$.
 
-\section{Notes}\label{sec:notes}
+\section{Modeling angular correlations}
 
-\subsection{2D statistics}
-% Need beter section title.
+\section{Estimating angular correlations}
 
-Here we consider two dimentional statistics where the cosmological information
-lies in the correlations between dispersion measures at a given angular
-separation.  The information that is in principle available in the angular
-clustering of the FRB events is ignored.
+We observe a set of observed dispersion measures
+$\boldsymbol \Delta$ (whose members are $\delta D_i$)
+with known angular positions, $\hat n_i$, but with unknown
+redshifts, $z_i$.  The Covariance matrix is
+${\boldsymbol C} \equiv
+\langle \boldsymbol \Delta \boldsymbol \Delta^T \rangle$.
+The off diagonal elements depend on cosmology
+$C_{ij} = w(\hat{n}_i\cdot\hat{n}_j)$ while the diagonal part is dominated by noise.
 
-As a cosmological probe this almost perfectly analogouse to the weak lensing 
-of galaxies.
-We wish to estimate the line of site electron column density,
-which, like lensing shear, is an integral along the line-of-site to a source at an
-uncertain redshift. Our observerable the dispersion measure, like galaxy
-elipticity, gives a noisy estimate.  In both cases the angular clustering of
-the sources is ignored.
+\subsection{Noise}
 
-The dispersion measures of two different FRBs are correlated by two effects.
-The first is correlations in the intervening line-of-site large-scale
-structure.  This correlates the $D^{\delta_e}$ part of the dispersion measures.
-The second effect is that two FRBs with small angular separation are likely to
-be at small redshift separations if FRB events trace large-scale structure.
-This correlates the $D^{\bar{n}_e}$ of the two FRBs.  In principle all
-permutations of $D^{\bar{n}_e}$, $D^{\delta_e}$ and $D^{\rm src}$ should be
-correlated to some degree, however we believe that the two effect described
-here are the dominatnt contributions and defer investications of other effect
-to future work.
+The noise will be dominated by contributions from $\Dsrc$, $\Dne$ and $\Dde$.
 
-\subsubsection{The dispersion measure angular power-spectrum}
-
-\subsubsection{estimating the dispersion measure angular power-spectrum}
-
-\subsubsection{sensitivity estimates}
-
-\subsection{Random notes about correlation function normalization}
-
-\begin{equation}
-\langle D_i \rangle =  \langle D^{\rm src}_i \rangle
-    + \langle D^{\bar{n}_e}_i \rangle
-\end{equation}
-
-If $i \neq j$:
-\begin{align}
-\langle D_i D_j \rangle - \langle D_i \rangle \langle D_j \rangle
-    =& \langle (D^{\delta_e}_i + D^{\rm src}_i +  D^{\bar{n}_e}_i)
-              (D^{\delta_e}_j + D^{\rm src}_j +  D^{\bar{n}_e}_j) \rangle
-              - \langle D_i \rangle \langle D_j \rangle
-    \\
-    =& \langle [
-        D^{\delta_e}_i
-        + (D^{\rm src}_i - \langle D^{\rm src}_i \rangle)
-        + \langle D^{\rm src}_i \rangle
-        +  (D^{\bar{n}_e}_i -  \langle D^{\bar{n}_e}_i \rangle)
-        + \langle D^{\bar{n}_e}_i \rangle
-    ]
-    \nonumber \\
-    & \qquad [
-        D^{\delta_e}_j
-       + (D^{\rm src}_j - \langle D^{\rm src}_j \rangle)
-        + \langle D^{\rm src}_j \rangle
-        +  (D^{\bar{n}_e}_j -  \langle D^{\bar{n}_e}_j \rangle)
-        + \langle D^{\bar{n}_e}_j \rangle
-    ] \rangle
-    \nonumber \\
-    & \qquad - \langle D_i \rangle \langle D_j \rangle
-    \\
-    =& \langle D^{\delta_e}_i D^{\delta_e}_j \rangle
-        + \langle (D^{\rm src}_i - \langle D^{\rm src}_i \rangle)
-                 (D^{\rm src}_j - \langle D^{\rm src}_j \rangle) \rangle
-        + \langle (D^{\bar{n}_e}_i -  \langle D^{\bar{n}_e}_i \rangle)
-                  (D^{\bar{n}_e}_j -  \langle D^{\bar{n}_e}_j \rangle) \rangle
-    \nonumber \\
-    & \qquad
-        + \langle D^{\rm src}_i \rangle \langle D^{\rm src}_j \rangle
-        + \langle D^{\bar{n}_e}_i \rangle \langle D^{\bar{n}_e}_j \rangle
-        + \langle D^{\rm src}_i \rangle \langle D^{\bar{n}_e}_j \rangle
-        + \langle D^{\bar{n}_e}_i \rangle \langle D^{\rm src}_j \rangle
-    \nonumber \\
-    & \qquad - \langle D_i \rangle \langle D_j \rangle
-    \\
-    =& \langle D^{\delta_e}_i D^{\delta_e}_j \rangle
-        + \langle (D^{\rm src}_i - \langle D^{\rm src}_i \rangle)
-                 (D^{\rm src}_j - \langle D^{\rm src}_j \rangle) \rangle
-        + \langle (D^{\bar{n}_e}_i -  \langle D^{\bar{n}_e}_i \rangle)
-                  (D^{\bar{n}_e}_j -  \langle D^{\bar{n}_e}_j \rangle) \rangle
-\end{align}
-In the last equation, the first term is the term we've been dealing with, the
-second term is hopefully zero, and the third term is what Ue-Li is worried
-about, which we still have to calculate. I don't see anything unexpeced.
-
-\subsection{Relating dispersion measure angular power-spectrum to cosmology}
-
-The angular correlation function of dispersion distance between two lines of sight at redshift $z$ and direction $\hat{n}$ and redshift $z'$ and direction $\hat{n}'$ is
-\begin{equation}
-w^{z z'}(\hat{n}\cdot\hat{n}') = \langle D^{\delta_e}(\hat{n}, z) D^{\delta_e}(\hat{n}', z') \rangle
-\end{equation}
-and the corresponding angular power spectrum is
-\begin{equation}
-w^{z z'}(\hat{n}\cdot\hat{n}') = \sum_l \frac{2l+1}{4 \pi} C_l^{z z'} P_l(\hat{n}\cdot\hat{n}')
-\end{equation}
-
-We can decompose the dispersion-distance field into spherical harmonics as
-\begin{equation}
-    D^{\delta_e}(\hat{n}, z) = \sum_{l m} D^{\delta_e}_{l m}(z) Y_{l m} (\hat{n})
-\end{equation}
-
-A plane wave can be expanded in terms of spherical eigenfunctions using the Rayleigh expansion
-\begin{equation}
-e^{i \vec{k}\cdot \hat{n} \eta} = 4\pi \sum_{l m} i^l j_{l}(k\eta) Y^*_{lm}(\hat{k})Y_{lm}(\hat{n})
-\end{equation}
-If we define 
-\begin{equation}
-n_e(\vec{k}) = \int d^3 \vec{x} e^{-i \vec{x}\cdot\vec{k}} n_e(\vec{x})
-\end{equation}
-to be the Fourier transform of the comoving electron density field then we can write
-\begin{equation}
-    D^{\delta_e}_{l m}(z) = \frac{4 \pi i^{l}}{\bar{n}_{e0}} \int \frac{d^3
-    \vec{k}}{(2\pi)^3} n_e(\vec{k}) Y^*_{l m}(\hat{k}) \int_0^{\eta^z} d\eta a^{-1}(\eta) j_{l}(k\eta)
-\end{equation}
-and the angular power spectra of dispersion-distance, assumed to be an isotropic random field, is thus
-\begin{equation}
-    \langle D^{\delta_e}_{l m}(z) D^{\delta_e}_{l' m'}(z') \rangle = C_l^{z z'} \delta_{l l'} \delta_{m m'}
-\end{equation}
-Now since we have 
-\begin{equation}
-\langle n_e(\vec{k}) n_e(\vec{k}')\rangle = \bar{n}_{e0}^2\left[\langle \delta_e(\vec{k})\delta_e(\vec{k}')\rangle + 1 \right]
-\end{equation}
-where
-\begin{equation}
-\langle \delta_e(\vec{k})\delta_e(\vec{k}')\rangle = (2\pi)^3 \delta_{D}^3(\vec{k}-\vec{k}') P_{ee}(k)
-\end{equation}
-we finally have
-\begin{equation}
-C_l^{zz'}=\frac{2}{\pi} \int_0^{\infty}k^2 dk P_{ee}(k) \int_0^{\eta^z}\frac{d\eta}{a(\eta)} \int_0^{\eta^{z'}}\frac{d\eta'}{a(\eta')}  j_l(k\eta) j_l(k\eta')
-\end{equation}
-The one-point variance in the dispersion-distance from a redshift $z$ is just
-\begin{equation}
-(\sigma^2)^{zz}=\sum_{l} \frac{2l+1}{4\pi} C_l^{zz}
-\end{equation}
-Using the addition identify for a complete sum over spherical bessel functions we find that
-\begin{equation}
-(\sigma^2)^{zz}= \frac{1}{2\pi^2} \int_0^{\infty}k^2 dk P_{ee}(k) \int_0^{\eta^z}\frac{d\eta}{a(\eta)} \int_0^{\eta^{z}}\frac{d\eta'}{a(\eta')}  j_0(k\eta-k\eta')
-\end{equation}
-
-Given a source-population redshift distribution ${\cal P}(\eta^z)$, where 
-\begin{equation}
-\int d\eta^z {\cal P}(\eta^z) = 1
-\end{equation}
-
-The observable power spectrum of mean dispersion distance $\bar{D}$ is then
-\begin{equation}
-C_l^{\bar{D}\bar{D}} = \int d\eta^z \int d\eta^{z'} {\cal P}(\eta^z){\cal P}(\eta^{z'}) C_l^{z z'}
-\end{equation}
-
-We use the halo model to calculate $P_{ee}(k)$ and a potential ${\cal P}(z)$.
-
-\subsection{Estimating the DM angular power spectrum from a sample of observed
-FRBs}
-
-To relate observations to cosmology, we wish to determine how a set of observed
-dispersion measures $\boldsymbol D$ (whose members are $D_i$)
-with known angular positions, $\hat n_i$, but with unknown
-redshifts, $z_i$, depends on cosmological parameters.  We begin by defining the
-redshift probability distribution function $p(\boldsymbol z)$. We assume that the
-redshifts of the FRB sources are independent, \emph{i.e.}~we assume
-\begin{equation}
-    p(\boldsymbol z) = \prod_i p(z_i).
-\end{equation}
-This may not be strictly true since FRBs are expected to cluster and trace the
-large-scale structure. This is a potential source of bias in the estimator we
-derive.  From this assumption it follows that the $D^{\bar{n}_e}_i$ have
-uncorrelated probability distributions
-\begin{align}
-    p(D^{\bar{n}_e}_i)
-    &= p(z_i) \left|\frac{\ud D^{\bar{n}_e}}{\ud z} \right|_{z_i}^{-1} \\
-        &= p(z_i) \left(\frac{\ud \eta}{\ud z} \right)_{z_i}^{-1},
-\end{align}
-whose second moment is
 \begin{align}
     \label{e:sig_nebar}
-    \langle D^{\bar{n}_e}_i D^{\bar{n}_e}_j \rangle
-        &- \langle D^{\bar{n}_e}_i \rangle \langle D^{\bar{n}_e}_j \rangle \\
-        &= \delta_{ij} \left[ \int_0^\infty \ud D^{\bar{n}_e} (D^{\bar{n}_e})^2
+    \langle \delta D^{\bar{n}_e}_i \delta D^{\bar{n}_e}_i \rangle
+        &= \left[ \int_0^\infty \ud D^{\bar{n}_e} (D^{\bar{n}_e})^2
             p(D^{\bar{n}_e})
@@
         p(D^{\bar{n}_e}) \right)^2 \right]\\
-        &\equiv \delta_{ij} \sigma_{\bar{n}_e}^2
+        &\equiv  \sigma_{\bar{n}_e}^2
 \end{align}
 
-We further assume that $D^{\rm src}_i$ are uncorrelated. Again this may not
-be strictly true due to clustering of FRB sources and again this may bias our
-estimator. We parameterized the variance from this term as 
 \begin{equation}
     \label{e:sig_src}
-    \langle D^{\rm src}_i D^{\rm src}_j \rangle
-    - \langle D^{\rm src}_i \rangle \langle D^{\rm src}_j \rangle
-    = \delta_{ij} \sigma^2_{\rm src}.
+    \langle \delta D^{\rm src}_i \delta D^{\rm src}_i \rangle
+    \equiv \sigma^2_{\rm src}.
 \end{equation}
 
-\red{$D^{\bar{n}_e}_i$ and $D^{\rm src}_i$ are likely correlated due to
-    redshift evolution of source events, but this does not affect the
-    measurement since both are treated as noise terms.}
+\begin{equation}
+    \label{e:sig_delta}
+    \langle \delta \Dde_i \delta \Dde_i \rangle
+		= \int d\eta^z \int d\eta^{z'} \delta(\eta^z - \eta^{z'}) 
+		p(\eta^{z}) w^{z z'}(0)
+\end{equation}
 
-The cosmological information lies in the correlations between the
-$D^{\delta_e}_i$. If the redshifts of the observed FRBs where known, we
-would write the probability density function of this set as
-$p(\boldsymbol D^{\delta_e} | \boldsymbol z)$, which has second moments
-\begin{equation}
-    w^{z_i z_j}(\hat{n}_i\cdot\hat{n}_j) \equiv \int \ud \boldsymbol D^{\delta_e}
-        D^{\delta_e}_i D^{\delta_e}_j p(\boldsymbol D^{\delta_e} | \boldsymbol z).
-\end{equation}
-$w^{z_i z_j}(\hat{n}_i\cdot\hat{n}_j)$ is the redshift dependant DM angular
-correlation function, whose dependence on cosmology is derived below.
-Marginalizing $p(\boldsymbol D^{\delta_e} | \boldsymbol z)$ over the unknown redshifts
-yields
-\begin{equation}
-    p(\boldsymbol D^{\delta_e}) = \int_0^\infty \ud \boldsymbol z
-        p(\boldsymbol z) p(\boldsymbol D^{\delta_e} | \boldsymbol z).
-\end{equation}
-The second moment of the marginalized distribution is
+\subsection{Estimators}
+
+Here we sketch how the dispersion mearure angular power-spectrum, $C_l$
+could be estimated from a sample of observed dispersion-measures.
+
+The covariance matrix of the sample is:
+
 \begin{align}
-    \langle D^{\delta_e}_i D^{\delta_e}_j \rangle =& \\
-        =&
-        \begin{cases}
-            \int \ud z \ud z' p(z) p(z') w^{z z'}(\hat{n}_i\cdot\hat{n}_j) 
-                &  \text{if } (i \neq j) \\
-            \int \ud z \ud z' \delta(z - z') p(z) w^{z z'}(\hat{n}_i\cdot\hat{n}_j)
-                &  \text{if } (i = j)
-        \end{cases}
-\end{align}
-
-The covariance matrix is
-\begin{align}
-    C_{ij} \equiv& \langle D_i D_j \rangle - \langle D_i \rangle \langle D_j
-    \rangle\\
+    C_{ij} \equiv& \langle \delta D_i \delta D_j \rangle \\
     =&
@@
 
-\red{The cosmological term is probably negligible for the diagonal elements.}
-
-We have written the covariance matrix in terms of $C_l$, the
-redshift distribution function for FRBs, $p(z)$, and the unknown parameter
-$\sigma^2_{\rm src}$.  This will enable us to construct a quadratic estimator
-for a desired set of cosmological parameters from the observed set of
-dispersion measures.
-
-Now that we have the covariance matrix, we construct a quadratic estimator
-($\hat{\lambda}_\alpha$) for
-chosen parameters $\lambda_\alpha$. The estimator is Equation~11.94 from
-Dodelson, although we have to modify it slightly to exclude the
-auto-correlations.  The error (assuming Gaussianity) is Equation~11.100.
-
-Defining data vector $\bDelta = \bD - \bar{D}$ where $\bar{D}$ is the sample
-mean of dispersion measures.
-
-\begin{equation}
-    \label{e:est_dod}
-    \hat{\lambda}_\alpha = \lambda_0
-        + \frac{F^{-1}_{\alpha\beta}}{2} 
-        \left[ \bDelta^T \bC^{-1} \bC_{,\beta} \bC^{-1} \bDelta
-        - \mathrm{Tr}\left[\bC^{-1} \bC_{,\beta}\right] \right],
-\end{equation}
-for some fiducial value of the parameter $\lambda_0$.  $F_{\alpha\beta}$ is the
-Fisher matrix, given by
-\begin{equation}
-    F_{\alpha \beta} = \frac{1}{2} \mathrm{Tr} 
-        \left[ \bC_{,\alpha} \bC^{-1} \bC_{,\beta} \bC^{-1} \right]
-\end{equation}
-
-The covariance of this estimator (assuming Gaussianity of the original
-data) is
-\begin{equation}
-    \langle \lambda_\alpha \lambda_\beta \rangle
-        - \langle \lambda_\alpha \rangle \langle \lambda_\beta \rangle
-        = F^{-1}_{\alpha\beta}
-\end{equation}
-
-The dispersion measure angular correlation function 
-$w(\hat{n}_i\cdot\hat{n}_j)$ depends on the cosmology
-and the redshift distribution function $p(z)$, for which we may parameterize
-our ignorance. The
-cross-correlations between the observed dispersion measures are thus useful
-probes of cosmology.  The auto-correlations on the other hand are contaminated
-by the highly uncertain $\sigma^2_{\rm src}$ as well as the $C^{zz'}_\ell$ on
-very small scales and zero redshift separation, which is difficult to model
-theoretically.  As such they do not carry useful information.
-
-To explicitly ignore the information in the auto-correlations we define
+We see that the off diagonal terms depend on the angular power-spectrum of
+interest while the diagonal is contaminiated by the unknown parameter
+$\sigma_{\rm src}^2$. This is again in analogue to weak lensing where the
+correlations between galaxy elipticty are caused primarily by cosmic leansing shear
+while an individual galaxies elipticity is dominated the galaxy's intrinsic
+elipticity. To remove the information in the diagonal, we define a
+modified covariance matrix derivative such that:
 \begin{equation}
@@
 \end{equation}
-By replacing $C_{ij,\alpha}$ with this quantity in the above estimator, we
-obtain an estimator which explicitly excludes information in the auto-products
-and only uses the diagonal of the covariance in the noise weights. Our
-ignorance of $\sigma^2_{\rm src}$ then only affects the optimality of the
-estimator, although in practise
-$\langle D_i D_i \rangle - \langle D_i \rangle \langle D_i \rangle$ would
-simply be measured directly from the data to obtain accurate noise weights.
 
-We can simplify our estimator by choosing band powers of $C_l$ as our
-parameters:
+We will parameterize the angular power spectrum using band powers, such that:
 \begin{equation}
@@
 
-Because the covariance matrix is linear in our parameters, and because we are
-explicitly ignoring the noise biased auto-products in our estimator, we can
-safely drop the first and third terms in Equation~\ref{e:est_dod}.  Our final
-estimator is
+The estimator is then
+
 \begin{equation}
@@
 
-%We further assume that the terms in Equation \ref{e:D_sep} are mutually uncorrelated
+\subsection{Sensitivity Estimates}
 
-\begin{comment}
-is the dispersion-measure random field in angular direction $\hat{n}$ where
-\begin{equation}
-n_e(\eta^z\hat{n}) \equiv n_e(z,\hat{n}) =  \bar{n}_{e0} (1+z)^3 \left[1+\delta_e(z,\hat{n})\right]
-\end{equation}
-is the electron distribution of the Universe and $\bar{n}_{e0}$ is the mean cosmological density of free electrons today, and $\delta_e(z,\hat{n})$ is 
-the fractional over-density of electrons.
-\end{comment}
+\section{Extensions to 3D}
 
-\begin{comment}
+\subsection{Dispersion measure space distortions}
 
-\subsection{Sensitivity}
+\subsection{Four point statistics}
 
-In this section we calculate the sensitivity of a hypothetical survey observing
-X FRBs. Because $C_\ell$ contains the all the information we use bins
-of $C_\ell$ as our parameters. We use the error bar on these parameters given
-in Equation~\ref{e:error}.  We note that it is highly unlikely that an observed
-set $\{D_i\}$ is even remotely Gaussian, and as such our error-bars are likely
-underestimated and out estimator sub-optimal at the order unity level. 
-However since given that the statistics of FRBs are currently essentially
-unconstrained, we continue with this assumption.
-
-% Note about cosmological parameters
-
-\end{comment}
-
-\subsection{Simplified sensitivity calculation}
-
-In this section we present a simplified calculation for the sensitivity of the
-above estimator which is valid for sample of observed
-FRBs distributed roughly uniformly over some fraction of the sky.
-
-The error bar on the redshift averaged dispersion measure angular power spectrum
-is
-\begin{equation}
-    \sigma_{C_l} = \sqrt{\frac{2}{(2 l + 1) f_{\rm sky}}} (C_l + C^N_l),
-\end{equation}
-where the noise power spectrum is
-\begin{equation}
-    C^N_l = \frac{4 \pi \sigma_D^2 \sqrt{f_{\rm sky}}}{N_{\rm FRB}}.
-\end{equation}
-Here $N_{\rm FRB}$ is the number of dispersion measures measured from fast
-radio bursts.
-%\red{I'm only 80\% sure about the factors of $f_{\rm sky}$}.
-
-$\sigma_D^2$ is the variance of the dispersion measures.  This would in
-practise be measured directly from the observed set, but in terms of
-theoretical parameters is
-\begin{equation}
-\sigma_D^2 = \sigma_{\bar{n}_e}^2 + \sigma^2_{\rm src} + \int \ud z \ud z'
-\delta(z - z') p(z) w^{z z'}(1),
-\end{equation}
-where the first two terms are defined above in equations \ref{e:sig_nebar}
-through
-\ref{e:sig_src}. The third term is likely
-negligible and could also be written as
-\begin{equation}
-    \int \ud z \ud z' \delta(z - z') p(z) w^{z z'}(1) = \int \ud z \ud z'
-    \delta(z - z') p(z) \sum_{l} \frac{2l+1}{4\pi} C_l^{zz}.
-\end{equation}
-
-\bigskip
-\section*{Acknowledgments}
-\medskip
-
-\bibliographystyle{apsrevM}
-\bibliography{BBD-Draft}
+\section{Conclusions}
 

### 2015-01-26 writeup/dm_notes.tex
Reorganized... again.

%\documentclass[onecolumn,amsmath,amssymb,floatfix,12pt,nofootinbib]{revtex4}
\documentclass[onecolumn,prd,noshowpacs,nofootinbib,amsmath,amssymb]{revtex4}
\usepackage{graphicx,epsfig,psfrag,bm,amssymb}
\usepackage{dcolumn}
\usepackage{bm}
\usepackage{mciteplus}
\usepackage{color}
\usepackage{mathrsfs,amsfonts,hepunits, color}
\usepackage{mciteplus}
\usepackage{tikz}
\usepackage{slashed}
\usepackage{verbatim}
\usetikzlibrary{arrows,shapes}
\usetikzlibrary{trees}
\usetikzlibrary{matrix,arrows} 				% For commutative diagram
											% http://www.felixl.de/commu.pdf
\usetikzlibrary{positioning}				% For "above of=" commands
\usetikzlibrary{calc,through}				% For coordinates
\usetikzlibrary{decorations.pathreplacing}  % For curly braces
\usepackage{pgffor}							% For repeating patterns

\usetikzlibrary{decorations.pathmorphing}	% For Feynman Diagrams
\usetikzlibrary{decorations.markings}
\usetikzlibrary{snakes}

\tikzset{
	% >=stealth', %%  Uncomment for more conventional arrows
    vector/.style={decorate, decoration={snake}, draw},
	provector/.style={decorate, decoration={snake,amplitude=2.5pt}, draw},
	antivector/.style={decorate, decoration={snake,amplitude=-2.5pt}, draw},
    fermion/.style={draw, postaction={decorate},
        decoration={markings,mark=at position .55 with {\arrow[draw]{>}}}},
    fermionbar/.style={draw, postaction={decorate},
        decoration={markings,mark=at position .55 with {\arrow[draw=black]{<}}}},
    fermionnoarrow/.style={draw},
    gluon/.style={decorate, draw,decoration={coil,amplitude=4pt, segment length=6pt}, line width=1},
    scalar/.style={dashed,draw, postaction={decorate},
        decoration={markings,mark=at position .55 with {\arrow[draw]{>}}}},
    scalarbar/.style={dashed,draw, postaction={decorate},
        decoration={markings,mark=at position .55 with {\arrow[draw]{<}}}},
    scalarnoarrow/.style={dash pattern = on 6 pt off 3 pt,draw},
    electron/.style={draw, postaction={decorate},
        decoration={markings,mark=at position .55 with {\arrow[draw]{>}}}},
	bigvector/.style={decorate, decoration={snake,amplitude=4pt}, draw},
	vectorscalar/.style={loosely dotted,draw, postaction={decorate}},
}
\RequirePackage{xspace}
\usepackage{relsize}
\usepackage{slashed}
\newcommand{\fb}{{\rm fb}}
\newcommand{\ab}{{\rm ab}}

\newcommand{\be}{\begin{eqnarray}}
\newcommand{\ee}{\end{eqnarray}}
\def\lsim{\mathrel{\rlap{\lower4pt\hbox{\hskip 0.5 pt$\sim$}}
    \raise1pt\hbox{$<$}}}                % less than or approx. symbol
\def\gsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
    \raise1pt\hbox{$>$}}}

\newcommand{\schi}{s_{\chi\bar\chi}}  % tried to use this throughout off-shell derivation so that we can change notation later if desired.
\newcommand{\scratch}[1]{{\textcolor{red}{ #1}}}
\newcommand{\f}{\frac}
\newcommand{\pf}[2]{\left(\frac{#1}{#2}\right)}
\newcommand{\g}{{\rm g}}
\newcommand{\s}{{\rm s}}
\newcommand{\m}{{\rm m}}
\def\lsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
    \raise1pt\hbox{$<$}}}
\def\gsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
    \raise1pt\hbox{$>$}}}
\newcommand{\vev}[1]{ \left\langle {#1} \right\rangle }
\newcommand{\bra}[1]{ \langle {#1} | }
\newcommand{\ket}[1]{ | {#1} \rangle }
\newcommand{\ev}{ {\rm eV} }
\newcommand{\kev}{{\rm keV}}
\newcommand{\mev}{{\rm MeV}}
\newcommand{\gev}{{\rm GeV}}
\newcommand{\tev}{{\rm TeV}}
\newcommand{\mpl}{$M_{Pl}$}
\newcommand{\mw}{$M_{W}$}
\newcommand{\Ft}{F_{T}}
\newcommand{\Zparity}{\mathbb{Z}_2}
\newcommand{\BLambda}{\boldsymbol{\lambda}}

% shortcuts
\newcommand{\ud}{\,\mathrm{d}}
\newcommand{\bD}{\boldsymbol D}
\newcommand{\bC}{\boldsymbol C}
\newcommand{\bDelta}{\boldsymbol \Delta}
\newcommand{\Dgal}{D^{\rm gal}}
\newcommand{\Dne}{D^{\bar{n}_e}}
\newcommand{\Dde}{D^{\delta_e}}
\newcommand{\Dsrc}{D^{\rm src}}
\newcommand{\del}{\delta\!}
\newcommand{\calP}{{\cal P}}

% for draft comments.
\newcommand{\red}{\textcolor{red}}
\newcommand{\blue}{\textcolor{blue}}
\newcommand{\green}{\textcolor{green}}

\begin{document}

\title{Fast radio burst cosmology: dispersion measure angular power spectrum}

\author{Kris Sigurdson}
 \affiliation{Department of Physics and Astronomy, University of British 
Columbia, Vancouver, BC, Canada V6T 1Z1}

\author{Kiyoshi Wesley Masui}
 \affiliation{Department of Physics and Astronomy, University of British 
Columbia, Vancouver, BC, Canada V6T 1Z1}
 \affiliation{Canadian Institute for Advanced Research, CIFAR Program in
Cosmology and Gravity, Toronto, ON, M5G 1Z8}

\begin{abstract}
In recent years a new astrophysical phenomena, fast radio bursts (FRBs), has been detected that potentially originates from cosmological distances.  These broadband radio bursts  typically last for only milliseconds and are a \emph{standard ping} that can be used to map the properties of the Universe.  In this paper,  under the assumption that these bursts originate from cosmological distances, we discuss how the detection of a large enough population of these events can be used to map the cosmological properties of the Universe.    We first discuss one point statistics and show that, even if FRBs are not standard candles, the dispersion-measure distance vs. luminosity-distance distribution of any observed population is a strong constraint on cosmology.  We then discuss how the two point statistics of an observed population of FRBs traces the large-scale structure of the Universe and make predictions for the angular power spectra of dispersion-measure distance.  It is possible that FRBs do not originate at cosmological distances, but if they do, we argue that they could open a remarkable window to observe the properties of the Universe.
\end{abstract}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%					Introduction
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
Several years ago an unusual radio event was discovered at the Parks radio telescope while searching for millisecond pulsars.  In a direction out of the plane of the Galaxy an event was discovered with an unusually large dispersion-measure, implying a column of electrons much large than expected in the Galaxy.

In this \emph{ Letter} we consider the implications of of a cosmological population of fast radio bursts (FRBs). 
If FRBs originate at cosmological distances they provide a new window on the Universe. The key insight into the potential power of FRBs is that, while it is interesting and helpful to know the redshift of the burst, it is not necessary to do interesting studies of cosmology.

In this paper we consider only the simplest statistic that captures some of
the cosmological information present in an FRB survey.  This is the dispersion
measure angular power-spectrum, which is conceptually in vary close analogy to
the galaxy weak-lensing shear angular power spectrum. We start with a
population of FRB events (the analogue of lensed galaxies) whose redshifts are
unknown.  In the first instance we ignore the intrinsic clustering of these
background sources.  The principal observable is the dispersion measure
(shear) which is a line-of-sight integral of the intervening large-scale
structure.  This is contaminated by a noise term (analogue of intrinsic
ellipticity) which is the dispersion
measure originating from the host halo as well as the dispersion measure
originating from the spacial mean electron density coupled with the unknown
redshift.  In both cases there is a systematic effect originating from the
intrinsic clustering of source objects, which is that pairs of sources with
small angular separation are likely associated with the same large-scale
structure and thus have similar redshifts.  This induces correlations in the
noise tern associated with the unknown distance through the mean electron
density. The analogue in galaxy lensing is intrinsic alignments, however while
intrinsic alignments are a non-linear effect, the redshift clustering term occurs
at linear order.

The outline of this \emph{Letter} is as follows. In Section \ref{sec:notes} we discuss how dispersion measure provides a new distance measure in cosmology and how the joint distribution of dispersion-distance and luminosity-distance of a population of FRBs depends on cosmology and the intrinsic luminosity distance distribution.   In Section \ref{sec:notes} we then show how to calculate the angular power spectra of dispersion distance.  We then forecast how well these cosmological observables can be measured.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%					Basic Ingredients 
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Preliminaries}

%Let's define the dispersion-measure distance.

%The lets discuss how a given luminosity relationship and cosmology dictates an expected joint distribution of dispersion measure.

The dispersion measure of a FRB observed in some angular direction $\hat{n}$ and
originating from redshift $z$ is
\begin{equation}
    {\rm DM}(\hat{n}, z) = \int_0^{\eta(z)} d\eta'
        \frac{n_e(\hat{n}, z')}{(1+z')^2}.
\end{equation}
Here, $\eta$ is the conformal distance as a function of redshift, and
$n_e(\hat{n}, z)$ is the three dimensional electron density.  We choose to
separate $n_e$ into four components as follows:
\begin{equation}
\label{e:ne_sep}
n_e(\hat{n}, z) = n_e^{\rm gal}(\hat{n}, z) + \bar{n}_e(z) +
    \bar{n}_e(z)\delta_e(\hat{n}, z) + n_e^{\rm src}(\hat{n}, z).
\end{equation}
Here $n_e^{\rm gal}(\hat{n}, z)$ is the contribution to the electron density
from the Milky Way galaxy and other local structures and only contributes at
low redshift. $\bar{n}_e(z)$ is the mean electron density is and related to the
current day electron density by $\bar{n}_e = \bar{n}_{e0} (1+z)^3$. 
$\delta_e(z,\hat{n})$ is the large-scale fractional over-density of electrons.
$n_e^{\rm src}(\hat{n}, z)$ are the electrons associated with the FRB source,
which only contributes as $z \approx z^{\rm src}$ and accounts for two effects.
First the FRB itself
may have some intrinsic dispersion measure due to the environment of the
progenitor.  Second, it is unlikely that FRB events are uniformly distributed
throughout the Universe and they presumably trace matter in some way. When
considering statics of FRB dispersion measures it is necessary to account for
this bias.

We define the dispersion-measure distance (or dispersion distance),
the equivalent distance required to
produce a given amount of dispersion in an observed radio signal in the
Universe today, as $ D = {{\rm DM}}/{\bar{n}_{e0}}$
We separate the dispersion distance into the contributions from each
term in Equation~\ref{e:ne_sep}:
\begin{equation}
\label{e:D_sep}
D = \Dgal + \Dne + \Dde + \Dsrc
\end{equation}
For a population of FRBs originating at cosmological distances, $\Dgal$
is only a single function of $\hat{n}$ which can presumably be well
measured.  In addition, this function could in principal be well characterized
by independent data such as observations of pulsars.  As such, we will
here-after we ignore this term.

In addition, we define the mean subtracted values of the of the variouse dispersion
measure quantites, $\del D = D - \langle D \rangle$. Here the angular brackets represent
the ensemble average.

We are principally interested in the $D^{\delta_e}$ term as it is a probe of
large-scale structure. In the next section we relate the statistics of this
term to cosmology.

\red{Introduce the redshift distribution function, assumption that FRB's trace
LSS, bias, etc.}

\red{Convensions: we use subscripts $i$, $j$, etc.~on coordinate-like
    quantities to label observed FRB events. Thus $\vec x_i$ and $\hat{n}_i$
    are respectively the 3D coordinates of and unit vector pointing to event $i$.
    This should not be confused with superscripts, denoting the
component of a vector, such that $x^1$ is the first componenent of vector $\vec
x$.  }

\red{$\calP$ is a probability, while $p$ is a PDF. $\calP(x < X < x + \ud x) =
p(x) \ud x$ always.}

\section{Dispersion measure angular correlations}

The principle observable which we would like to consider is the correlations
between the dispersion measures of observed fast radio bursts as a function of
their angular separation.  For observed FRB events labeled by the indices $i$
and $j$, and assuming $i \neq j$, we define the dispersion measure angular
correlation function as
\begin{equation}
    w(\hat{n}_i\cdot\hat{n}_j) \equiv \langle \del D_i \del D_j \rangle.
\end{equation}
A move convienient quantity to work with is the corresponding angular
power spectrum
\begin{equation}
w(\hat{n}_i \cdot\hat{n}_j) = \sum_l \frac{2l+1}{4 \pi} C_l
P_l(\hat{n}_i\cdot\hat{n}_j).
\end{equation}

We have identified two effects that dominate the angular
correlations and which depend on the large-scale structure of the Universe and
thus cosmology.  The first effect is that the signals from two FRB events may
propagate through shared structures along the line of sight.  Thus correlations
in the election overdensities along the line of sight will correlate the 
$\Dde$.  The second effect is that due to the intrisic clustering of source
events, a pair of FRBs that are nearby in the angular coordinates are more
likely to also be nearby in the line of sight coordinate, thus causing
correations in $\Dne$.  In the remainder of this section we will calculate the
contributions from each of these effects.

\subsection{Correlations in $\Dde$}

\begin{equation}
C_l^{zz'}=\frac{2}{\pi} \int_0^{\infty}k^2 dk P_{ee}(k) \int_0^{\eta^z}\frac{d\eta}{a(\eta)} \int_0^{\eta^{z'}}\frac{d\eta'}{a(\eta')}  j_l(k\eta) j_l(k\eta')
\end{equation}
\begin{equation}
C_l^{\Dde \Dde} = \int d\eta^z \int d\eta^{z'} p(\eta^z)p(\eta^{z'}) C_l^{z z'}
\end{equation}

\subsection{Correlations in $\Dne$}

The joint probablility of observing a pair of FRB events at 3D coordinates
$\vec x_i$ and $\vec x_j$ in infintessimal volumes $\ud^3\vec x_i$ and
$\ud^3\vec x_j$ is
\begin{equation}
    \calP(\vec x_i, \vec x_j) = p(\eta_i) p(\eta_j) \left[ 1 + b(z_i)
    b(z_j) \xi(\vec x_i - \vec x_j) \right] \frac{\ud^3\vec x_i}{\eta_i^2}
    \frac{\ud^3\vec x_j}{\eta_j^2}.
\end{equation}
The factors of $1/\eta^2$ are nessisary to achive the proper volume weighting,
a fact that can be seen by taking the limit of $\xi \to 0$ and integrating of
the angular coordinates. Noting that $p(\eta_i)$ has units 
$({\rm MPc}\,{\rm rad}^2)^{-1}$.

An observed event has known angular coordinates, and we are interested in
correlations in $\Dne$ which is directly related to the line of sight
coordinate.  Fixing the angular coordinates:
\begin{equation}
    \calP(\eta_i, \eta_j | \hat{n}_i, \hat{n}_i) = N(\hat{n}_i, \hat{n}_i)
    p(\eta_i)p(\eta_j) \left[ 1 + b(z_i)
    b(z_j) \xi(\vec x_i - \vec x_j) \right] \ud \eta_i \ud \eta_j,
\end{equation}
where $N(\hat{n}_i, \hat{n}_i)$ is a normalizing factor which ensures the
expression integrates to unity over $\eta_i$ and $\eta_j$. The factors of
$1/\eta^2$ have been canceled when converting $\ud^3 \vec x = \eta^2 \ud \eta \ud^2
\vec \theta$. If the second term in brackets is small, then the normalizations
$N$ is 1 (since the distributions $p{\eta_i}$ are already normalized. 
This expression is
only valid if $i \ne j$.
Transforming to $\Dne$ as our distance measure, we obtain
\begin{align}
\calP(\Dne_i, \Dne_j | \hat{n}_i, \hat{n}_i)
    &= p(\eta_i)p(\eta_j) \left[ 1 + b(z_i)
        b(z_j) \xi(\vec x_i - \vec x_j) \right]
        \frac{\ud \eta_i}{\ud \Dne_i} \frac{\ud \eta_j}{\ud \Dne_j}
        \ud \Dne_i\ud \Dne_j
        \\
    &= p(\eta_i)p(\eta_j) \left[ 1 + b(z_i)
        b(z_j) \xi(\vec x_i - \vec x_j) \right]
        \frac{\ud \Dne_i}{1 + z_i}\frac{\ud \Dne_j}{1 + z_j}
\end{align}
Finally, taking the second moment and subtracting off the product of the first
moments:
\begin{equation}
\langle \Dne_i \Dne_j \rangle
    - \langle \Dne_i \rangle \langle \Dne_j \rangle =
    \int \Dne_i \Dne_j
    \frac{p(\eta_i)}{1 + z_i}\frac{p(\eta_j)}{1 + z_j}
    b(z_i) b(z_j) \xi(\vec x_i - \vec x_j)
        \ud \Dne_i\ud \Dne_j
\end{equation}
And thus we have:
\begin{equation}
    w^{\bar{n}_e \bar{n}_e}(\hat{n}_i\cdot\hat{n}_j)
        =\int \Dne_i \Dne_j
    \frac{p(\eta_i)}{1 + z_i}\frac{p(\eta_j)}{1 + z_j}
    b(z_i) b(z_j) \xi(\eta_i \hat{n}_i - \eta_j \hat{n}_j)
        \ud \Dne_i\ud \Dne_j
\end{equation}
Where $\eta$ and $z$ are understood to be functions of $\Dne$.

\section{Notes}\label{sec:notes}

\subsection{2D statistics}
% Need beter section title.

Here we consider two dimentional statistics where the cosmological information
lies in the correlations between dispersion measures at a given angular
separation.  The information that is in principle available in the angular
clustering of the FRB events is ignored.

As a cosmological probe this almost perfectly analogouse to the weak lensing 
of galaxies.
We wish to estimate the line of site electron column density,
which, like lensing shear, is an integral along the line-of-site to a source at an
uncertain redshift. Our observerable the dispersion measure, like galaxy
elipticity, gives a noisy estimate.  In both cases the angular clustering of
the sources is ignored.

The dispersion measures of two different FRBs are correlated by two effects.
The first is correlations in the intervening line-of-site large-scale
structure.  This correlates the $D^{\delta_e}$ part of the dispersion measures.
The second effect is that two FRBs with small angular separation are likely to
be at small redshift separations if FRB events trace large-scale structure.
This correlates the $D^{\bar{n}_e}$ of the two FRBs.  In principle all
permutations of $D^{\bar{n}_e}$, $D^{\delta_e}$ and $D^{\rm src}$ should be
correlated to some degree, however we believe that the two effect described
here are the dominatnt contributions and defer investications of other effect
to future work.

\subsubsection{The dispersion measure angular power-spectrum}

\subsubsection{estimating the dispersion measure angular power-spectrum}

\subsubsection{sensitivity estimates}

\subsection{Random notes about correlation function normalization}

\begin{equation}
\langle D_i \rangle =  \langle D^{\rm src}_i \rangle
    + \langle D^{\bar{n}_e}_i \rangle
\end{equation}

If $i \neq j$:
\begin{align}
\langle D_i D_j \rangle - \langle D_i \rangle \langle D_j \rangle
    =& \langle (D^{\delta_e}_i + D^{\rm src}_i +  D^{\bar{n}_e}_i)
              (D^{\delta_e}_j + D^{\rm src}_j +  D^{\bar{n}_e}_j) \rangle
              - \langle D_i \rangle \langle D_j \rangle
    \\
    =& \langle [
        D^{\delta_e}_i
        + (D^{\rm src}_i - \langle D^{\rm src}_i \rangle)
        + \langle D^{\rm src}_i \rangle
        +  (D^{\bar{n}_e}_i -  \langle D^{\bar{n}_e}_i \rangle)
        + \langle D^{\bar{n}_e}_i \rangle
    ]
    \nonumber \\
    & \qquad [
        D^{\delta_e}_j
       + (D^{\rm src}_j - \langle D^{\rm src}_j \rangle)
        + \langle D^{\rm src}_j \rangle
        +  (D^{\bar{n}_e}_j -  \langle D^{\bar{n}_e}_j \rangle)
        + \langle D^{\bar{n}_e}_j \rangle
    ] \rangle
    \nonumber \\
    & \qquad - \langle D_i \rangle \langle D_j \rangle
    \\
    =& \langle D^{\delta_e}_i D^{\delta_e}_j \rangle
        + \langle (D^{\rm src}_i - \langle D^{\rm src}_i \rangle)
                 (D^{\rm src}_j - \langle D^{\rm src}_j \rangle) \rangle
        + \langle (D^{\bar{n}_e}_i -  \langle D^{\bar{n}_e}_i \rangle)
                  (D^{\bar{n}_e}_j -  \langle D^{\bar{n}_e}_j \rangle) \rangle
    \nonumber \\
    & \qquad
        + \langle D^{\rm src}_i \rangle \langle D^{\rm src}_j \rangle
        + \langle D^{\bar{n}_e}_i \rangle \langle D^{\bar{n}_e}_j \rangle
        + \langle D^{\rm src}_i \rangle \langle D^{\bar{n}_e}_j \rangle
        + \langle D^{\bar{n}_e}_i \rangle \langle D^{\rm src}_j \rangle
    \nonumber \\
    & \qquad - \langle D_i \rangle \langle D_j \rangle
    \\
    =& \langle D^{\delta_e}_i D^{\delta_e}_j \rangle
        + \langle (D^{\rm src}_i - \langle D^{\rm src}_i \rangle)
                 (D^{\rm src}_j - \langle D^{\rm src}_j \rangle) \rangle
        + \langle (D^{\bar{n}_e}_i -  \langle D^{\bar{n}_e}_i \rangle)
                  (D^{\bar{n}_e}_j -  \langle D^{\bar{n}_e}_j \rangle) \rangle
\end{align}
In the last equation, the first term is the term we've been dealing with, the
second term is hopefully zero, and the third term is what Ue-Li is worried
about, which we still have to calculate. I don't see anything unexpeced.

\subsection{Relating dispersion measure angular power-spectrum to cosmology}

The angular correlation function of dispersion distance between two lines of sight at redshift $z$ and direction $\hat{n}$ and redshift $z'$ and direction $\hat{n}'$ is
\begin{equation}
w^{z z'}(\hat{n}\cdot\hat{n}') = \langle D^{\delta_e}(\hat{n}, z) D^{\delta_e}(\hat{n}', z') \rangle
\end{equation}
and the corresponding angular power spectrum is
\begin{equation}
w^{z z'}(\hat{n}\cdot\hat{n}') = \sum_l \frac{2l+1}{4 \pi} C_l^{z z'} P_l(\hat{n}\cdot\hat{n}')
\end{equation}

We can decompose the dispersion-distance field into spherical harmonics as
\begin{equation}
    D^{\delta_e}(\hat{n}, z) = \sum_{l m} D^{\delta_e}_{l m}(z) Y_{l m} (\hat{n})
\end{equation}

A plane wave can be expanded in terms of spherical eigenfunctions using the Rayleigh expansion
\begin{equation}
e^{i \vec{k}\cdot \hat{n} \eta} = 4\pi \sum_{l m} i^l j_{l}(k\eta) Y^*_{lm}(\hat{k})Y_{lm}(\hat{n})
\end{equation}
If we define 
\begin{equation}
n_e(\vec{k}) = \int d^3 \vec{x} e^{-i \vec{x}\cdot\vec{k}} n_e(\vec{x})
\end{equation}
to be the Fourier transform of the comoving electron density field then we can write
\begin{equation}
    D^{\delta_e}_{l m}(z) = \frac{4 \pi i^{l}}{\bar{n}_{e0}} \int \frac{d^3
    \vec{k}}{(2\pi)^3} n_e(\vec{k}) Y^*_{l m}(\hat{k}) \int_0^{\eta^z} d\eta a^{-1}(\eta) j_{l}(k\eta)
\end{equation}
and the angular power spectra of dispersion-distance, assumed to be an isotropic random field, is thus
\begin{equation}
    \langle D^{\delta_e}_{l m}(z) D^{\delta_e}_{l' m'}(z') \rangle = C_l^{z z'} \delta_{l l'} \delta_{m m'}
\end{equation}
Now since we have 
\begin{equation}
\langle n_e(\vec{k}) n_e(\vec{k}')\rangle = \bar{n}_{e0}^2\left[\langle \delta_e(\vec{k})\delta_e(\vec{k}')\rangle + 1 \right]
\end{equation}
where
\begin{equation}
\langle \delta_e(\vec{k})\delta_e(\vec{k}')\rangle = (2\pi)^3 \delta_{D}^3(\vec{k}-\vec{k}') P_{ee}(k)
\end{equation}
we finally have
\begin{equation}
C_l^{zz'}=\frac{2}{\pi} \int_0^{\infty}k^2 dk P_{ee}(k) \int_0^{\eta^z}\frac{d\eta}{a(\eta)} \int_0^{\eta^{z'}}\frac{d\eta'}{a(\eta')}  j_l(k\eta) j_l(k\eta')
\end{equation}
The one-point variance in the dispersion-distance from a redshift $z$ is just
\begin{equation}
(\sigma^2)^{zz}=\sum_{l} \frac{2l+1}{4\pi} C_l^{zz}
\end{equation}
Using the addition identify for a complete sum over spherical bessel functions we find that
\begin{equation}
(\sigma^2)^{zz}= \frac{1}{2\pi^2} \int_0^{\infty}k^2 dk P_{ee}(k) \int_0^{\eta^z}\frac{d\eta}{a(\eta)} \int_0^{\eta^{z}}\frac{d\eta'}{a(\eta')}  j_0(k\eta-k\eta')
\end{equation}

Given a source-population redshift distribution ${\cal P}(\eta^z)$, where 
\begin{equation}
\int d\eta^z {\cal P}(\eta^z) = 1
\end{equation}

The observable power spectrum of mean dispersion distance $\bar{D}$ is then
\begin{equation}
C_l^{\bar{D}\bar{D}} = \int d\eta^z \int d\eta^{z'} {\cal P}(\eta^z){\cal P}(\eta^{z'}) C_l^{z z'}
\end{equation}

We use the halo model to calculate $P_{ee}(k)$ and a potential ${\cal P}(z)$.

\subsection{Estimating the DM angular power spectrum from a sample of observed
FRBs}

To relate observations to cosmology, we wish to determine how a set of observed
dispersion measures $\boldsymbol D$ (whose members are $D_i$)
with known angular positions, $\hat n_i$, but with unknown
redshifts, $z_i$, depends on cosmological parameters.  We begin by defining the
redshift probability distribution function $p(\boldsymbol z)$. We assume that the
redshifts of the FRB sources are independent, \emph{i.e.}~we assume
\begin{equation}
    p(\boldsymbol z) = \prod_i p(z_i).
\end{equation}
This may not be strictly true since FRBs are expected to cluster and trace the
large-scale structure. This is a potential source of bias in the estimator we
derive.  From this assumption it follows that the $D^{\bar{n}_e}_i$ have
uncorrelated probability distributions
\begin{align}
    p(D^{\bar{n}_e}_i)
    &= p(z_i) \left|\frac{\ud D^{\bar{n}_e}}{\ud z} \right|_{z_i}^{-1} \\
        &= p(z_i) \left(\frac{\ud \eta}{\ud z} \right)_{z_i}^{-1},
\end{align}
whose second moment is
\begin{align}
    \label{e:sig_nebar}
    \langle D^{\bar{n}_e}_i D^{\bar{n}_e}_j \rangle
        &- \langle D^{\bar{n}_e}_i \rangle \langle D^{\bar{n}_e}_j \rangle \\
        &= \delta_{ij} \left[ \int_0^\infty \ud D^{\bar{n}_e} (D^{\bar{n}_e})^2
            p(D^{\bar{n}_e})
            - \left( \int_0^\infty \ud D^{\bar{n}_e} D^{\bar{n}_e}
        p(D^{\bar{n}_e}) \right)^2 \right]\\
        &\equiv \delta_{ij} \sigma_{\bar{n}_e}^2
\end{align}

We further assume that $D^{\rm src}_i$ are uncorrelated. Again this may not
be strictly true due to clustering of FRB sources and again this may bias our
estimator. We parameterized the variance from this term as 
\begin{equation}
    \label{e:sig_src}
    \langle D^{\rm src}_i D^{\rm src}_j \rangle
    - \langle D^{\rm src}_i \rangle \langle D^{\rm src}_j \rangle
    = \delta_{ij} \sigma^2_{\rm src}.
\end{equation}

\red{$D^{\bar{n}_e}_i$ and $D^{\rm src}_i$ are likely correlated due to
    redshift evolution of source events, but this does not affect the
    measurement since both are treated as noise terms.}

The cosmological information lies in the correlations between the
$D^{\delta_e}_i$. If the redshifts of the observed FRBs where known, we
would write the probability density function of this set as
$p(\boldsymbol D^{\delta_e} | \boldsymbol z)$, which has second moments
\begin{equation}
    w^{z_i z_j}(\hat{n}_i\cdot\hat{n}_j) \equiv \int \ud \boldsymbol D^{\delta_e}
        D^{\delta_e}_i D^{\delta_e}_j p(\boldsymbol D^{\delta_e} | \boldsymbol z).
\end{equation}
$w^{z_i z_j}(\hat{n}_i\cdot\hat{n}_j)$ is the redshift dependant DM angular
correlation function, whose dependence on cosmology is derived below.
Marginalizing $p(\boldsymbol D^{\delta_e} | \boldsymbol z)$ over the unknown redshifts
yields
\begin{equation}
    p(\boldsymbol D^{\delta_e}) = \int_0^\infty \ud \boldsymbol z
        p(\boldsymbol z) p(\boldsymbol D^{\delta_e} | \boldsymbol z).
\end{equation}
The second moment of the marginalized distribution is
\begin{align}
    \langle D^{\delta_e}_i D^{\delta_e}_j \rangle =& \\
        =&
        \begin{cases}
            \int \ud z \ud z' p(z) p(z') w^{z z'}(\hat{n}_i\cdot\hat{n}_j) 
                &  \text{if } (i \neq j) \\
            \int \ud z \ud z' \delta(z - z') p(z) w^{z z'}(\hat{n}_i\cdot\hat{n}_j)
                &  \text{if } (i = j)
        \end{cases}
\end{align}

The covariance matrix is
\begin{align}
    C_{ij} \equiv& \langle D_i D_j \rangle - \langle D_i \rangle \langle D_j
    \rangle\\
    =&
        \begin{cases}
            \sum_l \frac{2l+1}{4 \pi} C_l P_l(\hat{n}_i\cdot\hat{n}_j)
                &  \text{if } (i \neq j) \\
            \sigma_{\bar{n}_e}^2 + \sigma^2_{\rm src}
                + \textrm{(the $w$ term)}
                &  \text{if } (i = j)
        \end{cases}
\end{align}

\red{The cosmological term is probably negligible for the diagonal elements.}

We have written the covariance matrix in terms of $C_l$, the
redshift distribution function for FRBs, $p(z)$, and the unknown parameter
$\sigma^2_{\rm src}$.  This will enable us to construct a quadratic estimator
for a desired set of cosmological parameters from the observed set of
dispersion measures.

Now that we have the covariance matrix, we construct a quadratic estimator
($\hat{\lambda}_\alpha$) for
chosen parameters $\lambda_\alpha$. The estimator is Equation~11.94 from
Dodelson, although we have to modify it slightly to exclude the
auto-correlations.  The error (assuming Gaussianity) is Equation~11.100.

Defining data vector $\bDelta = \bD - \bar{D}$ where $\bar{D}$ is the sample
mean of dispersion measures.

\begin{equation}
    \label{e:est_dod}
    \hat{\lambda}_\alpha = \lambda_0
        + \frac{F^{-1}_{\alpha\beta}}{2} 
        \left[ \bDelta^T \bC^{-1} \bC_{,\beta} \bC^{-1} \bDelta
        - \mathrm{Tr}\left[\bC^{-1} \bC_{,\beta}\right] \right],
\end{equation}
for some fiducial value of the parameter $\lambda_0$.  $F_{\alpha\beta}$ is the
Fisher matrix, given by
\begin{equation}
    F_{\alpha \beta} = \frac{1}{2} \mathrm{Tr} 
        \left[ \bC_{,\alpha} \bC^{-1} \bC_{,\beta} \bC^{-1} \right]
\end{equation}

The covariance of this estimator (assuming Gaussianity of the original
data) is
\begin{equation}
    \langle \lambda_\alpha \lambda_\beta \rangle
        - \langle \lambda_\alpha \rangle \langle \lambda_\beta \rangle
        = F^{-1}_{\alpha\beta}
\end{equation}

The dispersion measure angular correlation function 
$w(\hat{n}_i\cdot\hat{n}_j)$ depends on the cosmology
and the redshift distribution function $p(z)$, for which we may parameterize
our ignorance. The
cross-correlations between the observed dispersion measures are thus useful
probes of cosmology.  The auto-correlations on the other hand are contaminated
by the highly uncertain $\sigma^2_{\rm src}$ as well as the $C^{zz'}_\ell$ on
very small scales and zero redshift separation, which is difficult to model
theoretically.  As such they do not carry useful information.

To explicitly ignore the information in the auto-correlations we define
\begin{equation}
    \tilde{C}_{ij,\alpha} \equiv
\begin{cases}
    C_{ij,\alpha} & \text{if } i \neq j,\\
0 & \text{if } i = j
\end{cases}.
\end{equation}
By replacing $C_{ij,\alpha}$ with this quantity in the above estimator, we
obtain an estimator which explicitly excludes information in the auto-products
and only uses the diagonal of the covariance in the noise weights. Our
ignorance of $\sigma^2_{\rm src}$ then only affects the optimality of the
estimator, although in practise
$\langle D_i D_i \rangle - \langle D_i \rangle \langle D_i \rangle$ would
simply be measured directly from the data to obtain accurate noise weights.

We can simplify our estimator by choosing band powers of $C_l$ as our
parameters:
\begin{equation}
    C_l \approx c_\alpha \quad \textrm{for $l^{min}_\alpha \leq l <
        l^{min}_{\alpha +1}$}
\end{equation}
giving
\begin{equation}
    C_{ij, \alpha} = \sum_{l = l^{min}_\alpha}^{l^{min}_{\alpha +1} - 1}
        \frac{2l+1}{4 \pi} P_l(\hat{n}_i\cdot\hat{n}_j)
        \quad\textrm{for $i \neq j$}.
\end{equation}

Because the covariance matrix is linear in our parameters, and because we are
explicitly ignoring the noise biased auto-products in our estimator, we can
safely drop the first and third terms in Equation~\ref{e:est_dod}.  Our final
estimator is
\begin{equation}
    \hat{c}_\alpha = \frac{\tilde F^{-1}_{\alpha\beta}}{2} 
        \left[ \bDelta^T \bC^{-1} \tilde\bC_{,\beta} \bC^{-1} \bDelta \right],
\end{equation}
with
\begin{equation}
    \tilde F_{\alpha \beta} = \frac{1}{2} \mathrm{Tr} 
        \left[ \tilde \bC_{,\alpha} \bC^{-1} \tilde\bC_{,\beta} \bC^{-1}
        \right].
\end{equation}

%We further assume that the terms in Equation \ref{e:D_sep} are mutually uncorrelated

\begin{comment}
is the dispersion-measure random field in angular direction $\hat{n}$ where
\begin{equation}
n_e(\eta^z\hat{n}) \equiv n_e(z,\hat{n}) =  \bar{n}_{e0} (1+z)^3 \left[1+\delta_e(z,\hat{n})\right]
\end{equation}
is the electron distribution of the Universe and $\bar{n}_{e0}$ is the mean cosmological density of free electrons today, and $\delta_e(z,\hat{n})$ is 
the fractional over-density of electrons.
\end{comment}

\begin{comment}

\subsection{Sensitivity}

In this section we calculate the sensitivity of a hypothetical survey observing
X FRBs. Because $C_\ell$ contains the all the information we use bins
of $C_\ell$ as our parameters. We use the error bar on these parameters given
in Equation~\ref{e:error}.  We note that it is highly unlikely that an observed
set $\{D_i\}$ is even remotely Gaussian, and as such our error-bars are likely
underestimated and out estimator sub-optimal at the order unity level. 
However since given that the statistics of FRBs are currently essentially
unconstrained, we continue with this assumption.

% Note about cosmological parameters

\end{comment}

\subsection{Simplified sensitivity calculation}

In this section we present a simplified calculation for the sensitivity of the
above estimator which is valid for sample of observed
FRBs distributed roughly uniformly over some fraction of the sky.

The error bar on the redshift averaged dispersion measure angular power spectrum
is
\begin{equation}
    \sigma_{C_l} = \sqrt{\frac{2}{(2 l + 1) f_{\rm sky}}} (C_l + C^N_l),
\end{equation}
where the noise power spectrum is
\begin{equation}
    C^N_l = \frac{4 \pi \sigma_D^2 \sqrt{f_{\rm sky}}}{N_{\rm FRB}}.
\end{equation}
Here $N_{\rm FRB}$ is the number of dispersion measures measured from fast
radio bursts.
%\red{I'm only 80\% sure about the factors of $f_{\rm sky}$}.

$\sigma_D^2$ is the variance of the dispersion measures.  This would in
practise be measured directly from the observed set, but in terms of
theoretical parameters is
\begin{equation}
\sigma_D^2 = \sigma_{\bar{n}_e}^2 + \sigma^2_{\rm src} + \int \ud z \ud z'
\delta(z - z') p(z) w^{z z'}(1),
\end{equation}
where the first two terms are defined above in equations \ref{e:sig_nebar}
through
\ref{e:sig_src}. The third term is likely
negligible and could also be written as
\begin{equation}
    \int \ud z \ud z' \delta(z - z') p(z) w^{z z'}(1) = \int \ud z \ud z'
    \delta(z - z') p(z) \sum_{l} \frac{2l+1}{4\pi} C_l^{zz}.
\end{equation}

\bigskip
\section*{Acknowledgments}
\medskip

\bibliographystyle{apsrevM}
\bibliography{BBD-Draft}

\end{document}

### 2015-02-05 writeup/dm_angular_ps.tex
Wrote very rough extensions section.

@@
  \affiliation{Department of Physics and Astronomy, University of British 
-Columbia, Vancouver, BC, Canada V6T 1Z1}
+Columbia, Vancouver, BC, Canada, V6T 1Z1}
 
@@
  \affiliation{Department of Physics and Astronomy, University of British 
-Columbia, Vancouver, BC, Canada V6T 1Z1}
+Columbia, Vancouver, BC, Canada, V6T 1Z1}
  \affiliation{Canadian Institute for Advanced Research, CIFAR Program in
-Cosmology and Gravity, Toronto, ON, M5G 1Z8}
+Cosmology and Gravity, Toronto, ON, Canada, M5G 1Z8}
 
@@
 \section{Preliminaries}
+
+% Dodelson uses \chi not \eta... should we used \chi?
 
@@
 
+In this section we present a simplified calculation for the sensitivity of the
+above estimator which is valid for sample of observed
+FRBs distributed roughly uniformly over some fraction of the sky.
+
+The error bar on the redshift averaged dispersion measure angular power spectrum
+is
+\begin{equation}
+    \sigma_{C_l} = \sqrt{\frac{2}{(2 l + 1) f_{\rm sky}}} (C_l + C^N_l),
+\end{equation}
+where the noise power spectrum is
+\begin{equation}
+    C^N_l = \frac{4 \pi \sigma_D^2 \sqrt{f_{\rm sky}}}{N_{\rm FRB}}.
+\end{equation}
+Here $N_{\rm FRB}$ is the number of dispersion measures measured from fast
+radio bursts. \red{this depends on the off diagonals of the covariance being
+small compared to the diagonals}.
+%\red{I'm only 80\% sure about the factors of $f_{\rm sky}$}.
+
+$\sigma_D^2$ is the variance of the dispersion measures.  This would in
+practise be measured directly from the observed set, but in terms of
+theoretical parameters is
+\begin{equation}
+\sigma_D^2 = \sigma_{\bar{n}_e}^2 + \sigma^2_{\rm src} + \int \ud z \ud z'
+\delta(z - z') p(z) w^{z z'}(1),
+\end{equation}
+where the first two terms are defined above in equations \ref{e:sig_nebar}
+through
+\ref{e:sig_src}. The third term is likely
+negligible and could also be written as
+\begin{equation}
+    \int \ud z \ud z' \delta(z - z') p(z) w^{z z'}(1) = \int \ud z \ud z'
+    \delta(z - z') p(z) \sum_{l} \frac{2l+1}{4\pi} C_l^{zz}.
+\end{equation}
+
 \section{Extensions to 3D}
+
+In the above discussions we have focused on the dispersion measure angular
+power spectrum due to its conceptual and mathematical simplicity.
+However, it is unlikely that this 2D statistic captures all or even most of the
+LSS information in a survey.  In this section we discuss possible extensions to
+3D statistics that might capture a larger portion of the total available
+information.
+
+When discussing the DM angular power spectrum, we treated the dispersion
+measure as the \emph{dependant} variable and considered statics. However,
+$\Dne$ is in one to one relation to source redshift, and as such the dispersion
+measure can be used as a proxy for radial distance.  As such we promote the
+dispersion measure to be the \emph{independent} variable and consider the
+statistics of the 3D number density field of FRB source events.
+If $\Dne$ were the only contribution to the dispersion measure then, assuming
+the FRB source events are a biased tracer of matter structure on large scales,
+this probe would be broadly similar to galaxy redshift surveys.  Variations in
+$\Dsrc$ produce a 'redshift smearing', limiting the effective resolution in the
+radial direction. The contributions to the dispersion measure from the electron
+over densities, $\Dde$, produce a variety of cosmological signals which we
+describe below.
 
@@
 
+Perturbations in the electron column density due to the intervening large-scale
+structure of free electrons results in a mis-estimation of radial distance
+from dispersion measure.  We've identified two effects through which this
+mis-estimation can cause \emph{unclustered} FRB source events to appear
+clustered, which we call the 'dilution effect' and the 'scattering effect'.
+
+In the dilution effect, FRB events embedded in electron over densities have
+additional elections (relative to the mean electron density) between them and
+thus appear to be more separated along the line of sight and less
+clustered.  If both the free electrons and the FRB source events trace the
+large-scale structure, this effect is anti correlated with the intrinsic
+clustering of the source events, although highly anisotropic.
+
+The scattering effect occurs when perturbations in the foreground free electrons
+cause the radial distances to background source events to be mis-estimated. 
+When coupled with a non-constant radial distribution
+function, $p(\eta)$, this can cause FRB source events to
+appear clustered. For instance, if there is an electron over-density in some
+direction background FRB events in that direction will be interpreted to be at
+a greater radial distance than they are. If $\ud p(\eta) /\ud \eta)$ is
+negative, there will be an excess of source events assigned to a given radial
+distance behind the electron over density which can be interpreted as apparent
+clustering of intrinsically unclustered source events.
+
+Collectively we dub these effects 'dispersion measure space distortions' due
+to its broad
+similarity to redshift space distortions. In redshift space distortions peculiar
+velocities of tracers induce a mis-estimation of radial distance using redshift.
+The convergence of these mis-estimations, proportional to the convergence of the
+peculiar velocities causes unclustered tracers to appear clustered along the line
+of sight. Since the velocity convergence and the over density are perfectly
+correlated in linear theory this manifests as an enhancement of line of sight
+clustering.
+
+By moving to 3D we fully exploit the redshift information inherent in $\Dne$ as
+opposed to treating it largely as a noise term as in our above discussion on
+the dispersion measure angular power spectrum. As such we expect such a
+treatment would greatly increase the amount of information extracted from an
+FRB survey, although we make no effort to quantify this statement.
+
+In addition we expect that in such a treatment the degeneracy between FRB
+source clustering and free electron clustering would be significantly less
+severe. This is because in 3D, the intrinsic source clustering should be perfectly
+isotropic while the electron clustering induces apparent source clustering
+only in the radial direction and should thus be highly anisotropic.
+
 \subsection{Four point statistics}
+
+In the above dispersion measure space distortions discussion, we discussed how
+scattering and dilution can cause unclustered FRB source events to appear to
+be clustered in three dimensions.  These effects also have an effect on the
+clustered source events. By scattering or diluting the radial distance of
+clustered source events, the free electron density field modulates the
+statistics of the source clustering. The two point statistics become
+non-stationary, which can be measure in the four-point statistics of the source
+event density as a non-gaussianity.
 

### 2015-02-05 writeup/dm_notes.tex
Wrote very rough extensions section.

@@
 
-\subsection{Simplified sensitivity calculation}
-
-In this section we present a simplified calculation for the sensitivity of the
-above estimator which is valid for sample of observed
-FRBs distributed roughly uniformly over some fraction of the sky.
-
-The error bar on the redshift averaged dispersion measure angular power spectrum
-is
-\begin{equation}
-    \sigma_{C_l} = \sqrt{\frac{2}{(2 l + 1) f_{\rm sky}}} (C_l + C^N_l),
-\end{equation}
-where the noise power spectrum is
-\begin{equation}
-    C^N_l = \frac{4 \pi \sigma_D^2 \sqrt{f_{\rm sky}}}{N_{\rm FRB}}.
-\end{equation}
-Here $N_{\rm FRB}$ is the number of dispersion measures measured from fast
-radio bursts.
-%\red{I'm only 80\% sure about the factors of $f_{\rm sky}$}.
-
-$\sigma_D^2$ is the variance of the dispersion measures.  This would in
-practise be measured directly from the observed set, but in terms of
-theoretical parameters is
-\begin{equation}
-\sigma_D^2 = \sigma_{\bar{n}_e}^2 + \sigma^2_{\rm src} + \int \ud z \ud z'
-\delta(z - z') p(z) w^{z z'}(1),
-\end{equation}
-where the first two terms are defined above in equations \ref{e:sig_nebar}
-through
-\ref{e:sig_src}. The third term is likely
-negligible and could also be written as
-\begin{equation}
-    \int \ud z \ud z' \delta(z - z') p(z) w^{z z'}(1) = \int \ud z \ud z'
-    \delta(z - z') p(z) \sum_{l} \frac{2l+1}{4\pi} C_l^{zz}.
-\end{equation}
-
 \bigskip

### 2015-02-26 writeup/dm_angular_ps.tex
dm_space_distortions

@@
 
-In this \emph{ Letter} we consider the implications of of a cosmological population of fast radio bursts (FRBs). 
+In this \emph{Letter} we consider the implications of of a cosmological population of fast radio bursts (FRBs). 
 If FRBs originate at cosmological distances they provide a new window on the Universe.
@@
 
-In addition, we define the mean subtracted values of the of the variouse dispersion
-measure quantites, $\del D = D - \langle D \rangle$. Here the angular brackets represent
+In addition, we define the mean subtracted values of the of the various dispersion
+measure quantities, $\del D = D - \langle D \rangle$. Here the angular brackets represent
 the ensemble average.
@@
 
-\red{Convensions: we use subscripts $i$, $j$, etc.~on coordinate-like
+\red{Conventions: we use subscripts $i$, $j$, etc.~on coordinate-like
     quantities to label observed FRB events. Thus $\vec x_i$ and $\hat{n}_i$
@@
     This should not be confused with superscripts, denoting the
-component of a vector, such that $x^1$ is the first componenent of vector $\vec
+component of a vector, such that $x^1$ is the first component of vector $\vec
 x$.  }
@@
 
+An important characteristic for an FRB survey is the ensemble radial distribution
+function $p(\eta_i)$ which gives the probability density that an FRB source event 
+occurred at radial distance $\eta_i$. The number events between radial distance
+$\eta$ and $\eta + \ud \eta$ is
+$N p(\eta)$ where $N$ is the cumulative number of events in the sample. The 3D source
+event density is $\bar{n}(\eta) = N p(\eta) / (4 \pi \eta^2)$. Because the
+radial distance cannot be measured directly, this function is unknown and must
+be fit for in the analysis.
+
 \section{Dispersion Measure angular correlations}
@@
 between the dispersion measures of observed fast radio bursts as a function of
-their angular separation.  For observed FRB events labeled by the indices $i$
+their angular separation.  For observed FRB events labelled by the indices $i$
 and $j$, and assuming $i \neq j$, we define the dispersion measure angular
@@
 \end{equation}
-A move convienient quantity to work with is the corresponding angular
+A more convenient quantity to work with is the corresponding angular
 power spectrum
@@
 thus cosmology.  The first effect is that the signals from two FRB events may
-propagate through shared structures along the line of sight.  Thus correlations
-in the election overdensities along the line of sight will correlate the 
-$\Dde$.  The second effect is that due to the intrisic clustering of source
+propagate through shared large-scale structure along the line of sight.
+Thus correlations
+in the election over densities along the line of sight will correlate
+$\Dde$.  The second effect is that due to the intrinsic clustering of source
 events, a pair of FRBs that are nearby in the angular coordinates are more
 likely to also be nearby in the line of sight coordinate, thus causing
-correations in $\Dne$.  In the remainder of this section we will calculate the
+correlations in $\Dne$.  In the remainder of this section we will calculate the
 contributions from each of these effects.
@@
 be strictly true due to clustering of FRB sources and environmental effects
-and this may bias results.  In addition $\Dsrc$ and $\Dne$ may be correlated due
-to redshift evolution of source events.
+and this may bias results.  \red{I don't thing the following matter for $i \neq
+j$} In addition $\Dsrc$ and $\Dne$ may be correlated due
+to redshift evolution of source events. Finally, redshift evolution of the
+source events and their environments could correlate $\Dsrc$ with $\Dde$. Here
+we do not attempt to quantify these correlations.
 
@@
 
+\red{I think this is wrong. It is missing factors of $1/(1+z)$.}
+
+This would be true if FRB's we uniformly distributed on the sky.  However their
+locations correlate with LSS, and as such we get cross terms.
+
 \subsection{Correlations in $\Dne$}
 
-The joint probablility of observing a pair of FRB events at 3D coordinates
-$\vec x_i$ and $\vec x_j$ in infintessimal volumes $\ud^3\vec x_i$ and
+The joint probability of observing a pair of FRB events at 3D coordinates
+$\vec x_i$ and $\vec x_j$ in infinitesimal volumes $\ud^3\vec x_i$ and
 $\ud^3\vec x_j$ is
 \begin{equation}
-    \calP(\vec x_i, \vec x_j) = p(\eta_i) p(\eta_j) \left[ 1 + b(z_i)
-    b(z_j) \xi(\vec x_i - \vec x_j) \right] \frac{\ud^3\vec x_i}{\eta_i^2}
-    \frac{\ud^3\vec x_j}{\eta_j^2}.
+    \calP(\vec x_i, \vec x_j) =
+    \frac{N^2 p(\eta_i) p(\eta_j)}{(4 \pi)^2 \eta_i^2 \eta_j^2}
+    \left[ 1 + b(z_i) b(z_j) \xi(\vec x_i - \vec x_j) \right]
+    \ud^3\vec x_i \ud^3\vec x_j.
 \end{equation}
-The factors of $1/\eta^2$ are nessisary to achive the proper volume weighting,
+The factors of $1/\eta^2$ are necessary to achieve the proper volume weighting,
 a fact that can be seen by taking the limit of $\xi \to 0$ and integrating of
@@
 expression integrates to unity over $\eta_i$ and $\eta_j$. The factors of
-$1/\eta^2$ have been canceled when converting $\ud^3 \vec x = \eta^2 \ud \eta \ud^2
+$1/\eta^2$ have been cancelled when converting $\ud^3 \vec x = \eta^2 \ud \eta \ud^2
 \vec \theta$. If the second term in brackets is small, then the normalizations
-$N$ is 1 (since the distributions $p{\eta_i}$ are already normalized. 
+$N$ is 1 (since the distributions $p(\eta_i)$ are already normalized. 
 This expression is
@@
 
-Here we sketch how the dispersion mearure angular power-spectrum, $C_l$
+Here we sketch how the dispersion measure angular power-spectrum, $C_l$
 could be estimated from a sample of observed dispersion-measures.
@@
 We see that the off diagonal terms depend on the angular power-spectrum of
-interest while the diagonal is contaminiated by the unknown parameter
+interest while the diagonal is contaminated by the unknown parameter
 $\sigma_{\rm src}^2$. This is again in analogue to weak lensing where the
-correlations between galaxy elipticty are caused primarily by cosmic leansing shear
-while an individual galaxies elipticity is dominated the galaxy's intrinsic
-elipticity. To remove the information in the diagonal, we define a
+correlations between galaxy ellipticity are caused primarily by cosmic lensing shear
+while an individual galaxies ellipticity is dominated the galaxy's intrinsic
+ellipticity. To remove the information in the diagonal, we define a
 modified covariance matrix derivative such that:

### 2015-02-26 writeup/dm_space_distortions.tex
dm_space_distortions

\documentclass[onecolumn,prd,nofootinbib]{revtex4-1}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{color}
\usepackage{verbatim}

% shortcuts
%\newcommand{\ud}{\,\mathrm{d}}
\newcommand{\bD}{\boldsymbol D}
\newcommand{\bC}{\boldsymbol C}
\newcommand{\bDelta}{\boldsymbol \Delta}
\newcommand{\Dgal}{D^{\rm gal}}
\newcommand{\Dne}{D^{\bar{n}_e}}
\newcommand{\Dde}{D^{\delta_e}}
\newcommand{\Dsrc}{D^{\rm src}}
\newcommand{\del}{\delta\!}
\newcommand{\calP}{{\cal P}}
\newcommand{\ud}{\,\mathrm{d}}

% for draft comments.
\newcommand{\red}{\textcolor{red}}
\newcommand{\blue}{\textcolor{blue}}
\newcommand{\green}{\textcolor{green}}

\begin{document}

\title{The large scale clustering of fast radio bursts in dispersion measure space}

\author{Kiyoshi Wesley Masui}
 \affiliation{Department of Physics and Astronomy, University of British 
Columbia, Vancouver, BC, Canada, V6T 1Z1}
 \affiliation{Canadian Institute for Advanced Research, CIFAR Program in
Cosmology and Gravity, Toronto, ON, Canada, M5G 1Z8}

\author{Kris Sigurdson}
 \affiliation{Department of Physics and Astronomy, University of British 
Columbia, Vancouver, BC, Canada, V6T 1Z1}

\begin{abstract}

\end{abstract}

\maketitle

\section{FRB density perturnbations in DM space}

\begin{equation}
D(\hat n, \chi) = \int_0^\chi \ud \chi' a(\chi')^2
   \left[1 + \delta_e(\hat{n}\chi')\right]
\end{equation}

This defines DM space:
\begin{equation}
D(\chi_s) =  \int_0^{\chi_s} \ud \chi' a(\chi')^2
\end{equation}

Combining the above, we find that:
\begin{equation}
\frac{\ud \chi_s}{\ud \chi} = (1 + \delta_e),
\end{equation}
and
\begin{equation}
\chi_s - \chi = \int_0^\chi \ud \chi' \delta_e(\hat n \chi').
\end{equation}

\begin{equation}
\label{e:density}
n_{fs}(\vec x_s) \ud^3\vec x_s = n_{f}(\vec x) \ud^3\vec x
\end{equation}

Averaged over the sky, the galaxy density should be the same in DM 
space as in real space.
\begin{equation}
\bar{n}_{fs}(\chi_s)\left[ 1 + \delta_f(\vec x_s)\right] \ud^3\vec x_s
    = \bar{n}_{f}(\chi)\left[ 1 + \delta_f(\vec x)\right] \ud^3\vec x
\end{equation}

\begin{equation}
\bar{n}_{fs}(\chi) = \bar{n}_f(\chi)
\end{equation}
Therefore,
\begin{align}
\bar{n}_{fs}(\chi_s) 
    &= \bar{n}_{f}(\chi) + (\chi_s - \chi)\frac{\ud \bar{n}_f}{\ud \chi}\\
    &= \bar{n}_{f}(\chi)
       + \frac{\ud \bar{n}_f}{\ud \chi}\int_0^\chi \ud \chi' \delta_e(\hat n \chi')
       \label{e:nfs}
\end{align}

The jacobian in spherical coordinates is:
\begin{align}
\left| \frac{\ud^3\vec x}{\ud^3\vec x_s} \right|
    &= \frac{\ud \chi}{\ud \chi_s}\frac{\chi^2}{\chi_s^2}\\
    &= (1 + \delta_e)^{-1}
       \left(1 + \frac{\int_0^\chi \ud \chi' \delta_e(\hat n \chi')}
                      {\chi}\right)^{-2}\\
    &\approx 1 - \delta_e
        - \frac{2}{\chi}\int_0^\chi \ud \chi' \delta_e(\hat n \chi')
        \label{e:jac}
\end{align}
Following Kaiser, the third line follows since the
second factor in parenthases on the second line, which is the
average overdensity along the line of sight, is much
closer to unity than the first due to cancelations.

Substituting Equations~\ref{e:nfs}~and~\ref{e:jac} into Equation~\ref{e:density},
we obtain:
\begin{equation}
\label{e:delta_s}
    \delta_{fs} = \delta_f - \delta_e
    - \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi}
    + \frac{2}{\chi} \right)
        \int_0^\chi \ud \chi' \delta_e(\hat n \chi')
\end{equation}

\section{Two-point statistics in DM space}

In this section all quantities are already first order in the perturbations so
there is no need to distinguish between the DM space coordinates and the real
space coordintes. The correction is higher order. Still need to distinguish
between DM space and real space fields ($\delta_{fs} \neq \delta_f$, but
$\delta_f(\vec x_s) \approx \delta_f(\vec x)$).

Unlike in redshift-space distortions, Equation~\ref{e:delta_s} does not have a
simple form in harmonic space. The equations third term couples harmonic modes
and thus the two-point statistic cannot be phrased as a simple power spectrum.
We will phrase the two point statistic in terms of $C^{ss}_{\ell D D'}$, which is
the cross-correlation angular power-spectrum of the DM space source overdensity
on DM shells at $D$ and $D'$.

Because the expression for the density perturbations in DM space involves an
integral over the line of sight, which for far off sources may cover a
significant amount of the Universe's expansion, it is nessisary to explicitly
account for light cone effects. This is most easily done in linear theory,
where these effects are scale independant, a factorization that allows certian
integral to be performed. In reality, non-linear growth causes both the bias
and the growth factor to be scale and time dependant. As in weak lensing, this
would need to be simulated.

We use the following convensions:
\begin{equation}
    P_X(k, \chi) = b_X^2 g(\chi)^2 a(\chi)^2 P(k, 0)
\end{equation}

\begin{equation}
    \delta_X(\vec x, \chi) =  b_X g(\chi) a(\chi) \int\frac{\ud^3\vec k}{(2 \pi)^3}
        e^{i\vec k \cdot \vec x} \delta(\vec k, 0)
\end{equation}

\begin{equation}
    w^{XX}(\hat n \cdot \hat n', \chi, \chi')
    \equiv \langle \delta_X(\vec x) \delta_X(\vec x') \rangle
\end{equation}

For dark matter:
\begin{align}
w(\hat n \cdot \hat n', \chi, \chi') 
    &= gg'aa'
        \int\frac{\ud^3\vec k}{(2 \pi)^3} \frac{\ud^3\vec k'}{(2 \pi)^3}
        e^{i\vec k \cdot \vec x} e^{i\vec k' \cdot \vec x'}
        \langle \delta(\vec k, 0) \delta(\vec k', 0) \rangle\\
    &= gg'aa'
        \int\frac{\ud^3\vec k}{(2 \pi)^3} 
        e^{i\vec k \cdot (\vec x - \vec x')} P(k, 0)\\
    &= gg'aa'
        \int\frac{\ud^3\vec k}{(2 \pi)^3} 
        e^{i\vec k \cdot (\vec x - \vec x')} P(k)\\
    &= gg'aa'
        \int\frac{k^2 \sin(\theta_k) \ud k \ud \theta_k \ud \phi_k}{(2 \pi)^3} 
        e^{i k |\vec x - \vec x'| \cos\theta_k} P(k, 0)\\
    &= gg'aa'
        \int_0^\infty\frac{\ud k}{2 \pi^2} k^2
        \frac{\sin(k |\vec x - \vec x'|)}{k |\vec x - \vec x'|} P(k, 0)\\
    &= gg'aa'
        \int_0^\infty\frac{\ud k}{2 \pi^2} k^2
        j_0 (k \sqrt{\chi^2 + \chi'^{^2} - \chi \chi' \hat n \cdot \hat n'})
        P(k, 0)
\end{align}
Somehow when I integrate this against a lengendre polynomial, $P_\ell(\mu)$,
to get $C_\ell$
I'm going to get Bessel functions. Lets assume that works (Kris, how does this
work?) to get:
\begin{equation}
    C_{\ell\chi\chi'} = \frac{2 gg'aa'}{\pi}
    \int_0^\infty\ud k k^2 j_\ell(k \chi) j_\ell(k \chi')
        P(k, 0)
\end{equation}

Define $\delta_d$ as:
\begin{equation}
    \delta_d(\hat n \chi) = \int_0^\chi \ud \chi' \delta_e(\hat n \chi')
\end{equation}
which doesn't have the same units as overdensity, but that is okay.
\begin{align}
    w^{dd}(\hat n \cdot \hat n', \chi, \chi')
    &= \int_0^\chi \ud \chi'' \int_0^{\chi'} \ud \chi'''
         \langle \delta_e(\hat n \chi'') \delta_e(\hat n' \chi''') \rangle\\
    &= b_e^2\int_0^\chi \ud \chi'' \int_0^{\chi'} \ud \chi'''
        g''g'''a''a'''
        \int\frac{\ud^3\vec k}{(2 \pi)^3} \frac{\ud^3\vec k'}{(2 \pi)^3}
        e^{i\vec k \cdot \vec x''} e^{i\vec k' \cdot \vec x'''}
        \langle \delta(\vec k, 0) \delta(\vec k', 0) \rangle\\
    &= b_e^2\int_0^\chi \ud \chi'' \int_0^{\chi'} \ud \chi'''
        g''g'''a''a'''
        \int_0^\infty\frac{\ud k}{2 \pi^2} k^2
        j_0 (k \sqrt{\chi''^2 + \chi'''^{^2} - \chi'' \chi''' \hat n \cdot \hat n'})
        P(k, 0)
\end{align}

\end{document}

### 2015-03-19 writeup/dm_space_distortions.tex
Many changes.

@@
 
-\section{FRB density perturnbations in DM space}
+\section{FRB density perturbations in DM space}
 
 \begin{equation}
-D(\hat n, \chi) = \int_0^\chi \ud \chi' a(\chi')^2
+D(\hat n, \chi) = \int_0^\chi \frac{\ud\chi'}{a(\chi')}
    \left[1 + \delta_e(\hat{n}\chi')\right]
@@
 \begin{equation}
-D(\chi_s) =  \int_0^{\chi_s} \ud \chi' a(\chi')^2
+D(\chi_s) = \int_0^{\chi_s}\frac{\ud\chi'}{a(\chi')}
 \end{equation}
@@
 Following Kaiser, the third line follows since the
-second factor in parenthases on the second line, which is the
+second factor in parentheses on the second line, which is the
 average overdensity along the line of sight, is much
-closer to unity than the first due to cancelations.
+closer to unity than the first due to cancellations.
 
@@
 there is no need to distinguish between the DM space coordinates and the real
-space coordintes. The correction is higher order. Still need to distinguish
+space coordinates. The correction is higher order. Still need to distinguish
 between DM space and real space fields ($\delta_{fs} \neq \delta_f$, but
@@
 integral over the line of sight, which for far off sources may cover a
-significant amount of the Universe's expansion, it is nessisary to explicitly
+significant amount of the Universe's expansion, it is necessary to explicitly
 account for light cone effects. This is most easily done in linear theory,
-where these effects are scale independant, a factorization that allows certian
+where these effects are scale independent, a factorization that allows certain
 integral to be performed. In reality, non-linear growth causes both the bias
@@
 
-We use the following convensions:
+We use the following conventions:
 \begin{equation}
-    P_X(k, \chi) = b_X^2 g(\chi)^2 a(\chi)^2 P(k, 0)
+    P_{xy}(k, \chi) = b_x b_y g(\chi)^2 a(\chi)^2 P(k, 0)
 \end{equation}
@@
 \begin{equation}
-    \delta_X(\vec x, \chi) =  b_X g(\chi) a(\chi) \int\frac{\ud^3\vec k}{(2 \pi)^3}
+    \delta_x(\vec x, \chi) =  b_x g(\chi) a(\chi) \int\frac{\ud^3\vec k}{(2 \pi)^3}
         e^{i\vec k \cdot \vec x} \delta(\vec k, 0)
@@
 \begin{equation}
-    w^{XX}(\hat n \cdot \hat n', \chi, \chi')
-    \equiv \langle \delta_X(\vec x) \delta_X(\vec x') \rangle
+    w^{xy}(\hat n \cdot \hat n', \chi, \chi')
+    \equiv \langle \delta_x(\vec x) \delta_y(\vec x') \rangle
 \end{equation}
 
-For dark matter:
+For dark matter, ignoring time dependance (redshift evolution)
+of the power spectrum:
+\begin{align}
+\delta_{\ell\ell'}\delta_{mm'}C_\ell(\chi, \chi')
+    &= \int\ud\Omega\ud\Omega'Y_{\ell m}(\hat n) Y_{\ell' m'}(\hat n')
+        \langle \delta(\hat n \chi) \delta(\hat n' \chi') \rangle
+        \\
+    &= gg'aa'
+        \int\ud\Omega\ud\Omega'Y_{\ell m}(\hat n) Y_{\ell' m'}(\hat n')
+        \int\frac{\ud^3\vec k}{(2 \pi)^3} \frac{\ud^3\vec k'}{(2 \pi)^3}
+        e^{i\vec k \cdot \vec x} e^{i\vec k' \cdot \vec x'}
+        \langle \delta(\vec k, 0) \delta(\vec k', 0) \rangle
+        \\
+    &= gg'aa'
+        \int\ud\Omega\ud\Omega'Y_{\ell m}(\hat n) Y_{\ell' m'}(\hat n')
+        \int\frac{\ud^3\vec k}{(2 \pi)^3} 
+        e^{i\vec k \cdot (\vec x - \vec x')} P(k, 0)
+        \\
+    &= gg'aa'
+        \int\frac{\ud^3\vec k}{(2 \pi)^3} P(k, 0)
+        \int\ud\Omega Y_{\ell m}(\hat n)
+        e^{i\vec k \cdot \vec x}
+        \int\ud\Omega' Y_{\ell' m'}(\hat n')
+        e^{-i\vec k \cdot \vec x'}
+        \\
+    &= gg'aa'
+        \int\frac{\ud^3\vec k}{(2 \pi)^3} P(k, 0)
+        \left[(4 \pi) i^\ell j_\ell(k\chi) Y_{\ell m}^*(\hat k)\right]
+        \left[(4 \pi) i^{-\ell'} j_{\ell'}(k\chi') Y_{\ell' m'}(\hat
+        k)\right]
+        \\
+    &= gg'aa'\frac{2}{\pi}
+        \int\ud k k^2 j_\ell(k\chi) j_{\ell'}(k\chi')P(k, 0)
+        \int\ud \Omega_k i^{(\ell - \ell')}
+        Y_{\ell' m'}^*(\hat k) Y_{\ell m}(\hat k)
+        \\
+    &= \delta_{\ell\ell'}\delta_{mm'}gg'aa'\frac{2}{\pi}
+        \int\ud k k^2  j_\ell(k\chi) j_{\ell}(k\chi')P(k, 0)
+        \\
+C_\ell(\chi,\chi') 
+    &= gg'aa'\frac{2}{\pi}
+        \int\ud k k^2 j_\ell(k\chi) j_{\ell}(k\chi')P(k, 0)
+\end{align}
+
+\section{Small angles and Limber}
+
+Alternately, on the flat sky and for small angles:
+\begin{align}
+(2\pi)^2\delta^2(\vec \ell - \vec \ell')C_\ell(\chi, \chi')
+    &=
+        \int\ud^2\vec\theta\ud^2\vec\theta'
+        e^{-i\vec\ell\cdot\vec\theta} e^{-i\vec\ell'\cdot\vec\theta'}
+        \langle \delta(\hat n \chi) \delta(\hat n' \chi') \rangle
+        \\
+    &= gg'aa'
+        \int\ud^2\vec\theta\ud^2\vec\theta'
+        e^{-i\vec\ell\cdot\vec\theta} e^{-i\vec\ell'\cdot\vec\theta'}
+        \int\frac{\ud^3\vec k}{(2 \pi)^3} 
+        e^{i\vec k \cdot (\vec x - \vec x')} P(k, 0)
+        \\
+    &= gg'aa'
+        \int\frac{\ud^3\vec k}{(2 \pi)^3} 
+        e^{i k_\parallel (\chi - \chi')} P(k, 0)
+        \int\ud^2\vec\theta e^{-i(\vec\ell-\bar\chi\vec k_\bot)\cdot\vec\theta}
+        \int\ud^2\vec\theta' e^{-i(\vec\ell'-\bar\chi\vec k_\bot)\cdot\vec\theta'}
+        \\
+    &= gg'aa'
+        \int\frac{\ud^3\vec k}{(2 \pi)^3} 
+        e^{i k_\parallel (\chi - \chi')} P(\sqrt{k_\parallel^2 + k_\bot^2}, 0)
+        (2\pi)^4 \delta^2(\vec\ell - \bar\chi \vec k_\bot)
+        \delta^2(\vec\ell' - \bar\chi\vec k_\bot)
+        \\
+    &= gg'aa'
+        \int_{-\infty}^\infty\frac{\ud k_\parallel}{(2 \pi)} 
+        e^{i k_\parallel (\chi - \chi')}
+        P(\sqrt{k_\parallel^2 + \ell^2/\bar\chi^2}, 0)
+        \frac{(2\pi)^2\delta^2(\vec\ell' - \vec \ell)}{\bar\chi^2}
+        \\
+C_\ell(\chi, \chi')
+    &= \frac{gg'aa'}{\bar\chi^2}
+        \int_{-\infty}^\infty\frac{\ud k_\parallel}{(2 \pi)} 
+        e^{i k_\parallel (\chi - \chi')}
+        P(\sqrt{k_\parallel^2 + \ell^2/\bar\chi^2}, 0)
+\end{align}
+Which is valid for $\ell \gg 1$ and $\chi - \chi' \ll \bar\chi$.
+$\bar \chi \equiv (\chi + \chi') /2$
+
+Define $\delta_d$ as:
+\begin{equation}
+    \delta_d(\hat n \chi) = \int_0^\chi \ud \chi' \delta_e(\hat n \chi')
+\end{equation}
+which doesn't have the same units as over-density, but that is okay.
+\begin{equation}
+C^{dd}_\ell(\chi,\chi') 
+    =
+    \frac{2}{\pi}
+    \int_0^\chi\ud\chi''g''a''
+    \int_0^{\chi'}\ud\chi'''
+    g'''a'''
+    \int\ud k k^2 j_\ell(k\chi'') j_{\ell}(k\chi''')P_{ee}(k, 0)
+\end{equation}
+At this point we could again to the transformation to $C_{\ell\chi\chi'}$
+leaving the expression as a triple integral. This is not as computationally
+costly as might be expected at first glance, since the $\chi''$ and $\chi'''$
+integrals are almost the same for all $\chi$, $\chi'$ pairs with only the
+limits of integration changing. Thus the full set of $C_{\ell\chi\chi'}$'s can
+be computed with a cumulative sum, only performing one new integral (over $k$)
+for each element.
+
+Or for flat sky and small angles:
+\begin{align}
+C^{dd}_\ell(\chi,\chi') 
+    &=
+    \int_0^\chi\ud\chi''g''a''
+    \int_0^{\chi'}\ud\chi'''g'''a'''
+    \frac{1}{\bar\chi^2}
+    \int_{-\infty}^\infty\frac{\ud k_\parallel}{(2 \pi)} 
+    e^{i k_\parallel (\chi'' - \chi''')}
+    P_{ee}(\sqrt{k_\parallel^2 + \ell^2/\bar\chi^2}, 0)
+    \\
+    &\approx
+    \int_0^\chi\ud\chi''g''a''
+    \int_0^{\chi'}\ud\chi'''g'''a'''
+    \frac{1}{\bar\chi^2}
+    \int_{-\infty}^\infty\frac{\ud k_\parallel}{(2 \pi)} 
+    e^{i k_\parallel (\chi'' - \chi''')}
+    P_{ee}(\ell/\bar\chi, 0)
+    \\
+    &=
+    \int_0^\chi\ud\chi''g''a''
+    \int_0^{\chi'}\ud\chi'''g'''a'''
+    \frac{1}{\bar\chi^2}
+    \delta(\chi'' - \chi''')
+    P_{ee}(\ell/\bar\chi, 0)
+    \\
+    &=
+    \int_0^{\min(\chi,\chi')}\ud\chi''
+    \left(\frac{g''a''}{\chi''}\right)^2
+    P_{ee}(\ell/\chi'', 0)
+\end{align}
+\red{Double check the $\min$.}
+where the second line applies Limber's approximation.
+
+Finally, the cross terms:
+\begin{equation}
+C^{dx}_\ell(\chi,\chi')
+    =
+    g'a'
+    \frac{2}{\pi}
+    \int_0^\chi\ud\chi''g''a''
+    \int\ud k k^2 j_\ell(k\chi'') j_{\ell}(k\chi')P_{ex}(k, 0)
+\end{equation}
+Or under Limber:
+\begin{align}
+C^{dx}_\ell(\chi,\chi')
+    &=
+    g'a'
+    \int_0^\chi\ud\chi''g''a''
+    \frac{1}{\bar\chi^2}
+    \delta(\chi'' - \chi')
+    P_{ex}(\ell/\bar\chi, 0)
+    \\
+    &=
+    \left(\frac{g'a'}{\chi'}\right)^2
+    P_{ex}(\ell/\chi', 0)
+    \qquad \textrm{if $\chi' < \chi$ and 0 otherwise.}
+    \\
+C^{dx}_\ell(\chi,\chi') + C^{xd}_\ell(\chi,\chi')
+    &=
+    \left(\frac{g^ma^m}{\chi^m}\right)^2
+    P_{ex}(\ell/\chi^m, 0)
+\end{align}
+
+Accumulating all terms for Limber and assuming a linear bias model:
+\begin{align}
+C^{ss}_\ell(\chi_m,\Delta\chi) =&~
+    (b_f - b_e)^2 \left(\frac{g_m a_m}{\chi_m}\right)^2
+        \int_{-\infty}^\infty\frac{\ud k_\parallel}{(2 \pi)} 
+        e^{i k_\parallel \Delta\chi}
+        P(\sqrt{k_\parallel^2 + \ell^2/\chi_m^2}, 0)
+    \\ &+
+    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi}
+    + \frac{2}{\chi} \right)_{\chi_m}^2
+    b_e^2 \int_0^{\chi_m}\ud\chi''
+        \left(\frac{g''a''}{\chi''}\right)^2
+        P(\ell/\chi'', 0)
+    \\ &+
+    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi}
+    + \frac{2}{\chi} \right)_{\chi_m}
+    b_e(b_f - b_e)\left(\frac{g_m a_m}{\chi_m}\right)^2
+        P(\ell/\chi_m, 0)
+\end{align}
+
+%%%% SCRAP
+
+\begin{comment}
 \begin{align}
@@
 \end{align}
-Somehow when I integrate this against a lengendre polynomial, $P_\ell(\mu)$,
+Somehow when I integrate this against a Legendre polynomial, $P_\ell(\mu)$,
 to get $C_\ell$
@@
 \end{equation}
+\end{comment}
 
-Define $\delta_d$ as:
-\begin{equation}
-    \delta_d(\hat n \chi) = \int_0^\chi \ud \chi' \delta_e(\hat n \chi')
-\end{equation}
-which doesn't have the same units as overdensity, but that is okay.
+\begin{comment}
 \begin{align}
@@
 
+Alternately, we can make the limber approximation (replacing
+$a(\chi'')g(\chi'')$ and $a(\chi''')g(\chi''')$ with 
+$a(\bar \chi)g(\bar \chi)$) and small angle approximations
+(replacing the argument of the spherical Bessel with
+$k\sqrt{\Delta \chi^2 + (\bar \chi (\hat n - \hat n'))^2}$).
+\begin{align}
+    w^{dd}(\hat n \cdot \hat n', \chi, \chi')
+    &= b_e^2\int_0^\chi \ud \chi'' \int_0^{\chi'} \ud \chi'''
+        (g(\bar \chi) a(\bar \chi))^2
+        \int_0^\infty\frac{\ud k}{2 \pi^2} k^2
+        j_0 (k \sqrt{\Delta \chi^2 + (\bar \chi (\hat n - \hat n'))^2})
+        P(k, 0)\\
+    &= b_e^2\int_0^{(\chi + \chi')/2} \ud \bar\chi 
+        (g(\bar \chi) a(\bar \chi))^2
+        \int_0^\infty\frac{\ud k}{2 \pi^2} k^2
+        P(k, 0)
+        \int_{-\infty}^{\infty} \ud \Delta\chi
+        j_0 (k \sqrt{\Delta \chi^2 + (\bar \chi (\hat n - \hat n'))^2})\\
+\end{align}
+
+\end{comment}
+
 \end{document}

### 2015-03-21 writeup/dm_space_distortions.tex
started code to do integrals.

@@
 
-For dark matter, ignoring time dependance (redshift evolution)
+For any statistically stationary tracers $x$ and $y$,
+ignoring time dependance (redshift evolution)
 of the power spectrum:
 \begin{align}
-\delta_{\ell\ell'}\delta_{mm'}C_\ell(\chi, \chi')
+    \delta_{\ell\ell'}\delta_{mm'}C^{xy}_\ell(\chi, \chi')
     &= \int\ud\Omega\ud\Omega'Y_{\ell m}(\hat n) Y_{\ell' m'}(\hat n')
-        \langle \delta(\hat n \chi) \delta(\hat n' \chi') \rangle
+        \langle \delta^x(\hat n \chi) \delta^y(\hat n' \chi') \rangle
         \\
-    &= gg'aa'
+    &=
         \int\ud\Omega\ud\Omega'Y_{\ell m}(\hat n) Y_{\ell' m'}(\hat n')
@@
         e^{i\vec k \cdot \vec x} e^{i\vec k' \cdot \vec x'}
-        \langle \delta(\vec k, 0) \delta(\vec k', 0) \rangle
+        \langle \delta(\vec k) \delta(\vec k') \rangle
         \\
-    &= gg'aa'
+    &=
         \int\ud\Omega\ud\Omega'Y_{\ell m}(\hat n) Y_{\ell' m'}(\hat n')
         \int\frac{\ud^3\vec k}{(2 \pi)^3} 
-        e^{i\vec k \cdot (\vec x - \vec x')} P(k, 0)
+        e^{i\vec k \cdot (\vec x - \vec x')} P_{xy}(k)
         \\
-    &= gg'aa'
-        \int\frac{\ud^3\vec k}{(2 \pi)^3} P(k, 0)
+    &=
+        \int\frac{\ud^3\vec k}{(2 \pi)^3} P_{xy}(k)
         \int\ud\Omega Y_{\ell m}(\hat n)
@@
         \\
-    &= gg'aa'
-        \int\frac{\ud^3\vec k}{(2 \pi)^3} P(k, 0)
+    &=
+        \int\frac{\ud^3\vec k}{(2 \pi)^3} P_{xy}(k)
         \left[(4 \pi) i^\ell j_\ell(k\chi) Y_{\ell m}^*(\hat k)\right]
@@
         \\
-    &= gg'aa'\frac{2}{\pi}
-        \int\ud k k^2 j_\ell(k\chi) j_{\ell'}(k\chi')P(k, 0)
+    &=
+        \frac{2}{\pi}
+        \int_0^\infty\ud k k^2 j_\ell(k\chi) j_{\ell'}(k\chi')P_{xy}(k)
         \int\ud \Omega_k i^{(\ell - \ell')}
@@
         \\
-    &= \delta_{\ell\ell'}\delta_{mm'}gg'aa'\frac{2}{\pi}
-        \int\ud k k^2  j_\ell(k\chi) j_{\ell}(k\chi')P(k, 0)
+    &= \delta_{\ell\ell'}\delta_{mm'}\frac{2}{\pi}
+        \int_0^\infty\ud k k^2  j_\ell(k\chi) j_{\ell}(k\chi')P_{xy}(k)
         \\
-C_\ell(\chi,\chi') 
-    &= gg'aa'\frac{2}{\pi}
-        \int\ud k k^2 j_\ell(k\chi) j_{\ell}(k\chi')P(k, 0)
+    C^{xy}_\ell(\chi,\chi') 
+    &= \frac{2}{\pi}
+\int_0^\infty\ud k k^2 j_\ell(k\chi) j_{\ell}(k\chi')P_{xy}(k)
 \end{align}
+
+It is convienient to reparameterize this in terms of
+$\bar\chi \equiv (\chi + \chi') /2$ and $\Delta \chi \equiv \chi' - \chi$.
+We expect the power spectrum to vary slowly as a function of $\bar\chi$ and
+very quickly as a function of $\Delta\chi$. However it will be highly
+suppressed for $\ell \gg \bar\chi/\Delta\chi$. These facts will be very
+helpfull in subsequent numerical integrals.
+
+Also since smallish value of $\Delta\chi$ are of interest, this leads us to
+an obviouse way to include redshift dependance of the
+power spectrum:
+\begin{equation}
+C^{xy}_\ell(\bar\chi,\Delta\chi) 
+    = \frac{2}{\pi}
+    \int_0^\infty\ud k k^2
+    j_\ell(k\chi) j_{\ell}(k\chi')
+    P_{xy}(k,\bar\chi) \qquad \Delta\chi \ll 1/aH
+\end{equation}
+
+Define $\delta_d$ as:
+\begin{equation}
+    \delta_d(\hat n \chi) = \int_0^\chi \ud \chi' \delta_e(\hat n \chi')
+\end{equation}
+which doesn't have the same units as over-density, but that is okay.
+\begin{equation}
+C^{dd}_\ell(\chi,\chi')
+    =
+    \frac{2}{\pi}
+    \int_0^\chi\ud\chi''
+    \int_0^{\chi'}\ud\chi'''
+    \int_0^\infty\ud k k^2 j_\ell(k\chi'') j_{\ell}(k\chi'''
+    )P_{ee}(k, (\chi''+\chi''')/2)
+\end{equation}
+
+For numerical integration, perform the following change of variables to make
+things much easier.
+\begin{equation}
+C^{dd}_\ell(\chi,\chi')
+    =
+    \frac{2}{\pi}
+    \int_0^{(\chi' + \chi)/2}\ud\bar\chi'
+    \int_{\max(-2\bar\chi', -2(\chi -\bar\chi'))}^{\min(2\bar\chi', 2(\chi' -
+    \bar\chi'))}\ud\Delta'
+    \int_0^\infty\ud k k^2 j_\ell(k(\bar\chi' - \Delta'/2))
+    j_{\ell}(k(\bar\chi' + \Delta'/2))
+    P_{ee}(k, \bar\chi')
+\end{equation}
+At this point we could again to the transformation to $C_{\ell\chi\chi'}$
+leaving the expression as a triple integral. This is not as computationally
+costly as might be expected at first glance, since the $\chi''$ and $\chi'''$
+integrals are almost the same for all $\chi$, $\chi'$ pairs with only the
+limits of integration changing. Thus the full set of $C_{\ell\chi\chi'}$'s can
+be computed with a cumulative sum, only performing one new integral (over $k$)
+for each element.
+
+Finally, the cross terms:
+\begin{equation}
+C^{dx}_\ell(\chi,\chi')
+    =
+    \frac{2}{\pi}
+    \int_0^\chi\ud\chi''
+    \int_0^\infty\ud k k^2 
+    j_\ell(k\chi') j_{\ell}(k\chi'')P_{ex}(k, (\chi' + \chi'')/2)
+\end{equation}
+\begin{equation}
+    C^{dx}_\ell(\chi,\chi') + C^{xd}_\ell(\chi,\chi')
+    =
+    \frac{2}{\pi}
+    \int_0^\chi\ud\chi''
+    \int_0^\infty\ud k k^2 
+    j_\ell(k\chi') j_{\ell}(k\chi'')P_{ex}(k, (\chi' + \chi'')/2)
+\end{equation}
+
+with the following change of variables for numerical integration:
+\begin{align}
+C^{dx}_\ell(\chi,\chi')
+    =&
+    \frac{2}{\pi}
+    \int_{-\chi'}^{\chi - \chi'}\ud\Delta'
+    \int_0^\infty\ud k k^2 j_\ell(k\chi')
+    j_{\ell}(k(\chi'+\Delta'))
+    P_{ex}(k, \chi' + \Delta'/2)
+    \\
+C^{dx}_\ell(\chi,\chi') + C^{xd}_\ell(\chi,\chi')
+    \approx&
+    \frac{2}{\pi}
+    \int_{-\chi'}^{\chi - \chi'}\ud\Delta'
+    \int_0^\infty\ud k k^2 j_\ell(k(\chi'-\Delta/2))
+    j_{\ell}(k(\chi'+\Delta'/2))
+    P_{ex}(k, \chi')
+    \nonumber\\
+    &+
+    \frac{2}{\pi}
+    \int_{-\chi}^{\chi' - \chi}\ud\Delta'
+    \int_0^\infty\ud k k^2 j_\ell(k(\chi-\Delta/2))
+    j_{\ell}(k(\chi+\Delta'/2))
+    P_{ex}(k, \chi)
+\end{align}
+The second line exploits the fact that for $\ell \gg 1$, $\chi \gg \chi'/\ell$ and
+$\chi' \gg \chi/\ell$, only $\Delta'\ll\chi$ contributes significantly to the
+integral. Also the expressions are very weak functions of $\chi$ and thus
+may be shifted by $\Delta/2$ without incurring much error.
 
@@
 
-Define $\delta_d$ as:
-\begin{equation}
-    \delta_d(\hat n \chi) = \int_0^\chi \ud \chi' \delta_e(\hat n \chi')
-\end{equation}
-which doesn't have the same units as over-density, but that is okay.
-\begin{equation}
-C^{dd}_\ell(\chi,\chi') 
-    =
-    \frac{2}{\pi}
-    \int_0^\chi\ud\chi''g''a''
-    \int_0^{\chi'}\ud\chi'''
-    g'''a'''
-    \int\ud k k^2 j_\ell(k\chi'') j_{\ell}(k\chi''')P_{ee}(k, 0)
-\end{equation}
-At this point we could again to the transformation to $C_{\ell\chi\chi'}$
-leaving the expression as a triple integral. This is not as computationally
-costly as might be expected at first glance, since the $\chi''$ and $\chi'''$
-integrals are almost the same for all $\chi$, $\chi'$ pairs with only the
-limits of integration changing. Thus the full set of $C_{\ell\chi\chi'}$'s can
-be computed with a cumulative sum, only performing one new integral (over $k$)
-for each element.
-
 Or for flat sky and small angles:
@@
 
-Finally, the cross terms:
-\begin{equation}
-C^{dx}_\ell(\chi,\chi')
-    =
-    g'a'
-    \frac{2}{\pi}
-    \int_0^\chi\ud\chi''g''a''
-    \int\ud k k^2 j_\ell(k\chi'') j_{\ell}(k\chi')P_{ex}(k, 0)
-\end{equation}
 Or under Limber:

### 2015-03-21 python/matter_power.py

@@ -1,0 +1,23 @@
+from os import path
+
+import numpy as np
+from scipy import interpolate
+
+from cora.util.cosmology import Cosmology
+
+
+DATA_DIR = path.join(path.dirname(__file__), 'data')
+FILE_PAT = "Pk_z%3.1f.dat"
+REDSHIFTS = np.arange(0, 2.001, 0.2)
+
+# k values are the same for all redshifts.
+K = np.loadtxt(path.join(DATA_DIR, FILE_PAT % REDSHIFTS[0]))[:,0]
+DATA = np.concatenate([np.loadtxt(path.join(DATA_DIR, FILE_PAT % z))[None,:,1]
+                       for z in REDSHIFTS])
+
+
+def interpolator():
+    c = Cosmology()
+    chi = c.comoving_distance(REDSHIFTS)
+    interpolator = interpolate.interp2d(K, chi, DATA, kind='cubic')
+    return interpolator

### 2015-03-21 python/sph_bessel.py

@@ -1,0 +1,98 @@
+"""Spherical bessel functions and an integrator."""
+
+import numpy as np
+import math
+
+from scipy import special, integrate
+
+
+def jn(n, x):
+    """Not safe for x = 0."""
+    return np.sqrt(np.pi / (2 * x)) * special.jv(n + 1./2, x)
+
+
+def approx_jn(n, x):
+    nu = n + 1./2
+    arg = np.pi / 4
+    arg -= np.arccos(nu / x) * nu
+    arg += np.sqrt(x * x - nu * nu)
+    out = np.sin(arg)
+    out /= x * (1 - nu * nu / x / x)**(1./4)
+    return out
+
+
+def jnjn(n, mean, delta, x):
+    a = mean - delta/2
+    b = mean + delta/2
+    return jn(n, a * x) * jn(n, b * x)
+
+
+def approx_jnjn(n, mean, delta, x):
+    a = mean - delta/2
+    b = mean + delta/2
+    nu = n + 1./2
+    t = np.sqrt(mean**2 * x**2 - nu**2)
+    arg = (mean * delta) * (x**2 / t)
+    arg += (delta**2 / 2) * (x**2 / t)
+    arg -= (mean**2 * delta**2 / 2) * (x**4 / t**3)
+    arg -= np.arccos(nu / b / x) * nu
+    arg += np.arccos(nu / a / x) * nu
+    out = (1./2) * np.cos(arg)
+    out /= a * x * (1 - nu**2 / (a * x)**2)**(1./4)
+    out /= b * x * (1 - nu**2 / (b * x)**2)**(1./4)
+    return out
+
+
+def sample_jnjn(n, mean, delta, x_max):
+    """Doesn't work for n=0.
+
+    Notes
+    -----
+
+    Integration is in 4 Sections:
+    - 0: x*mean = 0 to n - 2*sqrt(n), 0 points
+    - 1: x*mean = n-2*sqrt(n) to n, 9 points
+    - 2: x*mean = n to 2n, n points
+    - 3: x*mean = 2n to max
+
+    """
+
+    # Figure out total number of samples:
+    bound_lower = max((n - 1 * math.sqrt(n)) / mean, 0)
+    bound_middle = n / mean
+    bound_upper = (n + 5 * math.sqrt(n)) / mean
+    if bound_upper > x_max:
+        bound_upper = x_max
+        nparts_upper = 0
+        delta_upper = 0
+    else:
+        nparts_upper = max(pow_2_gt((x_max - bound_upper) * delta), 8)
[…]

### 2015-03-21 python/tests/test_matter_power.py

@@ -1,0 +1,23 @@
+import unittest
+
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy import interpolate, special
+
+import matter_power
+
+
+
+class TestInterpolator(unittest.TestCase):
+
+    def test_z0(self):
+        i = matter_power.interpolator()
+        k = matter_power.K.copy()
+        ans = matter_power.DATA[0.,:]
+        self.assertTrue(np.allclose(i(k, 0.0001), ans))
+
+
+
+
+if __name__ == "__main__":
+    unittest.main()

### 2015-03-21 python/tests/test_sph_bessel.py

@@ -1,0 +1,84 @@
+import unittest
+
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy import interpolate, special
+
+import sph_bessel
+
+
+camb_dat = np.loadtxt("matter_power_z1.dat")
+matter_power = interpolate.interp1d(camb_dat[:,0], camb_dat[:,1])
+k_camb = camb_dat[1:-1,0].copy()
+
+
+class TestSph_jn(unittest.TestCase):
+
+    def test_j0(self):
+        x = np.arange(1, 1000) / 10.
+        right_ans = np.sin(x) / x
+        sph_j0 = sph_bessel.jn(0, x)
+        self.assertTrue(np.allclose(sph_j0, right_ans))
+
+    def test_jn(self):
+        n = 1234
+        x = 2300.
+        right_ans = special.sph_jn(n, x)[0][-1]
+        j = sph_bessel.jn(n, x)
+        self.assertTrue(np.allclose(j, right_ans))
+
+    def test_approx(self):
+        x = np.arange(10, 50, 0.1)
+        n = 5
+        j = sph_bessel.jn(n, x)
+        approx_j = sph_bessel.approx_jn(n, x)
+        #plt.plot(x, j)
+        #plt.plot(x, approx_j)
+        #plt.plot(x, approx_j-j)
+        #plt.show()
+        self.assertTrue(np.allclose(j, approx_j, atol=0.003))
+
+    def test_approx_prod(self):
+        n = 50
+        mean = 1000.
+        delta = 10.
+        x = np.arange(0.1, 2, 0.001)
+        approx = sph_bessel.approx_jnjn(n, mean, delta, x)
+        right_ans = sph_bessel.jnjn(n, mean, delta, x)
+        ra_s = np.cumsum(right_ans[::-1])
+        a_s = np.cumsum(approx[::-1])
+        #plt.plot(a * x[::-1], ra_s)
+        #plt.plot(a * x[::-1], a_s)
+        #plt.show()
+        self.assertTrue(np.allclose(a_s, ra_s, atol=0.0001))
+
+class TestIntegration(unittest.TestCase):
+
+    def test_sample(self):
+        n = 10
+        mean = 1000.
+        delta = 1.
+        k_max = 2
+        x_dense = np.arange(0.001, 2, 0.0001)
+        x, n_tuple, delta_tuple = sph_bessel.sample_jnjn(n, mean, delta, k_max)
+        print np.diff(x)
[…]

### 2015-03-22 python/sph_bessel.py
k integral finsihed.

@@ -4,6 +4,7 @@ import numpy as np
 import math
 
 from scipy import special, integrate
+import matplotlib.pyplot as plt
 
 
 def jn(n, x):
@@ -44,7 +45,7 @@ def approx_jnjn(n, mean, delta, x):
 
 
 def sample_jnjn(n, mean, delta, x_max):
-    """Doesn't work for n=0.
+    """
 
     Notes
     -----
@@ -57,31 +58,93 @@ def sample_jnjn(n, mean, delta, x_max):
 
     """
 
+    adelta = abs(delta)
+    if adelta <= mean * 1e-6:
+        adelta = mean * 1e-6
+    umean = mean + delta / 2
+    lmean = mean - delta / 2
     # Figure out total number of samples:
-    bound_lower = max((n - 1 * math.sqrt(n)) / mean, 0)
-    bound_middle = n / mean
-    bound_upper = (n + 5 * math.sqrt(n)) / mean
-    if bound_upper > x_max:
+    bound_lower = max((n - 1.5 * math.sqrt(n)) / umean, 0)
+    #bound_middle = n / mean
+    bound_upper = max(n + 3 * math.sqrt(n), n + 30) / lmean
+    if bound_upper >= x_max:
         bound_upper = x_max
         nparts_upper = 0
         delta_upper = 0
     else:
-        nparts_upper = max(pow_2_gt((x_max - bound_upper) * delta), 8)
+        nparts_upper = max(pow_2_gt(1 * (x_max - bound_upper) * adelta), 128)
         delta_upper = (x_max - bound_upper) / nparts_upper
     
-    nparts_middle = pow_2_gt((bound_upper - bound_middle) * mean)
-    nparts_lower = 8
-    delta_lower = (bound_middle - bound_lower) / nparts_lower
-    delta_middle = (bound_upper - bound_middle) / nparts_middle
+    nparts_lower = pow_2_gt(2. * (bound_upper - bound_lower) * mean)
+    #nparts_lower = 8
+    #delta_lower = (bound_middle - bound_lower) / nparts_lower
+    delta_lower = (bound_upper - bound_lower) / nparts_lower
     
     points_lower = bound_lower + np.arange(nparts_lower) * delta_lower
-    points_middle = bound_middle + np.arange(nparts_middle) * delta_middle
+    #points_middle = bound_middle + np.arange(nparts_middle) * delta_middle
[…]

### 2015-03-22 python/tests/test_sph_bessel.py

@@ -7,7 +7,7 @@ from scipy import interpolate, special
 import sph_bessel
 
 
-camb_dat = np.loadtxt("matter_power_z1.dat")
+camb_dat = np.loadtxt("data/Pk_z0.0.dat")
 matter_power = interpolate.interp1d(camb_dat[:,0], camb_dat[:,1])
 k_camb = camb_dat[1:-1,0].copy()
 
@@ -55,28 +55,48 @@ class TestSph_jn(unittest.TestCase):
 class TestIntegration(unittest.TestCase):
 
     def test_sample(self):
-        n = 10
+        n = 4
         mean = 1000.
-        delta = 1.
+        delta = 100.
         k_max = 2
         x_dense = np.arange(0.001, 2, 0.0001)
         x, n_tuple, delta_tuple = sph_bessel.sample_jnjn(n, mean, delta, k_max)
-        print np.diff(x)
-        print n_tuple, delta_tuple
-        approx = sph_bessel.approx_jnjn(n, mean, delta, x)
-        right_ans = sph_bessel.jnjn(n, mean, delta, x)
-        right_ans_d = sph_bessel.jnjn(n, mean, delta, x_dense)
-        approx_d = sph_bessel.approx_jnjn(n, mean, delta, x_dense)
+        #print np.diff(x)
+        #print n_tuple, delta_tuple
+        #approx = sph_bessel.approx_jnjn(n, mean, delta, x)
+        #right_ans = sph_bessel.jnjn(n, mean, delta, x)
+        #right_ans_d = sph_bessel.jnjn(n, mean, delta, x_dense)
+        #approx_d = sph_bessel.approx_jnjn(n, mean, delta, x_dense)
         #ra_s = np.cumsum(right_ans[::-1])
         #a_s = np.cumsum(approx[::-1])
-        plt.figure()
-        plt.plot(mean * x_dense, right_ans_d)
-        plt.plot(mean * x_dense, approx_d)
-        plt.plot(mean * x, right_ans, '.')
+        #plt.figure()
+        #plt.plot(mean * x_dense, right_ans_d)
+        #plt.plot(mean * x_dense, approx_d)
+        #plt.plot(mean * x, right_ans, '.')
         #plt.figure()
         #plt.plot(mean * x[::-1], ra_s)
         #plt.plot(mean * x[::-1], a_s)
-        plt.show()
+        #plt.show()
+
+    def test_integrate(self):
[…]

### 2015-03-25 writeup/dm_space_distortions.tex
Plotter made

@@
 things much easier.
-\begin{equation}
+\begin{align}
 C^{dd}_\ell(\chi,\chi')
-    =
+&=
     \frac{2}{\pi}
@@
     P_{ee}(k, \bar\chi')
-\end{equation}
+    \\
+    &\approx
+    \frac{4}{\pi}
+    \int_0^{\chi_m}\ud\bar\chi'
+    \int_{0}^{\infty}\ud\Delta'
+    \int_0^\infty\ud k k^2 j_\ell(k(\bar\chi' - \Delta'/2))
+    j_{\ell}(k(\bar\chi' + \Delta'/2))
+    P_{ee}(k, \bar\chi')
+\end{align}
 At this point we could again to the transformation to $C_{\ell\chi\chi'}$
@@
 C^{dx}_\ell(\chi,\chi')
-    =
-    \frac{2}{\pi}
-    \int_0^\chi\ud\chi''
-    \int_0^\infty\ud k k^2 
-    j_\ell(k\chi') j_{\ell}(k\chi'')P_{ex}(k, (\chi' + \chi'')/2)
-\end{equation}
-\begin{equation}
-    C^{dx}_\ell(\chi,\chi') + C^{xd}_\ell(\chi,\chi')
     =
@@
     \int_{-\chi'}^{\chi - \chi'}\ud\Delta'
-    \int_0^\infty\ud k k^2 j_\ell(k(\chi'-\Delta/2))
+    \int_0^\infty\ud k k^2 j_\ell(k(\chi'-\Delta'/2))
     j_{\ell}(k(\chi'+\Delta'/2))
@@
     \int_{-\chi}^{\chi' - \chi}\ud\Delta'
-    \int_0^\infty\ud k k^2 j_\ell(k(\chi-\Delta/2))
+    \int_0^\infty\ud k k^2 j_\ell(k(\chi-\Delta'/2))
     j_{\ell}(k(\chi+\Delta'/2))
-    P_{ex}(k, \chi)
+    P_{ex}(k, \chi)\\
+    \approx&
+    \frac{4}{\pi}
+    \int_{0}^{\infty}\ud\Delta'
+    \int_0^\infty\ud k k^2 j_\ell(k(\chi_m-\Delta'/2))
+    j_{\ell}(k(\chi_m+\Delta'/2))
+    P_{ex}(k, \chi_m)
 \end{align}
@@
 integral. Also the expressions are very weak functions of $\chi$ and thus
-may be shifted by $\Delta/2$ without incurring much error.
+may be shifted by $\Delta/2$ without incurring much error. The third line
+exploits the fact that only one term contributes if $\chi$ and $\chi'$ are
+widely separated, and if they are close then the two terms combine to the given
+expression.
+
+\red{Actually, with the approximations we've made, we can actually do the
+$\Delta$ integrals analytically by transferring all the $\Delta$ to a single
+Bessel and shifting the power spectrum to be independent of $\Delta$.  Should
+be pretty good for $\ell > 10$.  That is nice because it will control all our
+numerical issues with oscillating Bessel functions.}
 

### 2015-03-25 python/angular_terms.py

@@ -1,0 +1,128 @@
+"""Computes the variouse integrals, each of which is a term in the angular
+PS."""
+
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy import integrate, interpolate
+
+import sph_bessel
+import matter_power
+
+
+
+class SingleEll(object):
+
+    def __init__(self, ell, chi_max):
+        ell = int(ell)
+        chi_max = float(chi_max)
+        self._ell = ell
+        self._chi_max = chi_max
+
+        nchi = 20
+        #chi_list = np.linspace(0, chi_max, nchi, endpoint=True)
+        delta_chi = chi_max / nchi
+        chi_list = np.arange(1, nchi + 1, dtype=float) / nchi * chi_max
+
+        data = []
+
+        n_total = 0
+        for chi in chi_list:
+            this_chi_data = {}
+            p_k_interp = matter_power.p_k_interp(chi)
+            # Put in Gaussian cut-off to control oscillations.
+            # XXX Move this to sph_bessel... obviously.
+            #p_k = lambda k: (np.exp(-k**2 / (2 * (matter_power.K_MAX / 4)**2)) * k**2
+            #                 * p_k_interp(k))
+            p_k = lambda k: k**2 * p_k_interp(k)
+
+            scale = ell / chi
+            nscales = min(5, 2 * ell - 1)
+            # These deltas for the integral.
+            deltas, delta_u = exp_sample(scale, nscales)
+            ndelta_int = len(deltas)
+            # Extra deltas for interpolation.
+            delta_max = min(1.99 * chi, 1.99 * (chi_max - chi))
+            factor = 1.5
+            deltas = list(deltas)
+            while factor * deltas[-1] < delta_max:
+                deltas.append(factor * deltas[-1])
+            deltas.append(delta_max)
+            deltas = np.array(deltas)
+
+            n_total += len(deltas)
+            I1 = np.empty_like(deltas)
+            for ii in range(len(deltas)):
+                I1[ii] = sph_bessel.integrate_f_jnjn(p_k, ell, chi_max, deltas[ii],
+                        matter_power.K_MAX) * (2 / np.pi)
+            I2 = integrate.romb(I1[:ndelta_int] * np.exp(scale * deltas[:ndelta_int]),
+                                dx=delta_u) * 2
+
[…]

### 2015-03-25 python/assemble_terms.py

@@ -1,0 +1,132 @@
+import numpy as np
+
+from scipy import special, integrate, interpolate
+from cora.util.cosmology import Cosmology
+import matplotlib.pyplot as plt
+import matplotlib
+
+import matter_power
+import angular_terms
+
+# Redshift at which we can detect event of luminocity L*.
+Z_STAR = 0.8
+ALPHA = -0.7
+
+B_E = 1.5
+B_F = 0.75
+
+
+def d_ln_n(chi):
+    """Not vecotized"""
+
+    delta_chi = 0.01 * chi
+    n = n_chi(np.array([chi, chi + delta_chi]))
+
+    d_ln_n_d_chi = (n[1] - n[0]) / delta_chi / n[0]
+    #print n
+    #print d_ln_n_d_chi
+
+    #plt.plot(redshifts, n*chi_s**2)
+    #plt.figure()
+    #plt.plot(redshifts, n)
+
+    # Finite difference derivative and normalize.
+    return d_ln_n_d_chi
+
+
+def n_chi(chi):
+    """Vectorized."""
+    # Invert the distance redshift relation by interpolating.
+    c = Cosmology()
+    redshifts_s = np.linspace(0.01, 3, 50)
+    chi_s = c.comoving_distance(redshifts_s)
+    redshift_interp = interpolate.interp1d(chi_s, redshifts_s, kind='cubic')
+    redshifts = redshift_interp(chi)
+
+    # Calculate the source density at both redshifts.
+    dL = c.luminosity_distance(redshifts)
+    dL_star = c.luminosity_distance(Z_STAR)
+    # Minimum detectable L/L*
+    x_min = (dL / dL_star)**2
+    # Get source density by integrating the luminocity function.
+    n = []
+    dndL_fun = lambda x : x**ALPHA * np.exp(-x)
+    for x_m in x_min:
+        this_n, err = integrate.quad(dndL_fun, x_m, np.inf)
+        n.append(this_n)
+    n = np.array(n)
+    return n
+
+
+def apply_coeffs(mult_ell, chi, delta):
+
+    coeff = d_ln_n(chi) + 2./chi
+    i1, i2, i3 = mult_ell.get_integrals(chi, delta)
+    t1 = (B_F - B_E)**2 * i1
+    t2 = (B_F - B_E) * B_E * coeff * i2
[…]

### 2015-03-25 python/matter_power.py

@@ -9,6 +9,7 @@ from cora.util.cosmology import Cosmology
 DATA_DIR = path.join(path.dirname(__file__), 'data')
 FILE_PAT = "Pk_z%3.1f.dat"
 REDSHIFTS = np.arange(0, 2.001, 0.2)
+K_MAX = 2.
 
 # k values are the same for all redshifts.
 K = np.loadtxt(path.join(DATA_DIR, FILE_PAT % REDSHIFTS[0]))[:,0]
@@ -21,3 +22,15 @@ def interpolator():
     chi = c.comoving_distance(REDSHIFTS)
     interpolator = interpolate.interp2d(K, chi, DATA, kind='cubic')
     return interpolator
+
+
+INTERPOLATOR = interpolator()
+
+def p_k_chi_interp():
+    return INTERPOLATOR
+
+
+def p_k_interp(chi):
+    i = INTERPOLATOR
+    data = i(K, chi)
+    return interpolate.interp1d(K, data, kind='cubic')

### 2015-03-25 python/sph_bessel.py

@@ -32,10 +32,14 @@ def approx_jnjn(n, mean, delta, x):
     a = mean - delta/2
     b = mean + delta/2
     nu = n + 1./2
-    t = np.sqrt(mean**2 * x**2 - nu**2)
-    arg = (mean * delta) * (x**2 / t)
-    arg += (delta**2 / 2) * (x**2 / t)
-    arg -= (mean**2 * delta**2 / 2) * (x**4 / t**3)
+    # The following is the tailor expantion of around delta. Not accurate
+    # enough.
+    #t = np.sqrt(mean**2 * x**2 - nu**2)
+    #arg = (mean * delta) * (x**2 / t)
+    #arg += (delta**2 / 2) * (x**2 / t)
+    #arg -= (mean**2 * delta**2 / 2) * (x**4 / t**3)
+    arg = np.sqrt((b*x)**2 - nu**2)
+    arg -= np.sqrt((a*x)**2 - nu**2)
     arg -= np.arccos(nu / b / x) * nu
     arg += np.arccos(nu / a / x) * nu
     out = (1./2) * np.cos(arg)
@@ -61,21 +65,25 @@ def sample_jnjn(n, mean, delta, x_max):
     adelta = abs(delta)
     if adelta <= mean * 1e-6:
         adelta = mean * 1e-6
-    umean = mean + delta / 2
-    lmean = mean - delta / 2
+    umean = mean + adelta / 2
+    lmean = mean - adelta / 2
     # Figure out total number of samples:
-    bound_lower = max((n - 1.5 * math.sqrt(n)) / umean, 0)
+    bound_lower = max((n - 2 * math.sqrt(n)) / umean, 0)
     #bound_middle = n / mean
-    bound_upper = max(n + 3 * math.sqrt(n), n + 30) / lmean
+    bound_upper = max(n + 15 * math.sqrt(n), n + 40) / lmean
     if bound_upper >= x_max:
         bound_upper = x_max
         nparts_upper = 0
         delta_upper = 0
+        if bound_lower > x_max:
+            bound_lower = x_max - 1. / umean
     else:
-        nparts_upper = max(pow_2_gt(1 * (x_max - bound_upper) * adelta), 128)
+        nparts_upper = max(pow_2_gt(4. * (x_max - bound_upper) * adelta), 128)
         delta_upper = (x_max - bound_upper) / nparts_upper
     
-    nparts_lower = pow_2_gt(2. * (bound_upper - bound_lower) * mean)
+    #print bound_upper, bound_lower, x_max
[…]

### 2015-03-25 python/tests/test_angular_terms.py

@@ -1,0 +1,30 @@
+import unittest
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+import angular_terms
+
+class TestSingleEll(unittest.TestCase):
+
+    def test_init(self):
+        pass
+        s = angular_terms.SingleEll(80, 3000)
+        delta = np.arange(0.1, 1800, 5)
+        plt.loglog(delta, abs(s.i1(2000, delta)))
+        plt.show()
+
+
+class TestMultiEll(unittest.TestCase):
+
+    def test_init(self):
+        pass
+        #ells = np.arange(10, 800, 10)
+        #at = angular_terms.MultiEll(ells, 3000)
+        #plt.show()
+
+
+
+#s = angular_terms.SingleEll(200, 1000)
+if __name__ == "__main__":
+    unittest.main()

### 2015-03-25 python/tests/test_sph_bessel.py

@@ -9,6 +9,7 @@ import sph_bessel
 
 camb_dat = np.loadtxt("data/Pk_z0.0.dat")
 matter_power = interpolate.interp1d(camb_dat[:,0], camb_dat[:,1])
+matter_power_k2 = lambda k: matter_power(k) * k**2
 k_camb = camb_dat[1:-1,0].copy()
 
 
@@ -81,14 +82,14 @@ class TestIntegration(unittest.TestCase):
     def test_integrate(self):
         n_l = [2**i for i in range(12)]
         mean = 1000.
-        delta_l = [0., 1., 10., 100., 300.]
+        delta_l = [0., 1., 10., 20, 50, 100., 300., 600, 1200, 1980]
         k_max = 2
         for n in n_l:
             first = True
             for delta in delta_l:
-                I = sph_bessel.integrate_f_jnjn(matter_power, n, mean, delta,
+                I = sph_bessel.integrate_f_jnjn(matter_power_k2, n, mean, delta,
                         k_max)
-                I2 = sph_bessel.integrate_f_jnjn_brute(matter_power, n, mean,
+                I2 = sph_bessel.integrate_f_jnjn_brute(matter_power_k2, n, mean,
                         delta, k_max)
                 if first:
                     atol = I2 * 0.05

### 2015-03-25 python/assemble_terms.py
refined plot maker.

@@ -95,17 +95,18 @@ def get_mult_ell(ells=None):
 
 
 def my_plots(mult_ell):
-    matplotlib.rcParams.update({'font.size': 14})
+    matplotlib.rcParams.update({'font.size': 14,
+                                'text.usetex' : False,
+                                'figure.autolayout': True})
     CHI = 2000.
     DELTAS = [5., 20., 50.]
     Y_MIN = 1e-7
-    Y_MAX = 2e-5
+    Y_MAX = 4e-5
     X_MIN = 9
     X_MAX = 1001
     
     kwargs = {
             "linewidth" : 2.,
-
              }
 
     title = "$\\bar\\chi=%d\\,\\rm{MPc}/h$, $\\Delta\\chi=%d\\,\\rm{MPc}/h$"
@@ -116,15 +117,26 @@ def my_plots(mult_ell):
         plt.ylim([Y_MIN, Y_MAX])
         plt.xlim([X_MIN, X_MAX])
         plt.title(title % (CHI, delta))
-        plt.xlabel(r"$\ell$")
-        plt.ylabel(r"$C^{ss}_\ell(\chi,\chi')$")
+        plt.xlabel(r"$\ell$",
+                   fontsize=18,
+                   )
+        plt.ylabel(r"$C^{ss}_\ell(\chi,\chi')$",
+                   fontsize=18,
+                   )
         plt.legend(loc="lower left", labelspacing=.1, frameon=False)
 
-    chi_s = np.linspace(100, 3600, 50)
+    chi_s = np.linspace(500, 3500, 50)
     coef_s = np.array([  d_ln_n(chi) + 2./chi for chi in chi_s ])
 
     plt.figure()
-    plt.plot(chi_s, coef_s)
+    plt.plot(chi_s, coef_s, **kwargs)
+    plt.xlabel(r"$\chi$ ($\rm{MPc}/h$)",
+               fontsize=18,
+               )
+    plt.ylabel(r"$(\frac{1}{\bar{n}_f}\frac{d \bar{n}_f}{d \chi}"
+               r"+ \frac{2}{\chi})$  ($h/\rm{MPc})$",
+               fontsize=18,
+               )
     
 
 

### 2015-04-01 writeup/dm_space_distortions.tex
Cleaned up limber.

@@
 
+Assembling terms:
+\begin{align}
+C^{ss}_\ell(\chi,\chi') = &
+    \frac{2}{\pi}
+    \int_0^\infty\ud k k^2
+    j_\ell(k\chi) j_{\ell}(k\chi')
+    \left[ P_{ff}(k, \bar\chi)
+    + P_{ee}(k, \bar\chi)
+    - 2P_{fe}(k, \bar\chi) \right]
+    \nonumber\\
+    & +
+    \frac{2}{\pi}
+    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi}
+    + \frac{2}{\chi} \right)
+    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi'}
+    + \frac{2}{\chi'} \right)
+    \int_0^\chi\ud\chi''
+    \int_0^{\chi'}\ud\chi'''
+    \int_0^\infty\ud k k^2 j_\ell(k\chi'') j_{\ell}(k\chi''')
+    P_{ee}(k, (\chi''+\chi''')/2)
+    \nonumber\\
+    & +
+    \frac{2}{\pi}
+    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi}
+    + \frac{2}{\chi} \right)
+    \int_0^\chi\ud\chi''
+    \int_0^\infty\ud k k^2 
+    j_\ell(k\chi') j_{\ell}(k\chi'')
+    \left[ P_{ee}(k, (\chi' + \chi'')/2)
+    - P_{fe}(k, (\chi' + \chi'')/2) \right]
+    \nonumber\\
+    & +
+    \frac{2}{\pi}
+    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi'}
+    + \frac{2}{\chi'} \right)
+    \int_0^{\chi'}\ud\chi''
+    \int_0^\infty\ud k k^2 
+    j_\ell(k\chi) j_{\ell}(k\chi'')
+    \left[ P_{ee}(k, (\chi + \chi'')/2)
+    - P_{fe}(k, (\chi + \chi'')/2) \right]
+\end{align}
+
 \section{Small angles and Limber}
@@
         \\
-    &= gg'aa'
+    &\approx
         \int\ud^2\vec\theta\ud^2\vec\theta'
@@
         \int\frac{\ud^3\vec k}{(2 \pi)^3} 
-        e^{i\vec k \cdot (\vec x - \vec x')} P(k, 0)
+        e^{i\vec k \cdot (\vec x - \vec x')} P(k, \bar\chi)
         \\
-    &= gg'aa'
+    &=
         \int\frac{\ud^3\vec k}{(2 \pi)^3} 
-        e^{i k_\parallel (\chi - \chi')} P(k, 0)
+        e^{i k_\parallel (\chi - \chi')} P(k, \bar\chi)
         \int\ud^2\vec\theta e^{-i(\vec\ell-\bar\chi\vec k_\bot)\cdot\vec\theta}
@@
         \\
-    &= gg'aa'
+    &=
         \int\frac{\ud^3\vec k}{(2 \pi)^3} 
-        e^{i k_\parallel (\chi - \chi')} P(\sqrt{k_\parallel^2 + k_\bot^2}, 0)
+        e^{i k_\parallel (\chi - \chi')} P(\sqrt{k_\parallel^2 + k_\bot^2}, \bar\chi)
         (2\pi)^4 \delta^2(\vec\ell - \bar\chi \vec k_\bot)
@@
         \\
-    &= gg'aa'
+    &=
         \int_{-\infty}^\infty\frac{\ud k_\parallel}{(2 \pi)} 
         e^{i k_\parallel (\chi - \chi')}
-        P(\sqrt{k_\parallel^2 + \ell^2/\bar\chi^2}, 0)
+        P(\sqrt{k_\parallel^2 + \ell^2/\bar\chi^2}, \bar\chi)
         \frac{(2\pi)^2\delta^2(\vec\ell' - \vec \ell)}{\bar\chi^2}
@@
 C_\ell(\chi, \chi')
-    &= \frac{gg'aa'}{\bar\chi^2}
+    &= \frac{1}{\bar\chi^2}
         \int_{-\infty}^\infty\frac{\ud k_\parallel}{(2 \pi)} 
         e^{i k_\parallel (\chi - \chi')}
-        P(\sqrt{k_\parallel^2 + \ell^2/\bar\chi^2}, 0)
+        P(\sqrt{k_\parallel^2 + \ell^2/\bar\chi^2}, \bar\chi)
 \end{align}
@@
     &=
-    \int_0^\chi\ud\chi''g''a''
-    \int_0^{\chi'}\ud\chi'''g'''a'''
-    \frac{1}{\bar\chi^2}
+    \int_0^\chi\ud\chi''
+    \int_0^{\chi'}\ud\chi'''
+    \frac{1}{\bar\chi^{\prime 2}}
     \int_{-\infty}^\infty\frac{\ud k_\parallel}{(2 \pi)} 
     e^{i k_\parallel (\chi'' - \chi''')}
-    P_{ee}(\sqrt{k_\parallel^2 + \ell^2/\bar\chi^2}, 0)
+    P_{ee}(\sqrt{k_\parallel^2 + \ell^2/\bar\chi^2}, (\chi'' + \chi''')/2)
     \\
     &\approx
-    \int_0^\chi\ud\chi''g''a''
-    \int_0^{\chi'}\ud\chi'''g'''a'''
-    \frac{1}{\bar\chi^2}
+    \int_0^\chi\ud\chi''
+    \int_0^{\chi'}\ud\chi'''
+    \frac{1}{\bar\chi^{\prime 2}}
     \int_{-\infty}^\infty\frac{\ud k_\parallel}{(2 \pi)} 
     e^{i k_\parallel (\chi'' - \chi''')}
-    P_{ee}(\ell/\bar\chi, 0)
+    P_{ee}(\ell/\bar\chi', (\chi'' + \chi''')/2)
     \\
     &=
-    \int_0^\chi\ud\chi''g''a''
-    \int_0^{\chi'}\ud\chi'''g'''a'''
-    \frac{1}{\bar\chi^2}
+    \int_0^\chi\ud\chi''
+    \int_0^{\chi'}\ud\chi'''
+    \frac{1}{\bar\chi^{\prime 2}}
     \delta(\chi'' - \chi''')
-    P_{ee}(\ell/\bar\chi, 0)
+    P_{ee}(\ell/\bar\chi', (\chi'' + \chi''')/2)
     \\
@@
     \int_0^{\min(\chi,\chi')}\ud\chi''
-    \left(\frac{g''a''}{\chi''}\right)^2
-    P_{ee}(\ell/\chi'', 0)
+    \left(\frac{1}{\chi''}\right)^2
+    P_{ee}(\ell/\chi'', \chi'')
 \end{align}
-\red{Double check the $\min$.}
 where the second line applies Limber's approximation. 
+$\bar\chi' \equiv (\chi'' + \chi''')/2$.
 
@@
     &=
-    g'a'
-    \int_0^\chi\ud\chi''g''a''
-    \frac{1}{\bar\chi^2}
+    \int_0^\chi\ud\chi''
+    \frac{1}{\bar\chi^{\prime 2}}
     \delta(\chi'' - \chi')
-    P_{ex}(\ell/\bar\chi, 0)
+    P_{ex}(\ell/{\bar\chi'}, (\chi'' + \chi')/2)
     \\
     &=
-    \left(\frac{g'a'}{\chi'}\right)^2
-    P_{ex}(\ell/\chi', 0)
+    \left(\frac{1}{\chi'}\right)^2
+    P_{ex}(\ell/\chi', \chi')
     \qquad \textrm{if $\chi' < \chi$ and 0 otherwise.}
-    \\
-C^{dx}_\ell(\chi,\chi') + C^{xd}_\ell(\chi,\chi')
-    &=
-    \left(\frac{g^ma^m}{\chi^m}\right)^2
-    P_{ex}(\ell/\chi^m, 0)
+%    \\
+%C^{dx}_\ell(\chi,\chi') + C^{xd}_\ell(\chi,\chi')
+%    &=
+%    \left(\frac{1}{\chi^m}\right)^2
+%    P_{ex}(\ell/\chi^m, \chi_m)
 \end{align}
@@
 \begin{align}
-C^{ss}_\ell(\chi_m,\Delta\chi) =&~
-    (b_f - b_e)^2 \left(\frac{g_m a_m}{\chi_m}\right)^2
+C^{ss}_\ell(\chi, \chi') =&~
+    \left(\frac{b_f - b_e }{\bar\chi}\right)^2
         \int_{-\infty}^\infty\frac{\ud k_\parallel}{(2 \pi)} 
         e^{i k_\parallel \Delta\chi}
-        P(\sqrt{k_\parallel^2 + \ell^2/\chi_m^2}, 0)
+        P(\sqrt{k_\parallel^2 + \ell^2/\bar\chi^2}, \bar\chi)
     \\ &+
-    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi}
-    + \frac{2}{\chi} \right)_{\chi_m}^2
+    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi_m}
+    + \frac{2}{\chi_m} \right)^2
     b_e^2 \int_0^{\chi_m}\ud\chi''
-        \left(\frac{g''a''}{\chi''}\right)^2
-        P(\ell/\chi'', 0)
+    \frac{1}{\chi^{\prime\prime 2}}
+        P(\ell/\chi'',\chi'')
     \\ &+
-    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi}
-    + \frac{2}{\chi} \right)_{\chi_m}
-    b_e(b_f - b_e)\left(\frac{g_m a_m}{\chi_m}\right)^2
-        P(\ell/\chi_m, 0)
+    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi_m}
+    + \frac{2}{\chi_m} \right)
+    \frac{b_e(b_f - b_e)}{\chi_m^2}
+        P(\ell/\chi_m, \chi_m)
 \end{align}
-
-%%%% SCRAP
-
-\begin{comment}
-\begin{align}
-w(\hat n \cdot \hat n', \chi, \chi') 
-    &= gg'aa'
-        \int\frac{\ud^3\vec k}{(2 \pi)^3} \frac{\ud^3\vec k'}{(2 \pi)^3}
-        e^{i\vec k \cdot \vec x} e^{i\vec k' \cdot \vec x'}
-        \langle \delta(\vec k, 0) \delta(\vec k', 0) \rangle\\
-    &= gg'aa'
-        \int\frac{\ud^3\vec k}{(2 \pi)^3} 
-        e^{i\vec k \cdot (\vec x - \vec x')} P(k, 0)\\
-    &= gg'aa'
-        \int\frac{\ud^3\vec k}{(2 \pi)^3} 
-        e^{i\vec k \cdot (\vec x - \vec x')} P(k)\\
-    &= gg'aa'
-        \int\frac{k^2 \sin(\theta_k) \ud k \ud \theta_k \ud \phi_k}{(2 \pi)^3} 
-        e^{i k |\vec x - \vec x'| \cos\theta_k} P(k, 0)\\
-    &= gg'aa'
-        \int_0^\infty\frac{\ud k}{2 \pi^2} k^2
-        \frac{\sin(k |\vec x - \vec x'|)}{k |\vec x - \vec x'|} P(k, 0)\\
-    &= gg'aa'
-        \int_0^\infty\frac{\ud k}{2 \pi^2} k^2
-        j_0 (k \sqrt{\chi^2 + \chi'^{^2} - \chi \chi' \hat n \cdot \hat n'})
-        P(k, 0)
-\end{align}
-Somehow when I integrate this against a Legendre polynomial, $P_\ell(\mu)$,
-to get $C_\ell$
-I'm going to get Bessel functions. Lets assume that works (Kris, how does this
-work?) to get:
-\begin{equation}
-    C_{\ell\chi\chi'} = \frac{2 gg'aa'}{\pi}
-    \int_0^\infty\ud k k^2 j_\ell(k \chi) j_\ell(k \chi')
-        P(k, 0)
-\end{equation}
-\end{comment}
-
-\begin{comment}
-\begin{align}
-    w^{dd}(\hat n \cdot \hat n', \chi, \chi')
-    &= \int_0^\chi \ud \chi'' \int_0^{\chi'} \ud \chi'''
-         \langle \delta_e(\hat n \chi'') \delta_e(\hat n' \chi''') \rangle\\
-    &= b_e^2\int_0^\chi \ud \chi'' \int_0^{\chi'} \ud \chi'''
-        g''g'''a''a'''
-        \int\frac{\ud^3\vec k}{(2 \pi)^3} \frac{\ud^3\vec k'}{(2 \pi)^3}
-        e^{i\vec k \cdot \vec x''} e^{i\vec k' \cdot \vec x'''}
-        \langle \delta(\vec k, 0) \delta(\vec k', 0) \rangle\\
-    &= b_e^2\int_0^\chi \ud \chi'' \int_0^{\chi'} \ud \chi'''
-        g''g'''a''a'''
-        \int_0^\infty\frac{\ud k}{2 \pi^2} k^2
-        j_0 (k \sqrt{\chi''^2 + \chi'''^{^2} - \chi'' \chi''' \hat n \cdot \hat n'})
-        P(k, 0)
-\end{align}
-
-Alternately, we can make the limber approximation (replacing
-$a(\chi'')g(\chi'')$ and $a(\chi''')g(\chi''')$ with 
-$a(\bar \chi)g(\bar \chi)$) and small angle approximations
-(replacing the argument of the spherical Bessel with
-$k\sqrt{\Delta \chi^2 + (\bar \chi (\hat n - \hat n'))^2}$).
-\begin{align}
-    w^{dd}(\hat n \cdot \hat n', \chi, \chi')
-    &= b_e^2\int_0^\chi \ud \chi'' \int_0^{\chi'} \ud \chi'''
-        (g(\bar \chi) a(\bar \chi))^2
-        \int_0^\infty\frac{\ud k}{2 \pi^2} k^2
-        j_0 (k \sqrt{\Delta \chi^2 + (\bar \chi (\hat n - \hat n'))^2})
-        P(k, 0)\\
-    &= b_e^2\int_0^{(\chi + \chi')/2} \ud \bar\chi 
-        (g(\bar \chi) a(\bar \chi))^2
-        \int_0^\infty\frac{\ud k}{2 \pi^2} k^2
-        P(k, 0)
-        \int_{-\infty}^{\infty} \ud \Delta\chi
-        j_0 (k \sqrt{\Delta \chi^2 + (\bar \chi (\hat n - \hat n'))^2})\\
-\end{align}
-
-\end{comment}
+where $\chi_m \equiv \min(\chi, \chi')$.
 

### 2015-04-01 python/assemble_terms.py

@@ -12,8 +12,8 @@ import angular_terms
 Z_STAR = 0.8
 ALPHA = -0.7
 
-B_E = 1.5
-B_F = 0.75
+B_E = 0.9
+B_F = 1.3
 
 
 def d_ln_n(chi):
@@ -98,10 +98,10 @@ def my_plots(mult_ell):
     matplotlib.rcParams.update({'font.size': 14,
                                 'text.usetex' : False,
                                 'figure.autolayout': True})
-    CHI = 2000.
-    DELTAS = [5., 20., 50.]
-    Y_MIN = 1e-7
-    Y_MAX = 4e-5
+    CHI = 1000.
+    DELTAS = [5., 20., 50., 100.]
+    Y_MIN = 4e-8
+    Y_MAX = 1e-5
     X_MIN = 9
     X_MAX = 1001
     
@@ -125,7 +125,7 @@ def my_plots(mult_ell):
                    )
         plt.legend(loc="lower left", labelspacing=.1, frameon=False)
 
-    chi_s = np.linspace(500, 3500, 50)
+    chi_s = np.linspace(100, 3500, 50)
     coef_s = np.array([  d_ln_n(chi) + 2./chi for chi in chi_s ])
 
     plt.figure()
@@ -135,6 +135,15 @@ def my_plots(mult_ell):
                )
     plt.ylabel(r"$(\frac{1}{\bar{n}_f}\frac{d \bar{n}_f}{d \chi}"
                r"+ \frac{2}{\chi})$  ($h/\rm{MPc})$",
+               fontsize=18,
+               )
+
+    plt.figure()
+    plt.plot(chi_s, chi_s**2 * n_chi(chi_s), **kwargs)
+    plt.xlabel(r"$\chi$ ($\rm{MPc}/h$)",
+               fontsize=18,
+               )
+    plt.ylabel(r"$\chi^2\bar{n}_f$  ($h/\rm{MPc})$",
                fontsize=18,
                )
     

### 2015-04-01 python/angular_terms.py
Developing limber I1.

@@ -3,7 +3,7 @@ PS."""
 
 import numpy as np
 import matplotlib.pyplot as plt
-from scipy import integrate, interpolate
+from scipy import integrate, interpolate, fftpack, signal
 
 import sph_bessel
 import matter_power
@@ -83,6 +83,60 @@ class SingleEll(object):
         self.i2 = interpolate.interp1d(chi_list, I2[1:], kind="cubic")
         self.i3 = interpolate.interp1d(chi_list, I3, kind="cubic")
         self.data = data
+
+
+
+class SingleEllLimber(object):
+
+    def __init__(self, ell, chi_max):
+        
+        ell = int(ell)
+        chi_max = float(chi_max)
+        self._ell = ell
+        self._chi_max = chi_max
+        
+        # XXX
+        nchi = 1
+        #chi_list = np.linspace(0, chi_max, nchi, endpoint=True)
+        delta_chi = chi_max / nchi
+        chi_list = np.arange(1, nchi + 1, dtype=float) / nchi * chi_max
+
+        data = []
+
+        n_total = 0
+        for chi in chi_list:
+            # Matter power at this redshift.
+            p_k_interp = matter_power.p_k_interp(chi)
+
+            # Local term.
+            delta_k = 2 * np.pi / (2 * chi)
+            k_max = 2.
+            k = np.arange(0, k_max, delta_k)
+            k = np.concatenate((k, -k[:0:-1]))
+            nk = len(k)   # Guaranteed to be odd.
+            #print k
+            p_k_local = p_k_interp(np.sqrt((ell/chi)**2 + k**2))
+            #plt.semilogy(k, p_k_local, '.')
+            window = fftpack.ifftshift(signal.kaiser(nk, beta=14, sym=True))
+            #window = fftpack.ifftshift(signal.gaussian(nk, std=0.5/delta_k, sym=True))
+            #plt.figure(1)
+            #plt.loglog(k, p_k_local)
+            #plt.loglog(k, p_k_local * window)
+            p_k_local *= window
+            #nk1 = nk//2
+            #zeros = np.zeros(nk1)
+            #plt.figure(4)
+            #plt.plot(p_k_local)
+            #p_k_local = np.concatenate((p_k_local[:nk1 + 1], zeros, zeros,
+            #    p_k_local[nk1 + 1:]))
+            #plt.figure(3)
+            #plt.plot(p_k_local)
[…]

### 2015-04-01 python/tests/test_angular_terms.py

@@ -9,9 +9,13 @@ class TestSingleEll(unittest.TestCase):
 
     def test_init(self):
         pass
-        s = angular_terms.SingleEll(80, 3000)
-        delta = np.arange(0.1, 1800, 5)
-        plt.loglog(delta, abs(s.i1(2000, delta)))
+        #s = angular_terms.SingleEll(80, 3000)
+        #delta = np.arange(0.1, 1800, 5)
+        #plt.loglog(delta, abs(s.i1(2000, delta)))
+        #plt.show()
+
+    def test_limber(self):
+        s = angular_terms.SingleEllLimber(80, 3000)
         plt.show()
 
 

### 2015-04-01 python/angular_terms.py
Developing limber I1.

@@ -12,7 +12,7 @@ import matter_power
 
 class SingleEll(object):
 
-    def __init__(self, ell, chi_max):
+    def __init__(self, ell, chi_max, limber=False):
         ell = int(ell)
         chi_max = float(chi_max)
         self._ell = ell
@@ -30,32 +30,33 @@ class SingleEll(object):
             this_chi_data = {}
             p_k_interp = matter_power.p_k_interp(chi)
             # Put in Gaussian cut-off to control oscillations.
-            # XXX Move this to sph_bessel... obviously.
-            #p_k = lambda k: (np.exp(-k**2 / (2 * (matter_power.K_MAX / 4)**2)) * k**2
-            #                 * p_k_interp(k))
-            p_k = lambda k: k**2 * p_k_interp(k)
 
-            scale = ell / chi
-            nscales = min(5, 2 * ell - 1)
-            # These deltas for the integral.
-            deltas, delta_u = exp_sample(scale, nscales)
-            ndelta_int = len(deltas)
-            # Extra deltas for interpolation.
-            delta_max = min(1.99 * chi, 1.99 * (chi_max - chi))
-            factor = 1.5
-            deltas = list(deltas)
-            while factor * deltas[-1] < delta_max:
-                deltas.append(factor * deltas[-1])
-            deltas.append(delta_max)
-            deltas = np.array(deltas)
+            if limber:
+                pass
+            else:
+                p_k = lambda k: k**2 * p_k_interp(k)
 
-            n_total += len(deltas)
-            I1 = np.empty_like(deltas)
-            for ii in range(len(deltas)):
-                I1[ii] = sph_bessel.integrate_f_jnjn(p_k, ell, chi_max, deltas[ii],
-                        matter_power.K_MAX) * (2 / np.pi)
-            I2 = integrate.romb(I1[:ndelta_int] * np.exp(scale * deltas[:ndelta_int]),
-                                dx=delta_u) * 2
+                scale = ell / chi
+                nscales = min(5, 2 * ell - 1)
+                # These deltas for the integral.
+                deltas, delta_u = exp_sample(scale, nscales)
+                ndelta_int = len(deltas)
+                # Extra deltas for interpolation.
+                delta_max = min(1.99 * chi, 1.99 * (chi_max - chi))
+                factor = 1.5
+                deltas = list(deltas)
[…]

### 2015-04-23 writeup/dm_space_distortions.tex
Starting to clean up paper.

@@
-\documentclass[onecolumn,prd,nofootinbib]{revtex4-1}
+\documentclass[twocolumn,prl,nofootinbib]{revtex4-1}
 \usepackage{graphicx}
@@
 \usepackage{verbatim}
+\usepackage{times}
 
@@
 
-\title{The large scale clustering of fast radio bursts in dispersion measure space}
+\title{The large scale clustering in dispersion measure space}
 
@@
 
+    The recently discovered fast radio bursts are a new class of radio
+    transient that, due to thier high dispersion from interviening plasma,
+    have been interpreted as
+    origionating from cosmological distances.  The rate of fast radio bursts
+    has been estimated to be as high as 10\,000 per sky per day.  If
+    cosmological, these events should trace the large-scale structure of the
+    Universe in some way. Furthermore, because the disperion measure (DM) can be
+    used as a proxy for radial distance (like redshift),
+    clustering can be studied in three dimensions. Due to inhomogenaities in
+    the plasma's density dispersion measure is an imperfect proxy or radial
+    distance and we show that this leads to additional clustering terms---the
+    dispersion measure space distortions. We calculate the DM space
+    powerspectra for a toy model of electron and FRB clustering and show that
+    the clustering signal could be detected in a survey of \red{10000} FRB
+    events, as is expected to be produced by the Canadian Hydrogen Intensity
+    Mapping Experiment.
+
 \end{abstract}
@@
 
-\section{FRB density perturbations in DM space}
+\section{Introduction}
 
+\section{Density perturbations in dispersion measure space}
+
+The dispersion measure of a signal observed in some angular direction $\hat{n}$ and
+originating from comoving radial distance $\chi$ is
 \begin{equation}
-D(\hat n, \chi) = \int_0^\chi \frac{\ud\chi'}{a(\chi')}
-   \left[1 + \delta_e(\hat{n}\chi')\right]
+    {\rm DM}(\hat{n}, \chi) = \int_0^{\chi} \ud\chi' a(\chi)^2
+        n_e(\hat{n}\chi', \chi').
+\end{equation}
+Here
+$n_e(\vec{x}, \chi)$ is the free electron density as a function of location and
+conformal time. Note that we use $\chi$ as our radial distance and time
+coordinate, as opposed to redshift which is more approprite for spectroscopic
+applications. We model the cosmological 
+electron density as containing a homogenious part
+and perturbations
+$n_e(\vec x, \chi) = \bar{n}_e(\chi) \left[1 + \delta_e(\vec x, \chi)\right]$.  \red{We take
+all of the electrons to be in a diffuse ionized state such that
+$\bar{n}_e(\chi) = \bar{n}_{e0} / a(\chi)^3$ (not nessisary).} The dispersion
+measure is thus
+\begin{equation}
+    {\rm DM}(\hat n, \chi) = \int_0^\chi \ud\chi' a(\chi')^2 \bar{n}_e(\chi')
+       \left[1 + \delta_e(\hat{n}\chi',\chi')\right].
 \end{equation}
 
-This defines DM space:
+\emph{Dispersion measure space} is the three dimensional coordinates,
+$\vec x_s$ inferred from the dispersion measure assuming that the electrons are
+homogenious. This only affect the radial coordinate such that $\vec x_s = \hat
+n \chi_s$ with $\chi_s$ defined by the equation
 \begin{equation}
-D(\chi_s) = \int_0^{\chi_s}\frac{\ud\chi'}{a(\chi')}
+    {\rm DM}(\chi_s) = \int_0^\chi \ud\chi' a(\chi')^2 \bar{n}_e(\chi').
 \end{equation}
 
-Combining the above, we find that:
+Combining the above equations (keeping only terms first order in the density
+perturbations), we find that
 \begin{equation}
-\frac{\ud \chi_s}{\ud \chi} = (1 + \delta_e),
+\frac{\ud \chi_s}{\ud \chi} = (1 + \delta_e(\hat n \chi, \chi),
 \end{equation}
-and
+and thus
 \begin{equation}
@@
 
+We wish to relate the density of a tracer $f$ measured in DM space to its
+density in real space. We follow the derivation in \citet{Kaiser} of the
+redshift space distortions. Start by noting that the total number of tracers
+in a volume element is the same in both spaces:
 \begin{equation}
 \label{e:density}
-n_{fs}(\vec x_s) \ud^3\vec x_s = n_{f}(\vec x) \ud^3\vec x
+n_{fs}(\vec x_s) \ud^3\vec x_s = n_{f}(\vec x) \ud^3\vec x.
 \end{equation}
-
-Averaged over the sky, the galaxy density should be the same in DM 
-space as in real space.
+We split the density into a homogenious part plus perturbations,
 \begin{equation}
-\bar{n}_{fs}(\chi_s)\left[ 1 + \delta_f(\vec x_s)\right] \ud^3\vec x_s
-    = \bar{n}_{f}(\chi)\left[ 1 + \delta_f(\vec x)\right] \ud^3\vec x
+    \bar{n}_{fs}(\chi_s)\left[ 1 + \delta_{fs}(\vec x_s)\right] \ud^3\vec x_s
+    = \bar{n}_{f}(\chi)\left[ 1 + \delta_f(\vec x)\right] \ud^3\vec x.
 \end{equation}
-
+Averaged over the sky, the density should be the same in DM 
+space as in real space,
 \begin{equation}
-\bar{n}_{fs}(\chi) = \bar{n}_f(\chi)
+\bar{n}_{fs}(\chi) = \bar{n}_f(\chi).
 \end{equation}
@@
 
-The jacobian in spherical coordinates is:
+The jacobian in spherical coordinates is
 \begin{align}
@@
 \end{align}
-Following Kaiser, the third line follows since the
-second factor in parentheses on the second line, which is the
-average overdensity along the line of sight, is much
-closer to unity than the first due to cancellations.
 
 Substituting Equations~\ref{e:nfs}~and~\ref{e:jac} into Equation~\ref{e:density},
-we obtain:
+we obtain
 \begin{equation}
@@
     + \frac{2}{\chi} \right)
-        \int_0^\chi \ud \chi' \delta_e(\hat n \chi')
+        \int_0^\chi \ud \chi' \delta_e(\hat n \chi').
 \end{equation}
+In the equation above, the $-\delta_e$ term is most analogous to the Kaiser
+redshift space distortions.  It is a dillution of tracers in DM space due to an
+excess of electrons in between the tracers. However we note that this term is isotropic
+in cotrast to Kaiser.  This is because any wave vector electron perturbation
+causes DM space distortions, whereas the radial velocities that cause
+redshift space distortions are only sourced by perterbations with radial wave
+vectors.
+
+The $\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi}$ arise since the
+misinterpretation of the radial distance causes the observed tracer density to
+be compared to the wrong background density. The $\frac{2}{\chi}$ term is
+caused by a misinterpretation of angular distances when the radial distance is
+mismeasured.  Both term are in-prociple present in redshift space but are
+negligable. Because radial veolocities are only sourced by modes with large
+radial wave vector, there is near perfect cancelation along the line of sight
+and thus is very little net error in radial distance.
 
@@
 
-In this section all quantities are already first order in the perturbations so
-there is no need to distinguish between the DM space coordinates and the real
-space coordinates. The correction is higher order. Still need to distinguish
-between DM space and real space fields ($\delta_{fs} \neq \delta_f$, but
-$\delta_f(\vec x_s) \approx \delta_f(\vec x)$).
+Unlike in redshift-space distortions, Equation~\ref{e:delta_s} does not have a
+simple form in harmonic space. The equation's third term couples harmonic modes
+and thus the two-point statistics cannot be phrased as a simple power spectrum.
+We will phrase the two point statistic in terms of $C^{ss}_\ell(\chi,\chi')$, which is
+the cross-correlation angular power-spectrum of the DM space overdensity
+on shells at $\chi$ and $\chi'$.
+\begin{align}
+    &\delta_{\ell\ell'}\delta_{mm'}C^{ss}_\ell(\chi, \chi') = \nonumber \\
+    & \quad
+        \left\langle
+        \int\ud\Omega Y_{\ell m}(\hat n)
+       \delta_{fs}(\hat n \chi, \chi)
+        \int\ud\Omega' Y_{\ell' m'}(\hat n')
+        \delta_{fs}(\hat n' \chi', \chi')
+        \right\rangle
+\end{align}
+The first two term in Equation~\ref{e:delta_s} are stationary. For stationary,
+isotropic, tracers $x$ and $y$ we have 
+$\langle \delta_x(\vec k, \chi) \delta_y(\vec k', \chi) \rangle = (2\pi)^3
+\delta^3(\vec k - \vec k') P_{xy}(k, \chi)$.  If for a moment we ignore time
+dependance, the angular cross power spectrum of such tracers is
+\begin{align}
+    %\delta_{\ell\ell'}\delta_{mm'}C^{xy}_\ell(\chi, \chi')
+    %&= \int\ud\Omega\ud\Omega'Y_{\ell m}(\hat n) Y_{\ell' m'}(\hat n')
+    %    \langle \delta_x(\hat n \chi) \delta_y(\hat n' \chi') \rangle,
+    %    \\
+    C^{xy}_\ell(\chi,\chi')
+    &= \frac{2}{\pi}
+\int_0^\infty\ud k k^2 j_\ell(k\chi) j_{\ell}(k\chi')P_{xy}(k).
+\end{align}
+In reality the powerspectrum evolves on the order of a (conformal) Hubble time.
+The angular cross-correlations will be very small unless $\chi$ and $\chi'$ are
+within a few correlation lengths of one another, roughly a few hundred
+megaparsecs.  The evolution of the power-spectrum is negligable over these time
+differences which leads to a straight forward way to include the evolution of
+the perturbations:
+\begin{align}
+C^{xy}_\ell(\chi,\chi') 
+    \approx \frac{2}{\pi}
+    \int_0^\infty\ud k k^2
+    j_\ell(k\chi) j_{\ell}(k\chi')
+    P_{xy}(k,(\chi + \chi')/2),\nonumber &\\
+    |\chi - \chi'| \ll 1/aH.&
+\end{align}
 
-Unlike in redshift-space distortions, Equation~\ref{e:delta_s} does not have a
-simple form in harmonic space. The equations third term couples harmonic modes
-and thus the two-point statistic cannot be phrased as a simple power spectrum.
-We will phrase the two point statistic in terms of $C^{ss}_{\ell D D'}$, which is
-the cross-correlation angular power-spectrum of the DM space source overdensity
-on DM shells at $D$ and $D'$.
+The thrid term in Equation~\ref{e:delta_s} is not stationary but is an integral
+over the stationary field $\delta_e$.
+Define $\delta_d$ as
+\begin{equation}
+    \delta_d(\hat n \chi) \equiv \int_0^\chi \ud \chi' \delta_e(\hat n \chi').
+\end{equation}
+It is straight-forward to show that
+\begin{widetext}
+\begin{equation}
+C^{dd}_\ell(\chi,\chi')
+    =
+    \frac{2}{\pi}
+    \int_0^\chi\ud\chi''
+    \int_0^{\chi'}\ud\chi'''
+    \int_0^\infty\ud k k^2 j_\ell(k\chi'') j_{\ell}(k\chi''')
+    P_{ee}(k, (\chi''+\chi''')/2).
+\end{equation}
 
-Because the expression for the density perturbations in DM space involves an
-integral over the line of sight, which for far off sources may cover a
-significant amount of the Universe's expansion, it is necessary to explicitly
-account for light cone effects. This is most easily done in linear theory,
-where these effects are scale independent, a factorization that allows certain
-integral to be performed. In reality, non-linear growth causes both the bias
-and the growth factor to be scale and time dependant. As in weak lensing, this
-would need to be simulated.
+Finally, $C^{ss}_\ell$ will contain cross terms between the stationary terms
+and the integral terms.  These will have the form
+\begin{equation}
+C^{dx}_\ell(\chi,\chi')
+    =
+    \frac{2}{\pi}
+    \int_0^\chi\ud\chi''
+    \int_0^\infty\ud k k^2 
+    j_\ell(k\chi') j_{\ell}(k\chi'')P_{ex}(k, (\chi' + \chi'')/2).
+\end{equation}
+
+Assembling all these expressions with the proper coefficients we have
+\begin{align}
+    \label{e:Clss}
+C^{ss}_\ell(\chi,\chi') = &~
+    \frac{2}{\pi}
+    \int_0^\infty\ud k k^2
+    j_\ell(k\chi) j_{\ell}(k\chi')
+    P_{[ff + ee - 2ef]}(k, (\chi + \chi')/2)
+    %\left[
+    %P_{ff}(k, \bar\chi)
+    %+ P_{ee}(k, \bar\chi)
+    %- 2P_{fe}(k, \bar\chi)
+    %\right]
+    \nonumber\\
+    & +
+    \frac{2}{\pi}
+    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi}
+    + \frac{2}{\chi} \right)
+    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi'}
+    + \frac{2}{\chi'} \right)
+    \int_0^\chi\ud\chi''
+    \int_0^{\chi'}\ud\chi'''
+    \int_0^\infty\ud k k^2 j_\ell(k\chi'') j_{\ell}(k\chi''')
+    P_{ee}(k, (\chi''+\chi''')/2)
+    \nonumber\\
+    & +
+    \frac{2}{\pi}
+    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi}
+    + \frac{2}{\chi} \right)
+    \int_0^\chi\ud\chi''
+    \int_0^\infty\ud k k^2 
+    j_\ell(k\chi') j_{\ell}(k\chi'')
+    P_{[ee - fe]}(k, (\chi' + \chi'')/2)
+    %\left[
+    %P_{ee}(k, (\chi' + \chi'')/2)
+    %- P_{fe}(k, (\chi' + \chi'')/2) 
+    %\right]
+    \nonumber\\
+    & +
+    \frac{2}{\pi}
+    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi'}
+    + \frac{2}{\chi'} \right)
+    \int_0^{\chi'}\ud\chi''
+    \int_0^\infty\ud k k^2 
+    j_\ell(k\chi) j_{\ell}(k\chi'')
+    P_{[ee - fe]}(k, (\chi + \chi'')/2).
+    %\left[ 
+    %P_{ee}(k, (\chi + \chi'')/2)
+    %- P_{fe}(k, (\chi + \chi'')/2) 
+    %\right].
+\end{align}
+Here, espressions like $P_{[ff + ee - 2ef]}$ are short hand for $P_{ff} +
+P_{ee} - 2P_{ef}$.
+
+Equation~\ref{e:Clss} can be simplifed substantially by adopting the small
+angle and Limber approximations \citep{extened_limber}.  The small angle
+approximation eliminates the $k$ integral over sperical Bessel functions, replacing it
+with a Forrier transform, and is valid for $\ell \gg 1$. The Limber
+approximation assumes that only modes with small radial component of thier wave
+vector contribute to the radial integrals and is valid if the power spectra
+evolve slowly compared to the correlation length (which has already been
+assumed). With these approximations we have
+\begin{align}
+C^{ss}_\ell(\chi, \chi') \approx&~
+    \frac{1}{\bar\chi^2}
+        \int_{-\infty}^\infty\frac{\ud k_\parallel}{(2 \pi)} 
+        e^{i k_\parallel (\chi - \chi')}
+        P_{[ee + ff - 2ef]}
+        (\sqrt{k_\parallel^2 + \ell(\ell + 1)/\bar\chi^2}, \bar\chi)
+        %\left[
+        %P_{ee}(\sqrt{k_\parallel^2 + \ell^2/\bar\chi^2}, \bar\chi)
+        %+ P_{ff}(\sqrt{k_\parallel^2 + \ell^2/\bar\chi^2}, \bar\chi)
+        %- 2 P_{ef}(\sqrt{k_\parallel^2 + \ell^2/\bar\chi^2}, \bar\chi)
+        %\right]
+    \nonumber \\ &+
+    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi}
+    + \frac{2}{\chi} \right)
+    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi'}
+    + \frac{2}{\chi'} \right)
+    \int_0^{\chi_{\rm min}}\ud\chi''
+    \frac{1}{\chi^{\prime\prime 2}}
+    P_{ee}((\ell + 1/2)/\chi'',\chi'')
+    \nonumber \\ &+
+    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi_{\max}}
+    + \frac{2}{\chi_{\max}} \right)
+    \frac{1}{\chi_{\min}^2}
+    P_{[ee - ef]}((\ell + 1/2)/\chi_{\min}, \chi_{\min}),
+        %\left[
+        %    P_{ee}(\ell/\chi_{\min}, \chi_{\min})
+        %    - P_{fe}(\ell/\chi_{\min}, \chi_{\min})
+        %\right],
+\end{align}
+where $\chi_{\min} \equiv \min(\chi, \chi')$ and $\chi_{\max} \equiv \max(\chi,
+\chi')$ .  We've found that these approximations are excelent for $\ell > 10$
+and use this form for the remainder of the paper.
+\end{widetext}
+
+\section{Observational considerations}
+
+DM contribution intrinsic to the source will have a few effects: There will be
+an offset which will change the DM-distance relation in some way that can
+hopefully be characterized. Also there will be a stocastic piece which will
+smear out DM-distance relations and limit the effective width of the radial
+shells. Detailed considereation of these effects is beyond the scope of this
+work but to crudely deal with this, we don't consider any $\chi - \chi'$
+smaller than \red{$10\,{\rm MPc}/h$}.
+
+Contributions from local Universe probably not an issue. Can be measure by
+other means and subtracted off.
+
+Tomography is exact.  Get excellent separation of scales, unlike lensing.
+
+\section{Detectability}
+
+\section{Conclustions}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%            Scrap           %%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{widetext}
+
+\newpage
+
+\section{Details not to be included}
 
@@
     \approx&
-    \frac{4}{\pi}
+    \frac{\red{4}}{\pi}
     \int_{0}^{\infty}\ud\Delta'
@@
         P(\sqrt{k_\parallel^2 + \ell^2/\bar\chi^2}, \bar\chi)
-    \\ &+
+    \nonumber \\ &+
     \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi_m}
@@
         P(\ell/\chi'',\chi'')
-    \\ &+
+    \nonumber \\ &+
     \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi_m}
     + \frac{2}{\chi_m} \right)
-    \frac{b_e(b_f - b_e)}{\chi_m^2}
+    \frac{b_e(-b_f + b_e)}{\chi_m^2}
         P(\ell/\chi_m, \chi_m)
@@
 
+\end{widetext}
+
 \end{document}

### 2015-04-23 python/angular_terms.py

@@ -19,9 +19,12 @@ class SingleEll(object):
         self._chi_max = chi_max
 
         nchi = 20
-        #chi_list = np.linspace(0, chi_max, nchi, endpoint=True)
-        delta_chi = chi_max / nchi
-        chi_list = np.arange(1, nchi + 1, dtype=float) / nchi * chi_max
+        #delta_chi = chi_max / nchi
+        #chi_list = np.arange(1, nchi + 1, dtype=float) / nchi * chi_max
+        
+        chi_min = 500.
+        chi_list = np.linspace(chi_min, chi_max, nchi, endpoint=True)
+        delta_chi = chi_list[1] - chi_list[0]
 
         data = []
 
@@ -32,7 +35,30 @@ class SingleEll(object):
             # Put in Gaussian cut-off to control oscillations.
 
             if limber:
-                pass
+                # Local term.
+                delta_k = 2 * np.pi / (2 * chi)
+                k_max = np.sqrt(max(matter_power.K_MAX**2 - (ell/chi)**2, 0))
+                k = np.arange(0, k_max, delta_k)
+                k = np.concatenate((k, -k[:0:-1]))
+                nk = len(k)   # Guaranteed to be odd.
+                if nk > 10:
+                    p_k_local = p_k_interp(np.sqrt((ell/chi)**2 + k**2))
+                    #window = fftpack.ifftshift(signal.kaiser(nk, beta=14, sym=True))
+                    window = fftpack.ifftshift(signal.hann(nk, sym=True))
+                    p_k_local *= window
+                    fft_norm = len(k) * delta_k / 2 / np.pi / chi**2
+                    I1 = fftpack.ifft(p_k_local).real
+                    I1 = fftpack.fftshift(I1) * fft_norm
+                    deltas = np.linspace(-chi, chi, len(I1), endpoint=True)
+                else:
+                    I1 = np.zeros(10, dtype=float)
+                    deltas = np.linspace(-chi, chi, len(I1), endpoint=True)
+
+                # Limber term.
+                if ell/chi > matter_power.K_MAX:
+                    I2 = 0
+                else:
+                    I2 = p_k_interp(ell/chi) / chi**2
             else:
                 p_k = lambda k: k**2 * p_k_interp(k)
 
@@ -50,10 +76,9 @@ class SingleEll(object):
                 deltas.append(delta_max)
                 deltas = np.array(deltas)
 
[…]

### 2015-04-23 python/assemble_terms.py

@@ -86,22 +86,25 @@ def get_ells():
     return np.array(ells)
 
 
-def get_mult_ell(ells=None):
+def get_mult_ell(ells=None, limber=False):
     if ells is None:
         ells = get_ells()
     CHI_MAX = 3600.
-    mell = angular_terms.MultiEll(ells, CHI_MAX)
+    mell = angular_terms.MultiEll(ells, CHI_MAX, limber)
     return mell
 
 
-def my_plots(mult_ell):
+def my_plots(mult_ell=None, chi=1800):
     matplotlib.rcParams.update({'font.size': 14,
                                 'text.usetex' : False,
                                 'figure.autolayout': True})
-    CHI = 1000.
+
+    if mult_ell is None:
+        mult_ell = get_mult_ell()
+    CHI = float(chi)
     DELTAS = [5., 20., 50., 100.]
-    Y_MIN = 4e-8
-    Y_MAX = 1e-5
+    Y_MIN = 4e-7
+    Y_MAX = 1e-4
     X_MIN = 9
     X_MAX = 1001
     
@@ -123,7 +126,7 @@ def my_plots(mult_ell):
         plt.ylabel(r"$C^{ss}_\ell(\chi,\chi')$",
                    fontsize=18,
                    )
-        plt.legend(loc="lower left", labelspacing=.1, frameon=False)
+        plt.legend(loc="upper right", labelspacing=.1, frameon=False)
 
     chi_s = np.linspace(100, 3500, 50)
     coef_s = np.array([  d_ln_n(chi) + 2./chi for chi in chi_s ])

### 2015-04-23 python/sph_bessel.py

@@ -113,7 +113,7 @@ def integrate_f_jnjn(f, n, mean, delta, x_max):
         envelop_width = 1000 * x_max
     else:
         envelop_width = 5 * (2 * np.pi / delta)
-    x_max = min(x_max, 4 * envelop_width)
+    x_max = min(x_max, 5 * envelop_width)
 
     x, ntuple, delta_tuple = sample_jnjn(n, mean, delta, x_max)
 

### 2015-04-23 python/tests/test_angular_terms.py

@@ -15,7 +15,7 @@ class TestSingleEll(unittest.TestCase):
         #plt.show()
 
     def test_limber(self):
-        s = angular_terms.SingleEllLimber(80, 3000)
+        s = angular_terms.SingleEll(80, 3000, limber=True)
         plt.show()
 
 

### 2015-04-27 writeup/dm_space_distortions.tex
Added first figure.

@@
 \usepackage{times}
+\usepackage{afterpage}
 
@@
     The recently discovered fast radio bursts are a new class of radio
-    transient that, due to thier high dispersion from interviening plasma,
+    transient that, due to their high dispersion from intervening plasma,
     have been interpreted as
-    origionating from cosmological distances.  The rate of fast radio bursts
+    originating from cosmological distances.  The rate of fast radio bursts
     has been estimated to be as high as 10\,000 per sky per day.  If
     cosmological, these events should trace the large-scale structure of the
-    Universe in some way. Furthermore, because the disperion measure (DM) can be
+    Universe in some way. Furthermore, because the dispersion measure (DM) can be
     used as a proxy for radial distance (like redshift),
-    clustering can be studied in three dimensions. Due to inhomogenaities in
+    clustering can be studied in three dimensions. Due to inhomogeneities in
     the plasma's density dispersion measure is an imperfect proxy or radial
@@
     dispersion measure space distortions. We calculate the DM space
-    powerspectra for a toy model of electron and FRB clustering and show that
+    power spectra for a toy model of electron and FRB clustering and show that
     the clustering signal could be detected in a survey of \red{10000} FRB
@@
 The dispersion measure of a signal observed in some angular direction $\hat{n}$ and
-originating from comoving radial distance $\chi$ is
+originating from co moving radial distance $\chi$ is
 \begin{equation}
@@
 conformal time. Note that we use $\chi$ as our radial distance and time
-coordinate, as opposed to redshift which is more approprite for spectroscopic
+coordinate, as opposed to redshift which is more appropriate for spectroscopic
 applications. We model the cosmological 
-electron density as containing a homogenious part
+electron density as containing a homogeneous part
 and perturbations
@@
 all of the electrons to be in a diffuse ionized state such that
-$\bar{n}_e(\chi) = \bar{n}_{e0} / a(\chi)^3$ (not nessisary).} The dispersion
+$\bar{n}_e(\chi) = \bar{n}_{e0} / a(\chi)^3$ (not necessary).} The dispersion
 measure is thus
@@
 \end{equation}
-We split the density into a homogenious part plus perturbations,
+We split the density into a homogeneous part plus perturbations,
 \begin{equation}
@@
 
-The jacobian in spherical coordinates is
+The Jacobian in spherical coordinates is
 \begin{align}
@@
 In the equation above, the $-\delta_e$ term is most analogous to the Kaiser
-redshift space distortions.  It is a dillution of tracers in DM space due to an
+redshift space distortions.  It is a dilution of tracers in DM space due to an
 excess of electrons in between the tracers. However we note that this term is isotropic
-in cotrast to Kaiser.  This is because any wave vector electron perturbation
+in contrast to Kaiser.  This is because any wave vector electron perturbation
 causes DM space distortions, whereas the radial velocities that cause
-redshift space distortions are only sourced by perterbations with radial wave
+redshift space distortions are only sourced by perturbations with radial wave
 vectors.
@@
 caused by a misinterpretation of angular distances when the radial distance is
-mismeasured.  Both term are in-prociple present in redshift space but are
-negligable. Because radial veolocities are only sourced by modes with large
-radial wave vector, there is near perfect cancelation along the line of sight
+mis measured.  Both terms are in-principle present in redshift space but are
+negligible. Because radial velocities are only sourced by modes with large
+radial wave vector, there is near perfect cancellation along the line of sight
 and thus is very little net error in radial distance.
+
+For brevity in the following sections we define the coefficient of the integral
+term as
+\begin{equation}
+    A(\chi) \equiv \frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi}
+    + \frac{2}{\chi}.
+\end{equation}
 
@@
 We will phrase the two point statistic in terms of $C^{ss}_\ell(\chi,\chi')$, which is
-the cross-correlation angular power-spectrum of the DM space overdensity
+the cross-correlation angular power-spectrum of the DM space over-density
 on shells at $\chi$ and $\chi'$.
@@
 \end{align}
-In reality the powerspectrum evolves on the order of a (conformal) Hubble time.
+In reality the power spectrum evolves on the order of a Hubble time.
 The angular cross-correlations will be very small unless $\chi$ and $\chi'$ are
 within a few correlation lengths of one another, roughly a few hundred
-megaparsecs.  The evolution of the power-spectrum is negligable over these time
+megaparsecs.  The evolution of the power-spectrum is negligible over these time
 differences which leads to a straight forward way to include the evolution of
@@
     \frac{2}{\pi}
-    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi}
-    + \frac{2}{\chi} \right)
-    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi'}
-    + \frac{2}{\chi'} \right)
+    %\left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi}
+    %+ \frac{2}{\chi} \right)
+    %\left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi'}
+    %+ \frac{2}{\chi'} \right)
+    A(\chi) A(\chi')
     \int_0^\chi\ud\chi''
@@
     \frac{2}{\pi}
-    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi}
-    + \frac{2}{\chi} \right)
+    %\left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi}
+    %+ \frac{2}{\chi} \right)
+    A(\chi)
     \int_0^\chi\ud\chi''
@@
     \frac{2}{\pi}
-    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi'}
-    + \frac{2}{\chi'} \right)
+    %\left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi'}
+    %+ \frac{2}{\chi'} \right)
+    A(\chi')
     \int_0^{\chi'}\ud\chi''
@@
 \end{align}
-Here, espressions like $P_{[ff + ee - 2ef]}$ are short hand for $P_{ff} +
+\end{widetext}
+Here, expressions such as $P_{[ff + ee - 2ef]}$ are short hand for $P_{ff} +
 P_{ee} - 2P_{ef}$.
 
-Equation~\ref{e:Clss} can be simplifed substantially by adopting the small
+Equation~\ref{e:Clss} can be simplified substantially by adopting the small
 angle and Limber approximations \citep{extened_limber}.  The small angle
-approximation eliminates the $k$ integral over sperical Bessel functions, replacing it
-with a Forrier transform, and is valid for $\ell \gg 1$. The Limber
-approximation assumes that only modes with small radial component of thier wave
+approximation eliminates the $k$ integral over spherical Bessel functions, replacing it
+with a Fourier transform, and is valid for $\ell \gg 1$. The Limber
+approximation assumes that only modes with small radial component of their wave
 vector contribute to the radial integrals and is valid if the power spectra
@@
 assumed). With these approximations we have
+\begin{comment}
 \begin{align}
@@
     \nonumber \\ &+
-    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi}
-    + \frac{2}{\chi} \right)
-    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi'}
-    + \frac{2}{\chi'} \right)
+    %\left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi}
+    %+ \frac{2}{\chi} \right)
+    %\left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi'}
+    %+ \frac{2}{\chi'} \right)
+    A(\chi) A(\chi')
     \int_0^{\chi_{\rm min}}\ud\chi''
@@
     \nonumber \\ &+
-    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi_{\max}}
-    + \frac{2}{\chi_{\max}} \right)
-    \frac{1}{\chi_{\min}^2}
+    %\left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi_{\max}}
+    %+ \frac{2}{\chi_{\max}} \right)
+    \frac{A(\chi_{\max})}{\chi_{\min}^2}
     P_{[ee - ef]}((\ell + 1/2)/\chi_{\min}, \chi_{\min}),
@@
 \end{align}
-where $\chi_{\min} \equiv \min(\chi, \chi')$ and $\chi_{\max} \equiv \max(\chi,
-\chi')$ .  We've found that these approximations are excelent for $\ell > 10$
+\end{comment}
+\begin{align}
+    &C^{ss}_\ell(\chi, \chi') \approx
+    \nonumber \\ & \quad
+    \frac{1}{\bar\chi^2}
+        \int_{-\infty}^\infty\frac{\ud k_\parallel}{(2 \pi)} 
+        e^{i k_\parallel (\chi - \chi')}
+        P_{[ee + ff - 2ef]}
+        (\sqrt{k_\parallel^2 + \nu^2/\bar\chi^2}, \bar\chi)
+    \nonumber \\ & \quad +
+    A(\chi) A(\chi')
+    \int_0^{\chi_{\rm min}}\ud\chi''
+    \frac{1}{\chi^{\prime\prime 2}}
+    P_{ee}(\nu/\chi'',\chi'')
+    \nonumber \\ & \quad +
+    \frac{A(\chi_{\max})}{\chi_{\min}^2}
+    P_{[ee - ef]}(\nu/\chi_{\min}, \chi_{\min}),
+\end{align}
+where $\nu\equiv\ell + 1/2$, $\chi_{\min} \equiv \min(\chi, \chi')$,
+and $\chi_{\max} \equiv \max(\chi,
+\chi')$ .  We've found that these approximations are excellent for $\ell
+\gtrsim 10$
 and use this form for the remainder of the paper.
-\end{widetext}
 
-\section{Observational considerations}
+\subsection{Modelling the angular power-spectrum}
+
+Description of the input power-spectra, $\bar n_f$ and figures.
+Figure~\ref{f:n_f}
+
+\begin{figure}
+    \includegraphics[scale=0.42]{"figures/n_f"}
+    \caption{
+        \label{f:n_f}
+        \red{Need to fix normalization of top panel.}
+    }
+\end{figure}
+
+\section{Measurement}
 
@@
 an offset which will change the DM-distance relation in some way that can
-hopefully be characterized. Also there will be a stocastic piece which will
+hopefully be characterized. Also there will be a stochastic piece which will
 smear out DM-distance relations and limit the effective width of the radial
-shells. Detailed considereation of these effects is beyond the scope of this
+shells. Detailed consideration of these effects is beyond the scope of this
 work but to crudely deal with this, we don't consider any $\chi - \chi'$
-smaller than \red{$10\,{\rm MPc}/h$}.
+smaller than \red{$100\,{\rm MPc}/h$}.
 
@@
 Tomography is exact.  Get excellent separation of scales, unlike lensing.
+The integral over $\chi$ couples many scales. In particular small scales (which
+are difficult to model) will
+be coupled to large angular scales by screens near the observer.  However
+because tomography is exact, it would be possible to set up estimators that
+decouple these scales, for instance by estimating the difference in power
+between radial shells.  For this reason we start all radial integrals as
+$\chi = 500\,{\rm MPc}/h$, which saves us from the difficulties in modelling the
+small scale power.
 
-\section{Detectability}
+\subsection{Detectability}
 
-\section{Conclustions}
+Here we present sensitivity estimates for a survey \ldots
+
+We assume that the survey will be shot noise dominated as would be the case for
+an initial detection.  The noise powerspectrum on a shells with of width
+$\Delta \chi$ is
+\begin{equation}
+    C^N_{\ell, ij} = \frac{\delta_{ij}}{\bar n_f(\chi_i)\chi_i^2\Delta\chi},
+\end{equation}
+Here, to indicate that we are now working with quantities binned in the radial
+direction instead of
+continuous functions, we've switched to $C_{\ell,ij}$ over 
+$C_\ell(\chi, \chi')$. The error bar on the angular
+cross-power spectrum is then
+\begin{align}
+    (\Delta{C^{ss}_{\ell,ij}})^2 = 
+    \sqrt{\frac{1}{\ell(\ell + 1)\Delta \ell f_{\rm sky}}}
+        \left[C^N_{\ell,ii} C^N_{\ell,jj} +  (C^N_{\ell,ij})^2\right],
+\end{align}
+where the second term in brackets only contributes for $i = j$.
+
+To give an idea of the sensitivity of the survey, we collapse
+$C^{ss}_{\ell,ij}$ to a single function of $\ell$ by taking a weighted average
+of all pairs of radial bins. We use bin widths of $100\,{\rm MPc}/h$ over the
+range $500\,{\rm MPc}/h$ to $3600\,{\rm MPc}/h$.
+For weights in the radial bin average, we use the signal to noise-squared
+at $\ell=100$, which extracts all the signal to noise at that $\ell$.
+We exclude the $i = j$ bin pairs due to
+the presumed observational complications discussed in the previous section.
+This effectively discards the contribution from the local term.
+
+\section{Discussion and conclusions}
+
+\begin{acknowledgments}
+
+We would like to thank Ue-Li Pen and Mathew McQuinn for helpful discussions.
+%
+KWM is supported by the Canadian Institute for Advanced Research, Global Scalars
+Program.
+
+\end{acknowledgments}
+
+\bibliography{dm_space}
 

### 2015-04-27 python/angular_terms.py

@@ -22,8 +22,8 @@ class SingleEll(object):
         #delta_chi = chi_max / nchi
         #chi_list = np.arange(1, nchi + 1, dtype=float) / nchi * chi_max
         
-        chi_min = 500.
-        chi_list = np.linspace(chi_min, chi_max, nchi, endpoint=True)
+        CHI_MIN = 500.
+        chi_list = np.linspace(CHI_MIN, chi_max, nchi, endpoint=True)
         delta_chi = chi_list[1] - chi_list[0]
 
         data = []
@@ -80,7 +80,8 @@ class SingleEll(object):
                 for ii in range(len(deltas)):
                     I1[ii] = sph_bessel.integrate_f_jnjn(p_k, ell, chi, deltas[ii],
                             matter_power.K_MAX) * (2 / np.pi)
-                I2 = integrate.romb(I1[:ndelta_int] * np.exp(scale * deltas[:ndelta_int]),
+                I2 = integrate.romb(I1[:ndelta_int]
+                                    * np.exp(scale * deltas[:ndelta_int]),
                                     dx=delta_u) * 2
 
             this_chi_data['chi'] = chi
@@ -91,8 +92,8 @@ class SingleEll(object):
             n_total += len(deltas)
 
         I2 = [td["I2"] for td in data]
-        I2 = np.array([0] + I2)
-        I3 = integrate.cumtrapz(I2, dx=delta_chi)
+        I2 = np.array(I2)
+        I3 = integrate.cumtrapz(I2, dx=delta_chi, initial=0.)
         for ii in range(nchi):
             data[ii]["I3"] = I3[ii]
 
@@ -107,7 +108,7 @@ class SingleEll(object):
             ii += ndelta
 
         self.i1 = interpolate.LinearNDInterpolator(chi_delta, I1, fill_value=0.)
-        self.i2 = interpolate.interp1d(chi_list, I2[1:], kind="cubic")
+        self.i2 = interpolate.interp1d(chi_list, I2, kind="cubic")
         self.i3 = interpolate.interp1d(chi_list, I3, kind="cubic")
         self.data = data
 

### 2015-04-27 python/assemble_terms.py

@@ -12,8 +12,8 @@ import angular_terms
 Z_STAR = 0.8
 ALPHA = -0.7
 
-B_E = 0.9
-B_F = 1.3
+B_E = 1.0
+B_F = 0.7
 
 
 def d_ln_n(chi):
@@ -59,22 +59,28 @@ def n_chi(chi):
 
 
 def apply_coeffs(mult_ell, chi, delta):
+    
+    chi1 = chi - abs(delta) / 2
+    chi2 = chi + abs(delta) / 2
 
-    coeff = d_ln_n(chi) + 2./chi
+    coeff1 = d_ln_n(chi1) + 2./chi1
+    coeff2 = d_ln_n(chi2) + 2./chi2
     i1, i2, i3 = mult_ell.get_integrals(chi, delta)
     t1 = (B_F - B_E)**2 * i1
-    t2 = (B_F - B_E) * B_E * coeff * i2
-    t3 = B_E**2 * coeff**2 * i3
+    t2 = (B_E - B_F) * B_E * coeff2 * i2
+    t3 = B_E**2 * coeff1 * coeff2 * i3
 
     return t1, t2, t3
 
 def plot_spectra(mult_ell, chi, delta, **kwargs):
     ells = mult_ell.ells
     t1, t2, t3 = apply_coeffs(mult_ell, chi, delta)
-    plt.loglog(ells, t1 + t2 + t3, '-k', label='total', **kwargs)
-    plt.loglog(ells, t1, '--b', label='local term', **kwargs)
-    plt.loglog(ells, t2, '-.g', label='cross term', **kwargs)
-    plt.loglog(ells, t3, ':r', label='integral term', **kwargs)
+    #trans = lambda t: ells**2 * abs(t)
+    trans = lambda t: abs(t)
+    plt.loglog(ells, trans(t1 + t2 + t3), '-k', label='total', **kwargs)
+    plt.loglog(ells, trans(t1), '--b', label='local term', **kwargs)
+    plt.loglog(ells, trans(t2), '-.g', label='cross term', **kwargs)
+    plt.loglog(ells, trans(t3), ':r', label='integral term', **kwargs)
 
 
 def get_ells():
@@ -132,23 +138,33 @@ def my_plots(mult_ell=None, chi=1800):
     coef_s = np.array([  d_ln_n(chi) + 2./chi for chi in chi_s ])
 
     plt.figure()
-    plt.plot(chi_s, coef_s, **kwargs)
[…]

### 2015-05-06 writeup/dm_space_distortions.tex
Added sensitivity figure.

@@
 Description of the input power-spectra, $\bar n_f$ and figures.
-Figure~\ref{f:n_f}
+Figure~\ref{f:n_f}, Figure~\ref{f:terms}.
 
@@
         \red{Need to fix normalization of top panel.}
+    }
+\end{figure}
+
+\begin{figure}
+    \includegraphics[scale=0.42]{"figures/terms"}
+    \caption{
+        \label{f:terms}
+        Terms in the DM-space cross-correlation angular power spectrum.
+        All terms are evaluated at $\bar\chi=1000\,{\rm MPc}/h$ and 
+        $\chi - \chi' = 10\,{\rm MPc}/h$, except the lowest most 
+        ``local term'' curve which is for $\chi - \chi'=50\,{\rm MPc}/h$. 
+        While
+        the other two terms are highly insensitive to the separation of
+        the radial slices, the local term drops rapidly at high separations.
     }
@@
 continuous functions, we've switched to $C_{\ell,ij}$ over 
-$C_\ell(\chi, \chi')$. The error bar on the angular
+$C_\ell(\chi, \chi')$. The uncertainty on the angular
 cross-power spectrum is then
@@
     (\Delta{C^{ss}_{\ell,ij}})^2 = 
-    \sqrt{\frac{1}{\ell(\ell + 1)\Delta \ell f_{\rm sky}}}
+    {\frac{1}{\ell(\ell + 1)\Delta \ell f_{\rm sky}}}
         \left[C^N_{\ell,ii} C^N_{\ell,jj} +  (C^N_{\ell,ij})^2\right],
@@
 of all pairs of radial bins. We use bin widths of $100\,{\rm MPc}/h$ over the
-range $500\,{\rm MPc}/h$ to $3600\,{\rm MPc}/h$.
-For weights in the radial bin average, we use the signal to noise-squared
-at $\ell=100$, which extracts all the signal to noise at that $\ell$.
+range $500\,{\rm MPc}/h$ to $3500\,{\rm MPc}/h$.
+For weights in the radial bin average, we use the signal to uncertainty-squared
+at $\ell=100$, which extracts all the signal to noise at that $\ell$ and much
+of it at other multipoles.
 We exclude the $i = j$ bin pairs due to
 the presumed observational complications discussed in the previous section.
-This effectively discards the contribution from the local term.
+This effectively discards the contribution from the local term. This is shown
+in Figure~\ref{f:sensitivity}.
+
+\begin{figure}
+    \includegraphics[scale=0.42]{"figures/sensitivity"}
+    \caption{
+        \label{f:sensitivity}
+        Sensitivity of a survey with $10^4$ dispersion measures distributed
+        uniformly over half the sky.  Plotted is the cross-correlation
+        power spectrum weighted averaged over all pairs of radial bins. Weights
+        are chosen to maximize signal to noise at $\ell=100$.
+    }
+\end{figure}
 

### 2015-05-06 python/assemble_terms.py

@@ -72,15 +72,18 @@ def apply_coeffs(mult_ell, chi, delta):
 
     return t1, t2, t3
 
-def plot_spectra(mult_ell, chi, delta, **kwargs):
+def plot_spectra(mult_ell, chi, delta, local_only=False, **kwargs):
     ells = mult_ell.ells
     t1, t2, t3 = apply_coeffs(mult_ell, chi, delta)
     #trans = lambda t: ells**2 * abs(t)
     trans = lambda t: abs(t)
-    plt.loglog(ells, trans(t1 + t2 + t3), '-k', label='total', **kwargs)
-    plt.loglog(ells, trans(t1), '--b', label='local term', **kwargs)
-    plt.loglog(ells, trans(t2), '-.g', label='cross term', **kwargs)
-    plt.loglog(ells, trans(t3), ':r', label='integral term', **kwargs)
+    if local_only:
+        plt.loglog(ells, trans(t1), '--b', label='local term', **kwargs)
+    else:
+        plt.loglog(ells, trans(t1 + t2 + t3), '-k', label='total', **kwargs)
+        plt.loglog(ells, trans(t1), '--b', label='local term', **kwargs)
+        plt.loglog(ells, trans(t2), '-.g', label='cross term', **kwargs)
+        plt.loglog(ells, trans(t3), ':r', label='integral term', **kwargs)
 
 
 def get_ells():
@@ -92,7 +95,7 @@ def get_ells():
     return np.array(ells)
 
 
-def get_mult_ell(ells=None, limber=False):
+def get_mult_ell(ells=None, limber=True):
     if ells is None:
         ells = get_ells()
     CHI_MAX = 3600.
@@ -100,7 +103,7 @@ def get_mult_ell(ells=None, limber=False):
     return mell
 
 
-def my_plots(mult_ell=None, chi=1800):
+def my_plots(mult_ell=None, chi=1000):
     matplotlib.rcParams.update({'font.size': 14,
                                 'text.usetex' : False,
                                 'figure.autolayout': True})
@@ -108,8 +111,9 @@ def my_plots(mult_ell=None, chi=1800):
     if mult_ell is None:
         mult_ell = get_mult_ell()
     CHI = float(chi)
[…]

### 2015-05-14 writeup/dm_space_distortions.tex
Some writeup of systematics.

@@
 \newcommand{\green}{\textcolor{green}}
+
+\renewcommand{\section}[1]{\emph{#1}---\ignorespaces}
+\renewcommand{\subsection}[1]{}
 
@@
     power spectra for a toy model of electron and FRB clustering and show that
-    the clustering signal could be detected in a survey of \red{10000} FRB
+    the clustering signal could be detected in a survey of $10^4$ FRB
     events, as is expected to be produced by the Canadian Hydrogen Intensity
@@
 \section{Introduction}
+The clustering of matter on large scales has been
+heralded as the next great probe the Universe after the cosmic microwave
+background (CMB). The large-scale structure in principle contains far more
+information than the CMB, because it can be studied in three dimensions.
+Traditionally the redshift of spectral lines caused by the Hubble flow has
+been employed to measure position in the radial direction. Such redshift
+surveys have now aggregated the positions of millions of galaxies into three
+dimensional density maps exposing a rich structure of clusters, filaments,
+walls and voids.
+
+However, redshift is not the only measure of radial distance. In particular,
+dispersion of electromagnetic signals due to intervening plasma
+is readily measured from fast radio bursts (FRB) which are a class
+of radio transient first reported in \citet{lorimer}. The dispersion measure
+(DM) is a line-of-site integral of the free electron density and can thus be
+used as a distance estimate.
+% IF COSMOLOGICAL!!
+
+Neither redshift or dispersion measure are perfect proxies for radial distance.
+Redshifts are systematically biased by the peculiar velocities of the object
+relative to the Hubble flow. This leads to additional apparent clustering 
+in redshift
+space which was first calculated by \citet{kaiser} using linear theory.
+
+Similarly, distance estimates from dispersion measure will be biased by
+inhomogeneities in the electron density, again leading to additional apparent
+clustering of sources in dispersion measure space.  In this letter we calculate
+these DM space distortions and shaw that they could 
+be usefully measured in a
+survey detecting as few as 10\,000 fast radio bursts.
 
 \section{Density perturbations in dispersion measure space}
-
 The dispersion measure of a signal observed in some angular direction $\hat{n}$ and
-originating from co moving radial distance $\chi$ is
+originating from comoving radial distance $\chi$ is
 \begin{equation}
@@
 and perturbations
-$n_e(\vec x, \chi) = \bar{n}_e(\chi) \left[1 + \delta_e(\vec x, \chi)\right]$.  \red{We take
-all of the electrons to be in a diffuse ionized state such that
-$\bar{n}_e(\chi) = \bar{n}_{e0} / a(\chi)^3$ (not necessary).} The dispersion
+$n_e(\vec x, \chi) = \bar{n}_e(\chi) \left[1 + \delta_e(\vec x, \chi)\right]$.
+The dispersion
 measure is thus
@@
 \begin{equation}
-\frac{\ud \chi_s}{\ud \chi} = (1 + \delta_e(\hat n \chi, \chi),
+\frac{\ud \chi_s}{\ud \chi} = 1 + \delta_e(\hat n \chi, \chi),
 \end{equation}
@@
 
-\section{Two-point statistics in DM space}
-
+\section{Two-point statistics}
+Large-scale structure is usually studied through it two-point statistics, most
+commonly the power-spectrum, $P(k)$.
 Unlike in redshift-space distortions, Equation~\ref{e:delta_s} does not have a
@@
 and thus the two-point statistics cannot be phrased as a simple power spectrum.
-We will phrase the two point statistic in terms of $C^{ss}_\ell(\chi,\chi')$, which is
+We will instead use $C^{ss}_\ell(\chi,\chi')$, which is
 the cross-correlation angular power-spectrum of the DM space over-density
@@
 
-\subsection{Modelling the angular power-spectrum}
+\section{Modeling and measurement}
+There are a number of effects that will complicate the measurement of the
+above calculated angular power spectrum by a real survey of dispersion 
+measures.  The first is
+that the model that the free electron density decomposes into a homogeneous
+part plus a random field of perturbations is not correct. Firstly, all signals
+must pass through the Milky Way's galactic disk, halo and local environment
+which will contribute to the dispersion measure. However, this is only a 
+single function of $\hat n$  which can presumably be well
+measured. In addition, this function could in principal be well characterized
+by independent data such as observations of pulsars.  As such, the local
+contribution is unlikely to be a limiting obstacle.
+
+More concerning is the dispersion from the burst progenitor's environment
+as well as the halo in which it resides.
 
@@
 
-\section{Measurement}
+In this section we discuss some systematic effects that would affect a real
+survey of dispersion measures, complicating measurement. We then estimate the
+sensitivity of such a survey.
+
+\subsection{Systematics}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%            Scrap           %%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{widetext}
-
-\newpage
-
-\section{Details not to be included}
-
-We use the following conventions:
-\begin{equation}
-    P_{xy}(k, \chi) = b_x b_y g(\chi)^2 a(\chi)^2 P(k, 0)
-\end{equation}
-
-\begin{equation}
-    \delta_x(\vec x, \chi) =  b_x g(\chi) a(\chi) \int\frac{\ud^3\vec k}{(2 \pi)^3}
-        e^{i\vec k \cdot \vec x} \delta(\vec k, 0)
-\end{equation}
-
-\begin{equation}
-    w^{xy}(\hat n \cdot \hat n', \chi, \chi')
-    \equiv \langle \delta_x(\vec x) \delta_y(\vec x') \rangle
-\end{equation}
-
-For any statistically stationary tracers $x$ and $y$,
-ignoring time dependance (redshift evolution)
-of the power spectrum:
-\begin{align}
-    \delta_{\ell\ell'}\delta_{mm'}C^{xy}_\ell(\chi, \chi')
-    &= \int\ud\Omega\ud\Omega'Y_{\ell m}(\hat n) Y_{\ell' m'}(\hat n')
-        \langle \delta^x(\hat n \chi) \delta^y(\hat n' \chi') \rangle
-        \\
-    &=
-        \int\ud\Omega\ud\Omega'Y_{\ell m}(\hat n) Y_{\ell' m'}(\hat n')
-        \int\frac{\ud^3\vec k}{(2 \pi)^3} \frac{\ud^3\vec k'}{(2 \pi)^3}
-        e^{i\vec k \cdot \vec x} e^{i\vec k' \cdot \vec x'}
-        \langle \delta(\vec k) \delta(\vec k') \rangle
-        \\
-    &=
-        \int\ud\Omega\ud\Omega'Y_{\ell m}(\hat n) Y_{\ell' m'}(\hat n')
-        \int\frac{\ud^3\vec k}{(2 \pi)^3} 
-        e^{i\vec k \cdot (\vec x - \vec x')} P_{xy}(k)
-        \\
-    &=
-        \int\frac{\ud^3\vec k}{(2 \pi)^3} P_{xy}(k)
-        \int\ud\Omega Y_{\ell m}(\hat n)
-        e^{i\vec k \cdot \vec x}
-        \int\ud\Omega' Y_{\ell' m'}(\hat n')
-        e^{-i\vec k \cdot \vec x'}
-        \\
-    &=
-        \int\frac{\ud^3\vec k}{(2 \pi)^3} P_{xy}(k)
-        \left[(4 \pi) i^\ell j_\ell(k\chi) Y_{\ell m}^*(\hat k)\right]
-        \left[(4 \pi) i^{-\ell'} j_{\ell'}(k\chi') Y_{\ell' m'}(\hat
-        k)\right]
-        \\
-    &=
-        \frac{2}{\pi}
-        \int_0^\infty\ud k k^2 j_\ell(k\chi) j_{\ell'}(k\chi')P_{xy}(k)
-        \int\ud \Omega_k i^{(\ell - \ell')}
-        Y_{\ell' m'}^*(\hat k) Y_{\ell m}(\hat k)
-        \\
-    &= \delta_{\ell\ell'}\delta_{mm'}\frac{2}{\pi}
-        \int_0^\infty\ud k k^2  j_\ell(k\chi) j_{\ell}(k\chi')P_{xy}(k)
-        \\
-    C^{xy}_\ell(\chi,\chi') 
-    &= \frac{2}{\pi}
-\int_0^\infty\ud k k^2 j_\ell(k\chi) j_{\ell}(k\chi')P_{xy}(k)
-\end{align}
-
-It is convienient to reparameterize this in terms of
-$\bar\chi \equiv (\chi + \chi') /2$ and $\Delta \chi \equiv \chi' - \chi$.
-We expect the power spectrum to vary slowly as a function of $\bar\chi$ and
-very quickly as a function of $\Delta\chi$. However it will be highly
-suppressed for $\ell \gg \bar\chi/\Delta\chi$. These facts will be very
-helpfull in subsequent numerical integrals.
-
-Also since smallish value of $\Delta\chi$ are of interest, this leads us to
-an obviouse way to include redshift dependance of the
-power spectrum:
-\begin{equation}
-C^{xy}_\ell(\bar\chi,\Delta\chi) 
-    = \frac{2}{\pi}
-    \int_0^\infty\ud k k^2
-    j_\ell(k\chi) j_{\ell}(k\chi')
-    P_{xy}(k,\bar\chi) \qquad \Delta\chi \ll 1/aH
-\end{equation}
-
-Define $\delta_d$ as:
-\begin{equation}
-    \delta_d(\hat n \chi) = \int_0^\chi \ud \chi' \delta_e(\hat n \chi')
-\end{equation}
-which doesn't have the same units as over-density, but that is okay.
-\begin{equation}
-C^{dd}_\ell(\chi,\chi')
-    =
-    \frac{2}{\pi}
-    \int_0^\chi\ud\chi''
-    \int_0^{\chi'}\ud\chi'''
-    \int_0^\infty\ud k k^2 j_\ell(k\chi'') j_{\ell}(k\chi'''
-    )P_{ee}(k, (\chi''+\chi''')/2)
-\end{equation}
-
-For numerical integration, perform the following change of variables to make
-things much easier.
-\begin{align}
-C^{dd}_\ell(\chi,\chi')
-&=
-    \frac{2}{\pi}
-    \int_0^{(\chi' + \chi)/2}\ud\bar\chi'
-    \int_{\max(-2\bar\chi', -2(\chi -\bar\chi'))}^{\min(2\bar\chi', 2(\chi' -
-    \bar\chi'))}\ud\Delta'
-    \int_0^\infty\ud k k^2 j_\ell(k(\bar\chi' - \Delta'/2))
-    j_{\ell}(k(\bar\chi' + \Delta'/2))
-    P_{ee}(k, \bar\chi')
-    \\
-    &\approx
-    \frac{4}{\pi}
-    \int_0^{\chi_m}\ud\bar\chi'
-    \int_{0}^{\infty}\ud\Delta'
-    \int_0^\infty\ud k k^2 j_\ell(k(\bar\chi' - \Delta'/2))
-    j_{\ell}(k(\bar\chi' + \Delta'/2))
-    P_{ee}(k, \bar\chi')
-\end{align}
-At this point we could again to the transformation to $C_{\ell\chi\chi'}$
-leaving the expression as a triple integral. This is not as computationally
-costly as might be expected at first glance, since the $\chi''$ and $\chi'''$
-integrals are almost the same for all $\chi$, $\chi'$ pairs with only the
-limits of integration changing. Thus the full set of $C_{\ell\chi\chi'}$'s can
-be computed with a cumulative sum, only performing one new integral (over $k$)
-for each element.
-
-Finally, the cross terms:
-\begin{equation}
-C^{dx}_\ell(\chi,\chi')
-    =
-    \frac{2}{\pi}
-    \int_0^\chi\ud\chi''
-    \int_0^\infty\ud k k^2 
-    j_\ell(k\chi') j_{\ell}(k\chi'')P_{ex}(k, (\chi' + \chi'')/2)
-\end{equation}
-
-with the following change of variables for numerical integration:
-\begin{align}
-C^{dx}_\ell(\chi,\chi')
-    =&
-    \frac{2}{\pi}
-    \int_{-\chi'}^{\chi - \chi'}\ud\Delta'
-    \int_0^\infty\ud k k^2 j_\ell(k\chi')
-    j_{\ell}(k(\chi'+\Delta'))
-    P_{ex}(k, \chi' + \Delta'/2)
-    \\
-C^{dx}_\ell(\chi,\chi') + C^{xd}_\ell(\chi,\chi')
-    \approx&
-    \frac{2}{\pi}
-    \int_{-\chi'}^{\chi - \chi'}\ud\Delta'
-    \int_0^\infty\ud k k^2 j_\ell(k(\chi'-\Delta'/2))
-    j_{\ell}(k(\chi'+\Delta'/2))
-    P_{ex}(k, \chi')
-    \nonumber\\
-    &+
-    \frac{2}{\pi}
-    \int_{-\chi}^{\chi' - \chi}\ud\Delta'
-    \int_0^\infty\ud k k^2 j_\ell(k(\chi-\Delta'/2))
-    j_{\ell}(k(\chi+\Delta'/2))
-    P_{ex}(k, \chi)\\
-    \approx&
-    \frac{\red{4}}{\pi}
-    \int_{0}^{\infty}\ud\Delta'
-    \int_0^\infty\ud k k^2 j_\ell(k(\chi_m-\Delta'/2))
-    j_{\ell}(k(\chi_m+\Delta'/2))
-    P_{ex}(k, \chi_m)
-\end{align}
-The second line exploits the fact that for $\ell \gg 1$, $\chi \gg \chi'/\ell$ and
-$\chi' \gg \chi/\ell$, only $\Delta'\ll\chi$ contributes significantly to the
-integral. Also the expressions are very weak functions of $\chi$ and thus
-may be shifted by $\Delta/2$ without incurring much error. The third line
-exploits the fact that only one term contributes if $\chi$ and $\chi'$ are
-widely separated, and if they are close then the two terms combine to the given
-expression.
-
-\red{Actually, with the approximations we've made, we can actually do the
-$\Delta$ integrals analytically by transferring all the $\Delta$ to a single
-Bessel and shifting the power spectrum to be independent of $\Delta$.  Should
-be pretty good for $\ell > 10$.  That is nice because it will control all our
-numerical issues with oscillating Bessel functions.}
-
-Assembling terms:
-\begin{align}
-C^{ss}_\ell(\chi,\chi') = &
-    \frac{2}{\pi}
-    \int_0^\infty\ud k k^2
-    j_\ell(k\chi) j_{\ell}(k\chi')
-    \left[ P_{ff}(k, \bar\chi)
-    + P_{ee}(k, \bar\chi)
-    - 2P_{fe}(k, \bar\chi) \right]
-    \nonumber\\
-    & +
-    \frac{2}{\pi}
-    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi}
-    + \frac{2}{\chi} \right)
-    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi'}
-    + \frac{2}{\chi'} \right)
-    \int_0^\chi\ud\chi''
-    \int_0^{\chi'}\ud\chi'''
-    \int_0^\infty\ud k k^2 j_\ell(k\chi'') j_{\ell}(k\chi''')
-    P_{ee}(k, (\chi''+\chi''')/2)
-    \nonumber\\
-    & +
-    \frac{2}{\pi}
-    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi}
-    + \frac{2}{\chi} \right)
-    \int_0^\chi\ud\chi''
-    \int_0^\infty\ud k k^2 
-    j_\ell(k\chi') j_{\ell}(k\chi'')
-    \left[ P_{ee}(k, (\chi' + \chi'')/2)
-    - P_{fe}(k, (\chi' + \chi'')/2) \right]
-    \nonumber\\
-    & +
-    \frac{2}{\pi}
-    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi'}
-    + \frac{2}{\chi'} \right)
-    \int_0^{\chi'}\ud\chi''
-    \int_0^\infty\ud k k^2 
-    j_\ell(k\chi) j_{\ell}(k\chi'')
-    \left[ P_{ee}(k, (\chi + \chi'')/2)
-    - P_{fe}(k, (\chi + \chi'')/2) \right]
-\end{align}
-
-\section{Small angles and Limber}
-
-Alternately, on the flat sky and for small angles:
-\begin{align}
-(2\pi)^2\delta^2(\vec \ell - \vec \ell')C_\ell(\chi, \chi')
-    &=
-        \int\ud^2\vec\theta\ud^2\vec\theta'
-        e^{-i\vec\ell\cdot\vec\theta} e^{-i\vec\ell'\cdot\vec\theta'}
-        \langle \delta(\hat n \chi) \delta(\hat n' \chi') \rangle
-        \\
-    &\approx
-        \int\ud^2\vec\theta\ud^2\vec\theta'
-        e^{-i\vec\ell\cdot\vec\theta} e^{-i\vec\ell'\cdot\vec\theta'}
-        \int\frac{\ud^3\vec k}{(2 \pi)^3} 
-        e^{i\vec k \cdot (\vec x - \vec x')} P(k, \bar\chi)
-        \\
-    &=
-        \int\frac{\ud^3\vec k}{(2 \pi)^3} 
-        e^{i k_\parallel (\chi - \chi')} P(k, \bar\chi)
-        \int\ud^2\vec\theta e^{-i(\vec\ell-\bar\chi\vec k_\bot)\cdot\vec\theta}
-        \int\ud^2\vec\theta' e^{-i(\vec\ell'-\bar\chi\vec k_\bot)\cdot\vec\theta'}
-        \\
-    &=
-        \int\frac{\ud^3\vec k}{(2 \pi)^3} 
-        e^{i k_\parallel (\chi - \chi')} P(\sqrt{k_\parallel^2 + k_\bot^2}, \bar\chi)
-        (2\pi)^4 \delta^2(\vec\ell - \bar\chi \vec k_\bot)
-        \delta^2(\vec\ell' - \bar\chi\vec k_\bot)
-        \\
-    &=
-        \int_{-\infty}^\infty\frac{\ud k_\parallel}{(2 \pi)} 
-        e^{i k_\parallel (\chi - \chi')}
-        P(\sqrt{k_\parallel^2 + \ell^2/\bar\chi^2}, \bar\chi)
-        \frac{(2\pi)^2\delta^2(\vec\ell' - \vec \ell)}{\bar\chi^2}
-        \\
-C_\ell(\chi, \chi')
-    &= \frac{1}{\bar\chi^2}
-        \int_{-\infty}^\infty\frac{\ud k_\parallel}{(2 \pi)} 
-        e^{i k_\parallel (\chi - \chi')}
-        P(\sqrt{k_\parallel^2 + \ell^2/\bar\chi^2}, \bar\chi)
-\end{align}
-Which is valid for $\ell \gg 1$ and $\chi - \chi' \ll \bar\chi$.
-$\bar \chi \equiv (\chi + \chi') /2$
-
-Or for flat sky and small angles:
-\begin{align}
-C^{dd}_\ell(\chi,\chi') 
-    &=
-    \int_0^\chi\ud\chi''
-    \int_0^{\chi'}\ud\chi'''
-    \frac{1}{\bar\chi^{\prime 2}}
-    \int_{-\infty}^\infty\frac{\ud k_\parallel}{(2 \pi)} 
-    e^{i k_\parallel (\chi'' - \chi''')}
-    P_{ee}(\sqrt{k_\parallel^2 + \ell^2/\bar\chi^2}, (\chi'' + \chi''')/2)
-    \\
-    &\approx
-    \int_0^\chi\ud\chi''
-    \int_0^{\chi'}\ud\chi'''
-    \frac{1}{\bar\chi^{\prime 2}}
-    \int_{-\infty}^\infty\frac{\ud k_\parallel}{(2 \pi)} 
-    e^{i k_\parallel (\chi'' - \chi''')}
-    P_{ee}(\ell/\bar\chi', (\chi'' + \chi''')/2)
-    \\
-    &=
-    \int_0^\chi\ud\chi''
-    \int_0^{\chi'}\ud\chi'''
-    \frac{1}{\bar\chi^{\prime 2}}
-    \delta(\chi'' - \chi''')
-    P_{ee}(\ell/\bar\chi', (\chi'' + \chi''')/2)
-    \\
-    &=
-    \int_0^{\min(\chi,\chi')}\ud\chi''
-    \left(\frac{1}{\chi''}\right)^2
-    P_{ee}(\ell/\chi'', \chi'')
-\end{align}
-where the second line applies Limber's approximation. 
-$\bar\chi' \equiv (\chi'' + \chi''')/2$.
-
-Or under Limber:
-\begin{align}
-C^{dx}_\ell(\chi,\chi')
-    &=
-    \int_0^\chi\ud\chi''
-    \frac{1}{\bar\chi^{\prime 2}}
-    \delta(\chi'' - \chi')
-    P_{ex}(\ell/{\bar\chi'}, (\chi'' + \chi')/2)
-    \\
-    &=
-    \left(\frac{1}{\chi'}\right)^2
-    P_{ex}(\ell/\chi', \chi')
-    \qquad \textrm{if $\chi' < \chi$ and 0 otherwise.}
-%    \\
-%C^{dx}_\ell(\chi,\chi') + C^{xd}_\ell(\chi,\chi')
-%    &=
-%    \left(\frac{1}{\chi^m}\right)^2
-%    P_{ex}(\ell/\chi^m, \chi_m)
-\end{align}
-
-Accumulating all terms for Limber and assuming a linear bias model:
-\begin{align}
-C^{ss}_\ell(\chi, \chi') =&~
-    \left(\frac{b_f - b_e }{\bar\chi}\right)^2
-        \int_{-\infty}^\infty\frac{\ud k_\parallel}{(2 \pi)} 
-        e^{i k_\parallel \Delta\chi}
-        P(\sqrt{k_\parallel^2 + \ell^2/\bar\chi^2}, \bar\chi)
-    \nonumber \\ &+
-    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi_m}
-    + \frac{2}{\chi_m} \right)^2
-    b_e^2 \int_0^{\chi_m}\ud\chi''
-    \frac{1}{\chi^{\prime\prime 2}}
-        P(\ell/\chi'',\chi'')
-    \nonumber \\ &+
-    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi_m}
-    + \frac{2}{\chi_m} \right)
-    \frac{b_e(-b_f + b_e)}{\chi_m^2}
-        P(\ell/\chi_m, \chi_m)
-\end{align}
-where $\chi_m \equiv \min(\chi, \chi')$.
-
-\end{widetext}
-
 \end{document}

### 2015-05-14 writeup/dm_space_distortions.tex
Some text.

@@
 
-\renewcommand{\section}[1]{\emph{#1}---\ignorespaces}
+% Command to consume spaces and newlines.  Used to PRL style sections.
+\makeatletter
+\def\ignorespacesandimplicitepars{%
+  \begingroup
+  \catcode13=10
+  \@ifnextchar\relax
+    {\endgroup}%
+    {\endgroup}%
+}
+
+\makeatletter
+
+\renewcommand{\section}[1]{\emph{#1}---\ignorespacesandimplicitepars}
 \renewcommand{\subsection}[1]{}
@@
     originating from cosmological distances.  The rate of fast radio bursts
-    has been estimated to be as high as 10\,000 per sky per day.  If
+    has been estimated to be several thousand over the whole sky per day.  If
     cosmological, these events should trace the large-scale structure of the
@@
     clustering can be studied in three dimensions. Due to inhomogeneities in
-    the plasma's density dispersion measure is an imperfect proxy or radial
+    the plasma's density dispersion measure is an imperfect proxy for radial
     distance and we show that this leads to additional clustering terms---the
@@
 \section{Introduction}
+
 The clustering of matter on large scales has been
@@
 Traditionally the redshift of spectral lines caused by the Hubble flow has
-been employed to measure position in the radial direction. Such redshift
+been employed to measure radial distance. Such redshift
 surveys have now aggregated the positions of millions of galaxies into three
-dimensional density maps exposing a rich structure of clusters, filaments,
+dimensional density maps, exposing a rich structure of clusters, filaments,
 walls and voids.
 
+% This paragraph needs to be reorganized.
 However, redshift is not the only measure of radial distance. In particular,
@@
 is readily measured from fast radio bursts (FRB) which are a class
-of radio transient first reported in \citet{lorimer}. The dispersion measure
+of radio transient first reported in \citet{lorimer}. There have since been 
+\ldots such bursts detected \citep{all_bursts} and total rate of bursts
+been estimated to be \ldots. The dispersion measure
 (DM) is a line-of-site integral of the free electron density and can thus be
 used as a distance estimate.
-% IF COSMOLOGICAL!!
+If the progenitors of these bursts are at cosmological distances, with the
+majority of the dispersion caused by electrons in the inter-galactic medium,
+then the average DM-distance relation can be modelled \citep{someone}.
 
-Neither redshift or dispersion measure are perfect proxies for radial distance.
+Neither redshift nor dispersion measure are perfect proxies for radial distance.
 Redshifts are systematically biased by the peculiar velocities of the object
@@
 space which was first calculated by \citet{kaiser} using linear theory.
-
 Similarly, distance estimates from dispersion measure will be biased by
@@
 clustering of sources in dispersion measure space.  In this letter we calculate
-these DM space distortions and shaw that they could 
-be usefully measured in a
-survey detecting as few as 10\,000 fast radio bursts.
+these DM space distortions and consider the detectability of the signal by
+upcoming surveys.
 
-\section{Density perturbations in dispersion measure space}
+%\section{Density perturbations in dispersion measure space}
+\section{Clustering in dispersion measure space}
+
 The dispersion measure of a signal observed in some angular direction $\hat{n}$ and
@@
 
-\section{Two-point statistics}
+%\section{Two-point statistics}
+
 Large-scale structure is usually studied through it two-point statistics, most
@@
 assumed). With these approximations we have
-\begin{comment}
-\begin{align}
-C^{ss}_\ell(\chi, \chi') \approx&~
-    \frac{1}{\bar\chi^2}
-        \int_{-\infty}^\infty\frac{\ud k_\parallel}{(2 \pi)} 
-        e^{i k_\parallel (\chi - \chi')}
-        P_{[ee + ff - 2ef]}
-        (\sqrt{k_\parallel^2 + \ell(\ell + 1)/\bar\chi^2}, \bar\chi)
-        %\left[
-        %P_{ee}(\sqrt{k_\parallel^2 + \ell^2/\bar\chi^2}, \bar\chi)
-        %+ P_{ff}(\sqrt{k_\parallel^2 + \ell^2/\bar\chi^2}, \bar\chi)
-        %- 2 P_{ef}(\sqrt{k_\parallel^2 + \ell^2/\bar\chi^2}, \bar\chi)
-        %\right]
-    \nonumber \\ &+
-    %\left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi}
-    %+ \frac{2}{\chi} \right)
-    %\left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi'}
-    %+ \frac{2}{\chi'} \right)
-    A(\chi) A(\chi')
-    \int_0^{\chi_{\rm min}}\ud\chi''
-    \frac{1}{\chi^{\prime\prime 2}}
-    P_{ee}((\ell + 1/2)/\chi'',\chi'')
-    \nonumber \\ &+
-    %\left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi_{\max}}
-    %+ \frac{2}{\chi_{\max}} \right)
-    \frac{A(\chi_{\max})}{\chi_{\min}^2}
-    P_{[ee - ef]}((\ell + 1/2)/\chi_{\min}, \chi_{\min}),
-        %\left[
-        %    P_{ee}(\ell/\chi_{\min}, \chi_{\min})
-        %    - P_{fe}(\ell/\chi_{\min}, \chi_{\min})
-        %\right],
-\end{align}
-\end{comment}
 \begin{align}
@@
     P_{[ee - ef]}(\nu/\chi_{\min}, \chi_{\min}),
+    \label{e:Clss_limber}
 \end{align}
@@
 \section{Modeling and measurement}
+
 There are a number of effects that will complicate the measurement of the
@@
 by independent data such as observations of pulsars.  As such, the local
-contribution is unlikely to be a limiting obstacle.
+contribution is unlikely to be a limiting obstacle. \red{cite geansler paper?}
 
 More concerning is the dispersion from the burst progenitor's environment
-as well as the halo in which it resides.
+as well as the halo in which it resides. These electrons will presumably be
+clustered around the burst progenitor on scales far smaller than DM space
+structure maps and thus are not accounted for in the $\delta_e$--$\delta_f$
+correlations included in the above formalism.  This will have a mean
+contribution, common to all bursts and which may be epoch dependant, which will
+modify the mean DM--distance relation. This will need to be calibrated in some
+why or else fit with nuisance parameters during parameter estimation.  There
+will also be a stochastic piece which varies from burst to burst.  This will
+limit the precision at which $\chi_s$ can be measured, thus limiting the
+resolution of DM space density maps in the radial direction.
+
+Detailed treatment of these complications is beyond the scope of the current
+work. The magnitude of the contribution from the progenitor is at present
+unconstrained by data. To crudely deal with it here we use relatively large 
+$\chi$ bins of $100\,{\rm MPc}/h$ in sensitivity estimates.
+
+The second term in Equation~\ref{e:Clss_limber} is an integral that mixes
+many spacial scales, small scales from smaller radial distance and larger
+scales from greater distances. The mixing of scales complicates the
+interpretation of measurements, since structure formation on scales smaller
+than $\sim10\,{\rm MPc}/h$ is non-linear and hard to model. A similar issue
+exists in the field of weak gravitational lensing, where the formula for the
+angular power spectrum has a similar form.  However in lensing a kernel in
+the line-of-sight integral, arising from geometric effects, suppresses the
+contribution from small distances, partially alleviating the issue.
+
+There is an advantage to the lack of kernel in the DM space integral term.
+Lensing tomography---the use of sources at multiple redshifts to unmix
+spatial scales---is complicated by the kernel. The kernel's shape depends on
+the source redshift, reweighting the line of sight and
+making tomography inexact.  In contrast the integrand in the integral
+term is completely independent of the limit of integration, meaning
+contributions from different parts of the line of sight (and thus different
+spatial scales) can be separated exactly. Again, a detailed study of DM space
+tomography is beyond the scope of this work.  The avoid our results being
+sensitive to the hard-to-model small scales, we assume that the contribution to the
+integral term from radial distances $\chi'' < 500\,{\rm MPc}/h$ are well
+measured by the correlations with these radial slices. We thus neglect the
+information from these slices in our sensitivity measurements and ignore
+contributions to the integral term from below this distance. The smallest
+spatial scale that contributes the our plotted angular power spectra out to
+$\ell=1000$ is thus $k=2\,h/{\rm MPc}$.
 
@@
 
-In this section we discuss some systematic effects that would affect a real
-survey of dispersion measures, complicating measurement. We then estimate the
-sensitivity of such a survey.
-
-\subsection{Systematics}
-
-DM contribution intrinsic to the source will have a few effects: There will be
-an offset which will change the DM-distance relation in some way that can
-hopefully be characterized. Also there will be a stochastic piece which will
-smear out DM-distance relations and limit the effective width of the radial
-shells. Detailed consideration of these effects is beyond the scope of this
-work but to crudely deal with this, we don't consider any $\chi - \chi'$
-smaller than \red{$100\,{\rm MPc}/h$}.
-
-Contributions from local Universe probably not an issue. Can be measure by
-other means and subtracted off.
-
-Tomography is exact.  Get excellent separation of scales, unlike lensing.
-The integral over $\chi$ couples many scales. In particular small scales (which
-are difficult to model) will
-be coupled to large angular scales by screens near the observer.  However
-because tomography is exact, it would be possible to set up estimators that
-decouple these scales, for instance by estimating the difference in power
-between radial shells.  For this reason we start all radial integrals as
-$\chi = 500\,{\rm MPc}/h$, which saves us from the difficulties in modelling the
-small scale power.
-
-\subsection{Detectability}
-
-Here we present sensitivity estimates for a survey \ldots
-
-We assume that the survey will be shot noise dominated as would be the case for
-an initial detection.  The noise powerspectrum on a shells with of width
+In first measurements of the angular power spectra, uncertainty will be
+dominated by the finite number of observed dispersion measures, or shot noise.
+The noise power spectrum on a shells with of width
 $\Delta \chi$ is
@@
 
-To give an idea of the sensitivity of the survey, we collapse
+Here we consider the sensitivity of a survey with a total of $10^4$ dispersion
+measures from FRBs distributed uniformly over half the sky. This is in rough
+approximation to what could be achieved by the Canadian Hydrogen Intensity
+Mapping Experiment's now funded FRB instrument over a three year survey
+\citep{who}.
+To give an idea of the overall sensitivity of the survey, we collapse
 $C^{ss}_{\ell,ij}$ to a single function of $\ell$ by taking a weighted average
@@
 range $500\,{\rm MPc}/h$ to $3500\,{\rm MPc}/h$.
-For weights in the radial bin average, we use the signal to uncertainty-squared
-at $\ell=100$, which extracts all the signal to noise at that $\ell$ and much
-of it at other multipoles.
-We exclude the $i = j$ bin pairs due to
-the presumed observational complications discussed in the previous section.
-This effectively discards the contribution from the local term. This is shown
+For weights in the radial bin average, we use the signal to noise-squared
+at $\ell=100$, which maximizes the signal to noise at that $\ell$ and
+is near optimal at other multipoles.
+We exclude the $i = j$ bin pairs
+as they would be contaminated by noise bias in a real survey.
+This effectively discards the contribution from the local term. The result is shown
 in Figure~\ref{f:sensitivity}.

### 2015-05-18 writeup/dm_space_distortions.tex
Polished figures.

@@
 \usepackage{afterpage}
+\usepackage{epstopdf}
 
@@
 \renewcommand{\subsection}[1]{}
+
+\input{AAS_macros.tex}
 
@@
 is readily measured from fast radio bursts (FRB) which are a class
-of radio transient first reported in \citet{lorimer}. There have since been 
-\ldots such bursts detected \citep{all_bursts} and total rate of bursts
-been estimated to be \ldots. The dispersion measure
+of radio transient first reported in \citet{2007Sci...318..777L}.
+There have since been 
+10 such bursts detected \citep{2012MNRAS.425L..71K,2013Sci...341...53T, 2014ApJ...790..101S, 2014ApJ...792...19B, 2015MNRAS.447..246P,2015ApJ...799L...5R} and total rate of bursts
+been estimated to be $3.3^{+5}_{-2.5} \times 10^3$
+per sky per day \cite{2015arXiv150500834R}. 
+The dispersion measure
 (DM) is a line-of-site integral of the free electron density and can thus be
@@
 majority of the dispersion caused by electrons in the inter-galactic medium,
-then the average DM-distance relation can be modelled \citep{someone}.
+then the average DM-distance relation can be modelled
+\citep{2004MNRAS.348..999I, 2003ApJ...598L..79I}.
 
@@
 in redshift
-space which was first calculated by \citet{kaiser} using linear theory.
+space which was first calculated by \citet{1987MNRAS.227....1K}
+using linear theory.
 Similarly, distance estimates from dispersion measure will be biased by
-inhomogeneities in the electron density, again leading to additional apparent
+inhomogeneities in the electron density \citep{2014ApJ...780L..33M},
+again leading to additional apparent
 clustering of sources in dispersion measure space.  In this letter we calculate
@@
 We wish to relate the density of a tracer $f$ measured in DM space to its
-density in real space. We follow the derivation in \citet{Kaiser} of the
+density in real space. We follow the derivation in \citet{1987MNRAS.227....1K}
+of the
 redshift space distortions. Start by noting that the total number of tracers
@@
 \begin{equation}
+    \label{e:A}
     A(\chi) \equiv \frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi}
@@
 Equation~\ref{e:Clss} can be simplified substantially by adopting the small
-angle and Limber approximations \citep{extened_limber}.  The small angle
+angle and Limber approximations \citep{1953ApJ...117..134L,
+1992ApJ...388..272K, 1998ApJ...498...26K}.  The small angle
 approximation eliminates the $k$ integral over spherical Bessel functions, replacing it
@@
 vector contribute to the radial integrals and is valid if the power spectra
-evolve slowly compared to the correlation length (which has already been
+evolve slowly compared to the correlation length \citep{2008PhRvD..78l3506L}
+(which has already been
 assumed). With these approximations we have
@@
 measured. In addition, this function could in principal be well characterized
-by independent data such as observations of pulsars.  As such, the local
-contribution is unlikely to be a limiting obstacle. \red{cite geansler paper?}
+by independent data such as observations of pulsars.  As such, it should be
+possible to subtract the local
+contribution, as was done in
+\citet{2014arXiv1412.4829D}, and this is unlikely to be a limiting obstacle.
 
@@
 as well as the halo in which it resides. These electrons will presumably be
-clustered around the burst progenitor on scales far smaller than DM space
+clustered around the burst progenitor on scales far smaller than DM-space
 structure maps and thus are not accounted for in the $\delta_e$--$\delta_f$
@@
 
-There is an advantage to the lack of kernel in the DM space integral term.
+There is an advantage to the lack of kernel in the DM-space integral term.
 Lensing tomography---the use of sources at multiple redshifts to unmix
@@
 \begin{figure}
-    \includegraphics[scale=0.42]{"figures/n_f"}
+    \includegraphics[scale=0.42]{figures/n_f}
     \caption{
         \label{f:n_f}
-        \red{Need to fix normalization of top panel.}
+        \emph{Top:} Comoving density of sources for toy model, as given in
+        Equation~\ref{e:n_f}. Normalization is
+        such that the survey has a total of $10^4$ FRBs.
+        \emph{Bottom:} Coefficient $A(\chi)$ (defined in Equation~\ref{e:A})
+        in toy model.
     }
@@
 \begin{figure}
-    \includegraphics[scale=0.42]{"figures/terms"}
+    \includegraphics[scale=0.42]{figures/terms}
     \caption{
@@
 approximation to what could be achieved by the Canadian Hydrogen Intensity
-Mapping Experiment's now funded FRB instrument over a three year survey
-\citep{who}.
+Mapping Experiment's now funded FRB instrument over a three year survey.
 To give an idea of the overall sensitivity of the survey, we collapse
@@
 range $500\,{\rm MPc}/h$ to $3500\,{\rm MPc}/h$.
-For weights in the radial bin average, we use the signal to noise-squared
+For weights in the radial bin average, we use the signal over noise-squared
 at $\ell=100$, which maximizes the signal to noise at that $\ell$ and
@@
 \begin{figure}
-    \includegraphics[scale=0.42]{"figures/sensitivity"}
+    \includegraphics[scale=0.42]{figures/sensitivity}
     \caption{
@@
 
-\bibliography{dm_space}
+\bibliography{refs}
 

### 2015-05-18 python/assemble_terms.py

@@ -3,6 +3,7 @@ import numpy as np
 from scipy import special, integrate, interpolate
 from cora.util.cosmology import Cosmology
 import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
 import matplotlib
 
 import matter_power
@@ -104,7 +105,7 @@ def get_mult_ell(ells=None, limber=True):
 
 
 def my_plots(mult_ell=None, chi=1000):
-    matplotlib.rcParams.update({'font.size': 14,
+    matplotlib.rcParams.update({'font.size': 16,
                                 'text.usetex' : False,
                                 'figure.autolayout': True})
 
@@ -125,7 +126,7 @@ def my_plots(mult_ell=None, chi=1000):
     title = "$\\bar\\chi=%d\\,\\rm{MPc}/h$, $\\Delta\\chi=%d\\,\\rm{MPc}/h$"
     
     for delta in DELTAS:
-        plt.figure()
+        plt.figure(tight_layout=True)
         plot_spectra(mult_ell, CHI, delta, **kwargs)
         plt.ylim([Y_MIN, Y_MAX])
         plt.xlim([X_MIN, X_MAX])
@@ -146,7 +147,7 @@ def my_plots(mult_ell=None, chi=1000):
     D1 = 10.
     D2 = 50.
 
-    plt.figure()
+    plt.figure(tight_layout=True)
     plot_spectra(mult_ell, chi, D1, **kwargs)
     plt.ylim([Y_MIN, Y_MAX])
     plt.xlim([X_MIN, X_MAX])
@@ -158,6 +159,7 @@ def my_plots(mult_ell=None, chi=1000):
                )
     plt.legend(loc="upper right", labelspacing=.1, frameon=False)
     plot_spectra(mult_ell, chi, D2, local_only=True, **kwargs)
+    plt.savefig('terms.eps', tightlayout=True, bbox_inches='tight')
 
     # Mean source density plot
     N_TOTAL = 10000
@@ -171,20 +173,22 @@ def my_plots(mult_ell=None, chi=1000):
     norm /= N_TOTAL
     n_bar /= norm
 
-    plt.figure()
-    ax1 = plt.subplot(211)
+    f = plt.figure()
+    grid = gridspec.GridSpec(2, 1, wspace=0.0, hspace=0.0)
+    ax1 = plt.subplot(grid[0])
[…]

### 2015-05-20 writeup/dm_space_distortions.tex
Filled out some text.

@@
 There have since been 
-10 such bursts detected \citep{2012MNRAS.425L..71K,2013Sci...341...53T, 2014ApJ...790..101S, 2014ApJ...792...19B, 2015MNRAS.447..246P,2015ApJ...799L...5R} and total rate of bursts
+10 such bursts reported \citep{2012MNRAS.425L..71K,2013Sci...341...53T, 2014ApJ...790..101S, 2014ApJ...792...19B, 2015MNRAS.447..246P,2015ApJ...799L...5R} and total rate of bursts
 been estimated to be $3.3^{+5}_{-2.5} \times 10^3$
@@
 (DM) is a line-of-site integral of the free electron density and can thus be
-used as a distance estimate.
-If the progenitors of these bursts are at cosmological distances, with the
-majority of the dispersion caused by electrons in the inter-galactic medium,
+used as a distance estimate, as is routinely done for galactic pulsars.
+Because FRBs are observed to have dispersion measures greatly in excess of
+the galactic expectation they must be of extra-galactic origin, with their
+dispersion produced either by
+inter-galactic medium (IGM) \citep{2013Sci...341...53T} or the
+environment of the source
+\citep{2014ApJ...785L..26L,2015arXiv150101341P}.
+If the dispersion is dominated by the inter-galactic medium, then 
  then the average DM-distance relation can be modelled
-\citep{2004MNRAS.348..999I, 2003ApJ...598L..79I}.
+\citep{2004MNRAS.348..999I, 2003ApJ...598L..79I} and the sources are at
+cosmological distances of a few gigaparsecs. This would permit
+the study of the clustering of FRBs in three dimensions which should trace the
+large-scale structure of the Universe on linear scales.
 
@@
 
-Large-scale structure is usually studied through it two-point statistics, most
+Large-scale structure is usually studied through its two-point statistics, most
 commonly the power-spectrum, $P(k)$.
@@
 We will instead use $C^{ss}_\ell(\chi,\chi')$, which is
-the cross-correlation angular power-spectrum of the DM space over-density
+the cross-correlation angular power-spectrum of the DM space over-density,
 on shells at $\chi$ and $\chi'$.
@@
 \gtrsim 10$
-and use this form for the remainder of the paper.
+and use this form for the remainder of the paper. In the above equation we dub
+the three terms the `local', `integral' and `cross' terms respectively and will
+refer to them as such for the remainder of this work.
 
@@
 
-Description of the input power-spectra, $\bar n_f$ and figures.
-Figure~\ref{f:n_f}, Figure~\ref{f:terms}.
+For plotting the DM space power-spectra we use a toy model for the electron and
+FRB clustering that assumes both are biased tracers of the dark matter,
+\emph{i.e.}~$P_{xy}(k)=b_x b_y P(k)$.  We
+calculate the time dependant dark matter power-spectrum using {\tt CAMB} using
+the integrated {\tt HALOFIT} to approximate the non-linear evolution. We assume
+that the electron bias $b_e=1$, which should be true on large scales due to
+approximate conservation of free electrons. The bias of FRB sources is
+unconstrained by data and we choose it to be $b_f=1.3$. The coefficient
+$A(\chi)$ depends on the density of detected FRB sources, $\bar n_f(\chi)$.
+We use a simple model where all events above a fixed flux are detected,
+the intrinsic luminosity function has the
+\citet{1976ApJ...203..297S} form with index $-1$, and events at the cut off of the
+luminosity function and at
+a radial distance of $\chi=2350\,{\rm MPc}/h$ are at the detection threshold.
+This source density is shown in Figure~\ref{f:n_f} with the resulting DM-space
+power-spectrum in Figure~\ref{f:terms}.
 
@@
         \label{f:n_f}
-        \emph{Top:} Comoving density of sources for toy model, as given in
-        Equation~\ref{e:n_f}. Normalization is
+        \emph{Top:} Comoving density of sources in toy model, as described in
+        text. Normalization is
         such that the survey has a total of $10^4$ FRBs.
-        \emph{Bottom:} Coefficient $A(\chi)$ (defined in Equation~\ref{e:A})
-        in toy model.
+        \emph{Bottom:} Resulting coefficient $A(\chi)$ as given in
+        Equation~\ref{e:A}.
     }
@@
         Terms in the DM-space cross-correlation angular power spectrum.
-        All terms are evaluated at $\bar\chi=1000\,{\rm MPc}/h$ and 
+        All terms are evaluated at $\bar\chi=2000\,{\rm MPc}/h$ and 
         $\chi - \chi' = 10\,{\rm MPc}/h$, except the lowest most 
@@
         the other two terms are highly insensitive to the separation of
-        the radial slices, the local term drops rapidly at high separations.
+        the radial slices, the local term drops rapidly with separation.
     }
@@
 
+I can be seen in Figure~\ref{f:terms} that the integral term dominates the
+cross term and the local term except at small radial separations.  We've found
+that this is generically true for most $(\chi, \chi')$ pairs and that the
+sensitivity shown in Figure~\ref{f:sensitivity} is dominated by the integral
+term. Since the integral term only depends on the clustering of electrons, not
+sources, an FRB survey could be used to study the distribution of electrons and
+potentially solve the `missing baryon problem' as pointed out in
+\citet{2014ApJ...780L..33M}.
+
+We have calculated the clustering of sources in dispersion measure space and
+shown that a survey detecting a modest $10^4$ fast radio bursts of cosmological
+origin could detect the clustering signal.
+
+Looking forward, DM-space
+clustering could become a powerful probe of large-scale structure should
+observational factors turn out to be favourable compared to spectroscopic
+surveys. The baryon acoustic oscillation feature can be clearly seen in
+Figure~\ref{f:terms} in the cross term and both
+local-term curves. It might even be possible to extract it from the integral
+term using tomography.
+This however depends on the contribution to dispersion measure from
+the source's environment and host halo to be modest compared to the
+contribution from the IGM.
+
 \begin{acknowledgments}

### 2015-05-20 python/assemble_terms.py

@@ -10,11 +10,11 @@ import matter_power
 import angular_terms
 
 # Redshift at which we can detect event of luminocity L*.
-Z_STAR = 0.8
-ALPHA = -0.7
+Z_STAR = 1.
+ALPHA = -1.
 
 B_E = 1.0
-B_F = 0.7
+B_F = 1.3
 
 
 def d_ln_n(chi):
@@ -83,8 +83,8 @@ def plot_spectra(mult_ell, chi, delta, local_only=False, **kwargs):
     else:
         plt.loglog(ells, trans(t1 + t2 + t3), '-k', label='total', **kwargs)
         plt.loglog(ells, trans(t1), '--b', label='local term', **kwargs)
-        plt.loglog(ells, trans(t2), '-.g', label='cross term', **kwargs)
         plt.loglog(ells, trans(t3), ':r', label='integral term', **kwargs)
+        plt.loglog(ells, trans(t2), '-.g', label='cross term', **kwargs)
 
 
 def get_ells():
@@ -114,8 +114,8 @@ def my_plots(mult_ell=None, chi=1000):
     CHI = float(chi)
     #DELTAS = [5., 10., 20., 50., 100.]
     DELTAS = []
-    Y_MIN = 1e-7
-    Y_MAX = 1e-4
+    Y_MIN = 5e-8
+    Y_MAX = 5e-5
     X_MIN = 9
     X_MAX = 1001
     

### 2015-05-20 writeup/dm_space_distortions.tex
Many edits.

@@
-\documentclass[twocolumn,prl,nofootinbib]{revtex4-1}
+\documentclass[twocolumn,prl,nofootinbib,floatfix]{revtex4-1}
 \usepackage{graphicx}
@@
 The clustering of matter on large scales has been
-heralded as the next great probe the Universe after the cosmic microwave
+heralded as the next great probe of the Universe after the cosmic microwave
 background (CMB). The large-scale structure in principle contains far more
-information than the CMB, because it can be studied in three dimensions.
-Traditionally the redshift of spectral lines caused by the Hubble flow has
-been employed to measure radial distance. Such redshift
+information than the CMB because it can be studied in three dimensions.
+Traditionally the redshift of spectral lines, caused by the Hubble flow, has
+been employed to measure radial distance and provide the third dimension.
+Such redshift
 surveys have now aggregated the positions of millions of galaxies into three
@@
 
-% This paragraph needs to be reorganized.
 However, redshift is not the only measure of radial distance. In particular,
@@
 There have since been 
-10 such bursts reported \citep{2012MNRAS.425L..71K,2013Sci...341...53T, 2014ApJ...790..101S, 2014ApJ...792...19B, 2015MNRAS.447..246P,2015ApJ...799L...5R} and total rate of bursts
+10 such bursts reported
+\citep{2012MNRAS.425L..71K,2013Sci...341...53T,
+2014ApJ...790..101S, 2014ApJ...792...19B, 
+2015MNRAS.447..246P,2015ApJ...799L...5R} and total rate of bursts
 been estimated to be $3.3^{+5}_{-2.5} \times 10^3$
@@
 (DM) is a line-of-site integral of the free electron density and can thus be
-used as a distance estimate, as is routinely done for galactic pulsars.
+used as a distance estimate, as is routinely done with galactic pulsars.
 Because FRBs are observed to have dispersion measures greatly in excess of
@@
 clustering of sources in dispersion measure space.  In this letter we calculate
-these DM space distortions and consider the detectability of the signal by
+these DM-space distortions and consider the detectability of the signal by
 upcoming surveys.
@@
 $\vec x_s$ inferred from the dispersion measure assuming that the electrons are
-homogenious. This only affect the radial coordinate such that $\vec x_s = \hat
+homogeneous. This only affect the radial coordinate such that $\vec x_s = \hat
 n \chi_s$ with $\chi_s$ defined by the equation
@@
 \end{equation}
-Averaged over the sky, the density should be the same in DM 
-space as in real space,
+Averaged over the sky, $\langle \chi_s \rangle = \chi$ and thus `the density should
+be the same in DM space as in real space,
 \begin{equation}
@@
     &= \bar{n}_{f}(\chi)
-       + \frac{\ud \bar{n}_f}{\ud \chi}\int_0^\chi \ud \chi' \delta_e(\hat n \chi')
+       + \frac{\ud \bar{n}_f}{\ud \chi}\int_0^\chi \ud \chi' \delta_e(\hat n
+       \chi').
        \label{e:nfs}
@@
     &\approx 1 - \delta_e
-        - \frac{2}{\chi}\int_0^\chi \ud \chi' \delta_e(\hat n \chi')
+        - \frac{2}{\chi}\int_0^\chi \ud \chi' \delta_e(\hat n \chi').
         \label{e:jac}
@@
 caused by a misinterpretation of angular distances when the radial distance is
-mis measured.  Both terms are in-principle present in redshift space but are
+mismeasured.  In both cases analogous terms are in principle present in 
+redshift space but are
 negligible. Because radial velocities are only sourced by modes with large
@@
 Large-scale structure is usually studied through its two-point statistics, most
-commonly the power-spectrum, $P(k)$.
+commonly the power spectrum, $P(k)$.
 Unlike in redshift-space distortions, Equation~\ref{e:delta_s} does not have a
@@
 We will instead use $C^{ss}_\ell(\chi,\chi')$, which is
-the cross-correlation angular power-spectrum of the DM space over-density,
-on shells at $\chi$ and $\chi'$.
+the cross-correlation angular power spectrum of the DM-space over density,
+on shells at $\chi$ and $\chi'$:
 \begin{align}
@@
         \delta_{fs}(\hat n' \chi', \chi')
-        \right\rangle
+        \right\rangle.
 \end{align}
@@
 \delta^3(\vec k - \vec k') P_{xy}(k, \chi)$.  If for a moment we ignore time
-dependance, the angular cross power spectrum of such tracers is
+dependence, the angular cross-power spectrum of such tracers is
 \begin{align}
@@
 In reality the power spectrum evolves on the order of a Hubble time.
-The angular cross-correlations will be very small unless $\chi$ and $\chi'$ are
-within a few correlation lengths of one another, roughly a few hundred
+The angular cross correlations will be very small unless $\chi$ and $\chi'$ are
+within a few correlation lengths of one another, roughly a hundred
 megaparsecs.  The evolution of the power-spectrum is negligible over these time
-differences which leads to a straight forward way to include the evolution of
+differences which leads to a straight-forward way to include the evolution of
 the perturbations:
@@
 
-The thrid term in Equation~\ref{e:delta_s} is not stationary but is an integral
+The third term in Equation~\ref{e:delta_s} is not stationary but is an integral
 over the stationary field $\delta_e$.
@@
 the three terms the `local', `integral' and `cross' terms respectively and will
-refer to them as such for the remainder of this work.
+refer to them as such henceforth.
 
-\section{Modeling and measurement}
+\section{Modelling and measurement}
 
@@
 above calculated angular power spectrum by a real survey of dispersion 
-measures.  The first is
+measures.  The first effect is
 that the model that the free electron density decomposes into a homogeneous
-part plus a random field of perturbations is not correct. Firstly, all signals
-must pass through the Milky Way's galactic disk, halo and local environment
+part plus a random field of perturbations is not complete. Firstly, all signals
+must pass through the Milky Way's galactic disk, halo, and local environment,
 which will contribute to the dispersion measure. However, this is only a
 single function of $\hat n$  which can presumably be well
-measured. In addition, this function could in principal be well characterized
+measured. In addition, this function could in principle be well characterized
 by independent data such as observations of pulsars.  As such, it should be
@@
 
-More concerning is the dispersion from the burst progenitor's environment
+More concerning is the dispersion from the source's environment
 as well as the halo in which it resides. These electrons will presumably be
-clustered around the burst progenitor on scales far smaller than DM-space
-structure maps and thus are not accounted for in the $\delta_e$--$\delta_f$
+clustered around the source on scales far smaller than DM-space
+structure map pixels and thus are not accounted for in the $\delta_e$--$\delta_f$
 correlations included in the above formalism.  This will have a mean
-contribution, common to all bursts and which may be epoch dependant, which will
+contribution, common to all sources and which may be epoch dependant, which will
 modify the mean DM--distance relation. This will need to be calibrated in some
 why or else fit with nuisance parameters during parameter estimation.  There
-will also be a stochastic piece which varies from burst to burst.  This will
+will also be a stochastic piece which varies from source to source.  This will
 limit the precision at which $\chi_s$ can be measured, thus limiting the
@@
 work. The magnitude of the contribution from the progenitor is at present
-unconstrained by data. To crudely deal with it here we use relatively large 
+unknown. To crudely deal with it here we use relatively large 
 $\chi$ bins of $100\,{\rm MPc}/h$ in sensitivity estimates.
@@
 The second term in Equation~\ref{e:Clss_limber} is an integral that mixes
-many spacial scales, small scales from smaller radial distance and larger
+many spatial scales, small scales from smaller radial distance and larger
 scales from greater distances. The mixing of scales complicates the
@@
 exists in the field of weak gravitational lensing, where the formula for the
-angular power spectrum has a similar form.  However in lensing a kernel in
+angular power spectrum has a similar form.  In lensing a kernel in
 the line-of-sight integral, arising from geometric effects, suppresses the
@@
 spatial scales---is complicated by the kernel. The kernel's shape depends on
-the source redshift, reweighting the line of sight and
-making tomography inexact.  In contrast the integrand in the integral
+the source redshift, reweighting the line of sight integral and
+making tomography inexact.  In contrast the integrand in the DM-space integral
 term is completely independent of the limit of integration, meaning
@@
 spatial scales) can be separated exactly. Again, a detailed study of DM space
-tomography is beyond the scope of this work.  The avoid our results being
+tomography is beyond the scope of this work.  To avoid our results being
 sensitive to the hard-to-model small scales, we assume that the contribution to the
@@
 
-For plotting the DM space power-spectra we use a toy model for the electron and
-FRB clustering that assumes both are biased tracers of the dark matter,
+For plotting the DM-space power spectra we use a toy model for the electron and
+FRB clustering that assumes both are biased tracers of the dark matter:
 \emph{i.e.}~$P_{xy}(k)=b_x b_y P(k)$.  We
-calculate the time dependant dark matter power-spectrum using {\tt CAMB} using
+calculate the time dependant dark-matter power spectrum using {\tt CAMB} using
 the integrated {\tt HALOFIT} to approximate the non-linear evolution. We assume
-that the electron bias $b_e=1$, which should be true on large scales due to
+that the electron bias is $b_e=1$, which should be true on large scales due to
 approximate conservation of free electrons. The bias of FRB sources is
@@
 luminosity function and at
-a radial distance of $\chi=2350\,{\rm MPc}/h$ are at the detection threshold.
+a radial distance of $\chi=2350\,{\rm MPc}/h$ are at the flux detection threshold.
 This source density is shown in Figure~\ref{f:n_f} with the resulting DM-space
@@
 
-I can be seen in Figure~\ref{f:terms} that the integral term dominates the
+It can be seen in Figure~\ref{f:terms} that the integral term dominates the
 cross term and the local term except at small radial separations.  We've found
@@
 We have calculated the clustering of sources in dispersion measure space and
-shown that a survey detecting a modest $10^4$ fast radio bursts of cosmological
-origin could detect the clustering signal.
-
+shown that a survey detecting $10^4$ fast radio bursts of cosmological
+origin (as might be achieved by the CHIME FRB instrument) could detect the
+clustering signal.
 Looking forward, DM-space
@@
 Figure~\ref{f:terms} in the cross term and both
-local-term curves. It might even be possible to extract it from the integral
+local-term curves. It may also be possible to extract the BAO feature
+from the integral
 term using tomography.
-This however depends on the contribution to dispersion measure from
+This however requires that the contribution to dispersion measure from
 the source's environment and host halo to be modest compared to the

### 2015-05-26 writeup/dm_space_distortions.tex
Many edits.

@@
 
-\title{The large scale clustering in dispersion measure space}
+\title{The large-scale structure of the Universe in dispersion measure space}
 
@@
     has been estimated to be several thousand over the whole sky per day.  If
-    cosmological, these events should trace the large-scale structure of the
-    Universe in some way. Furthermore, because the dispersion measure (DM) can be
+    cosmological, the sources of these events should trace the large-scale
+    structure of the
+    Universe. Furthermore, because the dispersion measure (DM) can be
     used as a proxy for radial distance (like redshift),
     clustering can be studied in three dimensions. Due to inhomogeneities in
-    the plasma's density dispersion measure is an imperfect proxy for radial
+    the plasma's density, dispersion measure is an imperfect proxy for radial
     distance and we show that this leads to additional clustering terms---the
-    dispersion measure space distortions. We calculate the DM space
+    dispersion-measure-space distortions. We calculate the DM-space
     power spectra for a toy model of electron and FRB clustering and show that
@@
 is readily measured from fast radio bursts (FRB) which are a class
-of radio transient first reported in \citet{2007Sci...318..777L}.
+of radio transient first reported by \citet{2007Sci...318..777L}.
 There have since been 
@@
 used as a distance estimate, as is routinely done with galactic pulsars.
-Because FRBs are observed to have dispersion measures greatly in excess of
-the galactic expectation they must be of extra-galactic origin, with their
-dispersion produced either by
+FRB events are observed to have dispersion measures of order
+$1000\,{\rm pc} / {\rm cm}^3$, greatly in excess of
+the galactic expectation of order $100\,{\rm pc} / {\rm cm}^3$, depending on
+galactic latitude
+\cite{2014arXiv1412.4829D}.
+They must therefore be of extra-galactic origin, with their
+dispersion produced either by the
 inter-galactic medium (IGM) \citep{2013Sci...341...53T} or the
 environment of the source
-\citep{2014ApJ...785L..26L,2015arXiv150101341P}.
-If the dispersion is dominated by the inter-galactic medium, then
-then the average DM-distance relation can be modelled
-\citep{2004MNRAS.348..999I, 2003ApJ...598L..79I} and the sources are at
+\citep{2014ApJ...785L..26L,2015arXiv150101341P,2015arXiv150505535C}.
+If the dispersion is dominated by the inter-galactic medium,
+then the average DM--distance relation can be modelled
+\citep{2014ApJ...797...71Z,2004MNRAS.348..999I, 2003ApJ...598L..79I}
+and the sources are at
 cosmological distances of a few gigaparsecs. This would permit
-the study of the clustering of FRBs in three dimensions which should trace the
+the study of the clustering of FRB sources in three dimensions which should trace the
 large-scale structure of the Universe on linear scales.
@@
 electron density as containing a homogeneous part
-and perturbations
+and perturbations,
 $n_e(\vec x, \chi) = \bar{n}_e(\chi) \left[1 + \delta_e(\vec x, \chi)\right]$.
@@
 $\vec x_s$ inferred from the dispersion measure assuming that the electrons are
-homogeneous. This only affect the radial coordinate such that $\vec x_s = \hat
+homogeneous. This only affects the radial coordinate such that $\vec x_s = \hat
 n \chi_s$ with $\chi_s$ defined by the equation
@@
 
-We wish to relate the density of a tracer $f$ measured in DM space to its
+We wish to relate the density of a tracer, $f$, measured in DM space to its
 density in real space. We follow the derivation in \citet{1987MNRAS.227....1K}
 of the
-redshift space distortions. Start by noting that the total number of tracers
+redshift-space distortions. Start by noting that the total number of tracers
 in a volume element is the same in both spaces:
@@
 \end{equation}
-Averaged over the sky, $\langle \chi_s \rangle = \chi$ and thus `the density should
+Averaged over the sky, $\langle \chi_s \rangle = \chi$ and thus the background
+density should
 be the same in DM space as in real space,
@@
 In the equation above, the $-\delta_e$ term is most analogous to the Kaiser
-redshift space distortions.  It is a dilution of tracers in DM space due to an
-excess of electrons in between the tracers. However we note that this term is isotropic
+redshift-space distortions.  It is a dilution of tracers in DM space due to an
+excess of electrons between the tracers. However we note that this term is isotropic
 in contrast to Kaiser.  This is because any wave vector electron perturbation
 causes DM space distortions, whereas the radial velocities that cause
-redshift space distortions are only sourced by perturbations with radial wave
+redshift-space distortions are only sourced by perturbations with radial wave
 vectors.
@@
 caused by a misinterpretation of angular distances when the radial distance is
-mismeasured.  In both cases analogous terms are in principle present in 
+mis-measured.  In both cases analogous terms are in principle present in 
 redshift space but are
@@
 \end{align}
-The first two term in Equation~\ref{e:delta_s} are stationary. For stationary,
+The first two terms in Equation~\ref{e:delta_s} are stationary. For stationary,
 isotropic, tracers $x$ and $y$ we have 
@@
 correlations included in the above formalism.  This will have a mean
-contribution, common to all sources and which may be epoch dependant, which will
+contribution, common to all sources and which may be epoch dependant, that will
 modify the mean DM--distance relation. This will need to be calibrated in some
@@
 
-Detailed treatment of these complications is beyond the scope of the current
+Detailed treatment of the above complications is beyond the scope of this
 work. The magnitude of the contribution from the progenitor is at present
 unknown. To crudely deal with it here we use relatively large
-$\chi$ bins of $100\,{\rm MPc}/h$ in sensitivity estimates.
+$\chi$ bins of $100\,{\rm Mpc}/h$ in sensitivity estimates.
 
 The second term in Equation~\ref{e:Clss_limber} is an integral that mixes
-many spatial scales, small scales from smaller radial distance and larger
+many spatial scales: small scales from smaller radial distance and larger
 scales from greater distances. The mixing of scales complicates the
 interpretation of measurements, since structure formation on scales smaller
-than $\sim10\,{\rm MPc}/h$ is non-linear and hard to model. A similar issue
+than $\sim10\,{\rm Mpc}/h$ is non-linear and hard to model. A similar issue
 exists in the field of weak gravitational lensing, where the formula for the
-angular power spectrum has a similar form.  In lensing a kernel in
-the line-of-sight integral, arising from geometric effects, suppresses the
+angular power spectrum has a similar form.  In lensing, a kernel in
+the line-of-sight integral arising from geometric effects suppresses the
 contribution from small distances, partially alleviating the issue.
@@
 There is an advantage to the lack of kernel in the DM-space integral term.
-Lensing tomography---the use of sources at multiple redshifts to unmix
+Lensing tomography---the use of sources at multiple redshifts to un-mix
 spatial scales---is complicated by the kernel. The kernel's shape depends on
-the source redshift, reweighting the line of sight integral and
+the source redshift, re-weighting the line-of-sight integral and
 making tomography inexact.  In contrast the integrand in the DM-space integral
@@
 sensitive to the hard-to-model small scales, we assume that the contribution to the
-integral term from radial distances $\chi'' < 500\,{\rm MPc}/h$ are well
+integral term from radial distances $\chi'' < 500\,{\rm Mpc}/h$ are well
 measured by the correlations with these radial slices. We thus neglect the
@@
 spatial scale that contributes the our plotted angular power spectra out to
-$\ell=1000$ is thus $k=2\,h/{\rm MPc}$.
+$\ell=1000$ is thus $k=2\,h/{\rm Mpc}$.
 
@@
 that the electron bias is $b_e=1$, which should be true on large scales due to
-approximate conservation of free electrons. The bias of FRB sources is
+the approximate conservation of free electrons. The bias of FRB sources is
 unconstrained by data and we choose it to be $b_f=1.3$. The coefficient
@@
 luminosity function and at
-a radial distance of $\chi=2350\,{\rm MPc}/h$ are at the flux detection threshold.
+a radial distance of $\chi=2350\,{\rm Mpc}/h$ are at the flux detection threshold.
 This source density is shown in Figure~\ref{f:n_f} with the resulting DM-space
@@
         text. Normalization is
-        such that the survey has a total of $10^4$ FRBs.
+        such that the survey has a total of $10^4$ FRB events.
         \emph{Bottom:} Resulting coefficient $A(\chi)$ as given in
@@
         Terms in the DM-space cross-correlation angular power spectrum.
-        All terms are evaluated at $\bar\chi=2000\,{\rm MPc}/h$ and 
-        $\chi - \chi' = 10\,{\rm MPc}/h$, except the lowest most 
-        ``local term'' curve which is for $\chi - \chi'=50\,{\rm MPc}/h$. 
+        All terms are evaluated at $\bar\chi=2000\,{\rm Mpc}/h$ and 
+        $\chi - \chi' = 10\,{\rm Mpc}/h$, except the lowest most 
+        ``local term'' curve which is for $\chi - \chi'=50\,{\rm Mpc}/h$. 
         While
@@
 dominated by the finite number of observed dispersion measures, or shot noise.
-The noise power spectrum on a shells with of width
+The noise power spectrum on shells with of width
 $\Delta \chi$ is
 \begin{equation}
-    C^N_{\ell, ij} = \frac{\delta_{ij}}{\bar n_f(\chi_i)\chi_i^2\Delta\chi},
+    C^N_{\ell, ij} = \frac{\delta_{ij}}{\bar n_f(\chi_i)\chi_i^2\Delta\chi}.
 \end{equation}
@@
 Here we consider the sensitivity of a survey with a total of $10^4$ dispersion
-measures from FRBs distributed uniformly over half the sky. This is in rough
+measures from FRB events distributed uniformly over half the sky. This is in rough
 approximation to what could be achieved by the Canadian Hydrogen Intensity
@@
 $C^{ss}_{\ell,ij}$ to a single function of $\ell$ by taking a weighted average
-of all pairs of radial bins. We use bin widths of $100\,{\rm MPc}/h$ over the
-range $500\,{\rm MPc}/h$ to $3500\,{\rm MPc}/h$.
+of all pairs of radial bins. We use bin widths of $100\,{\rm Mpc}/h$ over the
+range $500\,{\rm Mpc}/h$ to $3500\,{\rm Mpc}/h$.
 For weights in the radial bin average, we use the signal over noise-squared
@@
 
-It can be seen in Figure~\ref{f:terms} that the integral term dominates the
-cross term and the local term except at small radial separations.  We've found
-that this is generically true for most $(\chi, \chi')$ pairs and that the
-sensitivity shown in Figure~\ref{f:sensitivity} is dominated by the integral
-term. Since the integral term only depends on the clustering of electrons, not
-sources, an FRB survey could be used to study the distribution of electrons and
-potentially solve the `missing baryon problem' as pointed out in
-\citet{2014ApJ...780L..33M}.
+We have proposed using FRB sources as 3D tracers of the large-scale structure,
+using dispersion measure to estimate radial distance. It can be seen in
+Figure~\ref{f:terms} that the signal is dominated by inhomogeneities in the
+electron density along the line of sight inducing mis-estimates of radial
+distance and thus apparent clustering. These DM-space distortions could be used
+to study the distribution of free electrons in the Universe on large-scales.
+There have been other proposals to use FRB events to study large-scale
+structure \citep{2014ApJ...780L..33M,2014MNRAS.443L..11D}, however these
+schemes have either been two dimensional or required externally measured redshifts
+for the sources. Additionally, there have been proposals to use the DM-redshift
+relation to probe the background density of electrons and thus the expansion
+history of the Universe
+\citep{2014ApJ...783L..35D,2014PhRvD..89j7303Z,2014ApJ...788..189G}.
 
-We have calculated the clustering of sources in dispersion measure space and
+We have
 shown that a survey detecting $10^4$ fast radio bursts of cosmological
@@
 This however requires that the contribution to dispersion measure from
-the source's environment and host halo to be modest compared to the
+the source's environment and host halo be modest compared to the
 contribution from the IGM.

### 2015-05-26 python/assemble_terms.py

@@ -123,7 +123,7 @@ def my_plots(mult_ell=None, chi=1000):
             "linewidth" : 2.,
              }
 
-    title = "$\\bar\\chi=%d\\,\\rm{MPc}/h$, $\\Delta\\chi=%d\\,\\rm{MPc}/h$"
+    title = "$\\bar\\chi=%d\\,\\rm{Mpc}/h$, $\\Delta\\chi=%d\\,\\rm{Mpc}/h$"
     
     for delta in DELTAS:
         plt.figure(tight_layout=True)
@@ -181,7 +181,7 @@ def my_plots(mult_ell=None, chi=1000):
     ax1.plot(chi_s, d, 'k', **kwargs)
     #plt.ylim(0., 1.1)
     #plt.yticks(np.arange(0.1, 1.0,  0.2))
-    plt.ylabel(r"$4\pi f_{\rm sky} \chi^2\bar{n}_f$ ($h/\rm{MPc})$",
+    plt.ylabel(r"$4\pi f_{\rm sky} \chi^2\bar{n}_f$ ($h/\rm{Mpc})$",
                fontsize=18,
                )
     
@@ -192,13 +192,13 @@ def my_plots(mult_ell=None, chi=1000):
     plt.ylim(-0.01, 0.02)
     plt.yticks(np.arange(-0.005, 0.02,  0.005))
     #plt.ylabel(r"$(\frac{1}{\bar{n}_f}\frac{d \bar{n}_f}{d \chi}"
-    #           r"+ \frac{2}{\chi})$  ($h/\rm{MPc})$",
+    #           r"+ \frac{2}{\chi})$  ($h/\rm{Mpc})$",
     #           fontsize=18,
     #           )
-    plt.ylabel(r"$A(\chi)$  ($h/\rm{MPc})$",
+    plt.ylabel(r"$A(\chi)$  ($h/\rm{Mpc})$",
                fontsize=18,
                )
-    plt.xlabel(r"$\chi$ ($\rm{MPc}/h$)",
+    plt.xlabel(r"$\chi$ ($\rm{Mpc}/h$)",
                fontsize=18,
                )
     xticklabels = ax1.get_xticklabels()

### 2015-06-03 writeup/dm_space_distortions.tex
Cafe edits.

@@
 
-    The recently discovered fast radio bursts are a new class of radio
+    The recently discovered fast radio bursts (FBRs) are a new class of radio
     transient that, due to their high dispersion from intervening plasma,
@@
     structure of the
-    Universe. Furthermore, because the dispersion measure (DM) can be
-    used as a proxy for radial distance (like redshift),
-    clustering can be studied in three dimensions. Due to inhomogeneities in
-    the plasma's density, dispersion measure is an imperfect proxy for radial
-    distance and we show that this leads to additional clustering terms---the
-    dispersion-measure-space distortions. We calculate the DM-space
-    power spectra for a toy model of electron and FRB clustering and show that
+    Universe.
+    We show here that, even without redshifts, these bursts can be used to
+    study the three-dimensional cluster of matter in the Universe.
+    This is because the dispersion of radio waves as they travel through the
+    Universe, like redshift, can be
+    used as a proxy for radial distance. 
+    Due to inhomogeneities in
+    the plasma's density, dispersion is an imperfect proxy for radial
+    distance and we show that this leads to calculable dispersion-space
+    distortions in the apparent clustering. We calculate the dispersion-space
+    power spectra for a simple model of electron and FRB clustering and show that
     the clustering signal could be detected in a survey of $10^4$ FRB
-    events, as is expected to be produced by the Canadian Hydrogen Intensity
+    events. This rate is \ldots as is expected to be produced by the Canadian Hydrogen Intensity
     Mapping Experiment.
@@
 the study of the clustering of FRB sources in three dimensions which should trace the
-large-scale structure of the Universe on linear scales.
+large-scale structure of the Universe on linear scales. Note that although we
+frame our discussions in terms of FRBs, dispersion may be
 
@@
 \begin{equation}
-    {\rm DM}(\chi_s) = \int_0^\chi \ud\chi' a(\chi')^2 \bar{n}_e(\chi').
+    {\rm DM}(\chi_s) = \int_0^{\chi_s} \ud\chi' a(\chi')^2 \bar{n}_e(\chi').
 \end{equation}
@@
 
-Here we consider the sensitivity of a survey with a total of $10^4$ dispersion
+We consider the sensitivity of a survey with a total of $10^4$ dispersion
 measures from FRB events distributed uniformly over half the sky. This is in rough
@@
 
-We would like to thank Ue-Li Pen and Mathew McQuinn for helpful discussions.
+We thank Ue-Li Pen and Mathew McQuinn for helpful discussions.
 %

### 2015-06-04 writeup/dm_space_distortions_vKris1_Jun3.tex
A bunch of edits to intro and abstract and title

--- 2015-06-03 writeup/dm_space_distortions.tex
@@
 
-\title{The large-scale structure of the Universe in dispersion measure space}
+%\title{The large-scale structure of the Universe in dispersion measure space}
+\title{Dispersion Distance and the Matter Distribution of the Universe in Dispersion Space}
 
@@
 
-    The recently discovered fast radio bursts (FBRs) are a new class of radio
-    transient that, due to their high dispersion from intervening plasma,
-    have been interpreted as
-    originating from cosmological distances.  The rate of fast radio bursts
-    has been estimated to be several thousand over the whole sky per day.  If
-    cosmological, the sources of these events should trace the large-scale
-    structure of the
-    Universe.
-    We show here that, even without redshifts, these bursts can be used to
-    study the three-dimensional cluster of matter in the Universe.
-    This is because the dispersion of radio waves as they travel through the
-    Universe, like redshift, can be
-    used as a proxy for radial distance. 
-    Due to inhomogeneities in
-    the plasma's density, dispersion is an imperfect proxy for radial
+    We propose that `standard pings', brief broadband radio impulses, can be used to
+    study the three-dimensional clustering of matter in the Universe even in the absence of redshift information.
+    The dispersion of radio waves as they travel through the
+    Universe, like redshift, can be used as a cosmological distance measure.
+    Due to inhomogeneities in the electron density along the line-of-siight dispersion is an imperfect proxy for radial
     distance and we show that this leads to calculable dispersion-space
-    distortions in the apparent clustering. We calculate the dispersion-space
-    power spectra for a simple model of electron and FRB clustering and show that
-    the clustering signal could be detected in a survey of $10^4$ FRB
-    events. This rate is \ldots as is expected to be produced by the Canadian Hydrogen Intensity
-    Mapping Experiment.
-
+    distortions in the apparent clustering of sources. Fast radio bursts (FRBs) are a new class of radio
+    transients that are the prototypical standard ping, and due to their high observed dispersion from intervening plasma,
+    have been interpreted as originating at cosmological distances.  The rate of fast radio bursts
+    has been estimated to be several thousand over the whole sky per day, and if cosmological, the sources of these events should trace the large-scale
+    structure of the Universe.  We calculate the dispersion-space
+    power spectra for a simple model where electrons and FRBs are biased tracers of the large-scale-structure of the Universe and show that
+    the clustering signal may be detectable in a survey with as few as $10000$ 
+    events.  Upcoming wide-field radio telescopes, like the Canadian Hydrogen Intensity Mapping Experiment (CHIME), are expected to detect...
 \end{abstract}
@@
 
-However, redshift is not the only measure of radial distance. In particular,
-dispersion of electromagnetic signals due to intervening plasma
+However, redshift is not the only measure of radial distance.   
+Standard candles and standard rulers can be used to estimate distance using brightness and angular size respectively.
+In the same way a \emph{standard ping}, a brief broadband radio impulse, can be used to estimate radial distance because of
+the characteristic $\lambda^2$ dispersion of electromagnetic signals along the line-of-sight as a function of wavelength.
+This technique, widely used as an approximate distance indicator to pulsars in the Galaxy, can be used to define the
+\emph{dispersion distance} to cosmological sources.
+
+due to intervening plasma
 is readily measured from fast radio bursts (FRB) which are a class

### 2015-06-04 writeup/dm_space_distortions.tex
rename file.

@@
 
-    The recently discovered fast radio bursts (FBRs) are a new class of radio
-    transient that, due to their high dispersion from intervening plasma,
-    have been interpreted as
-    originating from cosmological distances.  The rate of fast radio bursts
-    has been estimated to be several thousand over the whole sky per day.  If
-    cosmological, the sources of these events should trace the large-scale
-    structure of the
-    Universe.
-    We show here that, even without redshifts, these bursts can be used to
-    study the three-dimensional cluster of matter in the Universe.
-    This is because the dispersion of radio waves as they travel through the
-    Universe, like redshift, can be
-    used as a proxy for radial distance. 
-    Due to inhomogeneities in
-    the plasma's density, dispersion is an imperfect proxy for radial
-    distance and we show that this leads to calculable dispersion-space
-    distortions in the apparent clustering. We calculate the dispersion-space
-    power spectra for a simple model of electron and FRB clustering and show that
-    the clustering signal could be detected in a survey of $10^4$ FRB
-    events. This rate is \ldots as is expected to be produced by the Canadian Hydrogen Intensity
-    Mapping Experiment.
-
+    We propose that `standard pings', brief broadband radio impulses, can be
+    used to study the three-dimensional clustering of matter in the Universe
+    even in the absence of redshift information.  The dispersion of radio waves
+    as they travel through the Universe, like redshift, can be used as a
+    cosmological distance measure.  Due to inhomogeneities in the electron
+    density along the line-of-siight dispersion is an imperfect proxy for
+    radial distance and we show that this leads to calculable dispersion-space
+    distortions in the apparent clustering of sources. Fast radio bursts (FRBs)
+    are a new class of radio transients that are the prototypical standard
+    ping, and due to their high observed dispersion from intervening plasma,
+    have been interpreted as originating at cosmological distances.  The rate
+    of fast radio bursts has been estimated to be several thousand over the
+    whole sky per day, and if cosmological, the sources of these events should
+    trace the large-scale structure of the Universe.  We calculate the
+    dispersion-space power spectra for a simple model where electrons and FRBs
+    are biased tracers of the large-scale structure of the Universe and show
+    that the clustering signal may be detectable in a survey with as few as
+    $10000$ events.  Upcoming wide-field radio telescopes, like the Canadian
+    Hydrogen Intensity Mapping Experiment (CHIME), are expected to detect...
 \end{abstract}
@@
 
-However, redshift is not the only measure of radial distance. In particular,
-dispersion of electromagnetic signals due to intervening plasma
+However, redshift is not the only measure of radial distance.   Standard
+candles and standard rulers can be used to estimate distance using brightness
+and angular size respectively.  In the same way a \emph{standard ping}, a brief
+broadband radio impulse, can be used to estimate radial distance because of the
+characteristic $\lambda^2$ dispersion of electromagnetic signals along the
+line-of-sight as a function of wavelength.  This technique, widely used as an
+approximate distance indicator to pulsars in the Galaxy, can be used to define
+the \emph{dispersion distance} to cosmological sources.
+
+due to intervening plasma
 is readily measured from fast radio bursts (FRB) which are a class
@@
 \begin{align}
-    &\delta_{\ell\ell'}\delta_{mm'}C^{ss}_\ell(\chi, \chi') = \nonumber \\
-    & \quad
-        \left\langle
-        \int\ud\Omega Y_{\ell m}(\hat n)
-       \delta_{fs}(\hat n \chi, \chi)
-        \int\ud\Omega' Y_{\ell' m'}(\hat n')
-        \delta_{fs}(\hat n' \chi', \chi')
-        \right\rangle.
+    &C^{ss}_\ell(\chi, \chi') =
+    \int\ud\Omega\ud\Omega' Y_{\ell m}(\hat n) Y^*_{\ell m}(\hat n')
+    \langle \delta_{fs}(\hat n \chi) \delta_{fs}(\hat n' \chi')
+        \rangle.
 \end{align}

### 2015-06-04 writeup/dm_space_distortions.tex
Moved paragraphs.

@@
 and $\chi_{\max} \equiv \max(\chi,
-\chi')$ .  We've found that these approximations are excellent for $\ell
-\gtrsim 10$
+\chi')$ .  We've found that these approximations are accurate to within $3\%$ at
+$\ell \gtrsim 10$
 and use this form for the remainder of the paper. In the above equation we dub
@@
 \section{Modelling and measurement}
-
-There are a number of effects that will complicate the measurement of the
-above calculated angular power spectrum by a real survey of dispersion 
-measures.  The first effect is
-that the model that the free electron density decomposes into a homogeneous
-part plus a random field of perturbations is not complete. Firstly, all signals
-must pass through the Milky Way's galactic disk, halo, and local environment,
-which will contribute to the dispersion measure. However, this is only a
-single function of $\hat n$ which can presumably be well
-measured. In addition, this function could in principle be well characterized
-by independent data such as observations of pulsars.  As such, it should be
-possible to subtract the local
-contribution, as was done in
-\citet{2014arXiv1412.4829D}, and this is unlikely to be a limiting obstacle.
-
-More concerning is the dispersion from the source's environment
-as well as the halo in which it resides. These electrons will presumably be
-clustered around the source on scales far smaller than DM-space
-structure map pixels and thus are not accounted for in the $\delta_e$--$\delta_f$
-correlations included in the above formalism.  This will have a mean
-contribution, common to all sources and which may be epoch dependant, that will
-modify the mean DM--distance relation. This will need to be calibrated in some
-why or else fit with nuisance parameters during parameter estimation.  There
-will also be a stochastic piece which varies from source to source.  This will
-limit the precision at which $\chi_s$ can be measured, thus limiting the
-resolution of DM space density maps in the radial direction.
-
-Detailed treatment of the above complications is beyond the scope of this
-work. The magnitude of the contribution from the progenitor is at present
-unknown. To crudely deal with it here we use relatively large
-$\chi$ bins of $100\,{\rm Mpc}/h$ in sensitivity estimates.
 
@@
 contributions from different parts of the line of sight (and thus different
-spatial scales) can be separated exactly. Again, a detailed study of DM space
+spatial scales) can be separated exactly. A detailed study of dispersion space
 tomography is beyond the scope of this work.  To avoid our results being
@@
 
+There are a number of effects that will complicate the measurement of the
+above calculated angular power spectrum by a real survey of dispersion 
+measures.  The first effect is
+that the model that the free electron density decomposes into a homogeneous
+part plus a random field of perturbations is not complete. Firstly, all signals
+must pass through the Milky Way's galactic disk, halo, and local environment,
+which will contribute to the dispersion measure. However, this is only a
+single function of $\hat n$ which can presumably be well
+measured. In addition, this function could in principle be well characterized
+by independent data such as observations of pulsars.  As such, it should be
+possible to subtract the local
+contribution, as was done in
+\citet{2014arXiv1412.4829D}, and this is unlikely to be a limiting obstacle.
+
+Perhapse, more concerning is the dispersion from the source's environment
+as well as the halo in which it resides. These electrons will presumably be
+clustered around the source on scales far smaller than DM-space
+structure map pixels and thus are not accounted for in the $\delta_e$--$\delta_f$
+correlations included in the above formalism.  This will have a mean
+contribution, common to all sources and which may be epoch dependant, that will
+modify the mean DM--distance relation. This will need to be calibrated in some
+why or else fit with nuisance parameters during parameter estimation.  There
+will also be a stochastic piece which varies from source to source.  This will
+limit the precision at which $\chi_s$ can be measured, thus limiting the
+resolution of DM space density maps in the radial direction.
+
+Detailed treatment of the above complications is beyond the scope of this
+work. The magnitude of the contribution from the progenitor is at present
+unknown. To crudely deal with it here we use relatively large
+bins widths of $\Delta\chi = 100\,{\rm Mpc}/h$ 
+and exclude the $\chi_i = \chi_j$ bin pairs.
+Because the local term drops rapidly with radial separations, this effectively 
+discards the contribution from the local term which is most sensitive to having
+precise radial distances.
+
 We consider the sensitivity of a survey with a total of $10^4$ dispersion
@@
 $C^{ss}_{\ell,ij}$ to a single function of $\ell$ by taking a weighted average
-of all pairs of radial bins. We use bin widths of $100\,{\rm Mpc}/h$ over the
+of all pairs of radial bins over the
 range $500\,{\rm Mpc}/h$ to $3500\,{\rm Mpc}/h$.
@@
 is near optimal at other multipoles.
-We exclude the $i = j$ bin pairs
-as they would be contaminated by noise bias in a real survey.
-This effectively discards the contribution from the local term. The result is shown
+The result is shown
 in Figure~\ref{f:sensitivity}.

### 2015-06-04 writeup/dm_space_distortions.tex
More intro changes

@@
 characteristic $\lambda^2$ dispersion of electromagnetic signals along the
-line-of-sight as a function of wavelength.  This technique, widely used as an
-approximate distance indicator to pulsars in the Galaxy, can be used to define
-the \emph{dispersion distance} to cosmological sources.
-
-due to intervening plasma
-is readily measured from fast radio bursts (FRB) which are a class
-of radio transient first reported by \citet{2007Sci...318..777L}.
-There have since been 
-10 such bursts reported
+line-of-sight as a function of wavelength.  This technique, routinely done with pulsars in the Galaxy, can be used to define
+a \emph{dispersion distance} to cosmological sources.  Intriguingly, the dispersion of fast radio bursts (FRB), a new class
+of millisecond duration radio transients first reported by \citet{2007Sci...318..777L}, has been measured with high significance. 
+These bursts are the archetype of a standard ping with 
+10 reported
 \citep{2012MNRAS.425L..71K,2013Sci...341...53T,
 2014ApJ...790..101S, 2014ApJ...792...19B, 
-2015MNRAS.447..246P,2015ApJ...799L...5R} and total rate of bursts
+2015MNRAS.447..246P,2015ApJ...799L...5R} to date and total rate of bursts
 been estimated to be $3.3^{+5}_{-2.5} \times 10^3$
 per sky per day \cite{2015arXiv150500834R}. 
-The dispersion measure
-(DM) is a line-of-site integral of the free electron density and can thus be
-used as a distance estimate, as is routinely done with galactic pulsars.
+Dispersion is characterized by a line-of-site integral of the free electron density known the dispersion measure
+(DM).
 FRB events are observed to have dispersion measures of order
-$1000\,{\rm pc} / {\rm cm}^3$, greatly in excess of
-the galactic expectation of order $100\,{\rm pc} / {\rm cm}^3$, depending on
-galactic latitude
+$\sim\!\!1000 {\rm pc} / {\rm cm}^3$, greatly in excess of
+the galactic expectation of order $\sim\!\!100\,{\rm pc} / {\rm cm}^3$ (depending on
+galactic latitude)
 \cite{2014arXiv1412.4829D}.
-They must therefore be of extra-galactic origin, with their
+They  thus appear to be of extra-galactic origin, with their
 dispersion produced either by the
-inter-galactic medium (IGM) \citep{2013Sci...341...53T} or the
+inter-galactic medium (IGM) \citep{2013Sci...341...53T} surrounding galaxies or the
 environment of the source
 \citep{2014ApJ...785L..26L,2015arXiv150101341P,2015arXiv150505535C}.
-If the dispersion is dominated by the inter-galactic medium,
+If the dispersion is dominated by electrons along the line-of-sight,
 then the average DM--distance relation can be modelled
 \citep{2014ApJ...797...71Z,2004MNRAS.348..999I, 2003ApJ...598L..79I}
-and the sources are at
-cosmological distances of a few gigaparsecs. This would permit
-the study of the clustering of FRB sources in three dimensions which should trace the
+and the sources appear to be at
+cosmological distances of of order $\sim\!\!{\rm Gpc}$. Such cosmological distances permit
+the study of clustering of FRB sources in three dimensions with an expectation that these events trace the
 large-scale structure of the Universe on linear scales. Note that although we
-frame our discussions in terms of FRBs, dispersion may be
+frame our discussion in terms of FRBs, other bright radio transients that fluctuate on timescales less than the typical lag time of might also be used as standard pings.
 

### 2015-06-04 writeup/dm_space_distortions.tex
update to not-FRB caveat

@@
 the study of clustering of FRB sources in three dimensions with an expectation that these events trace the
-large-scale structure of the Universe on linear scales. Note that although we
-frame our discussion in terms of FRBs, other bright radio transients that fluctuate on timescales less than the typical lag time of might also be used as standard pings.
+large-scale structure of the Universe on linear scales.
+We note that while our discussion here is framed in terms of FRBs, other bright radio transients that fluctuate on timescales less than the typical differential lag of $\sim 1s/100 \,{\rm MHz} $ might also be useful as standard pings.
 

### 2015-06-04 writeup/dm_space_distortions.tex
dispersion measure -> dispersion

--- 2015-06-04 writeup/dm_space_distortions.tex
@@
 If the dispersion is dominated by electrons along the line-of-sight,
-then the average DM--distance relation can be modelled
+then the average dispersion--distance relation can be modelled
 \citep{2014ApJ...797...71Z,2004MNRAS.348..999I, 2003ApJ...598L..79I}
@@
 
-Neither redshift nor dispersion measure are perfect proxies for radial distance.
+Neither redshift nor dispersion are perfect proxies for radial distance.
 Redshifts are systematically biased by the peculiar velocities of the object
@@
 using linear theory.
-Similarly, distance estimates from dispersion measure will be biased by
+Similarly, distance estimates from dispersion will be biased by
 inhomogeneities in the electron density \citep{2014ApJ...780L..33M},
@@
 clustering of sources in dispersion measure space.  In this letter we calculate
-these DM-space distortions and consider the detectability of the signal by
+these dispersion-space distortions and consider the detectability of the signal by
 upcoming surveys.
@@
 %\section{Density perturbations in dispersion measure space}
-\section{Clustering in dispersion measure space}
+\section{Clustering in dispersion space}
 
@@
 
-\emph{Dispersion measure space} is the three dimensional coordinates,
+\emph{Dispersion space} is the three dimensional coordinates,
 $\vec x_s$ inferred from the dispersion measure assuming that the electrons are
@@
 
-We wish to relate the density of a tracer, $f$, measured in DM space to its
+We wish to relate the density of a tracer, $f$, measured in dispersion space to its
 density in real space. We follow the derivation in \citet{1987MNRAS.227....1K}
@@
 density should
-be the same in DM space as in real space,
+be the same in dispersion space as in real space,
 \begin{equation}
@@
 In the equation above, the $-\delta_e$ term is most analogous to the Kaiser
-redshift-space distortions.  It is a dilution of tracers in DM space due to an
+redshift-space distortions.  It is a dilution of tracers in dispersion space due to an
 excess of electrons between the tracers. However we note that this term is isotropic
 in contrast to Kaiser.  This is because any wave vector electron perturbation
-causes DM space distortions, whereas the radial velocities that cause
+causes dispertion space distortions, whereas the radial velocities that cause
 redshift-space distortions are only sourced by perturbations with radial wave
@@
 We will instead use $C^{ss}_\ell(\chi,\chi')$, which is
-the cross-correlation angular power spectrum of the DM-space over density,
+the cross-correlation angular power spectrum of the dispersion-space over density,
 on shells at $\chi$ and $\chi'$:
@@
 
-There is an advantage to the lack of kernel in the DM-space integral term.
+There is an advantage to the lack of kernel in the dispersion-space integral term.
 Lensing tomography---the use of sources at multiple redshifts to un-mix
@@
 the source redshift, re-weighting the line-of-sight integral and
-making tomography inexact.  In contrast the integrand in the DM-space integral
+making tomography inexact.  In contrast the integrand in the dispersion-space integral
 term is completely independent of the limit of integration, meaning
@@
 
-For plotting the DM-space power spectra we use a toy model for the electron and
+For plotting the dispersion-space power spectra we use a toy model for the electron and
 FRB clustering that assumes both are biased tracers of the dark matter:
@@
 We use a simple model where all events above a fixed flux are detected,
-the intrinsic luminosity function has the
-\citet{1976ApJ...203..297S} form with index $-1$, and events at the cut off of the
+the intrinsic luminosity function has the form from
+\citet{1976ApJ...203..297S} with index $-1$, and events at the cut off of the
 luminosity function and at
 a radial distance of $\chi=2350\,{\rm Mpc}/h$ are at the flux detection threshold.
-This source density is shown in Figure~\ref{f:n_f} with the resulting DM-space
+This source density is shown in Figure~\ref{f:n_f} with the resulting dispersion-space
 power-spectrum in Figure~\ref{f:terms}.
@@
         \label{f:terms}
-        Terms in the DM-space cross-correlation angular power spectrum.
+        Terms in the dispersion-space cross-correlation angular power spectrum.
         All terms are evaluated at $\bar\chi=2000\,{\rm Mpc}/h$ and 
@@
 In first measurements of the angular power spectra, uncertainty will be
-dominated by the finite number of observed dispersion measures, or shot noise.
+dominated by the finite number of observed events, or shot noise.
 The noise power spectrum on shells with of width
@@
 direction instead of
-continuous functions, we've switched to $C_{\ell,ij}$ over 
+continuous functions, we've switched to $C_{\ell,ij}$ instead of
 $C_\ell(\chi, \chi')$. The uncertainty on the angular
@@
 must pass through the Milky Way's galactic disk, halo, and local environment,
-which will contribute to the dispersion measure. However, this is only a
+which will contribute to the dispersion. However, this is only a
 single function of $\hat n$ which can presumably be well
@@
 as well as the halo in which it resides. These electrons will presumably be
-clustered around the source on scales far smaller than DM-space
+clustered around the source on scales far smaller than dispersion-space
 structure map pixels and thus are not accounted for in the $\delta_e$--$\delta_f$
@@
 contribution, common to all sources and which may be epoch dependant, that will
-modify the mean DM--distance relation. This will need to be calibrated in some
+modify the mean dispersion--distance relation. This will need to be calibrated in some
 why or else fit with nuisance parameters during parameter estimation.  There
@@
 limit the precision at which $\chi_s$ can be measured, thus limiting the
-resolution of DM space density maps in the radial direction.
+resolution of dispersion space density maps in the radial direction.
 
@@
 We have proposed using FRB sources as 3D tracers of the large-scale structure,
-using dispersion measure to estimate radial distance. It can be seen in
+using dispersion to estimate radial distance. It can be seen in
 Figure~\ref{f:terms} that the signal is dominated by inhomogeneities in the
 electron density along the line of sight inducing mis-estimates of radial
-distance and thus apparent clustering. These DM-space distortions could be used
+distance and thus apparent clustering. These dispersion-space distortions could be used
 to study the distribution of free electrons in the Universe on large-scales.
@@
 schemes have either been two dimensional or required externally measured redshifts
-for the sources. Additionally, there have been proposals to use the DM-redshift
+for the sources. Additionally, there have been proposals to use the dispersion-redshift
 relation to probe the background density of electrons and thus the expansion
@@
 clustering signal.
-Looking forward, DM-space
+Looking forward, dispersion-space
 clustering could become a powerful probe of large-scale structure should
@@
 term using tomography.
-This however requires that the contribution to dispersion measure from
-the source's environment and host halo be modest compared to the
+This however requires that the contribution to dispersion from
+the source's environment and host halo be small compared to the
 contribution from the IGM.

### 2015-06-04 writeup/dm_space_distortions.tex
many edits.

@@
 %\title{The large-scale structure of the Universe in dispersion measure space}
-\title{Dispersion Distance and the Matter Distribution of the Universe in Dispersion Space}
+\title{Dispersion distance and the matter distribution of the Universe in dispersion space}
 
@@
     even in the absence of redshift information.  The dispersion of radio waves
-    as they travel through the Universe, like redshift, can be used as a
+    as they travel through the intervening plasma can,
+    like redshift, be used as a
     cosmological distance measure.  Due to inhomogeneities in the electron
-    density along the line-of-siight dispersion is an imperfect proxy for
+    density along the line-of-sight, dispersion is an imperfect proxy for
     radial distance and we show that this leads to calculable dispersion-space
@@
     are a new class of radio transients that are the prototypical standard
-    ping, and due to their high observed dispersion from intervening plasma,
+    ping, and due to their high observed dispersion,
     have been interpreted as originating at cosmological distances.  The rate
@@
     are biased tracers of the large-scale structure of the Universe and show
-    that the clustering signal may be detectable in a survey with as few as
-    $10000$ events.  Upcoming wide-field radio telescopes, like the Canadian
-    Hydrogen Intensity Mapping Experiment (CHIME), are expected to detect...
+    that the clustering signal could be measured using as few as
+    $10000$ events. Such a survey is in-line with what may be achieved with
+    upcoming wide-field radio telescopes such as the Canadian
+    Hydrogen Intensity Mapping Experiment (CHIME).
 \end{abstract}
@@
 characteristic $\lambda^2$ dispersion of electromagnetic signals along the
-line-of-sight as a function of wavelength.  This technique, routinely done with pulsars in the Galaxy, can be used to define
-a \emph{dispersion distance} to cosmological sources.  Intriguingly, the dispersion of fast radio bursts (FRB), a new class
-of millisecond duration radio transients first reported by \citet{2007Sci...318..777L}, has been measured with high significance. 
-These bursts are the archetype of a standard ping with 
-10 reported
-\citep{2012MNRAS.425L..71K,2013Sci...341...53T,
-2014ApJ...790..101S, 2014ApJ...792...19B, 
-2015MNRAS.447..246P,2015ApJ...799L...5R} to date and total rate of bursts
-been estimated to be $3.3^{+5}_{-2.5} \times 10^3$
-per sky per day \cite{2015arXiv150500834R}. 
-Dispersion is characterized by a line-of-site integral of the free electron density known the dispersion measure
-(DM).
-FRB events are observed to have dispersion measures of order
-$\sim\!\!1000 {\rm pc} / {\rm cm}^3$, greatly in excess of
-the galactic expectation of order $\sim\!\!100\,{\rm pc} / {\rm cm}^3$ (depending on
-galactic latitude)
-\cite{2014arXiv1412.4829D}.
-They  thus appear to be of extra-galactic origin, with their
-dispersion produced either by the
-inter-galactic medium (IGM) \citep{2013Sci...341...53T} surrounding galaxies or the
-environment of the source
-\citep{2014ApJ...785L..26L,2015arXiv150101341P,2015arXiv150505535C}.
-If the dispersion is dominated by electrons along the line-of-sight,
-then the average dispersion--distance relation can be modelled
-\citep{2014ApJ...797...71Z,2004MNRAS.348..999I, 2003ApJ...598L..79I}
-and the sources appear to be at
-cosmological distances of of order $\sim\!\!{\rm Gpc}$. Such cosmological distances permit
-the study of clustering of FRB sources in three dimensions with an expectation that these events trace the
-large-scale structure of the Universe on linear scales.
-We note that while our discussion here is framed in terms of FRBs, other bright radio transients that fluctuate on timescales less than the typical differential lag of $\sim 1s/100 \,{\rm MHz} $ might also be useful as standard pings.
+line-of-sight as a function of wavelength.  This technique, routinely done with
+pulsars in the Galaxy, can be used to define a \emph{dispersion distance} to
+cosmological sources.  Intriguingly, the dispersion of fast radio bursts (FRB),
+a new class of millisecond duration radio transients first reported by
+\citet{2007Sci...318..777L}, has been measured with high significance.  These
+bursts are the archetype of a standard ping with 10 reported to date
+\citep{2012MNRAS.425L..71K,2013Sci...341...53T, 2014ApJ...790..101S,
+2014ApJ...792...19B, 2015MNRAS.447..246P,2015ApJ...799L...5R}, and with a total
+event rate estimated to be $3.3^{+5}_{-2.5} \times 10^3$ per sky per
+day \cite{2015arXiv150500834R}.  Dispersion is characterized by a line-of-site
+integral of the free electron density known the dispersion measure (DM).  FRB
+events are observed to have dispersion measures of order $\sim\!\!1000 {\rm pc}
+/ {\rm cm}^3$, greatly in excess of the galactic expectation of order
+$\sim\!\!100\,{\rm pc} / {\rm cm}^3$ (depending on galactic latitude)
+\cite{2014arXiv1412.4829D}.  They thus appear to be of extra-galactic origin,
+with their dispersion produced either by the inter-galactic medium (IGM)
+\citep{2013Sci...341...53T} surrounding galaxies along the line-of-sight
+or the environment of the
+source \citep{2014ApJ...785L..26L,2015arXiv150101341P,2015arXiv150505535C}.  If
+the dispersion is dominated by electrons along the line-of-sight, then the
+average dispersion--distance relation can be modelled
+\citep{2014ApJ...797...71Z,2004MNRAS.348..999I, 2003ApJ...598L..79I} and the
+sources appear to be at cosmological distances of of order $\sim\!\!{\rm Gpc}$.
+Such cosmological distances permit the study of clustering of FRB sources in
+three dimensions with an expectation that these events trace the large-scale
+structure of the Universe on linear scales. We note that while our discussion
+here is framed in terms of FRBs, other bright radio transients that fluctuate
+on timescales less than the typical differential lag of $\sim 1s/100 \,{\rm
+MHz} $ might also be useful as standard pings.
 
 Neither redshift nor dispersion are perfect proxies for radial distance.
-Redshifts are systematically biased by the peculiar velocities of the object
+Redshifts are systematically biased by the peculiar velocities of objects
 relative to the Hubble flow. This leads to additional apparent clustering
@@
 using linear theory.
-Similarly, distance estimates from dispersion will be biased by
+Similarly, as we show here, distance estimates from dispersion will be biased by
 inhomogeneities in the electron density \citep{2014ApJ...780L..33M},
@@
 \begin{equation}
-\label{e:density}
 n_{fs}(\vec x_s) \ud^3\vec x_s = n_{f}(\vec x) \ud^3\vec x.
@@
 \begin{equation}
+\label{e:density}
     \bar{n}_{fs}(\chi_s)\left[ 1 + \delta_{fs}(\vec x_s)\right] \ud^3\vec x_s
@@
 excess of electrons between the tracers. However we note that this term is isotropic
-in contrast to Kaiser.  This is because any wave vector electron perturbation
+in contrast to the Kaiser term.  This is because any wave vector electron perturbation
 causes dispertion space distortions, whereas the radial velocities that cause
@@
 
-The $\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi}$ arise since the
+The $\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi}$ term arises because the
 misinterpretation of the radial distance causes the observed tracer density to
@@
 commonly the power spectrum, $P(k)$.
-Unlike in redshift-space distortions, Equation~\ref{e:delta_s} does not have a
+Unlike the redshift-space distortions, Equation~\ref{e:delta_s} does not have a
 simple form in harmonic space. The equation's third term couples harmonic modes
@@
 within a few correlation lengths of one another, roughly a hundred
-megaparsecs.  The evolution of the power-spectrum is negligible over these time
+megaparsecs.  The evolution of the power spectrum is negligible over these time
 differences which leads to a straight-forward way to include the evolution of
@@
 the source redshift, re-weighting the line-of-sight integral and
-making tomography inexact.  In contrast the integrand in the dispersion-space integral
+making tomography inexact.  In contrast, the integrand in the dispersion-space integral
 term is completely independent of the limit of integration, meaning
@@
 This source density is shown in Figure~\ref{f:n_f} with the resulting dispersion-space
-power-spectrum in Figure~\ref{f:terms}.
+power spectrum in Figure~\ref{f:terms}.
 
@@
         text. Normalization is
-        such that the survey has a total of $10^4$ FRB events.
+        such that the survey has a total of $10000$ FRB events.
         \emph{Bottom:} Resulting coefficient $A(\chi)$ as given in
@@
 \end{figure}
-
-In first measurements of the angular power spectra, uncertainty will be
-dominated by the finite number of observed events, or shot noise.
-The noise power spectrum on shells with of width
-$\Delta \chi$ is
-\begin{equation}
-    C^N_{\ell, ij} = \frac{\delta_{ij}}{\bar n_f(\chi_i)\chi_i^2\Delta\chi}.
-\end{equation}
-Here, to indicate that we are now working with quantities binned in the radial
-direction instead of
-continuous functions, we've switched to $C_{\ell,ij}$ instead of
-$C_\ell(\chi, \chi')$. The uncertainty on the angular
-cross-power spectrum is then
-\begin{align}
-    (\Delta{C^{ss}_{\ell,ij}})^2 = 
-    {\frac{1}{\ell(\ell + 1)\Delta \ell f_{\rm sky}}}
-        \left[C^N_{\ell,ii} C^N_{\ell,jj} +  (C^N_{\ell,ij})^2\right],
-\end{align}
-where the second term in brackets only contributes for $i = j$.
 
@@
 bins widths of $\Delta\chi = 100\,{\rm Mpc}/h$ 
-and exclude the $\chi_i = \chi_j$ bin pairs.
+and exclude the $\chi = \chi'$ bin pairs.
 Because the local term drops rapidly with radial separations, this effectively 
@@
 
-We consider the sensitivity of a survey with a total of $10^4$ dispersion
+In first measurements of the angular power spectra, uncertainty will be
+dominated by the finite number of observed events, or shot noise.
+The noise power spectrum on shells with of width
+$\Delta \chi$ is
+\begin{equation}
+    C^N_{\ell, ij} = \frac{\delta_{ij}}{\bar n_f(\chi_i)\chi_i^2\Delta\chi}.
+\end{equation}
+Here, to indicate that we are now working with quantities binned in the radial
+direction instead of
+continuous functions, we've switched to $C_{\ell,ij}$ instead of
+$C_\ell(\chi, \chi')$. The uncertainty on the angular
+cross-power spectrum is then
+\begin{align}
+    (\Delta{C^{ss}_{\ell,ij}})^2 = 
+    {\frac{1}{\ell(\ell + 1)\Delta \ell f_{\rm sky}}}
+        \left[C^N_{\ell,ii} C^N_{\ell,jj} +  (C^N_{\ell,ij})^2\right],
+\end{align}
+where the second term in brackets only contributes for $i = j$.
+
+We consider the sensitivity of a survey with a total of $10000$ dispersion
 measures from FRB events distributed uniformly over half the sky. This is in rough
-approximation to what could be achieved by the Canadian Hydrogen Intensity
-Mapping Experiment's now funded FRB instrument over a three year survey.
+approximation to what might be achieved by the Canadian Hydrogen Intensity
+Mapping Experiment (CHIME) telescope over a three year survey.
 To give an idea of the overall sensitivity of the survey, we collapse
@@
 range $500\,{\rm Mpc}/h$ to $3500\,{\rm Mpc}/h$.
-For weights in the radial bin average, we use the signal over noise-squared
+For weights we use the signal over noise-squared
 at $\ell=100$, which maximizes the signal to noise at that $\ell$ and
@@
         \label{f:sensitivity}
-        Sensitivity of a survey with $10^4$ dispersion measures distributed
+        Sensitivity of a survey with $10000$ dispersion measures distributed
         uniformly over half the sky.  Plotted is the cross-correlation
@@
 distance and thus apparent clustering. These dispersion-space distortions could be used
-to study the distribution of free electrons in the Universe on large-scales.
+to study the distribution of free electrons in the Universe on large-scales and
+redshifts less than $\sim\!\!1$.
 There have been other proposals to use FRB events to study large-scale
@@
 We have
-shown that a survey detecting $10^4$ fast radio bursts of cosmological
+shown that a survey detecting $10000$ fast radio bursts of cosmological
 origin (as might be achieved by the CHIME FRB instrument) could detect the

### 2015-06-04 writeup/dm_space_distortions.tex
Edits to intro.

@@
 and angular size respectively.  In the same way a \emph{standard ping}, a brief
-broadband radio impulse, can be used to estimate radial distance because of the
-characteristic $\lambda^2$ dispersion of electromagnetic signals along the
-line-of-sight as a function of wavelength.  This technique, routinely done with
+broadband radio impulse, can be used to measure dispersion through the
+characteristic wavelength-squared delay of electromagnetic signals. The disperion is
+proportional to the amount of plasma along the
+line-of-sight and can thus be used to estimate radial distance.
+This technique, routinely done with
 pulsars in the Galaxy, can be used to define a \emph{dispersion distance} to
-cosmological sources.  Intriguingly, the dispersion of fast radio bursts (FRB),
+cosmological sources.
+%
+Dispersion is readily measured from fast radio bursts (FRB),
 a new class of millisecond duration radio transients first reported by
-\citet{2007Sci...318..777L}, has been measured with high significance.  These
-bursts are the archetype of a standard ping with 10 reported to date
+\citet{2007Sci...318..777L}, which are the archetype of a standard ping.
+Ten such bursts have been reported to date
 \citep{2012MNRAS.425L..71K,2013Sci...341...53T, 2014ApJ...790..101S,
-2014ApJ...792...19B, 2015MNRAS.447..246P,2015ApJ...799L...5R}, and with a total
-event rate estimated to be $3.3^{+5}_{-2.5} \times 10^3$ per sky per
-day \cite{2015arXiv150500834R}.  Dispersion is characterized by a line-of-site
+2014ApJ...792...19B, 2015MNRAS.447..246P,2015ApJ...799L...5R}, and the total
+event rate has been estimated to be $3.3^{+5}_{-2.5} \times 10^3$ per sky per
+day \cite{2015arXiv150500834R}.
+Dispersion is characterized by a line-of-site
 integral of the free electron density known the dispersion measure (DM).  FRB
-events are observed to have dispersion measures of order $\sim\!\!1000 {\rm pc}
+events are observed to have dispersion measures of order $\sim\!\!1000\,{\rm pc}
 / {\rm cm}^3$, greatly in excess of the galactic expectation of order
@@
 with their dispersion produced either by the inter-galactic medium (IGM)
-\citep{2013Sci...341...53T} surrounding galaxies along the line-of-sight
+surrounding galaxies along the line-of-sight \citep{2013Sci...341...53T}
 or the environment of the
@@
 integral term from radial distances $\chi'' < 500\,{\rm Mpc}/h$ are well
-measured by the correlations with these radial slices. We thus neglect the
-information from these slices in our sensitivity measurements and ignore
-contributions to the integral term from below this distance. The smallest
+measured by the correlations with these radial slices. We thus ignore
+contributions to the integral term from below this distance and neglect the
+information from these slices in our sensitivity measurements. The smallest
 spatial scale that contributes the our plotted angular power spectra out to

### 2015-06-04 writeup/dm_space_distortions.tex
Many small edits, mostly to makes things slightly more breif.

@@
-\documentclass[twocolumn,prl,nofootinbib,floatfix]{revtex4-1}
+\documentclass[twocolumn,prl,floatfix]{revtex4-1}
 \usepackage{graphicx}
@@
 \usepackage{epstopdf}
+\usepackage{url}
+\usepackage{hyperref}
 
@@
 broadband radio impulse, can be used to measure dispersion through the
-characteristic wavelength-squared delay of electromagnetic signals. The disperion is
+characteristic wavelength-squared delay of electromagnetic signals. The dispersion is
 proportional to the amount of plasma along the
 line-of-sight and can thus be used to estimate radial distance.
-This technique, routinely done with
+This technique, routinely used for
 pulsars in the Galaxy, can be used to define a \emph{dispersion distance} to
@@
 \cite{2014arXiv1412.4829D}.  They thus appear to be of extra-galactic origin,
-with their dispersion produced either by the inter-galactic medium (IGM)
-surrounding galaxies along the line-of-sight \citep{2013Sci...341...53T}
+with their dispersion produced either by the inter-galactic medium (IGM),
+associated with structure along line-of-sight \citep{2013Sci...341...53T},
 or the environment of the
@@
 here is framed in terms of FRBs, other bright radio transients that fluctuate
-on timescales less than the typical differential lag of $\sim 1s/100 \,{\rm
+on timescales shorter than the typical differential lag of $\sim 1s/100 \,{\rm
 MHz} $ might also be useful as standard pings.
@@
 conformal time. Note that we use $\chi$ as our radial distance and time
-coordinate, as opposed to redshift which is more appropriate for spectroscopic
-applications. We model the cosmological 
+coordinate, as opposed to redshift. We model the cosmological 
 electron density as containing a homogeneous part
@@
     &= \frac{\ud \chi}{\ud \chi_s}\frac{\chi^2}{\chi_s^2}\\
-    &= (1 + \delta_e)^{-1}
-       \left(1 + \frac{\int_0^\chi \ud \chi' \delta_e(\hat n \chi')}
-                      {\chi}\right)^{-2}\\
+%    &= (1 + \delta_e)^{-1}
+%       \left(1 + \frac{\int_0^\chi \ud \chi' \delta_e(\hat n \chi')}
+%                      {\chi}\right)^{-2}\\
     &\approx 1 - \delta_e
@@
 \end{equation}
-In the equation above, the $-\delta_e$ term is most analogous to the Kaiser
+In the above equation, the $-\delta_e$ term is most analogous to the Kaiser
 redshift-space distortions.  It is a dilution of tracers in dispersion space due to an
@@
 in contrast to the Kaiser term.  This is because any wave vector electron perturbation
-causes dispertion space distortions, whereas the radial velocities that cause
+causes dispersion space distortions, whereas the radial velocities that cause
 redshift-space distortions are only sourced by perturbations with radial wave
@@
 \begin{align}
-C^{xy}_\ell(\chi,\chi') 
-    \approx \frac{2}{\pi}
+    % I've tuned the alignment of the domain (using &)
+    % here to get the equation number and
+    % domain on the same line. Not elegant.
+    C^{xy}_\ell(\chi,\chi') \approx&
+        \frac{2}{\pi}
         \int_0^\infty\ud k k^2
         j_\ell(k\chi) j_{\ell}(k\chi')
-    P_{xy}(k,(\chi + \chi')/2),\nonumber &\\
-    |\chi - \chi'| \ll 1/aH.&
+        P_{xy}(k,(\chi + \chi')/2),\nonumber \\
+    &|\chi - \chi'| \ll 1/aH.
 \end{align}
@@
 exists in the field of weak gravitational lensing, where the formula for the
-angular power spectrum has a similar form.  In lensing, a kernel in
+shear angular power spectrum has a similar form.  In lensing, a kernel in
 the line-of-sight integral arising from geometric effects suppresses the
@@
 
-There is an advantage to the lack of kernel in the dispersion-space integral term.
-Lensing tomography---the use of sources at multiple redshifts to un-mix
-spatial scales---is complicated by the kernel. The kernel's shape depends on
-the source redshift, re-weighting the line-of-sight integral and
-making tomography inexact.  In contrast, the integrand in the dispersion-space integral
+However, the lack of a kernel simplifies tomography---the use of sources at
+multiple redshifts to unmix spatial scales.
+Lensing tomography is inexact because the kernel's shape depends on
+the source redshift, thus re-weighting the line-of-sight integral.
+In contrast, the integrand in the dispersion-space integral
 term is completely independent of the limit of integration, meaning
@@
 information from these slices in our sensitivity measurements. The smallest
-spatial scale that contributes the our plotted angular power spectra out to
+spatial scale that contributes to our plotted angular power spectra out to
 $\ell=1000$ is thus $k=2\,h/{\rm Mpc}$.
@@
 
-There are a number of effects that will complicate the measurement of the
-above calculated angular power spectrum by a real survey of dispersion 
-measures.  The first effect is
-that the model that the free electron density decomposes into a homogeneous
-part plus a random field of perturbations is not complete. Firstly, all signals
-must pass through the Milky Way's galactic disk, halo, and local environment,
-which will contribute to the dispersion. However, this is only a
+In a real survey, measurement of the dispersion-space clustering
+will be complicated by extra contributions to the dispersion.
+Firstly, all signals
+must pass through the Milky Way's galactic disk, halo, and local environment.
+However, the resulting dispersion is only a
 single function of $\hat n$ which can presumably be well
-measured. In addition, this function could in principle be well characterized
-by independent data such as observations of pulsars.  As such, it should be
+measured. As such, it should be
 possible to subtract the local
@@
 
-Perhapse, more concerning is the dispersion from the source's environment
+Perhaps, more concerning is the dispersion from the source's immediate environment
 as well as the halo in which it resides. These electrons will presumably be
-clustered around the source on scales far smaller than dispersion-space
-structure map pixels and thus are not accounted for in the $\delta_e$--$\delta_f$
+clustered around the source on scales far smaller than the survey
+resolution and are thus not accounted for in the
+$\delta_e$--$\delta_f$
 correlations included in the above formalism.  This will have a mean
@@
 modify the mean dispersion--distance relation. This will need to be calibrated in some
-why or else fit with nuisance parameters during parameter estimation.  There
+way or else fit with nuisance parameters during parameter estimation.  There
 will also be a stochastic piece which varies from source to source.  This will
@@
 dominated by the finite number of observed events, or shot noise.
-The noise power spectrum on shells with of width
+The noise power spectrum on shells at distance with of width
 $\Delta \chi$ is
@@
 Here, to indicate that we are now working with quantities binned in the radial
-direction instead of
-continuous functions, we've switched to $C_{\ell,ij}$ instead of
+direction, we've switched to $C_{\ell,ij}$ instead of
 $C_\ell(\chi, \chi')$. The uncertainty on the angular
@@
 We consider the sensitivity of a survey with a total of $10000$ dispersion
-measures from FRB events distributed uniformly over half the sky. This is in rough
-approximation to what might be achieved by the Canadian Hydrogen Intensity
-Mapping Experiment (CHIME) telescope over a three year survey.
+measures from FRB events distributed uniformly over half the sky.
 To give an idea of the overall sensitivity of the survey, we collapse
@@
 
-We have proposed using FRB sources as 3D tracers of the large-scale structure,
+We have proposed using cosmological FRB sources as 3D tracers of the
+large-scale structure,
 using dispersion to estimate radial distance. It can be seen in
 Figure~\ref{f:terms} that the signal is dominated by inhomogeneities in the
-electron density along the line of sight inducing mis-estimates of radial
-distance and thus apparent clustering. These dispersion-space distortions could be used
-to study the distribution of free electrons in the Universe on large-scales and
-redshifts less than $\sim\!\!1$.
-There have been other proposals to use FRB events to study large-scale
-structure \citep{2014ApJ...780L..33M,2014MNRAS.443L..11D}, however these
-schemes have either been two dimensional or required externally measured redshifts
-for the sources. Additionally, there have been proposals to use the dispersion-redshift
-relation to probe the background density of electrons and thus the expansion
-history of the Universe
-\citep{2014ApJ...783L..35D,2014PhRvD..89j7303Z,2014ApJ...788..189G}.
+electron density along the line of sight, inducing mis-estimates of radial
+distance and thus apparent clustering. These dispersion-space distortions could
+be used
+to study the distribution of free electrons in the Universe on large-scales.
+There have been other proposals to use FRBs in cosmology 
+\citep{2014ApJ...780L..33M,2014MNRAS.443L..11D,
+2014ApJ...783L..35D,2014PhRvD..89j7303Z,2014ApJ...788..189G}, however these
+schemes have either not been three dimensional
+or required externally measured redshifts
+for the sources.
 
 We have
-shown that a survey detecting $10000$ fast radio bursts of cosmological
-origin (as might be achieved by the CHIME FRB instrument) could detect the
-clustering signal.
+shown in Figure~\ref{f:sensitivity}
+that a survey detecting $10000$ fast radio bursts of cosmological
+origin could detect the
+clustering signal. This is in rough
+approximation to what might be achieved by the Canadian Hydrogen Intensity
+Mapping Experiment (CHIME)\footnote{\url{http://chime.phas.ubc.ca/}}
+or other upcoming wide-field telescopes.
 Looking forward, dispersion-space
-clustering could become a powerful probe of large-scale structure should
+clustering could become a precision probe of large-scale structure should
 observational factors turn out to be favourable compared to spectroscopic

### 2015-06-04 writeup/dm_space_distortions.tex
another roudn of edits.

@@
 cosmological sources.
-%
+
 Dispersion is readily measured from fast radio bursts (FRB),
@@
 \citep{2014ApJ...797...71Z,2004MNRAS.348..999I, 2003ApJ...598L..79I} and the
-sources appear to be at cosmological distances of of order $\sim\!\!{\rm Gpc}$.
-Such cosmological distances permit the study of clustering of FRB sources in
+sources appear to be at cosmological distances of order gigaparsecs.
+Such cosmological distances permit the study of the clustering of FRB sources in
 three dimensions with an expectation that these events trace the large-scale
@@
 again leading to additional apparent
-clustering of sources in dispersion measure space.  In this letter we calculate
+clustering of sources in dispersion space.  In this letter we calculate
 these dispersion-space distortions and consider the detectability of the signal by
@@
 We will instead use $C^{ss}_\ell(\chi,\chi')$, which is
-the cross-correlation angular power spectrum of the dispersion-space over density,
+the cross-correlation angular power spectrum of the dispersion-space over-density,
 on shells at $\chi$ and $\chi'$:
@@
 $\langle \delta_x(\vec k, \chi) \delta_y(\vec k', \chi) \rangle = (2\pi)^3
-\delta^3(\vec k - \vec k') P_{xy}(k, \chi)$.  If for a moment we ignore time
-dependence, the angular cross-power spectrum of such tracers is
+\delta^3(\vec k - \vec k') P_{xy}(k, \chi)$.  If for a moment we ignore
+structure evolution, the angular cross-power spectrum of such tracers is
 \begin{align}
@@
 megaparsecs.  The evolution of the power spectrum is negligible over these time
-differences which leads to a straight-forward way to include the evolution of
-the perturbations:
+differences which leads to a straight-forward way to include the evolution:
 \begin{align}
@@
 \emph{i.e.}~$P_{xy}(k)=b_x b_y P(k)$.  We
-calculate the time dependant dark-matter power spectrum using {\tt CAMB} using
+calculate the time dependant dark-matter power spectrum using {\tt CAMB}, using
 the integrated {\tt HALOFIT} to approximate the non-linear evolution. We assume

### 2015-06-04 writeup/dm_space_distortions.tex
Added mention of SKA.

@@
     $10000$ events. Such a survey is in-line with what may be achieved with
-    upcoming wide-field radio telescopes such as the Canadian
-    Hydrogen Intensity Mapping Experiment (CHIME).
+    upcoming wide-field radio telescopes.
 \end{abstract}
@@
 approximation to what might be achieved by the Canadian Hydrogen Intensity
-Mapping Experiment (CHIME)\footnote{\url{http://chime.phas.ubc.ca/}}
+Mapping Experiment (CHIME)\footnote{\url{http://chime.phas.ubc.ca/}}, the
+Square Kilometer Array\footnote{\url{http://www.skatelescope.org/}},
 or other upcoming wide-field telescopes.

### 2015-06-04 writeup/dm_space_distortions.tex
one more merger junk removal

@@
 information than the CMB because it can be studied in three dimensions.
-Traditionally the redshift of spectral lines, caused by the Hubble flow, has
+Traditionally the redshift of spectral lines of `standard atoms', caused by the Hubble flow, has
 been employed to measure radial distance and provide the third dimension.
@@
 again leading to additional apparent
-clustering of sources in dispersion space.  In this letter we calculate
+clustering of sources in dispersion space.  In this \emph{Letter} we calculate
 these dispersion-space distortions and consider the detectability of the signal by
@@
 within a few correlation lengths of one another, roughly a hundred
-megaparsecs.  The evolution of the power spectrum is negligible over these time
-differences which leads to a straight-forward way to include the evolution:
+megaparsecs.  differences which leads to a straight-forward way to include the evolution of
+the perturbations (essentially indistinguishable from the full expression):
 \begin{align}

### 2015-06-04 writeup/dm_space_distortions.tex
Added NSERC to acknowledgements.  Said 10000 is a modest amount of time for CHIME or SKA

@@
 clustering signal. This is in rough
-approximation to what might be achieved by the Canadian Hydrogen Intensity
+approximation to what might be achieved in a modest amount of time by the Canadian Hydrogen Intensity
 Mapping Experiment (CHIME)\footnote{\url{http://chime.phas.ubc.ca/}}, the
@@
 KWM is supported by the Canadian Institute for Advanced Research, Global Scalars
-Program.
+Program.  The research of KS is supported in part by a National Science and Engineering Research Council (NSERC) of Canada Discovery Grant.
 

### 2015-06-04 writeup/dm_space_distortions.tex
line of sight --> line-of-sight and reference 'standard ping' in conclusion

@@
 negligible. Because radial velocities are only sourced by modes with large
-radial wave vector, there is near perfect cancellation along the line of sight
+radial wave vector, there is near perfect cancellation along the line-of-sight
 and thus is very little net error in radial distance.
@@
 term is completely independent of the limit of integration, meaning
-contributions from different parts of the line of sight (and thus different
+contributions from different parts of the line-of-sight (and thus different
 spatial scales) can be separated exactly. A detailed study of dispersion space
@@
 
-We have proposed using cosmological FRB sources as 3D tracers of the
-large-scale structure,
-using dispersion to estimate radial distance. It can be seen in
+We have proposed using cosmological FRB sources as standard pings to trace the 3D 
+large-scale structure of the Universe using dispersion distance. It can be seen in
 Figure~\ref{f:terms} that the signal is dominated by inhomogeneities in the
-electron density along the line of sight, inducing mis-estimates of radial
+electron density along the line-of-sight in each sky direction, inducing mis-estimates of radial
 distance and thus apparent clustering. These dispersion-space distortions could

### 2015-06-04 writeup/dm_space_distortions.tex
Fixed small grammar issues.

@@
 again leading to additional apparent
-clustering of sources in dispersion space.  In this \emph{Letter} we calculate
+clustering of sources in dispersion space.  In this \emph{letter} we calculate
 these dispersion-space distortions and consider the detectability of the signal by
@@
 within a few correlation lengths of one another, roughly a hundred
-megaparsecs.  differences which leads to a straight-forward way to include the evolution of
-the perturbations (essentially indistinguishable from the full expression):
+megaparsecs.  The evolution of the power spectrum is negligible over these time 
+differences which leads to a straight-forward way to include the evolution of
+the perturbations:
 \begin{align}

### 2015-06-04 writeup/dm_space_distortions.tex
mention one-point statistics in paragraph intrinsic/stocastic DM

--- 2015-06-04 writeup/dm_space_distortions.tex
@@
 modify the mean dispersion--distance relation. This will need to be calibrated in some
-way or else fit with nuisance parameters during parameter estimation.  There
+way or else fit with nuisance parameters during parameter estimation.  
 will also be a stochastic piece which varies from source to source.  This will
 limit the precision at which $\chi_s$ can be measured, thus limiting the
-resolution of dispersion space density maps in the radial direction.
+resolution of dispersion space density maps in the radial direction.  However, we note that one-point statistics from the same dataset that is used to calculate clustering
+should provide empirical information about these properties independent of their physical origin.
 
-Detailed treatment of the above complications is beyond the scope of this
+Detailed treatment of the above source modelling is beyond the scope of this
 work. The magnitude of the contribution from the progenitor is at present

### 2015-06-04 writeup/dm_space_distortions.tex
edit to discussion.

--- 2015-06-04 writeup/dm_space_distortions.tex
@@
 Figure~\ref{f:terms} that the signal is dominated by inhomogeneities in the
-electron density along the line-of-sight in each sky direction, inducing mis-estimates of radial
+electron density along the different lines-of-sight,
+inducing mis-estimates of radial
 distance and thus apparent clustering. These dispersion-space distortions could

### 2015-06-04 writeup/dm_space_distortions.tex
rewording beyond the scope to future work
slight rewordings.

--- 2015-06-04 writeup/dm_space_distortions.tex
@@
 modify the mean dispersion--distance relation. This will need to be calibrated in some
-way or else fit with nuisance parameters during parameter estimation.  There
-will also be a stochastic piece which varies from source to source.  This will
+way or else fit with nuisance parameters during parameter estimation.
+There will also be a stochastic piece which varies from source to source.  This will
 limit the precision at which $\chi_s$ can be measured, thus limiting the
 resolution of dispersion space density maps in the radial direction.
+We note that one-point statistics from the same dataset 
+should provide empirical information about these properties independent
+of their physical origin.
 
-Detailed treatment of the above complications is beyond the scope of this
+Detailed treatment of the above source modelling is beyond the scope of this
 work. The magnitude of the contribution from the progenitor is at present

### 2015-06-04 writeup/dm_space_distortions.tex
footnotes.
end on positive note

@@
 contributions from different parts of the line-of-sight (and thus different
-spatial scales) can be separated exactly. A detailed study of dispersion space
-tomography is beyond the scope of this work.  To avoid our results being
+spatial scales) can be separated exactly. We leave a study of the potential of dispersion space
+tomography to future work.  To avoid our results being
 sensitive to the hard-to-model small scales, we assume that the contribution to the
@@
 term using tomography.
-This however requires that the contribution to dispersion from
-the source's environment and host halo be small compared to the
-contribution from the IGM.
+This however requires that the statistics of the contribution to dispersion from
+the source's environment and host halo to be well understood or small compared to the
+contribution from the line-of-sight.
+
+Finally, we note that alone or by combination of dispersion-space data with redshift-space data on a subset of the population, independent redshift surveys of large-scale-structure, or gravitational lensing data could yield very powerful probes of cosmology.
+Cosmological dispersion-space data could open a new window on to the structure of the Universe.
 

### 2015-06-04 writeup/dm_space_distortions.tex
As posted.

@@
-\documentclass[twocolumn,prl,floatfix]{revtex4-1}
+\documentclass[twocolumn,nofootinbib,prl,floatfix]{revtex4-1}
 \usepackage{graphicx}
@@
 %\title{The large-scale structure of the Universe in dispersion measure space}
-\title{Dispersion distance and the matter distribution of the Universe in dispersion space}
+\title{Dispersion Distance and the Matter Distribution of the Universe in
+Dispersion Space}
 
@@
 
-Finally, we note that alone or by combination of dispersion-space data with redshift-space data on a subset of the population, independent redshift surveys of large-scale-structure, or gravitational lensing data could yield very powerful probes of cosmology.
-Cosmological dispersion-space data could open a new window on to the structure of the Universe.
+Finally, we note that alone---or in combination with
+redshift data on a subset of the population, independent redshift surveys,
+or gravitational lensing surveys---dispersion-space surveys could yield very
+powerful probes of cosmology. Cosmological dispersion-space data could open a
+new window into the structure of the Universe.
 

### 2015-07-28 writeup/referee_response.txt
Started referee response.

> ----------------------------------------------------------------------
> Report of Referee A -- LF15118/Masui
> ----------------------------------------------------------------------
> 
> In this paper, the authors consider the use the dispersion measure of
> radio transients as a proxy for radial distance, and compute the
> expected angular cross-power spectra of biased sources. With simple
> estimates of shot noise, the authors then argue that such power
> spectra should be observable, and suggest that this could be a
> powerful probe of large scale structure.
> 
> The calculation that the authors perform is relatively straightforward
> (though worthwhile) and uncontroversial. To be fair, there are a
> number of details about fast radio bursts (such as their source
> environments) that are swept under the rug. I agree with the authors,
> however, that such issues are beyond the scope of this short paper,
> since investigations into the nature of fast radio bursts is still an
> active area of research for the community. I would be happy to
> recommend publication once the authors explore the following points a
> little more fully:
> 
> i) The authors pick b_f = 1.3 to be the bias of the FRB sources. Was
> this arbitrary?

This was chosen to be roughly the value for star forming galaxies at these
redshifts as measured by the WiggleZ survey. The assumption here is that FRBs
might trace star formation, although this is entirely speculative. It also
provides some contrast with the electrons, since some terms are proportional to
b_e - b_f. This is now stated in the text.

> Also, it would be good to discuss briefly (perhaps
> with a new plot) the dependence of the paper’s conclusions on the
> value of b_f. In principle, variations of b_f could cause interesting
> effects, since b_f affects some of the terms but not others in Eq.
> (22). My guess is that the effects won’t be too big, since Fig. 2
> shows that the integral term is the dominant contribution, but it’d be
> nice to numerically confirm this. If anything, it would be helpful to
> know that the predictions are robust to uncertainties in b_f.

> 
> ii) To plot Fig. 3, the authors summed over pairs of radial bins.
> However, this hides some of the interesting statistical properties of
> the signal. For example, I would expect the cross power spectrum of
> two widely separated radial bins to be much lower than the cross power
> of two nearby bins. I would like to see some quantification of these
> radial correlations, as it would give readers a better sense for how
> the signal-to-noise scales with bin size, number of bins, etc.
> 
> Finally, just an extremely minor pet peeve of mine: can we replace the
> error bars in Fig. 3 with a band around the curve? Real data would
> have scatter, and the error bars wouldn’t be centered on the “truth”.
> 
> Thank you to the authors for an interesting read!

### 2015-07-28 writeup/dm_space_distortions.tex
Started referee response.

@@
 the approximate conservation of free electrons. The bias of FRB sources is
-unconstrained by data and we choose it to be $b_f=1.3$. The coefficient
+unconstrained by data and we choose it to be $b_f=1.3$, \blue{roughly
+the value for star forming galaxies at the relevant
+redshifts \citep{2011MNRAS.415.2876B} and providing reasonable contrast to the
+electrons.}
+\blue{The amplitude of the local and cross terms depend on the difference
+    between 
+}
+The coefficient
 $A(\chi)$ depends on the density of detected FRB sources, $\bar n_f(\chi)$.
@@
 %
-KWM is supported by the Canadian Institute for Advanced Research, Global Scalars
-Program.  The research of KS is supported in part by a National Science and Engineering Research Council (NSERC) of Canada Discovery Grant.
+KWM is supported by the Canadian Institute for Advanced Research, Global
+Scholars Program.  The research of KS is supported in part by a National
+Science and Engineering Research Council (NSERC) of Canada Discovery Grant.
 

### 2015-07-29 writeup/referee_response.txt
referee response.

@@
 
+This was a very helpful comment and led us to include a b_f=0.7 line in
+Figure 3. We conclude that the sensitivity is indeed dominated by the
+integral term and that a survey with 10000 events is unlikely to distinguish
+any signature of the intrinsic clustering.
+
 > 
@@
 > the signal-to-noise scales with bin size, number of bins, etc.
+
+Figure 2 is intended to give a hint of this structure. The integral term and
+the cross term are fairly insensitive to radial separation since any structure
+in the radial integral will correlate. The radial dependence is actually
+dominated by A(\chi).  As shown in the figure, the local term drops rapidly at
+higher separations. We would very much like to show more curves in the style of
+Figure 2 but space constrains preclude this.
+
+We've added a brief statement about this in the discussion.
+We hope that the reviewer finds this satisfactory.
+
 > 
@@
 > have scatter, and the error bars wouldn’t be centered on the “truth”.
+
+Our error bars depend on \ell binning and thus a band is inappropriate.
+We have switched to filled boxes.  This is consistent with the style in 
+Scott Dodelson's text book.
+
 > 

### 2015-07-29 writeup/dm_space_distortions.tex
referee response.

--- 2015-06-04 writeup/dm_space_distortions.tex
@@
 the approximate conservation of free electrons. The bias of FRB sources is
-unconstrained by data and we choose it to be $b_f=1.3$. The coefficient
+unconstrained by data and we choose it to be $b_f=1.3$\blue{, roughly
+the value for star forming galaxies at the relevant
+redshifts \citep{2011MNRAS.415.2876B} and providing reasonable contrast to the
+electrons}.
+The coefficient
 $A(\chi)$ depends on the density of detected FRB sources, $\bar n_f(\chi)$.
@@
 
+\blue{
+The amplitude of the local and cross terms depend on the difference
+between the electron bias and highly uncertain FRB bias
+and the sign of the cross term depends on
+which of these is larger. However, since the
+integral term dominates for most radial distance pairs, our final sensitivity
+estimates are largely unaffected by this uncertainty (as shown below). In a
+high-precision survey the sensitivity of the cross and local terms to the
+difference in the biases may help break measurement degeneracies between terms.
+}
+
 In a real survey, measurement of the dispersion-space clustering
@@
 
-Perhaps, more concerning is the dispersion from the source's immediate environment
+Perhaps more concerning is the dispersion from the source's immediate environment
 as well as the halo in which it resides. These electrons will presumably be
@@
 is near optimal at other multipoles.
+\blue{
+To determine if such a survey would be
+able to distinguish between models of FRB clustering we plot the same quantity
+for $b_f=0.7$.
+}
 The result is shown
@@
         power spectrum weighted averaged over all pairs of radial bins. Weights
-        are chosen to maximize signal to noise at $\ell=100$.
+        are chosen to maximize signal to noise at $\ell=100$ for the $b_f=1.3$
+        case.
     }
@@
 inducing mis-estimates of radial
-distance and thus apparent clustering. These dispersion-space distortions could
+distance and thus apparent clustering.
+\blue{
+Because it is the line-of-sight integrated structure that correlates, the
+signal is fairly insensitive to radial distance and radial separation of
+slices, with these dependencies being dominated by the coefficient $A(\chi)$.
+}
+These dispersion-space distortions could
 be used
 to study the distribution of free electrons in the Universe on large-scales.
-There have been other proposals to use FRBs in cosmology 
+There have been other proposals to use FRBs for cosmology 
 \citep{2014ApJ...780L..33M,2014MNRAS.443L..11D,
@@
 origin could detect the
-clustering signal. This is in rough
-approximation to what might be achieved in a modest amount of time by the Canadian Hydrogen Intensity
+clustering signal\blue{, however such a survey would be mostly sensitive to the
+integral term and thus could not distinguish between FRB clustering models}.
+This is in rough
+approximation to what might be achieved in a reasonable amount of time by the
+Canadian Hydrogen Intensity
 Mapping Experiment (CHIME)\footnote{\url{http://chime.phas.ubc.ca/}}, the

### 2015-07-29 python/assemble_terms.py

@@ -217,12 +217,16 @@ def my_plots(mult_ell=None, chi=1000):
 
     delta_l = np.diff(ells[0::2])
     ell_bins = ells[1:-1:2]
+    ell_bins_l = ells[0:-2:2]
+    ell_bins_r = ells[2::2]
 
     noise = 1. / n_bar_bins / chi_bins**2 / delta_chi_bins
 
     cum_spectrum = 0.
+    cum_spectrum_1 = 0.
     normalization = 0.
     cum_var = 0.
+    global B_F
     #cum_noise = 0.
     for ii, chi1 in enumerate(chi_bins):
         for jj, chi2 in enumerate(chi_bins):
@@ -235,18 +239,33 @@ def my_plots(mult_ell=None, chi=1000):
             cum_spectrum += weight * spectrum
             cum_var += weight**2 * var
             normalization += abs(weight)
+            b_f_tmp = B_F
+            B_F = 0.7
+            t1, t2, t3 = apply_coeffs(mult_ell, (chi1 + chi2)/2, chi1 - chi2)
+            spectrum = t1 + t2 + t3
+            cum_spectrum_1 += weight * spectrum
+            B_F = b_f_tmp
     errors = np.sqrt(cum_var) / normalization
     spectrum = cum_spectrum / normalization
+    spectrum_1 = cum_spectrum_1 / normalization
     # Effective noise power spectrum.
     noise_spec = errors * np.sqrt(ell_bins*(ell_bins + 1)*delta_l*F_SKY)
     
     plt.figure(tight_layout=True)
-    plt.loglog(ells, spectrum, 'k', **kwargs)
     #plt.loglog(ell_bins, noise_spec, 'k--')
     spectrum_bins = interpolate.interp1d(ells, spectrum)(ell_bins)
     ax = plt.subplot(111)
-    plt.errorbar(ell_bins, spectrum_bins, errors, color='k', marker='', ls='',
-            **kwargs)
+    plt.bar(left=ell_bins_l,
+            height=2 * errors,
+            width=ell_bins_r - ell_bins_l,
+            bottom=spectrum_bins - errors, 
+            color='y',
+            lw=0.0,
+            )
+    #plt.errorbar(ell_bins, spectrum_bins, errors, color='k', marker='', ls='',
+    #        **kwargs)
[…]

### 2015-07-30 writeup/referee_response.txt
Change to bias answer.

@@
+We thank the review for the helpful suggestions and positive review. 
+In the revised version of the manuscript, changes are highlighted in blue for
+the reviewers and editor's convenience. Our responses to each of the reviewers
+comments are in-line below.
+
 > ----------------------------------------------------------------------
@@
 
-This was a very helpful comment and led us to include a b_f=0.7 line in
-Figure 3. We conclude that the sensitivity is indeed dominated by the
-integral term and that a survey with 10000 events is unlikely to distinguish
-any signature of the intrinsic clustering.
+This was a very helpful comment and led us to include a b_f=0.7 line in Figure
+3. We conclude that the sensitivity is indeed dominated by the integral term
+and that a survey with 10000 events is unlikely to distinguish any signature of
+the intrinsic clustering.
+
+Time dependence of b_f should similarly be a small effect on the final
+sensitivity. We've added a paragraph about the affect of the biases on the
+various terms in the modelling section.
 
@@
 
-We've added a brief statement about this in the discussion.
-We hope that the reviewer finds this satisfactory.
+We've added a brief statement about this in the discussion.  We hope that the
+reviewer finds this satisfactory.
 

### 2015-07-30 writeup/dm_space_distortions.tex
Change to bias answer.

@@
 high-precision survey the sensitivity of the cross and local terms to the
-difference in the biases may help break measurement degeneracies between terms.
+difference in the biases may help break measurement degeneracies.
 }

### 2015-08-05 writeup/referee_response.txt
As re-submitted.

@@
 Time dependence of b_f should similarly be a small effect on the final
-sensitivity. We've added a paragraph about the affect of the biases on the
-various terms in the modelling section.
+sensitivity, although we agree that the different effects of the bias could be
+exploited in a higher precision survey. We've added a paragraph about the
+effect of the biases on the various terms in the modelling section.
 
@@
 Figure 2 is intended to give a hint of this structure. The integral term and
-the cross term are fairly insensitive to radial separation since any structure
-in the radial integral will correlate. The radial dependence is actually
-dominated by A(\chi).  As shown in the figure, the local term drops rapidly at
-higher separations. We would very much like to show more curves in the style of
-Figure 2 but space constrains preclude this.
+the cross term are fairly insensitive to radial separation since any
+overlapping structure in the radial integral will correlate. The radial
+dependence is actually dominated by A(\chi).  As shown in Gigure 2, the local
+term drops rapidly at higher separations. We would very much like to show more
+curves in the style of Figure 2 but space constrains preclude this.
 
@@
 Our error bars depend on \ell binning and thus a band is inappropriate.
-We have switched to filled boxes.  This is consistent with the style in 
-Scott Dodelson's text book.
+However we agree with the points of the referee and we have thus switched to
+filled boxes to approximate a band.  This is consistent with the style in, for
+example, Scott Dodelson's text book.
 

### 2015-08-05 writeup/dm_space_distortions.tex
As re-submitted.

@@
 high-precision survey the sensitivity of the cross and local terms to the
-difference in the biases may help break measurement degeneracies.
+difference in the biases may help break measurement degeneracies, while sign
+changes of terms as a function of radial distance are a signature of
+bias evolution.
 }
@@
 able to distinguish between models of FRB clustering we plot the same quantity
-for $b_f=0.7$.
+for $b_f=0.8$.
 }
@@
 origin could detect the
-clustering signal\blue{, however such a survey would be mostly sensitive to the
-integral term and thus could not distinguish between FRB clustering models}.
+clustering signal.
 This is in rough
@@
 or other upcoming wide-field telescopes.
+\blue{Such a survey would be primarily sensitive to the integral 
+term and thus rather insensitive to the details of FRB clustering models.}
 Looking forward, dispersion-space

### 2015-08-05 python/assemble_terms.py

@@ -222,50 +222,51 @@ def my_plots(mult_ell=None, chi=1000):
 
     noise = 1. / n_bar_bins / chi_bins**2 / delta_chi_bins
 
-    cum_spectrum = 0.
-    cum_spectrum_1 = 0.
-    normalization = 0.
-    cum_var = 0.
-    global B_F
-    #cum_noise = 0.
-    for ii, chi1 in enumerate(chi_bins):
-        for jj, chi2 in enumerate(chi_bins):
-            if ii == jj:
-                continue
-            var = noise[ii]*noise[jj] / (ell_bins*(ell_bins + 1)*delta_l*F_SKY)
-            t1, t2, t3 = apply_coeffs(mult_ell, (chi1 + chi2)/2, chi1 - chi2)
-            spectrum = t1 + t2 + t3
-            weight = spectrum[ind_100] / (noise[ii]*noise[jj])
-            cum_spectrum += weight * spectrum
-            cum_var += weight**2 * var
-            normalization += abs(weight)
-            b_f_tmp = B_F
-            B_F = 0.7
-            t1, t2, t3 = apply_coeffs(mult_ell, (chi1 + chi2)/2, chi1 - chi2)
-            spectrum = t1 + t2 + t3
-            cum_spectrum_1 += weight * spectrum
-            B_F = b_f_tmp
-    errors = np.sqrt(cum_var) / normalization
-    spectrum = cum_spectrum / normalization
-    spectrum_1 = cum_spectrum_1 / normalization
-    # Effective noise power spectrum.
-    noise_spec = errors * np.sqrt(ell_bins*(ell_bins + 1)*delta_l*F_SKY)
-    
+
     plt.figure(tight_layout=True)
-    #plt.loglog(ell_bins, noise_spec, 'k--')
-    spectrum_bins = interpolate.interp1d(ells, spectrum)(ell_bins)
     ax = plt.subplot(111)
-    plt.bar(left=ell_bins_l,
-            height=2 * errors,
-            width=ell_bins_r - ell_bins_l,
-            bottom=spectrum_bins - errors, 
-            color='y',
-            lw=0.0,
-            )
-    #plt.errorbar(ell_bins, spectrum_bins, errors, color='k', marker='', ls='',
-    #        **kwargs)
-    s0 = plt.loglog(ells, spectrum, 'k-', **kwargs)
-    s1 = plt.loglog(ells, spectrum_1, 'b--', **kwargs)
+    global B_F
[…]

### 2015-08-05 writeup/summary.tex
started summary.tex

\documentclass{article}

\title{Mysterious radio flashes to be used to trace Universe's largest
structures}

\date{\today}

\author{Kiyoshi Wesley Masui and Kris Sigurdson}

\begin{document}

\maketitle

One of the most challenging aspects of astronomy is measuring distances.

\end{document}

### 2015-08-05 writeup/summary.tex
Added justification text.

@@
 
+%%%%% Justification text for submission. %%%%
+The study of the large-scale structure of the Universe has the potential to
+shed light on aspects of fundamental physics including the nature of
+cosmological inflation, the nature of dark energy, and the properties of
+neutrinos.  It is thus of broad appeal to the physics community. This work
+opens up a new way to study large-scale structure in three dimensions and is
+observationally relevant on short time scales of the next few years.
+
 \end{document}

### 2015-08-12 writeup/summary.tex
wrote summary

--- 2015-08-05 writeup/summary.tex
@@
 
-One of the most challenging aspects of astronomy is measuring distances.
+One of the most challenging aspects of astronomy is knowing distances to far
+off objects. Newly discovered fast radio bursts---originating from across the
+Universe---provide distance measurements that will enable the largest
+structures of the cosmos to be studied in three dimensions. Traditionally,
+cosmological distances are measured using Doppler shifts caused by the Hubble
+expansion of the Universe. Distortions to brief radio signals can be used to
+measure the total amount material between earth and the source, permitting
+another way to measure distance. However this process isn't perfect.
+Intervening clumps of matter can distort the distance measure, a fact that can
+be exploited to glean yet more information about the Universe's structure.
+Wide-field radio telescopes are expecting to detect thousands of these radio
+bursts, opening a new window for studying the cosmos.
 

### 2015-08-12 python/assemble_terms.py

@@ -112,8 +112,8 @@ def my_plots(mult_ell=None, chi=1000):
     if mult_ell is None:
         mult_ell = get_mult_ell()
     CHI = float(chi)
-    #DELTAS = [5., 10., 20., 50., 100.]
-    DELTAS = []
+    DELTAS = [5., 10., 20., 50., 100.]
+    #DELTAS = []
     Y_MIN = 5e-8
     Y_MAX = 5e-5
     X_MIN = 9
@@ -138,6 +138,9 @@ def my_plots(mult_ell=None, chi=1000):
                    fontsize=18,
                    )
         plt.legend(loc="upper right", labelspacing=.1, frameon=False)
+        plt.savefig("terms_chi%d_delta%d.pdf" % (CHI, delta),
+                tightlayout=True, bbox_inches='tight'
+                )
 
     
 
@@ -226,7 +229,8 @@ def my_plots(mult_ell=None, chi=1000):
     plt.figure(tight_layout=True)
     ax = plt.subplot(111)
     global B_F
-    for min_sep in [12, 8, 4, 1]:
+    #for min_sep in [12, 8, 4, 1]:
+    for min_sep in [1]:
         cum_spectrum = 0.
         cum_spectrum_1 = 0.
         normalization = 0.

### 2015-08-13 writeup/summary.tex
clairity edits to summary.

--- 2015-08-05 writeup/summary.tex
@@
 
-One of the most challenging aspects of astronomy is measuring distances.
+One of the most challenging aspects of astronomy is determining distances to
+far off objects. Newly discovered fast radio bursts---thought to originate from
+the far reaches of the Universe---provide distance measurements that will
+enable the largest structures of the cosmos to be studied in three dimensions.
+Traditionally, cosmological distances are obtained using Doppler shifts caused
+by the Hubble expansion of the Universe. In contrast, distortions to fast radio
+burst signals can be used to measure the total amount material between earth
+and the burst's source, permitting another way to determine distance.  However
+this process isn't perfect, as intervening clumps of excess matter can distort the
+measured distance. This fact can be exploited to glean yet more
+information through these intervening structures.  Wide-field radio telescopes
+are expecting to detect thousands of these bursts, opening a new window for
+studying the cosmos.
 

### 2015-08-14 writeup/dm_space_distortions.tex
Implemented copy-edits.

@@
 \newcommand{\calP}{{\cal P}}
-\newcommand{\ud}{\,\mathrm{d}}
+%\newcommand{\ud}{\,\mathrm{d}}
+\newcommand{\ud}{\,d}
 
@@
 \newcommand{\red}{\textcolor{red}}
-\newcommand{\blue}{\textcolor{blue}}
+\newcommand{\blue}{}
+%\newcommand{\blue}{\textcolor{blue}}
 \newcommand{\green}{\textcolor{green}}
@@
 
-\makeatletter
-
-\renewcommand{\section}[1]{\emph{#1}---\ignorespacesandimplicitepars}
+\renewcommand{\section}[1]{\emph{#1.}---\ignorespacesandimplicitepars}
 \renewcommand{\subsection}[1]{}
@@
 \input{AAS_macros.tex}
+
+\makeatother
 
@@
  \affiliation{Department of Physics and Astronomy, University of British 
-Columbia, Vancouver, BC, Canada, V6T 1Z1}
+Columbia, Vancouver, British Columbia, V6T 1Z1, Canada}
  \affiliation{Canadian Institute for Advanced Research, CIFAR Program in
-Cosmology and Gravity, Toronto, ON, Canada, M5G 1Z8}
+Cosmology and Gravity, Toronto, Ontario, M5G 1Z8, Canada}
 
@@
  \affiliation{Department of Physics and Astronomy, University of British 
-Columbia, Vancouver, BC, Canada, V6T 1Z1}
+Columbia, Vancouver, British Columbia, V6T 1Z1, Canada}
 
@@
 
-    We propose that `standard pings', brief broadband radio impulses, can be
+    We propose that ``standard pings'', brief broadband radio impulses, can be
     used to study the three-dimensional clustering of matter in the Universe
@@
     like redshift, be used as a
-    cosmological distance measure.  Due to inhomogeneities in the electron
-    density along the line-of-sight, dispersion is an imperfect proxy for
+    cosmological distance measure.  Because of inhomogeneities in the electron
+    density along the line of sight, dispersion is an imperfect proxy for
     radial distance and we show that this leads to calculable dispersion-space
@@
     are a new class of radio transients that are the prototypical standard
-    ping, and due to their high observed dispersion,
+    ping and, due to their high observed dispersion,
     have been interpreted as originating at cosmological distances.  The rate
     of fast radio bursts has been estimated to be several thousand over the
-    whole sky per day, and if cosmological, the sources of these events should
+    whole sky per day and, if cosmological, the sources of these events should
     trace the large-scale structure of the Universe.  We calculate the
     dispersion-space power spectra for a simple model where electrons and FRBs
-    are biased tracers of the large-scale structure of the Universe and show
+    are biased tracers of the large-scale structure of the Universe and we show
     that the clustering signal could be measured using as few as
-    $10000$ events. Such a survey is in-line with what may be achieved with
+    $10\,000$ events. Such a survey is in line with what may be achieved with
     upcoming wide-field radio telescopes.
@@
 heralded as the next great probe of the Universe after the cosmic microwave
-background (CMB). The large-scale structure in principle contains far more
+background (CMB). The large-scale structure, in principle, contains far more
 information than the CMB because it can be studied in three dimensions.
-Traditionally the redshift of spectral lines of `standard atoms', caused by the Hubble flow, has
+Traditionally, the redshift of spectral lines of ``standard atoms'', 
+caused by the Hubble flow, has
 been employed to measure radial distance and provide the third dimension.
@@
 dimensional density maps, exposing a rich structure of clusters, filaments,
-walls and voids.
+walls, and voids.
 
@@
 candles and standard rulers can be used to estimate distance using brightness
-and angular size respectively.  In the same way a \emph{standard ping}, a brief
+and angular size, respectively.  In the same way a ``standard ping'', a brief
 broadband radio impulse, can be used to measure dispersion through the
@@
 proportional to the amount of plasma along the
-line-of-sight and can thus be used to estimate radial distance.
+line of sight and can thus be used to estimate radial distance.
 This technique, routinely used for
@@
 
-Dispersion is readily measured from fast radio bursts (FRB),
+Dispersion is readily measured from fast radio bursts (FRBs),
 a new class of millisecond duration radio transients first reported by
@@
 $\sim\!\!100\,{\rm pc} / {\rm cm}^3$ (depending on galactic latitude)
-\cite{2014arXiv1412.4829D}.  They thus appear to be of extra-galactic origin,
-with their dispersion produced either by the inter-galactic medium (IGM),
-associated with structure along line-of-sight \citep{2013Sci...341...53T},
+\cite{2014arXiv1412.4829D}.  They thus appear to be of extragalactic origin,
+with their dispersion produced either by the intergalactic medium (IGM),
+associated with structure along line of sight \citep{2013Sci...341...53T},
 or the environment of the
 source \citep{2014ApJ...785L..26L,2015arXiv150101341P,2015arXiv150505535C}.  If
-the dispersion is dominated by electrons along the line-of-sight, then the
-average dispersion--distance relation can be modelled
+the dispersion is dominated by electrons along the line of sight, then the
+average dispersion--distance relation can be modeled
 \citep{2014ApJ...797...71Z,2004MNRAS.348..999I, 2003ApJ...598L..79I} and the
@@
 Such cosmological distances permit the study of the clustering of FRB sources in
-three dimensions with an expectation that these events trace the large-scale
+three dimensions, with an expectation that these events trace the large-scale
 structure of the Universe on linear scales. We note that while our discussion
 here is framed in terms of FRBs, other bright radio transients that fluctuate
-on timescales shorter than the typical differential lag of $\sim 1s/100 \,{\rm
+on time scales shorter than the typical differential lag of $\sim 1s/100 \,{\rm
 MHz} $ might also be useful as standard pings.
@@
 again leading to additional apparent
-clustering of sources in dispersion space.  In this \emph{letter} we calculate
+clustering of sources in dispersion space.  In this Letter we calculate
 these dispersion-space distortions and consider the detectability of the signal by
@@
 
-\emph{Dispersion space} is the three dimensional coordinates,
-$\vec x_s$ inferred from the dispersion measure assuming that the electrons are
+\emph{Dispersion space} is the three-dimensional coordinates,
+$\vec x_s$, inferred from the dispersion measure assuming that the electrons are
 homogeneous. This only affects the radial coordinate such that $\vec x_s = \hat
-n \chi_s$ with $\chi_s$ defined by the equation
+n \chi_s$, with $\chi_s$ defined by the equation
 \begin{equation}
@@
 \end{equation}
-Averaged over the sky, $\langle \chi_s \rangle = \chi$ and thus the background
+Averaged over the sky, $\langle \chi_s \rangle = \chi$, and thus the background
 density should
@@
 
-Substituting Equations~\ref{e:nfs}~and~\ref{e:jac} into Equation~\ref{e:density},
+Substituting Eqs.~\ref{e:nfs}~and~\ref{e:jac} into Eq.~\ref{e:density},
 we obtain
@@
 in contrast to the Kaiser term.  This is because any wave vector electron perturbation
-causes dispersion space distortions, whereas the radial velocities that cause
+causes dispersion-space distortions, whereas the radial velocities that cause
 redshift-space distortions are only sourced by perturbations with radial wave
@@
 caused by a misinterpretation of angular distances when the radial distance is
-mis-measured.  In both cases analogous terms are in principle present in 
+mismeasured.  In both cases, analogous terms are, in principle, present in 
 redshift space but are
-negligible. Because radial velocities are only sourced by modes with large
-radial wave vector, there is near perfect cancellation along the line-of-sight
-and thus is very little net error in radial distance.
+negligible. Because radial velocities are only sourced by modes with a large
+radial wave vector, there is near perfect cancellation along the line of sight,
+and thus there is very little net error in the radial distance.
 
-For brevity in the following sections we define the coefficient of the integral
+For brevity in the following sections, we define the coefficient of the integral
 term as
@@
 commonly the power spectrum, $P(k)$.
-Unlike the redshift-space distortions, Equation~\ref{e:delta_s} does not have a
-simple form in harmonic space. The equation's third term couples harmonic modes
+Unlike the redshift-space distortions, Eq.~\ref{e:delta_s} does not have a
+simple form in harmonic space. The equation's third term couples harmonic
+modes,
 and thus the two-point statistics cannot be phrased as a simple power spectrum.
 We will instead use $C^{ss}_\ell(\chi,\chi')$, which is
-the cross-correlation angular power spectrum of the dispersion-space over-density,
+the cross-correlation angular power spectrum of the dispersion-space overdensity,
 on shells at $\chi$ and $\chi'$:
@@
 \end{align}
-The first two terms in Equation~\ref{e:delta_s} are stationary. For stationary,
-isotropic, tracers $x$ and $y$ we have 
+The first two terms in Eq.~\ref{e:delta_s} are stationary. For stationary,
+isotropic tracers $x$ and $y$, we have 
 $\langle \delta_x(\vec k, \chi) \delta_y(\vec k', \chi) \rangle = (2\pi)^3
-\delta^3(\vec k - \vec k') P_{xy}(k, \chi)$.  If for a moment we ignore
+\delta^3(\vec k - \vec k') P_{xy}(k, \chi)$.  If, for a moment, we ignore
 structure evolution, the angular cross-power spectrum of such tracers is
@@
 megaparsecs.  The evolution of the power spectrum is negligible over these time
-differences which leads to a straight-forward way to include the evolution:
+differences, which leads to a straightforward way to include the evolution:
 \begin{align}
@@
 
-The third term in Equation~\ref{e:delta_s} is not stationary but is an integral
+The third term in Eq.~\ref{e:delta_s} is not stationary but is an integral
 over the stationary field $\delta_e$.
@@
 \end{equation}
-It is straight-forward to show that
+It is straightforward to show that
 \begin{widetext}
@@
 
-Assembling all these expressions with the proper coefficients we have
+Assembling all of these expressions with the proper coefficients, we have
 \begin{align}
@@
 \end{widetext}
-Here, expressions such as $P_{[ff + ee - 2ef]}$ are short hand for $P_{ff} +
+Here, expressions such as $P_{[ff + ee - 2ef]}$ are shorthand for $P_{ff} +
 P_{ee} - 2P_{ef}$.
@@
 with a Fourier transform, and is valid for $\ell \gg 1$. The Limber
-approximation assumes that only modes with small radial component of their wave
+approximation assumes that only modes with a small radial component of their wave
 vector contribute to the radial integrals and is valid if the power spectra
@@
 (which has already been
-assumed). With these approximations we have
+assumed). With these approximations, we have
 \begin{align}
@@
 and $\chi_{\max} \equiv \max(\chi,
-\chi')$ .  We've found that these approximations are accurate to within $3\%$ at
+\chi')$ .  We have found that these approximations are accurate to within $3\%$ at
 $\ell \gtrsim 10$
-and use this form for the remainder of the paper. In the above equation we dub
-the three terms the `local', `integral' and `cross' terms respectively and will
+and use this form for the remainder of the Letter. In the above equation, we dub
+the three terms the ``local'', ``integral'' and ``cross'' terms, respectively,
+and we will
 refer to them as such henceforth.
@@
 
-The second term in Equation~\ref{e:Clss_limber} is an integral that mixes
+The second term in Eq.~\ref{e:Clss_limber} is an integral that mixes
 many spatial scales: small scales from smaller radial distance and larger
 scales from greater distances. The mixing of scales complicates the
-interpretation of measurements, since structure formation on scales smaller
-than $\sim10\,{\rm Mpc}/h$ is non-linear and hard to model. A similar issue
+interpretation of measurements since structure formation on scales smaller
+than $\sim10\,{\rm Mpc}/h$ is nonlinear and hard to model. A similar issue
 exists in the field of weak gravitational lensing, where the formula for the
@@
 Lensing tomography is inexact because the kernel's shape depends on
-the source redshift, thus re-weighting the line-of-sight integral.
+the source redshift, thus reweighting the line-of-sight integral.
 In contrast, the integrand in the dispersion-space integral
 term is completely independent of the limit of integration, meaning
-contributions from different parts of the line-of-sight (and thus different
-spatial scales) can be separated exactly. We leave a study of the potential of dispersion space
+contributions from different parts of the line of sight (and thus different
+spatial scales) can be separated exactly. We leave a study of the potential
+of dispersion-space
 tomography to future work.  To avoid our results being
@@
 
-For plotting the dispersion-space power spectra we use a toy model for the electron and
+For plotting the dispersion-space power spectra,
+we use a toy model for the electron and
 FRB clustering that assumes both are biased tracers of the dark matter:
@@
 calculate the time dependant dark-matter power spectrum using {\tt CAMB}, using
-the integrated {\tt HALOFIT} to approximate the non-linear evolution. We assume
+the integrated {\tt HALOFIT} to approximate the nonlinear evolution. We assume
 that the electron bias is $b_e=1$, which should be true on large scales due to
@@
 the intrinsic luminosity function has the form from
-\citet{1976ApJ...203..297S} with index $-1$, and events at the cut off of the
+\citet{1976ApJ...203..297S} with index $-1$, and events at the cutoff of the
 luminosity function and at
 a radial distance of $\chi=2350\,{\rm Mpc}/h$ are at the flux detection threshold.
-This source density is shown in Figure~\ref{f:n_f} with the resulting dispersion-space
-power spectrum in Figure~\ref{f:terms}.
+This source density is shown in Fig.~\ref{f:n_f} with the resulting dispersion-space
+power spectrum in Fig.~\ref{f:terms}.
 
@@
         \label{f:n_f}
-        \emph{Top:} Comoving density of sources in toy model, as described in
+        (Top) Comoving density of sources in toy model, as described in
         text. Normalization is
-        such that the survey has a total of $10000$ FRB events.
-        \emph{Bottom:} Resulting coefficient $A(\chi)$ as given in
-        Equation~\ref{e:A}.
+        such that the survey has a total of $10\,000$ FRB events.
+        (Bottom) Resulting coefficient $A(\chi)$ as given in
+        Eq.~\ref{e:A}.
     }
@@
         $\chi - \chi' = 10\,{\rm Mpc}/h$, except the lowest most 
-        ``local term'' curve which is for $\chi - \chi'=50\,{\rm Mpc}/h$. 
+        local term curve, which is for $\chi - \chi'=50\,{\rm Mpc}/h$. 
         While
@@
 \blue{
-The amplitude of the local and cross terms depend on the difference
-between the electron bias and highly uncertain FRB bias
+The amplitudes of the local and cross terms depend on the difference
+between the electron bias and the highly uncertain FRB bias,
 and the sign of the cross term depends on
@@
 estimates are largely unaffected by this uncertainty (as shown below). In a
-high-precision survey the sensitivity of the cross and local terms to the
+high-precision survey, the sensitivity of the cross and local terms to the
 difference in the biases may help break measurement degeneracies, while sign
@@
 will be complicated by extra contributions to the dispersion.
-Firstly, all signals
+First, all signals
 must pass through the Milky Way's galactic disk, halo, and local environment.
 However, the resulting dispersion is only a
-single function of $\hat n$ which can presumably be well
+single function of $\hat n$ which presumably can be well
 measured. As such, it should be
@@
 correlations included in the above formalism.  This will have a mean
-contribution, common to all sources and which may be epoch dependant, that will
+contribution, which is common to all sources and which may be epoch dependant, 
+that will
 modify the mean dispersion--distance relation. This will need to be calibrated in some
@@
 limit the precision at which $\chi_s$ can be measured, thus limiting the
-resolution of dispersion space density maps in the radial direction.
-We note that one-point statistics from the same dataset 
+resolution of dispersion-space density maps in the radial direction.
+We note that one-point statistics from the same data set 
 should provide empirical information about these properties independent
@@
 Detailed treatment of the above source modelling is beyond the scope of this
-work. The magnitude of the contribution from the progenitor is at present
-unknown. To crudely deal with it here we use relatively large
-bins widths of $\Delta\chi = 100\,{\rm Mpc}/h$
+Letter. The magnitude of the contribution from the progenitor is, at present,
+unknown. To crudely deal with it here, we use relatively large
+bin widths of $\Delta\chi = 100\,{\rm Mpc}/h$
 and exclude the $\chi = \chi'$ bin pairs.
@@
 dominated by the finite number of observed events, or shot noise.
-The noise power spectrum on shells at distance with of width
+The noise power spectrum on shells at a distance $\chi_i$ with width
 $\Delta \chi$ is
@@
 Here, to indicate that we are now working with quantities binned in the radial
-direction, we've switched to $C_{\ell,ij}$ instead of
+direction, we have switched to $C_{\ell,ij}$ instead of
 $C_\ell(\chi, \chi')$. The uncertainty on the angular
@@
 
-We consider the sensitivity of a survey with a total of $10000$ dispersion
-measures from FRB events distributed uniformly over half the sky.
+We consider the sensitivity of a survey with a total of $10\,000$ dispersion
+measures from FRB events distributed uniformly over half of the sky.
 To give an idea of the overall sensitivity of the survey, we collapse
@@
 range $500\,{\rm Mpc}/h$ to $3500\,{\rm Mpc}/h$.
-For weights we use the signal over noise-squared
+For weights we use the signal over noise squared
 at $\ell=100$, which maximizes the signal to noise at that $\ell$ and
@@
 The result is shown
-in Figure~\ref{f:sensitivity}.
+in Fig.~\ref{f:sensitivity}.
 
@@
         \label{f:sensitivity}
-        Sensitivity of a survey with $10000$ dispersion measures distributed
-        uniformly over half the sky.  Plotted is the cross-correlation
+        Sensitivity of a survey with $10\,000$ dispersion measures distributed
+        uniformly over half of the sky.  Plotted is the cross-correlation
         power spectrum weighted averaged over all pairs of radial bins. Weights
@@
 large-scale structure of the Universe using dispersion distance. It can be seen in
-Figure~\ref{f:terms} that the signal is dominated by inhomogeneities in the
-electron density along the different lines-of-sight,
-inducing mis-estimates of radial
-distance and thus apparent clustering.
+Fig.~\ref{f:terms} that the signal is dominated by inhomogeneities in the
+electron density along the different lines of sight,
+inducing misestimates of radial
+distance, and thus apparent clustering.
 \blue{
 Because it is the line-of-sight integrated structure that correlates, the
-signal is fairly insensitive to radial distance and radial separation of
+signal is fairly insensitive to radial distance and the radial separation of
 slices, with these dependencies being dominated by the coefficient $A(\chi)$.
@@
 be used
-to study the distribution of free electrons in the Universe on large-scales.
+to study the distribution of free electrons in the Universe on large scales.
 There have been other proposals to use FRBs for cosmology 
 \citep{2014ApJ...780L..33M,2014MNRAS.443L..11D,
-2014ApJ...783L..35D,2014PhRvD..89j7303Z,2014ApJ...788..189G}, however these
+2014ApJ...783L..35D,2014PhRvD..89j7303Z,2014ApJ...788..189G}; however these
 schemes have either not been three dimensional
@@
 We have
-shown in Figure~\ref{f:sensitivity}
-that a survey detecting $10000$ fast radio bursts of cosmological
+shown in Fig.~\ref{f:sensitivity}
+that a survey detecting $10\,000$ fast radio bursts of cosmological
 origin could detect the
@@
 Mapping Experiment (CHIME)\footnote{\url{http://chime.phas.ubc.ca/}}, the
-Square Kilometer Array\footnote{\url{http://www.skatelescope.org/}},
+Square Kilometre Array\footnote{\url{http://www.skatelescope.org/}},
 or other upcoming wide-field telescopes.
@@
 clustering could become a precision probe of large-scale structure should
-observational factors turn out to be favourable compared to spectroscopic
+observational factors turn out to be favorable compared to spectroscopic
 surveys. The baryon acoustic oscillation feature can be clearly seen in
-Figure~\ref{f:terms} in the cross term and both
-local-term curves. It may also be possible to extract the BAO feature
+Fig.~\ref{f:terms} in the cross term and both
+local-term curves. It may also be possible to extract the baryon acoustic
+oscillation feature
 from the integral
 term using tomography.
-This however requires that the statistics of the contribution to dispersion from
+This, however, requires that the statistics of the contribution to dispersion from
 the source's environment and host halo to be well understood or small compared to the
-contribution from the line-of-sight.
+contribution from the line of sight.
 
@@
 
-We thank Ue-Li Pen and Mathew McQuinn for helpful discussions.
+We thank Ue-Li Pen and Mathew McQuinn the for helpful discussions.
 %
-KWM is supported by the Canadian Institute for Advanced Research, Global
-Scholars Program.  The research of KS is supported in part by a National
+K.W.\,M is supported by the Canadian Institute for Advanced Research, Global
+Scholars Program.  The research of K.\,S. is supported in part by a National
 Science and Engineering Research Council (NSERC) of Canada Discovery Grant.

### 2015-08-14 writeup/summary.tex
Implemented copy-edits.

@@
 One of the most challenging aspects of astronomy is determining distances to
-far off objects. Newly discovered fast radio bursts---thought to originate from
+far-off objects. Newly discovered fast radio bursts---thought to originate from
 the far reaches of the Universe---provide distance measurements that will
 enable the largest structures of the cosmos to be studied in three dimensions.
-Traditionally, cosmological distances are obtained using Doppler shifts caused
+Traditionally cosmological distances are obtained using Doppler shifts, caused
 by the Hubble expansion of the Universe. In contrast, distortions to fast radio

### 2015-08-14 writeup/dm_space_distortions.tex
Copy edits.

@@
 $\sim\!\!100\,{\rm pc} / {\rm cm}^3$ (depending on galactic latitude)
-\cite{2014arXiv1412.4829D}.  They thus appear to be of extragalactic origin,
-with their dispersion produced either by the intergalactic medium (IGM),
+\cite{2015MNRAS.451.4277D}.  They thus appear to be of extragalactic origin,
+with their dispersion produced either by the intergalactic medium,
 associated with structure along line of sight \citep{2013Sci...341...53T},
 or the environment of the
-source \citep{2014ApJ...785L..26L,2015arXiv150101341P,2015arXiv150505535C}.  If
+source \citep{2014ApJ...785L..26L,2015ApJ...807..179P,2015arXiv150505535C}.  If
 the dispersion is dominated by electrons along the line of sight, then the
@@
 dominated by the finite number of observed events, or shot noise.
-The noise power spectrum on shells at a distance $\chi_i$ with width
+The noise power spectrum on shells at a distance $\chi_i$ and with width
 $\Delta \chi$ is

### 2015-08-14 writeup/summary_krs.tex
whatever.

--- 2015-08-14 writeup/summary.tex
@@
 
-\title{Mysterious radio flashes to be used to trace Universe's largest
+\title{Mysterious radio flashes could be used to trace Universe's largest
 structures}
@@
 far-off objects. Newly discovered fast radio bursts---thought to originate from
-the far reaches of the Universe---provide distance measurements that will
+the far reaches of the Universe---provide distance measurements that may
 enable the largest structures of the cosmos to be studied in three dimensions.
-Traditionally cosmological distances are obtained using Doppler shifts, caused
-by the Hubble expansion of the Universe. In contrast, distortions to fast radio
+Traditionally cosmological distances are obtained using Doppler, caused
+by the Hubble expansion of the Universe. In contrast, delays to fast radio
 burst signals can be used to measure the total amount material between earth

### 2015-08-19 writeup/summary_krs.tex
New summary text for vKris

@@
 
-\title{Mysterious radio flashes could be used to trace Universe's largest
-structures}
+\title{Mysterious radio flashes could trace Universe's largest structures}
 
@@
 
-One of the most challenging aspects of astronomy is determining distances to
-far-off objects. Newly discovered fast radio bursts---thought to originate from
-the far reaches of the Universe---provide distance measurements that may
-enable the largest structures of the cosmos to be studied in three dimensions.
-Traditionally cosmological distances are obtained using Doppler, caused
-by the Hubble expansion of the Universe. In contrast, delays to fast radio
-burst signals can be used to measure the total amount material between earth
-and the burst's source, permitting another way to determine distance.  However
-this process isn't perfect, as intervening clumps of excess matter can distort the
-measured distance. This fact can be exploited to glean yet more
-information through these intervening structures.  Wide-field radio telescopes
-are expecting to detect thousands of these bursts, opening a new window for
-studying the cosmos.
+One fundamental aspect of astronomy is mapping the distances to far-off objects.
+Newly discovered fast radio bursts---thought to originate from the far reaches of the cosmos---signal distance measurements that may enable the largest structures in the Universe to be studied in three dimensions.
+Cosmological distances are traditionally determined using the redshift of photons induced by the expansion of the Universe.
+In contrast, delays to fast radio bursts at different wavelengths tally the total amount of material between the burst and Earth, enabling a new  way to infer cosmological distance.
+As cosmic matter distorts the inferred distances in a direction dependent way these dispersion distances don’t exactly match actual distances.
+However, these distortions reveal even more information about the intervening structure.
+Wide-field radio telescopes could detect thousands of these bursts, opening a new window for studying the cosmos.
 

### 2015-08-20 writeup/summary.tex
merged summaries.

@@
 
-\title{Mysterious radio flashes to be used to trace Universe's largest
+\title{Mysterious radio flashes could trace Universe's largest
 structures}
@@
 far-off objects. Newly discovered fast radio bursts---thought to originate from
-the far reaches of the Universe---provide distance measurements that will
+the far reaches of the Universe---provide distance measurements that may
 enable the largest structures of the cosmos to be studied in three dimensions.
-Traditionally cosmological distances are obtained using Doppler shifts, caused
-by the Hubble expansion of the Universe. In contrast, distortions to fast radio
-burst signals can be used to measure the total amount material between earth
-and the burst's source, permitting another way to determine distance.  However
-this process isn't perfect, as intervening clumps of excess matter can distort the
-measured distance. This fact can be exploited to glean yet more
-information through these intervening structures.  Wide-field radio telescopes
-are expecting to detect thousands of these bursts, opening a new window for
-studying the cosmos.
+Cosmological distances are traditionally determined using Doppler shifts, caused
+by the Hubble expansion of the Universe. In contrast, delays to fast radio
+burst signals can be used to tally the total amount of material between earth
+and the burst's source, permitting another way to determine distance.
+As intervening clumps of cosmic matter can add extra delay, these
+measured distances don't exactly match the actual distances.
+However, these distortions reveal information about the intervening
+structure.
+Wide-field radio telescopes could detect thousands of these bursts, opening a
+new window for studying the cosmos.
 

### 2019-06-11 writeup/dm_space_cross.tex
Work on cross correaltions.

--- 2015-08-14 writeup/dm_space_distortions.tex
@@
 %\title{The large-scale structure of the Universe in dispersion measure space}
-\title{Dispersion Distance and the Matter Distribution of the Universe in
-Dispersion Space}
+\title{Cross-Correlations Between Galaxies and Dispersion-Space Fast Radio
+Bursts}
 
 \author{Kiyoshi Wesley Masui}
- \affiliation{Department of Physics and Astronomy, University of British 
-Columbia, Vancouver, British Columbia, V6T 1Z1, Canada}
- \affiliation{Canadian Institute for Advanced Research, CIFAR Program in
-Cosmology and Gravity, Toronto, Ontario, M5G 1Z8, Canada}
-
-\author{Kris Sigurdson}
- \affiliation{Department of Physics and Astronomy, University of British 
-Columbia, Vancouver, British Columbia, V6T 1Z1, Canada}
 
@@
 
-    We propose that ``standard pings'', brief broadband radio impulses, can be
-    used to study the three-dimensional clustering of matter in the Universe
-    even in the absence of redshift information.  The dispersion of radio waves
-    as they travel through the intervening plasma can,
-    like redshift, be used as a
-    cosmological distance measure.  Because of inhomogeneities in the electron
-    density along the line of sight, dispersion is an imperfect proxy for
-    radial distance and we show that this leads to calculable dispersion-space
-    distortions in the apparent clustering of sources. Fast radio bursts (FRBs)
-    are a new class of radio transients that are the prototypical standard
-    ping and, due to their high observed dispersion,
-    have been interpreted as originating at cosmological distances.  The rate
-    of fast radio bursts has been estimated to be several thousand over the
-    whole sky per day and, if cosmological, the sources of these events should
-    trace the large-scale structure of the Universe.  We calculate the
-    dispersion-space power spectra for a simple model where electrons and FRBs
-    are biased tracers of the large-scale structure of the Universe and we show
-    that the clustering signal could be measured using as few as
-    $10\,000$ events. Such a survey is in line with what may be achieved with
-    upcoming wide-field radio telescopes.
 \end{abstract}
@@
 \maketitle
-
-\section{Introduction}
-
-The clustering of matter on large scales has been
-heralded as the next great probe of the Universe after the cosmic microwave
-background (CMB). The large-scale structure, in principle, contains far more
-information than the CMB because it can be studied in three dimensions.
-Traditionally, the redshift of spectral lines of ``standard atoms'', 
-caused by the Hubble flow, has
-been employed to measure radial distance and provide the third dimension.
-Such redshift
-surveys have now aggregated the positions of millions of galaxies into three
-dimensional density maps, exposing a rich structure of clusters, filaments,
-walls, and voids.
-
-However, redshift is not the only measure of radial distance. Standard
-candles and standard rulers can be used to estimate distance using brightness
-and angular size, respectively.  In the same way a ``standard ping'', a brief
-broadband radio impulse, can be used to measure dispersion through the
-characteristic wavelength-squared delay of electromagnetic signals. The dispersion is
-proportional to the amount of plasma along the
-line of sight and can thus be used to estimate radial distance.
-This technique, routinely used for
-pulsars in the Galaxy, can be used to define a \emph{dispersion distance} to
-cosmological sources.
-
-Dispersion is readily measured from fast radio bursts (FRBs),
-a new class of millisecond duration radio transients first reported by
-\citet{2007Sci...318..777L}, which are the archetype of a standard ping.
-Ten such bursts have been reported to date
-\citep{2012MNRAS.425L..71K,2013Sci...341...53T, 2014ApJ...790..101S,
-2014ApJ...792...19B, 2015MNRAS.447..246P,2015ApJ...799L...5R}, and the total
-event rate has been estimated to be $3.3^{+5}_{-2.5} \times 10^3$ per sky per
-day \cite{2015arXiv150500834R}.
-Dispersion is characterized by a line-of-site
-integral of the free electron density known the dispersion measure (DM). FRB
-events are observed to have dispersion measures of order $\sim\!\!1000\,{\rm pc}
-/ {\rm cm}^3$, greatly in excess of the galactic expectation of order
-$\sim\!\!100\,{\rm pc} / {\rm cm}^3$ (depending on galactic latitude)
-\cite{2015MNRAS.451.4277D}.  They thus appear to be of extragalactic origin,
-with their dispersion produced either by the intergalactic medium,
-associated with structure along line of sight \citep{2013Sci...341...53T},
-or the environment of the
-source \citep{2014ApJ...785L..26L,2015ApJ...807..179P,2015arXiv150505535C}.  If
-the dispersion is dominated by electrons along the line of sight, then the
-average dispersion--distance relation can be modeled
-\citep{2014ApJ...797...71Z,2004MNRAS.348..999I, 2003ApJ...598L..79I} and the
-sources appear to be at cosmological distances of order gigaparsecs.
-Such cosmological distances permit the study of the clustering of FRB sources in
-three dimensions, with an expectation that these events trace the large-scale
-structure of the Universe on linear scales. We note that while our discussion
-here is framed in terms of FRBs, other bright radio transients that fluctuate
-on time scales shorter than the typical differential lag of $\sim 1s/100 \,{\rm
-MHz} $ might also be useful as standard pings.
-
-Neither redshift nor dispersion are perfect proxies for radial distance.
-Redshifts are systematically biased by the peculiar velocities of objects
-relative to the Hubble flow. This leads to additional apparent clustering
-in redshift
-space which was first calculated by \citet{1987MNRAS.227....1K}
-using linear theory.
-Similarly, as we show here, distance estimates from dispersion will be biased by
-inhomogeneities in the electron density \citep{2014ApJ...780L..33M},
-again leading to additional apparent
-clustering of sources in dispersion space.  In this Letter we calculate
-these dispersion-space distortions and consider the detectability of the signal by
-upcoming surveys.
-
-%\section{Density perturbations in dispersion measure space}
 \section{Clustering in dispersion space}
@@
 
-%\section{Two-point statistics}
+\section{Cross-correlation}
 
@@
 and thus the two-point statistics cannot be phrased as a simple power spectrum.
-We will instead use $C^{ss}_\ell(\chi,\chi')$, which is
+We will instead use $C^{gs}_\ell(\chi,\chi')$, which is
 the cross-correlation angular power spectrum of the dispersion-space overdensity,
@@
 \begin{align}
-    &C^{ss}_\ell(\chi, \chi') =
+    &C^{gs}_\ell(\chi, \chi') =
     \int\ud\Omega\ud\Omega' Y_{\ell m}(\hat n) Y^*_{\ell m}(\hat n')
-    \langle \delta_{fs}(\hat n \chi) \delta_{fs}(\hat n' \chi')
+    \langle \delta_{g}(\hat n \chi) \delta_{fs}(\hat n' \chi')
         \rangle.
@@
 
-Finally, $C^{ss}_\ell$ will contain cross terms between the stationary terms
+Finally, $C^{gs}_\ell$ will contain cross terms between the stationary terms
 and the integral terms.  These will have the form
@@
     \label{e:Clss}
-C^{ss}_\ell(\chi,\chi') = &~
+C^{gs}_\ell(\chi,\chi') = &~
     \frac{2}{\pi}
@@
     j_\ell(k\chi) j_{\ell}(k\chi')
-    P_{[ff + ee - 2ef]}(k, (\chi + \chi')/2)
+    P_{[gf - ge]}(k, (\chi + \chi')/2)
     %\left[
@@
     %- 2P_{fe}(k, \bar\chi)
-    %\right]
-    \nonumber\\
-    & +
-    \frac{2}{\pi}
-    %\left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi}
-    %+ \frac{2}{\chi} \right)
-    %\left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi'}
-    %+ \frac{2}{\chi'} \right)
-    A(\chi) A(\chi')
-    \int_0^\chi\ud\chi''
-    \int_0^{\chi'}\ud\chi'''
-    \int_0^\infty\ud k k^2 j_\ell(k\chi'') j_{\ell}(k\chi''')
-    P_{ee}(k, (\chi''+\chi''')/2)
-    \nonumber\\
-    & +
-    \frac{2}{\pi}
-    %\left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi}
-    %+ \frac{2}{\chi} \right)
-    A(\chi)
-    \int_0^\chi\ud\chi''
-    \int_0^\infty\ud k k^2 
-    j_\ell(k\chi') j_{\ell}(k\chi'')
-    P_{[ee - fe]}(k, (\chi' + \chi'')/2)
-    %\left[
-    %P_{ee}(k, (\chi' + \chi'')/2)
-    %- P_{fe}(k, (\chi' + \chi'')/2) 
     %\right]
@@
     j_\ell(k\chi) j_{\ell}(k\chi'')
-    P_{[ee - fe]}(k, (\chi + \chi'')/2).
+    P_{[-ge]}(k, (\chi + \chi'')/2).
     %\left[ 
@@
 \begin{align}
-    &C^{ss}_\ell(\chi, \chi') \approx
+    &C^{gs}_\ell(\chi, \chi') \approx
     \nonumber \\ & \quad
@@
         e^{i k_\parallel (\chi - \chi')}
-        P_{[ee + ff - 2ef]}
+        P_{[gf - ge]}
         (\sqrt{k_\parallel^2 + \nu^2/\bar\chi^2}, \bar\chi)
     \nonumber \\ & \quad +
-    A(\chi) A(\chi')
-    \int_0^{\chi_{\rm min}}\ud\chi''
-    \frac{1}{\chi^{\prime\prime 2}}
-    P_{ee}(\nu/\chi'',\chi'')
-    \nonumber \\ & \quad +
-    \frac{A(\chi_{\max})}{\chi_{\min}^2}
-    P_{[ee - ef]}(\nu/\chi_{\min}, \chi_{\min}),
+    H(\chi' - \chi)
+    \frac{A(\chi')}{\chi^2}
+    P_{[- ge]}(\nu/\chi, \chi),
     \label{e:Clss_limber}
@@
 where $\nu\equiv\ell + 1/2$, $\chi_{\min} \equiv \min(\chi, \chi')$,
-and $\chi_{\max} \equiv \max(\chi,
-\chi')$ .  We have found that these approximations are accurate to within $3\%$ at
+$\chi_{\max} \equiv \max(\chi, \chi')$, and $H$ is the Heaviside step function.
+We have found that these approximations are accurate to within $3\%$ at
 $\ell \gtrsim 10$
-and use this form for the remainder of the Letter. In the above equation, we dub
-the three terms the ``local'', ``integral'' and ``cross'' terms, respectively,
-and we will
-refer to them as such henceforth.
-
-\section{Modelling and measurement}
-
-The second term in Eq.~\ref{e:Clss_limber} is an integral that mixes
-many spatial scales: small scales from smaller radial distance and larger
-scales from greater distances. The mixing of scales complicates the
-interpretation of measurements since structure formation on scales smaller
-than $\sim10\,{\rm Mpc}/h$ is nonlinear and hard to model. A similar issue
-exists in the field of weak gravitational lensing, where the formula for the
-shear angular power spectrum has a similar form.  In lensing, a kernel in
-the line-of-sight integral arising from geometric effects suppresses the
-contribution from small distances, partially alleviating the issue.
-
-However, the lack of a kernel simplifies tomography---the use of sources at
-multiple redshifts to unmix spatial scales.
-Lensing tomography is inexact because the kernel's shape depends on
-the source redshift, thus reweighting the line-of-sight integral.
-In contrast, the integrand in the dispersion-space integral
-term is completely independent of the limit of integration, meaning
-contributions from different parts of the line of sight (and thus different
-spatial scales) can be separated exactly. We leave a study of the potential
-of dispersion-space
-tomography to future work.  To avoid our results being
-sensitive to the hard-to-model small scales, we assume that the contribution to the
-integral term from radial distances $\chi'' < 500\,{\rm Mpc}/h$ are well
-measured by the correlations with these radial slices. We thus ignore
-contributions to the integral term from below this distance and neglect the
-information from these slices in our sensitivity measurements. The smallest
-spatial scale that contributes to our plotted angular power spectra out to
-$\ell=1000$ is thus $k=2\,h/{\rm Mpc}$.
-
-For plotting the dispersion-space power spectra,
-we use a toy model for the electron and
-FRB clustering that assumes both are biased tracers of the dark matter:
-\emph{i.e.}~$P_{xy}(k)=b_x b_y P(k)$.  We
-calculate the time dependant dark-matter power spectrum using {\tt CAMB}, using
-the integrated {\tt HALOFIT} to approximate the nonlinear evolution. We assume
-that the electron bias is $b_e=1$, which should be true on large scales due to
-the approximate conservation of free electrons. The bias of FRB sources is
-unconstrained by data and we choose it to be $b_f=1.3$\blue{, roughly
-the value for star forming galaxies at the relevant
-redshifts \citep{2011MNRAS.415.2876B} and providing reasonable contrast to the
-electrons}.
-The coefficient
-$A(\chi)$ depends on the density of detected FRB sources, $\bar n_f(\chi)$.
-We use a simple model where all events above a fixed flux are detected,
-the intrinsic luminosity function has the form from
-\citet{1976ApJ...203..297S} with index $-1$, and events at the cutoff of the
-luminosity function and at
-a radial distance of $\chi=2350\,{\rm Mpc}/h$ are at the flux detection threshold.
-This source density is shown in Fig.~\ref{f:n_f} with the resulting dispersion-space
-power spectrum in Fig.~\ref{f:terms}.
-
-\begin{figure}
-    \includegraphics[scale=0.42]{figures/n_f}
-    \caption{
-        \label{f:n_f}
-        (Top) Comoving density of sources in toy model, as described in
-        text. Normalization is
-        such that the survey has a total of $10\,000$ FRB events.
-        (Bottom) Resulting coefficient $A(\chi)$ as given in
-        Eq.~\ref{e:A}.
-    }
-\end{figure}
-
-\begin{figure}
-    \includegraphics[scale=0.42]{figures/terms}
-    \caption{
-        \label{f:terms}
-        Terms in the dispersion-space cross-correlation angular power spectrum.
-        All terms are evaluated at $\bar\chi=2000\,{\rm Mpc}/h$ and 
-        $\chi - \chi' = 10\,{\rm Mpc}/h$, except the lowest most 
-        local term curve, which is for $\chi - \chi'=50\,{\rm Mpc}/h$. 
-        While
-        the other two terms are highly insensitive to the separation of
-        the radial slices, the local term drops rapidly with separation.
-    }
-\end{figure}
-
-\blue{
-The amplitudes of the local and cross terms depend on the difference
-between the electron bias and the highly uncertain FRB bias,
-and the sign of the cross term depends on
-which of these is larger. However, since the
-integral term dominates for most radial distance pairs, our final sensitivity
-estimates are largely unaffected by this uncertainty (as shown below). In a
-high-precision survey, the sensitivity of the cross and local terms to the
-difference in the biases may help break measurement degeneracies, while sign
-changes of terms as a function of radial distance are a signature of
-bias evolution.
-}
-
-In a real survey, measurement of the dispersion-space clustering
-will be complicated by extra contributions to the dispersion.
-First, all signals
-must pass through the Milky Way's galactic disk, halo, and local environment.
-However, the resulting dispersion is only a
-single function of $\hat n$ which presumably can be well
-measured. As such, it should be
-possible to subtract the local
-contribution, as was done in
-\citet{2014arXiv1412.4829D}, and this is unlikely to be a limiting obstacle.
-
-Perhaps more concerning is the dispersion from the source's immediate environment
-as well as the halo in which it resides. These electrons will presumably be
-clustered around the source on scales far smaller than the survey
-resolution and are thus not accounted for in the
-$\delta_e$--$\delta_f$
-correlations included in the above formalism.  This will have a mean
-contribution, which is common to all sources and which may be epoch dependant, 
-that will
-modify the mean dispersion--distance relation. This will need to be calibrated in some
-way or else fit with nuisance parameters during parameter estimation.
-There will also be a stochastic piece which varies from source to source.  This will
-limit the precision at which $\chi_s$ can be measured, thus limiting the
-resolution of dispersion-space density maps in the radial direction.
-We note that one-point statistics from the same data set 
-should provide empirical information about these properties independent
-of their physical origin.
-
-Detailed treatment of the above source modelling is beyond the scope of this
-Letter. The magnitude of the contribution from the progenitor is, at present,
-unknown. To crudely deal with it here, we use relatively large
-bin widths of $\Delta\chi = 100\,{\rm Mpc}/h$
-and exclude the $\chi = \chi'$ bin pairs.
-Because the local term drops rapidly with radial separations, this effectively 
-discards the contribution from the local term which is most sensitive to having
-precise radial distances.
-
-In first measurements of the angular power spectra, uncertainty will be
-dominated by the finite number of observed events, or shot noise.
-The noise power spectrum on shells at a distance $\chi_i$ and with width
-$\Delta \chi$ is
-\begin{equation}
-    C^N_{\ell, ij} = \frac{\delta_{ij}}{\bar n_f(\chi_i)\chi_i^2\Delta\chi}.
-\end{equation}
-Here, to indicate that we are now working with quantities binned in the radial
-direction, we have switched to $C_{\ell,ij}$ instead of
-$C_\ell(\chi, \chi')$. The uncertainty on the angular
-cross-power spectrum is then
-\begin{align}
-    (\Delta{C^{ss}_{\ell,ij}})^2 = 
-    {\frac{1}{\ell(\ell + 1)\Delta \ell f_{\rm sky}}}
-        \left[C^N_{\ell,ii} C^N_{\ell,jj} +  (C^N_{\ell,ij})^2\right],
-\end{align}
-where the second term in brackets only contributes for $i = j$.
-
-We consider the sensitivity of a survey with a total of $10\,000$ dispersion
-measures from FRB events distributed uniformly over half of the sky.
-To give an idea of the overall sensitivity of the survey, we collapse
-$C^{ss}_{\ell,ij}$ to a single function of $\ell$ by taking a weighted average
-of all pairs of radial bins over the
-range $500\,{\rm Mpc}/h$ to $3500\,{\rm Mpc}/h$.
-For weights we use the signal over noise squared
-at $\ell=100$, which maximizes the signal to noise at that $\ell$ and
-is near optimal at other multipoles.
-\blue{
-To determine if such a survey would be
-able to distinguish between models of FRB clustering we plot the same quantity
-for $b_f=0.8$.
-}
-The result is shown
-in Fig.~\ref{f:sensitivity}.
-
-\begin{figure}
-    \includegraphics[scale=0.42]{figures/sensitivity}
-    \caption{
-        \label{f:sensitivity}
-        Sensitivity of a survey with $10\,000$ dispersion measures distributed
-        uniformly over half of the sky.  Plotted is the cross-correlation
-        power spectrum weighted averaged over all pairs of radial bins. Weights
-        are chosen to maximize signal to noise at $\ell=100$ for the $b_f=1.3$
-        case.
-    }
-\end{figure}
-
-\section{Discussion and conclusions}
-
-We have proposed using cosmological FRB sources as standard pings to trace the 3D
-large-scale structure of the Universe using dispersion distance. It can be seen in
-Fig.~\ref{f:terms} that the signal is dominated by inhomogeneities in the
-electron density along the different lines of sight,
-inducing misestimates of radial
-distance, and thus apparent clustering.
-\blue{
-Because it is the line-of-sight integrated structure that correlates, the
-signal is fairly insensitive to radial distance and the radial separation of
-slices, with these dependencies being dominated by the coefficient $A(\chi)$.
-}
-These dispersion-space distortions could
-be used
-to study the distribution of free electrons in the Universe on large scales.
-There have been other proposals to use FRBs for cosmology 
-\citep{2014ApJ...780L..33M,2014MNRAS.443L..11D,
-2014ApJ...783L..35D,2014PhRvD..89j7303Z,2014ApJ...788..189G}; however these
-schemes have either not been three dimensional
-or required externally measured redshifts
-for the sources.
-
-We have
-shown in Fig.~\ref{f:sensitivity}
-that a survey detecting $10\,000$ fast radio bursts of cosmological
-origin could detect the
-clustering signal.
-This is in rough
-approximation to what might be achieved in a reasonable amount of time by the
-Canadian Hydrogen Intensity
-Mapping Experiment (CHIME)\footnote{\url{http://chime.phas.ubc.ca/}}, the
-Square Kilometre Array\footnote{\url{http://www.skatelescope.org/}},
-or other upcoming wide-field telescopes.
-\blue{Such a survey would be primarily sensitive to the integral 
-term and thus rather insensitive to the details of FRB clustering models.}
-Looking forward, dispersion-space
-clustering could become a precision probe of large-scale structure should
-observational factors turn out to be favorable compared to spectroscopic
-surveys. The baryon acoustic oscillation feature can be clearly seen in
-Fig.~\ref{f:terms} in the cross term and both
-local-term curves. It may also be possible to extract the baryon acoustic
-oscillation feature
-from the integral
-term using tomography.
-This, however, requires that the statistics of the contribution to dispersion from
-the source's environment and host halo to be well understood or small compared to the
-contribution from the line of sight.
-
-Finally, we note that alone---or in combination with
-redshift data on a subset of the population, independent redshift surveys,
-or gravitational lensing surveys---dispersion-space surveys could yield very
-powerful probes of cosmology. Cosmological dispersion-space data could open a
-new window into the structure of the Universe.
-
-\begin{acknowledgments}
-
-We thank Ue-Li Pen and Mathew McQuinn the for helpful discussions.
-%
-K.W.\,M is supported by the Canadian Institute for Advanced Research, Global
-Scholars Program.  The research of K.\,S. is supported in part by a National
-Science and Engineering Research Council (NSERC) of Canada Discovery Grant.
-
-\end{acknowledgments}
+and use this form for the remainder of the Letter.
 

### 2019-06-11 python/angular_terms.py

@@ -21,8 +21,8 @@ class SingleEll(object):
         nchi = 20
         #delta_chi = chi_max / nchi
         #chi_list = np.arange(1, nchi + 1, dtype=float) / nchi * chi_max
-        
-        CHI_MIN = 500.
+
+        CHI_MIN = 50.
         chi_list = np.linspace(CHI_MIN, chi_max, nchi, endpoint=True)
         delta_chi = chi_list[1] - chi_list[0]
 
@@ -36,7 +36,9 @@ class SingleEll(object):
 
             if limber:
                 # Local term.
-                delta_k = 2 * np.pi / (2 * chi)
+                delta_max = 400 # XXX Pretty narrow, for speed. I1 negligable outside this range.
+                delta_k = 2 * np.pi / (2 * delta_max)
+                #delta_k = 2 * np.pi / (2 * chi)
                 k_max = np.sqrt(max(matter_power.K_MAX**2 - (ell/chi)**2, 0))
                 k = np.arange(0, k_max, delta_k)
                 k = np.concatenate((k, -k[:0:-1]))
@@ -44,15 +46,15 @@ class SingleEll(object):
                 if nk > 10:
                     p_k_local = p_k_interp(np.sqrt((ell/chi)**2 + k**2))
                     #window = fftpack.ifftshift(signal.kaiser(nk, beta=14, sym=True))
-                    window = fftpack.ifftshift(signal.hann(nk, sym=True))
+                    #window = fftpack.ifftshift(signal.hann(nk, sym=True))
+                    window = fftpack.ifftshift(signal.tukey(nk, alpha=0.5, sym=True))
                     p_k_local *= window
                     fft_norm = len(k) * delta_k / 2 / np.pi / chi**2
                     I1 = fftpack.ifft(p_k_local).real
                     I1 = fftpack.fftshift(I1) * fft_norm
-                    deltas = np.linspace(-chi, chi, len(I1), endpoint=True)
                 else:
                     I1 = np.zeros(10, dtype=float)
-                    deltas = np.linspace(-chi, chi, len(I1), endpoint=True)
+                deltas = np.linspace(-delta_max, delta_max, len(I1), endpoint=True)
 
                 # Limber term.
                 if ell/chi > matter_power.K_MAX:
@@ -108,8 +110,8 @@ class SingleEll(object):
             ii += ndelta
 
[…]

### 2019-06-11 python/assemble_terms.py

@@ -10,11 +10,12 @@ import matter_power
 import angular_terms
 
 # Redshift at which we can detect event of luminocity L*.
-Z_STAR = 1.
+Z_STAR = 0.5
 ALPHA = -1.
 
 B_E = 1.0
 B_F = 1.3
+B_G = 1.3
 
 
 def d_ln_n(chi):
@@ -73,6 +74,21 @@ def apply_coeffs(mult_ell, chi, delta):
 
     return t1, t2, t3
 
+
+def apply_coeffs_cross(mult_ell, chi_gal, chi_frb):
+    chi_bar = (chi_gal + chi_frb) / 2
+    delta = chi_frb - chi_gal
+    i1, i2, i3 = mult_ell.get_integrals(chi_bar, delta)
+    t1 = (B_F - B_E) * B_G * i1
+    t3 = np.zeros_like(t1)
+    if chi_gal > chi_frb:
+        t2 = t3.copy()
+    else:
+        coeff = d_ln_n(chi_frb) + 2./chi_frb
+        t2 = - B_E * B_G * coeff * i2
+    return t1, t2, t3
+
+
 def plot_spectra(mult_ell, chi, delta, local_only=False, **kwargs):
     ells = mult_ell.ells
     t1, t2, t3 = apply_coeffs(mult_ell, chi, delta)
@@ -90,7 +106,7 @@ def plot_spectra(mult_ell, chi, delta, local_only=False, **kwargs):
 def get_ells():
     ells = range(10, 101, 10)
     factor = 1.1
-    max = 1000
+    max = 5000
     while ells[-1] < max:
         ells.append(int(factor * ells[-1]))
     return np.array(ells)
@@ -99,9 +115,83 @@ def get_ells():
 def get_mult_ell(ells=None, limber=True):
     if ells is None:
         ells = get_ells()
-    CHI_MAX = 3600.
+    CHI_MAX = 5000.
     mell = angular_terms.MultiEll(ells, CHI_MAX, limber)
     return mell
+
+
+def cross_corr_plots(mult_ell=None):
+    kwargs = {
+            "linewidth" : 2.,
+             }
+
+
+    # Mean source density plot
+    N_TOTAL = 10000
+    F_SKY = 0.5
+
+    chi_s = np.linspace(100, 3500, 50.)
[…]

### 2019-06-11 python/cross_corr_cross_term.py

@@ -1,0 +1,125 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy import special, integrate
+
+import matter_power
+
+
+d_H = 3000.
+
+# Roughly volume limited between these limits.
+Z_MIN = 0.01
+Z_MAX = 0.05
+
+K_CUTOFF = 10.
+
+
+z_mean = (Z_MIN + Z_MAX) / 2
+
+thetas = np.radians(np.arange(0.1, 20, 0.05))
+
+chi_min = Z_MIN * d_H
+chi_max = Z_MAX * d_H
+
+chi = np.linspace(chi_min, chi_max, 4, endpoint=True)
+nchi = len(chi)
+
+pk = matter_power.p_k_interp(d_H * z_mean, fill_value=0.)
+if False:
+    k = np.logspace(-3, 1, 100)
+    #plt.figure()
+    #plt.plot(k, pk(k))
+    plt.figure()
+    plt.loglog(k, k * pk(k) * np.exp(-(k / K_CUTOFF)**2))
+
+    plt.figure()
+    plt.loglog(k, k**3 * pk(k) / (2 * np.pi**2) * np.exp(-(k / K_CUTOFF)**2))
+
+    #plt.figure()
+    #plt.loglog(matter_power.K, matter_power.K**2 * matter_power.DATA[0])
+
+
+ells = np.arange(5, 2000, 5)
+
+tmp_k = ells[:] / chi[:, None]
+P2 = pk(tmp_k) / chi[:, None]**2 * np.exp(-(tmp_k / K_CUTOFF)**2)
+
+plt.figure()
+for ii in range(nchi):
+    plt.plot(ells, ells * P2[ii])
+plt.plot(ells, 2 * special.jv(0, ells * thetas[0]))
+
+
+integrand = ells * P2[:, None, :] * special.jv(0, ells * thetas[None, :, None])
+integrand = integrand / (2 * np.pi)
+
+wtheta_chi = integrate.simps(integrand, ells, even='first')
+
+plt.figure()
+for ii in range(nchi):
+    plt.semilogx(np.degrees(thetas), wtheta_chi[ii])
+
+
+window = chi**2
+window /= integrate.simps(window, chi)
+
+wtheta = integrate.simps(wtheta_chi * window[:, None], chi, axis=0)
+
+plt.figure()
+plt.semilogx(np.degrees(thetas), wtheta)
+
+
+
[…]

### 2019-06-11 python/matter_power.py

@@ -7,9 +7,10 @@ from cora.util.cosmology import Cosmology
 
 
 DATA_DIR = path.join(path.dirname(__file__), 'data')
-FILE_PAT = "Pk_z%3.1f.dat"
+#FILE_PAT = "Pk_z%3.1f.dat"
+FILE_PAT = "camb_00891002_matterpower_z%3.1f.dat"
 REDSHIFTS = np.arange(0, 2.001, 0.2)
-K_MAX = 2.
+K_MAX = 20.
 
 # k values are the same for all redshifts.
 K = np.loadtxt(path.join(DATA_DIR, FILE_PAT % REDSHIFTS[0]))[:,0]
@@ -17,10 +18,15 @@ DATA = np.concatenate([np.loadtxt(path.join(DATA_DIR, FILE_PAT % z))[None,:,1]
                        for z in REDSHIFTS])
 
 
-def interpolator():
+def interpolator(fill_value=None):
     c = Cosmology()
     chi = c.comoving_distance(REDSHIFTS)
-    interpolator = interpolate.interp2d(K, chi, DATA, kind='cubic')
+    if fill_value is not None:
+        be = False
+    else:
+        be = True
+    interpolator = interpolate.interp2d(K, chi, DATA, kind='cubic', fill_value=fill_value,
+            bounds_error=be)
     return interpolator
 
 
@@ -30,7 +36,11 @@ def p_k_chi_interp():
     return INTERPOLATOR
 
 
-def p_k_interp(chi):
+def p_k_interp(chi, fill_value=None):
+    if fill_value is not None:
+        be = False
+    else:
+        be = True
     i = INTERPOLATOR
     data = i(K, chi)
-    return interpolate.interp1d(K, data, kind='cubic')
+    return interpolate.interp1d(K, data, kind='cubic', fill_value=fill_value, bounds_error=be)

### 2019-06-12 writeup/dm_space_cross.tex
Work through cross-correlation.

@@
 
+One thing that should be true is that the disperion-space distortions
+should no effect
+on observations that do not use DM information. Lets say we did not bin the
+FRBs by dispersion measure but just took the angular cross-power spectrum of the
+unbinned FRBs with the galaxies (which may still be binned), $C^{gf}_\ell(\chi)$.
+The number of FRBs per unit comoving distance is proportional to
+$\chi^2 \bar{n}_{f}(\chi)$, and so
+\begin{equation}
+    C^{gf}_\ell(\chi) \propto \int \ud\chi' {\chi'}^2 \bar{n}_{f}(\chi')
+    C^{gs}_\ell(\chi, \chi').
+\end{equation}
+Substituting Equation~\ref{e:Clss}, we find that integrating the cross term by
+parts gives exact expression required to cancel the $P_{ge}$ part of the local
+term and everything is miraculously consistent.
+
 \bibliography{refs}

### 2019-06-12 python/cross_corr_cross_term.py

@@ -1,6 +1,7 @@
 import numpy as np
 import matplotlib.pyplot as plt
-from scipy import special, integrate
+from scipy import special, integrate, interpolate
+from cora.util.cosmology import Cosmology
 
 import matter_power
 
@@ -71,15 +72,20 @@ plt.semilogx(np.degrees(thetas), wtheta)
 
 
 # Redshift at which we can detect event of luminocity L*.
-Z_STAR = 0.5
-ALPHA = -1.
+#Z_STAR = 1.5
+#ALPHA = -1.
 
+Z_STAR = 0.9
+ALPHA = -0.4
+
+#Z_STAR = 2.
+#ALPHA = -1
 
 def n_chi(chi):
     """Vectorized."""
     # Invert the distance redshift relation by interpolating.
     c = Cosmology()
-    redshifts_s = np.linspace(0.01, 3, 50)
+    redshifts_s = np.linspace(0.0, 5, 50)
     chi_s = c.comoving_distance(redshifts_s)
     redshift_interp = interpolate.interp1d(chi_s, redshifts_s, kind='cubic')
     redshifts = redshift_interp(chi)
@@ -99,23 +105,63 @@ def n_chi(chi):
     return n
 
 
-def d_ln_n(chi):
-    """Not vecotized"""
+def dndchi(chi):
 
-    delta_chi = 0.01 * chi
-    n = n_chi(np.array([chi, chi + delta_chi]))
+    delta_chi = 1.
+    chi = chi[:, None] + [-delta_chi / 2, delta_chi / 2]
+    s = chi.shape
+    n = n_chi(chi.flat)
+    n.shape = s
 
-    d_ln_n_d_chi = (n[1] - n[0]) / delta_chi / n[0]
-    #print n
-    #print d_ln_n_d_chi
-
-    #plt.plot(redshifts, n*chi_s**2)
-    #plt.figure()
-    #plt.plot(redshifts, n)
+    dndchi = (n[:, 1] - n[:, 0]) / delta_chi
 
     # Finite difference derivative and normalize.
-    return d_ln_n_d_chi
+    return dndchi
 
+
+def dm_to_z(dm):
+    return dm / 1000.
+
+
+dm_bin_edges = np.array([0, 300, 800, 5000])
+c = Cosmology()
[…]
